### 2018-07-17 sgpv_vs_TOST.Rmd
initial commit

---
title: "The Second Generation P-Value is Old Wine in New Bottles"
author: "Daniël Lakens"
date: "1 juli 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
library(TOSTER)
```

```{r, include=FALSE}
#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R

#' Second Generation P-value
p_delta <- function(lb, ub, delta_lb, delta_ub) {

  # special case: infinite CI and H0 bounds in the same direction
  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
    return(1)
  }

  # usual case: non-point CI & non-point Ho
  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
  if (delta_lb != delta_ub & lb != ub) {
    if (lb > delta_ub | ub < delta_lb) {
      return(0)
    } else if(lb > delta_lb & ub < delta_ub){
      return(1)
    } else {
      return(
        (min(ub, delta_ub) - max(lb, delta_lb)) /
          min(ub - lb, 2 * (delta_ub - delta_lb))
      )
    }
  }

  # special case 1: point CI, w/ or w/out a point H0
  # pdelta = 0 if CI is inside the Ho
  # pdelta = 1 if CI is inside the Ho
  if (lb == ub) {
    if (lb <= delta_ub & lb >= delta_lb){
      return(1)
    } else {
      return(0)
    }
  }

  # special case 2: point H0 & non-point CI
  # pdelta = 1/2 if H0 is inside the CI
  # pdelta = 0 if H0 is outside the CI
  if (delta_lb == delta_ub & lb != ub) {
    if (delta_lb <= ub & delta_lb >= lb) {
      return(1/2)
    } else {
      return(0)
    }
  }
}
```

The second generation p-value (SGPV) is the proportion of data-supported hypotheses that are also null hypotheses (Blume, McGowan, Dupont, & Greevy, (2018). The authors note that: "Using second-generation p-values can only improve rigor, reproducibility and transparency across science." 
It was quickly noted on Twitter that the SGPV is similar to equivalence testing (https://twitter.com/statsepi/status/997759878503550976, https://twitter.com/lakens/status/995171827692515328).

In the plot below I calculate p-values for the TOST equivalence testing procedure, and plot the SGPV for the same tests:

```{r, include=FALSE}
step = 0.01

p_tost_list <- numeric(length(seq(140, 146, step)))
sgpv_list <- numeric(length(seq(140, 146, step)))
p_list <- numeric(length(seq(140, 146, step)))
t_list <- numeric(length(seq(140, 146, step)))

count <- 0

for(i in seq(140, 146, step)){
  count <- count + 1
  m <- i
  mu <- 146
  sd <- 800
  n <- 1000000
  low_eqbound = -2 
  high_eqbound = 2 
  alpha = 0.05

  invisible(capture.output(res <- TOSTone.raw(m = m, 
                                              mu = mu,
                                              sd = sd, 
                                              n = n, 
                                              low_eqbound = low_eqbound, 
                                              high_eqbound = high_eqbound, 
                                              alpha = alpha,
                                              plot = FALSE
  )))
  t <- (m - mu)/(sd/sqrt(n))
  t_list[count] <- t
  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
  p_list[count] <- 2 * pt(-abs(t), df = n-1)
}
```

```{r sgpv_tost, echo=FALSE}
plot(sgpv_list, type="l", col = "blue")
lines(p_tost_list)
```

For ease of comparison, let me repeat the plot, now showing 1-TOST p-values:

```{r 1-sgpv_tost, echo=FALSE}
plot(sgpv_list, type="l", col = "blue")
lines(1-p_tost_list)
```

It is clear there is overlap. Some orientation in this plot. When the TOST p-value is 0.5, the SGPV is 0.5. This is because when the 95% CI overlaps 50% with the equivalence region, it falls exactly on the lowerbound. When this is the case, the probability of observing data as or more extreme as the data observed is also exactly 50%, and thus the TOST p-value is 0.5 as well.

Two other points always have to overlap. When the 95% CI falls completely inside the equivalence region, The TOST using a 95% (instead of the typical 90% CI) should be significant at the 5% level. Since TOST in this simulation uses a 90% CI, we can halve the alpha level, and thus we should expect that when the SGPV is is 1, and the 95% just touches the lower bound (around index 558) the TOST p-value is 2.5% (or 1-0.025=0.975 in the second plot). The opposite is also true: When the SGPV is changes from 0 to a positive value (around index 245) the 95% CI touches the outside of the lower bound, and the TOST p-value will be 0.975 (or in the lower plot showing 1-p_TOST, 0.025).

We can see SGPV is a straight line between these points, because each trial, the observed difference moves from m = 140 to 146 in steps of 0.01. When m = 146, there is perfect equivalence (since we are testing against a value of 146 in the one-sided test).

The only thing we need to explain is why the TOST p-value is curved, where the SGPV is a straight line as we reduce the mean difference with 0.01 steps as the index increases. The difference is that SGPV is a proportion from 0 to 1 (with it being 0 when there is no overlap, and 1 if there is perfect overlap) while the TOST p-value is a probability, which is never exactly 0 or one (but can get really close).

Let's look at an example, and write in full the calculation for the SGPV. We should be able to link it to the calculation for the TOST p-value.

```{r}
m <- 146
mu <- 144.5
sd <- 500
n <- 1000000
low_eqbound = -2 
high_eqbound = 2 
alpha = 0.05

res <- TOSTone.raw(m = m, 
                   mu = mu,
                   sd = sd, 
                   n = n, 
                   low_eqbound = low_eqbound, 
                   high_eqbound = high_eqbound, 
                   alpha = alpha
)

p_tost <- res$TOST_p2
p_delta(mu + res$LL_CI_TTEST,
        mu + res$UL_CI_TTEST, 
        mu + low_eqbound, 
        mu + high_eqbound)

#SGPV
ll_ci <- (m - mu)-(1.96*(sd/sqrt(n)))
ul_ci <- (m - mu)+(1.96*(sd/sqrt(n)))

(min(ul_ci, high_eqbound) - max(ll_ci, low_eqbound)) / min(ul_ci - ll_ci, 2 * (high_eqbound - low_eqbound))

#The TOST p-value is calculated as:

t <- (m - mu - low_eqbound)/(sd/sqrt(n))
p <- pt(t, n-1, lower.tail = FALSE)
p

pTOST_converter(p_tost=res$TOST_p2,
                bound = "high",
                sd = sd,
                n = n,
                alpha = alpha,
                low_eqbound = low_eqbound,
                high_eqbound = high_eqbound)

```

It should be possible to compute how these two are directly related, to calculate the one in the other! But how?

#References

Blume, J. D., McGowan, L. D., Dupont, W. D., & Greevy, R. A. (2018). Second-generation p-values: Improved rigor, reproducibility, & transparency in statistical analyses. PLOS ONE, 13(3), e0188299. https://doi.org/10.1371/journal.pone.0188299

### 2018-07-17 p_tost_converter.R

@@ -1,0 +1,71 @@
+# Input parameters
+
+# In order to be able to convert p_tost into SGPV, there are many parameters we need to know:
+
+# From which eqbound is computed p_tost?
+	# if p_tost = TOST_p1 (= p_tost is computed from the low_eqbound), then bound="low" 
+      # else if p_tost = TOST_p2 (= p-tost is computed from the high_eqbound), then bound="high" 
+# n, sd 
+# alpha
+# low_eqbound and high_eqbound
+
+#-----------------------------------------------------------------------------------------------
+
+pTOST_converter=function(p_tost, 
+                         sd, 
+                         n, 
+                         alpha, 
+                         low_eqbound, 
+                         high_eqbound, 
+                         bound){
+  
+  # computing t, based on p_tost
+  t <- abs((qt(p_tost, df = n-1))) 
+  
+  # computing I
+  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+  
+  #LAKENS: I think this is not right - you can't know based on non-sig if bound is left or right from alpha. 
+  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
+  if (bound=="low") {
+    if (p_tost < alpha){I = low_eqbound + dist}
+    if (p_tost > alpha){I = low_eqbound - dist}} 
+  
+  if (bound=="high") {
+    if (p_tost < alpha){I = high_eqbound - dist}
+    if (p_tost > alpha){I = high_eqbound + dist}}
+  
+  # Computing the CI around I
+  lb <- I - qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+  ub <- I + qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+  
+  if (lb > high_eqbound | ub < low_eqbound){SGPV = 0} 
+  else if(lb > low_eqbound & ub < high_eqbound){SGPV = 1} 
+  else {SGPV <- (min(ub, high_eqbound) - max(lb, low_eqbound))/min(ub - lb, 2 * (high_eqbound - low_eqbound))}
+  
+  return(SGPV)
+}
+
+
+
+
+m <- 143.9
+mu <- 146
+m-mu
+sd <- 3
+n <- 36
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
[…]

### 2018-07-17 sgpv_vs_TOST.R

@@ -1,0 +1,373 @@
+options(scipen = 99)
+
+#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
+
+#' Second Generation P-value
+p_delta <- function(lb, ub, delta_lb, delta_ub) {
+  
+  # special case: infinite CI and H0 bounds in the same direction
+  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
+    return(1)
+  }
+  
+  # usual case: non-point CI & non-point Ho
+  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
+  if (delta_lb != delta_ub & lb != ub) {
+    if (lb > delta_ub | ub < delta_lb) {
+      return(0)
+    } else if(lb > delta_lb & ub < delta_ub){
+      return(1)
+    } else {
+      return(
+        (min(ub, delta_ub) - max(lb, delta_lb)) /
+          min(ub - lb, 2 * (delta_ub - delta_lb))
+      )
+    }
+  }
+  
+  # special case 1: point CI, w/ or w/out a point H0
+  # pdelta = 0 if CI is inside the Ho
+  # pdelta = 1 if CI is inside the Ho
+  if (lb == ub) {
+    if (lb <= delta_ub & lb >= delta_lb){
+      return(1)
+    } else {
+      return(0)
+    }
+  }
+  
+  # special case 2: point H0 & non-point CI
+  # pdelta = 1/2 if H0 is inside the CI
+  # pdelta = 0 if H0 is outside the CI
+  if (delta_lb == delta_ub & lb != ub) {
+    if (delta_lb <= ub & delta_lb >= lb) {
+      return(1/2)
+    } else {
+      return(0)
+    }
+  }
+}
+
+# Recreate examples in Figure 2 just the check that functions work as they should ----
+#1
+res <- TOSTone.raw(m = 146, 
+                   mu = 146,
+                   sd = 500, 
+                   n = 1000000, 
+                   low_eqbound = -2, 
+                   high_eqbound = 2, 
+                   alpha = 0.05
+)
+
+p_delta(146+res$LL_CI_TTEST, 146+res$UL_CI_TTEST, 144, 148)
+
+#2
[…]

### 2018-07-17 p_tost_converter.R
use 0.5 instead of alpha

@@ -25,15 +25,15 @@ pTOST_converter=function(p_tost,
   # computing I
   dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
   
-  #LAKENS: I think this is not right - you can't know based on non-sig if bound is left or right from alpha. 
+  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
   #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
   if (bound=="low") {
-    if (p_tost < alpha){I = low_eqbound + dist}
-    if (p_tost > alpha){I = low_eqbound - dist}} 
+    if (p_tost < 0.5){I = low_eqbound + dist}
+    if (p_tost > 0.5){I = low_eqbound - dist}} 
   
   if (bound=="high") {
-    if (p_tost < alpha){I = high_eqbound - dist}
-    if (p_tost > alpha){I = high_eqbound + dist}}
+    if (p_tost < 0.5){I = high_eqbound - dist}
+    if (p_tost > 0.5){I = high_eqbound + dist}}
   
   # Computing the CI around I
   lb <- I - qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # lower bound

### 2018-07-18 TOST_to_SGPV.R
new TOST_to_SGPV file that uses one TOSTone.raw function output

@@ -1,0 +1,41 @@
+# Input parameters
+# res = the stored results from the TOST analysis
+# n is the sample size
+# sd is the standard deviation
+#-----------------------------------------------------------------------------------------------
+
+TOST_to_SGPV <- function(tost_res){
+  
+  # computing t, based on p_tost
+  t <- min(tost_res$TOST_t1, tost_res$TOST_t2) 
+  
+  n <- tost_res$TOST_df + 1
+  sd <- (tost_res$diff-tost_res$low_eqbound)/tost_res$TOST_t1 * sqrt(n)
+  
+  # computing I
+  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+  
+  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
+  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
+  if (tost_res$TOST_p1 > tost_res$TOST_p2) {
+    if (tost_res$TOST_p1 < 0.5){I = tost_res$low_eqbound + dist}
+    if (tost_res$TOST_p1 > 0.5){I = tost_res$low_eqbound - dist}} 
+  
+  if (tost_res$TOST_p2 > tost_res$TOST_p1) {
+    if (tost_res$TOST_p2 < 0.5){I = tost_res$low_eqbound - dist}
+    if (tost_res$TOST_p2 > 0.5){I = tost_res$low_eqbound + dist}} 
+  
+  # Computing the CI around I
+  lb <- I - qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+  ub <- I + qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+  
+  if (lb > tost_res$high_eqbound | ub < tost_res$low_eqbound){
+    SGPV = 0
+    } 
+  else if(lb > tost_res$low_eqbound & ub < tost_res$high_eqbound){
+    SGPV = 1
+    } 
+  else {SGPV <- (min(ub, tost_res$high_eqbound) - max(lb, tost_res$low_eqbound))/min(ub - lb, 2 * (tost_res$high_eqbound - tost_res$low_eqbound))}
+  
+  return(SGPV)
+}

### 2018-07-18 sgpv_vs_TOST.Rmd
new TOST_to_SGPV file that uses one TOSTone.raw function output
add plot

@@
 ---
-title: "The Second Generation P-Value is Old Wine in New Bottles"
-author: "Daniël Lakens"
+title: "Equivalence Testing and the Second Generation P-Value"
+author: "Daniël Lakens & Marie Delacre"
 date: "1 juli 2018"
@@
 }
+
+#Code to calculate SGPV fron TOST results
+# Input parameters
+# res = the stored results from the TOST analysis
+# n is the sample size
+# sd is the standard deviation
+#-----------------------------------------------------------------------
+TOST_to_SGPV <- function(tost_res){
+
+  # computing t, based on p_tost
+  t <- min(tost_res$TOST_t1, tost_res$TOST_t2)
+
+  n <- tost_res$TOST_df + 1
+  sd <- (tost_res$diff-tost_res$low_eqbound)/tost_res$TOST_t1 * sqrt(n)
+
+  # computing I
+  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+
+  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
+  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
+  if (tost_res$TOST_p1 > tost_res$TOST_p2) {
+    if (tost_res$TOST_p1 < 0.5){I = tost_res$low_eqbound + dist}
+    if (tost_res$TOST_p1 > 0.5){I = tost_res$low_eqbound - dist}}
+
+  if (tost_res$TOST_p2 > tost_res$TOST_p1) {
+    if (tost_res$TOST_p2 < 0.5){I = tost_res$low_eqbound - dist}
+    if (tost_res$TOST_p2 > 0.5){I = tost_res$low_eqbound + dist}}
+
+  # Computing the CI around I
+  lb <- I - qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+  ub <- I + qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+
+  if (lb > tost_res$high_eqbound | ub < tost_res$low_eqbound){
+    SGPV = 0
+    } 
+  else if(lb > tost_res$low_eqbound & ub < tost_res$high_eqbound){
+    SGPV = 1
+    } 
+  else {SGPV <- (min(ub, tost_res$high_eqbound) - max(lb, tost_res$low_eqbound))/min(ub - lb, 2 * (tost_res$high_eqbound - tost_res$low_eqbound))}
+
+  return(SGPV)
+}
+
 ```
@@
 
-res <- TOSTone.raw(m = m, 
+tost_res <- TOSTone.raw(m = m, 
                    mu = mu,
@@
 
-p_tost <- res$TOST_p2
-p_delta(mu + res$LL_CI_TTEST,
-        mu + res$UL_CI_TTEST, 
-        mu + low_eqbound, 
-        mu + high_eqbound)
-
-#SGPV
-ll_ci <- (m - mu)-(1.96*(sd/sqrt(n)))
-ul_ci <- (m - mu)+(1.96*(sd/sqrt(n)))
-
-(min(ul_ci, high_eqbound) - max(ll_ci, low_eqbound)) / min(ul_ci - ll_ci, 2 * (high_eqbound - low_eqbound))
-
-#The TOST p-value is calculated as:
-
-t <- (m - mu - low_eqbound)/(sd/sqrt(n))
-p <- pt(t, n-1, lower.tail = FALSE)
-p
-
-pTOST_converter(p_tost=res$TOST_p2,
-                bound = "high",
-                sd = sd,
-                n = n,
-                alpha = alpha,
-                low_eqbound = low_eqbound,
-                high_eqbound = high_eqbound)
+TOST_to_SGPV(tost_res = tost_res)
 
@@
 
-It should be possible to compute how these two are directly related, to calculate the one in the other! But how?
+The confidence interval width is a uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
+
+```{r}
+m <- 146
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res1 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)
+
+m <- 145.9
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res2 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
+
+m <- 145.8
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res3 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV3 <- TOST_to_SGPV(tost_res = tost_res3)
+
+m <- 145.7
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res4 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV4 <- TOST_to_SGPV(tost_res = tost_res4)
+
+0.7551064 - 0.7040851
+0.6530639 - 0.6020426
+
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(-3, 3),
+     yaxt = "n",
+     ylab = "",
+     xlab = "Mean Difference")
+axis(2, at = c(0.2,0.4,0.6,0.8), labels = c("D", "C", "B", "A"), las = 1)
+abline(v = tost_res1$high_eqbound, 
+       lty = 2)
+abline(v = tost_res1$low_eqbound, 
+       lty = 2)
+abline(v = 0, 
+       lty = 2, 
+       col = "grey")
+
+points(x = tost_res4$diff, 
+       y = 0.2, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res4$LL_CI_TOST, 
+         0.2, 
+         tost_res4$UL_CI_TOST, 
+         0.2, 
+         lwd = 3)
+
+points(x = tost_res3$diff, 
+       y = 0.4, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res3$LL_CI_TOST, 
+         0.4, 
+         tost_res3$UL_CI_TOST, 
+         0.4, 
+         lwd = 3)
+
+points(x = tost_res2$diff, 
+       y = 0.6, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res2$LL_CI_TOST, 
+         0.6, 
+         tost_res2$UL_CI_TOST, 
+         0.6, 
+         lwd = 3)
+
+points(x = tost_res1$diff, 
+       y = 0.8, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res1$LL_CI_TOST, 
+         0.8, 
+         tost_res1$UL_CI_TOST, 
+         0.8, 
+         lwd = 3)
+
+```
+
+For example, the SGPV from A to D is `r SGPV1`, `r SGPV2`, `r SGPV3`, and `r SGPV4`.
+The difference in the percentage of overlap between A and B (`r SGPV1-SGPV2`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r SGPV3-SGPV4`).
 

### 2018-07-18 sgpv_vs_TOST.Rmd
make github doc

@@
 date: "1 juli 2018"
-output: html_document
-editor_options: 
-  chunk_output_type: console
+output: github_document
 ---

### 2018-07-18 sgpv_vs_TOST.Rmd
add normal curves

@@
 
-#Code to calculate SGPV fron TOST results
-# Input parameters
-# res = the stored results from the TOST analysis
-# n is the sample size
-# sd is the standard deviation
-#-----------------------------------------------------------------------
-TOST_to_SGPV <- function(tost_res){
-
-  # computing t, based on p_tost
-  t <- min(tost_res$TOST_t1, tost_res$TOST_t2)
-
-  n <- tost_res$TOST_df + 1
-  sd <- (tost_res$diff-tost_res$low_eqbound)/tost_res$TOST_t1 * sqrt(n)
-
-  # computing I
-  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
-
-  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
-  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
-  if (tost_res$TOST_p1 > tost_res$TOST_p2) {
-    if (tost_res$TOST_p1 < 0.5){I = tost_res$low_eqbound + dist}
-    if (tost_res$TOST_p1 > 0.5){I = tost_res$low_eqbound - dist}}
-
-  if (tost_res$TOST_p2 > tost_res$TOST_p1) {
-    if (tost_res$TOST_p2 < 0.5){I = tost_res$low_eqbound - dist}
-    if (tost_res$TOST_p2 > 0.5){I = tost_res$low_eqbound + dist}}
-
-  # Computing the CI around I
-  lb <- I - qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
-  ub <- I + qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
-
-  if (lb > tost_res$high_eqbound | ub < tost_res$low_eqbound){
-    SGPV = 0
-    } 
-  else if(lb > tost_res$low_eqbound & ub < tost_res$high_eqbound){
-    SGPV = 1
-    } 
-  else {SGPV <- (min(ub, tost_res$high_eqbound) - max(lb, tost_res$low_eqbound))/min(ub - lb, 2 * (tost_res$high_eqbound - tost_res$low_eqbound))}
-
-  return(SGPV)
-}
-
+source("TOST_to_SGPV.R")
 ```
@@
 
-It is clear there is overlap.
-Some orientation in this plot.
-When the TOST p-value is 0.5, the SGPV is 0.5.
-This is because when the 95% CI overlaps 50% with the equivalence region, it falls exactly on the lowerbound.
-When this is the case, the probability of observing data as or more extreme as the data observed is also exactly 50%, and thus the TOST p-value is 0.5 as well.
+##SGPV as a uniform measure of overlap
 
-Two other points always have to overlap.
-When the 95% CI falls completely inside the equivalence region, The TOST using a 95% (instead of the typical 90% CI) should be significant at the 5% level.
-Since TOST in this simulation uses a 90% CI, we can halve the alpha level, and thus we should expect that when the SGPV is is 1, and the 95% just touches the lower bound (around index 558) the TOST p-value is 2.5% (or 1-0.025=0.975 in the second plot).
-The opposite is also true: When the SGPV is changes from 0 to a positive value (around index 245) the 95% CI touches the outside of the lower bound, and the TOST p-value will be 0.975 (or in the lower plot showing 1-p_TOST, 0.025).
+It is clear the SGPV and the p-value from TOST are closely related.
+We can think of the SGPV as a straight line that will always overlap the p-value from an equivalence test in 3 points.
+When the TOST p-value is 0.5, the SGPV is also 0.5.
+The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also so, and thus the *p*-value is 0.5.
 
-We can see SGPV is a straight line between these points, because each trial, the observed difference moves from m = 140 to 146 in steps of 0.01.
-When m = 146, there is perfect equivalence (since we are testing against a value of 146 in the one-sided test).
-
-The only thing we need to explain is why the TOST p-value is curved, where the SGPV is a straight line as we reduce the mean difference with 0.01 steps as the index increases.
-The difference is that SGPV is a proportion from 0 to 1 (with it being 0 when there is no overlap, and 1 if there is perfect overlap) while the TOST p-value is a probability, which is never exactly 0 or one (but can get really close).
-
-Let's look at an example, and write in full the calculation for the SGPV. We should be able to link it to the calculation for the TOST p-value.
-
-```{r}
-m <- 146
+```{r, include=FALSE}
+m <- 146.5
 mu <- 144.5
@@
 high_eqbound = 2 
-alpha = 0.05
+alpha = 0.025
 
-tost_res <- TOSTone.raw(m = m, 
+tost_res1 <- TOSTone.raw(m = m, 
                    mu = mu,
@@
 )
+SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)
 
-TOST_to_SGPV(tost_res = tost_res)
+m <- 145.520012
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.025
+
+tost_res2 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
+SGPV2
+
+m <- 147.48
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.025
+
+tost_res3 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV3 <- TOST_to_SGPV(tost_res = tost_res3)
+SGPV3
 
@@
 
+```{r, echo = FALSE}
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(-3, 5),
+     yaxt = "n",
+     ylab = "",
+     xlab = "Mean Difference")
+axis(2, at = c(0.25,0.5,0.75), labels = c("C", "B", "A"), las = 1)
+axis(1, at = c(-3,-2,-1,0,1,2,3,4,5), las = 1)
+abline(v = tost_res1$high_eqbound, 
+       lty = 2)
+abline(v = tost_res1$low_eqbound, 
+       lty = 2)
+abline(v = 0, 
+       lty = 2, 
+       col = "grey")
+
+points(x = tost_res3$diff, 
+       y = 0.25, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res3$LL_CI_TOST, 
+         0.25, 
+         tost_res3$UL_CI_TOST, 
+         0.25, 
+         lwd = 3)
+
+points(x = tost_res2$diff, 
+       y = 0.5, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res2$LL_CI_TOST, 
+         0.5, 
+         tost_res2$UL_CI_TOST, 
+         0.5, 
+         lwd = 3)
+
+points(x = tost_res1$diff, 
+       y = 0.75, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res1$LL_CI_TOST, 
+         0.75, 
+         tost_res1$UL_CI_TOST, 
+         0.75, 
+         lwd = 3)
+par(new=TRUE)
+curve(dnorm(x, 147.48 - 144.5, 0.5), from=1.5, to=4.5, ylim = c(-2, 6), xlim = c(-3, 5), xlab = "", ylab = "", axes = FALSE)
+par(new=TRUE)
+curve(dnorm(x, 145.520012 - 144.5, 0.5), from=-0.5, to=2.5, ylim = c(-4, 4), xlim = c(-3, 5), xlab = "", ylab = "", axes = FALSE)
+par(new=TRUE)
+curve(dnorm(x, 2, 0.5), from=0.5, to=3.5, ylim = c(-6, 2), xlim = c(-3, 5), xlab = "", ylab = "", axes = FALSE)
+```
+
+Two other points always have to overlap.
+When the 95% CI falls completely, but only just inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
+When the SGPV changes from 0.9999 to exactly 1 the 95% CI just touches the equivalence bound (see situation B in the plot above, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in the plot above).
+When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
+
 The confidence interval width is a uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
 
-```{r}
+```{r, include=FALSE}
 m <- 146
@@
 SGPV4 <- TOST_to_SGPV(tost_res = tost_res4)
+```
 
-0.7551064 - 0.7040851
-0.6530639 - 0.6020426
-
+```{r, echo = FALSE}
 plot(NA, 
@@
 
+par(new=TRUE)
+curve(dnorm(x, 1.2, 0.5), from=-0.3, to=2.7, ylim = c(-2, 8), xlim = c(-3, 3), xlab = "", ylab = "", axes = FALSE)
+par(new=TRUE)
+curve(dnorm(x, 1.3, 0.5), from=-0.2, to=2.8, ylim = c(-4, 6), xlim = c(-3, 3), xlab = "", ylab = "", axes = FALSE)
+par(new=TRUE)
+curve(dnorm(x, 1.4, 0.5), from=-0.1, to=2.9, ylim = c(-6, 4), xlim = c(-3, 3), xlab = "", ylab = "", axes = FALSE)
+par(new=TRUE)
+curve(dnorm(x, 1.5, 0.5), from=0, to=3, ylim = c(-8, 2), xlim = c(-3, 3), xlab = "", ylab = "", axes = FALSE)
 ```
@@
 The difference in the percentage of overlap between A and B (`r SGPV1-SGPV2`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r SGPV3-SGPV4`).
+
+```{r}
+tail1 <- 1-pnorm(2, 1.5, 0.5)
+tail2 <- 1-pnorm(2, 1.4, 0.5)
+tail3 <- 1-pnorm(2, 1.3, 0.5)
+tail4 <- 1-pnorm(2, 1.2, 0.5)
+
+tail1-tail2
+tail3-tail4
+
+1-pnorm(1.96, 0, 1)
+```
 

### 2018-07-18 TOST_to_SGPV.R

@@ -17,13 +17,13 @@ TOST_to_SGPV <- function(tost_res){
   
   #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
   #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
-  if (tost_res$TOST_p1 > tost_res$TOST_p2) {
-    if (tost_res$TOST_p1 < 0.5){I = tost_res$low_eqbound + dist}
-    if (tost_res$TOST_p1 > 0.5){I = tost_res$low_eqbound - dist}} 
+  if (tost_res$TOST_p1 >= tost_res$TOST_p2) {
+    if (tost_res$TOST_p1 <= 0.5){I = tost_res$low_eqbound + dist}
+    if (tost_res$TOST_p1 >= 0.5){I = tost_res$low_eqbound - dist}} 
   
-  if (tost_res$TOST_p2 > tost_res$TOST_p1) {
-    if (tost_res$TOST_p2 < 0.5){I = tost_res$low_eqbound - dist}
-    if (tost_res$TOST_p2 > 0.5){I = tost_res$low_eqbound + dist}} 
+  if (tost_res$TOST_p2 >= tost_res$TOST_p1) {
+    if (tost_res$TOST_p2 <= 0.5){I = tost_res$low_eqbound - dist}
+    if (tost_res$TOST_p2 >= 0.5){I = tost_res$low_eqbound + dist}} 
   
   # Computing the CI around I
   lb <- I - qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # lower bound

### 2018-07-18 sgpv_vs_TOST.Rmd
update doc

@@
 knitr::opts_chunk$set(echo = TRUE)
+options(scipen=99)
 ```
@@
 
-In the plot below I calculate p-values for the TOST equivalence testing procedure, and plot the SGPV for the same tests:
+In the plot below *p*-values are calculated for the TOST equivalence testing procedure where a true population mean ranging from 140 to 150 is compared to the test value of 145 in a one-sample equivalence test where equivalence bounds are set to difference of -2 and +2 around the test value of 145.
+In other words, the equivalence range in the test contains all means between 143 and 147.
+FOr clarity, sample sizes consist of 1000000 observations.
+The population standard deviation is set to 500.
 
@@
 
-p_tost_list <- numeric(length(seq(140, 146, step)))
-sgpv_list <- numeric(length(seq(140, 146, step)))
-p_list <- numeric(length(seq(140, 146, step)))
-t_list <- numeric(length(seq(140, 146, step)))
+p_tost_list <- numeric(length(seq(140, 150, step)))
+sgpv_list <- numeric(length(seq(140, 150, step)))
+p_list <- numeric(length(seq(140, 150, step)))
+t_list <- numeric(length(seq(140, 150, step)))
 
@@
 
-for(i in seq(140, 146, step)){
+for(i in seq(140, 150, step)){
   count <- count + 1
   m <- i
-  mu <- 146
-  sd <- 800
+  mu <- 145
+  sd <- 500
   n <- 1000000
@@
 
-```{r sgpv_tost, echo=FALSE}
-plot(sgpv_list, type="l", col = "blue")
-lines(p_tost_list)
+```{r sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1001),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "",
+     xlab = "Mean")
+axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
 ```
 
-For ease of comparison, let me repeat the plot, now showing 1-TOST p-values:
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV). We see that
 
-```{r 1-sgpv_tost, echo=FALSE}
-plot(sgpv_list, type="l", col = "blue")
-lines(1-p_tost_list)
+```{r 1-sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1001),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "",
+     xlab = "Mean")
+axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
 ```
+```{r, include=FALSE}
+m <- 145
+mu <- 145
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res1 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)
+
+m <- 140
+mu <- 145
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res2 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
+```
+
+When the population mean is 145, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
+Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1`.
+
+One the other hand, if the observed mean is 140, the equivalence test is not surprisingly not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1`.
+Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2`.
 
@@
 It is clear the SGPV and the p-value from TOST are closely related.
-We can think of the SGPV as a straight line that will always overlap the p-value from an equivalence test in 3 points.
+We can think of the SGPV as a straight line that will always overlap the *p*-value from an equivalence test in 3 points.
 When the TOST p-value is 0.5, the SGPV is also 0.5.
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also so, and thus the *p*-value is 0.5.
-
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also so, and thus the *p*-value is 0.5 (situation A).
 ```{r, include=FALSE}
@@
 ```
-
-```{r, echo = FALSE}
+```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=4}
 plot(NA, 
@@
 The confidence interval width is a uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
-
 ```{r, include=FALSE}
@@
 ```
-
-```{r, echo = FALSE}
+```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=5}
 plot(NA, 
@@
 The difference in the percentage of overlap between A and B (`r SGPV1-SGPV2`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r SGPV3-SGPV4`).
-
-```{r}
+```{r , echo=FALSE}
 tail1 <- 1-pnorm(2, 1.5, 0.5)
@@
 tail4 <- 1-pnorm(2, 1.2, 0.5)
+```
 
-tail1-tail2
-tail3-tail4
+As we move the means closer to the test value in steps of 0.1 across A to D the p-value calculated for normally distributed data is not uniformly distributed.
+The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r tail1`, `r tail2`, `r tail3`, and `r tail4`.
+As we can see, the difference between A and B (`r tail1-tail2`) is not the same as the difference between C And D (`r tail3-tail4`).
+Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure 1 is the steepest at p = 0.5.
+Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
 
-1-pnorm(1.96, 0, 1)
-```
+##What does SGPV add to Equivalence Testing?
+
+Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what a SGPV adds to our statistical toolbox.
+First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test).
+As a descriptive statistic it is somewhat limited.
+SGPV is 1 for a range of values (see Figure 1) where the p-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1).
+
+Second, the SGPV
 

### 2018-07-19 sgpv_vs_TOST.Rmd
first draft

@@
 author: "Daniël Lakens & Marie Delacre"
-date: "1 juli 2018"
+date: "19 juli 2018"
 output: github_document
@@
 
-The second generation p-value (SGPV) is the proportion of data-supported hypotheses that are also null hypotheses (Blume, McGowan, Dupont, & Greevy, (2018).
-The authors note that: "Using second-generation p-values can only improve rigor, reproducibility and transparency across science."
-It was quickly noted on Twitter that the SGPV is similar to equivalence testing (https://twitter.com/statsepi/status/997759878503550976, https://twitter.com/lakens/status/995171827692515328).
+The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, McGowan, Dupont, & Greevy, (2018).
+The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'.
+The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis.
+The SGPV is the proportion of the 95% confidence interval (CI) around the observed effect estimate that falls within this equivalence range.
+If the 95% CI falls completely inside the equivalence range the SGPV is 1, or if falls completely outside the SGPV is 0.
+
+The SGPV has clear similarities with an already existing approach that compared the data to an equivalence range, known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993).
+In the Two One-Sided Tests (TOST) procedure data is tested against the upper and lower bounds of the equivalence range.
+If both one-sided tests indicate that the presence of effects that fall outside of the equivalence range (or in other words, when a 90% CI falls completely within the equivalence range) an equivalence test can be used to support the abense of a meaningful effect.
+Surprisingly, Blume et al (2018) do not discuss equivalence testing in their article, despite the strong conceptual similarities.
+Here, we aim to examine the similarities and differences between equivalence testing using the TOST procedure and the SGPV.
+
+#The relationship between *p*values from TOST and SGPV
 
@@
 In other words, the equivalence range in the test contains all means between 143 and 147.
-FOr clarity, sample sizes consist of 1000000 observations.
+For clarity, sample sizes consist of 1000000 observations.
 The population standard deviation is set to 500.
@@
 ```
+*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.
 
-For ease of comparison we can reverse the SGPV (by calculating 1-SGPV). We see that
-
+The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the two tests more comparable.
+We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
 ```{r 1-sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
@@
      xaxt = "n",
-     ylab = "",
+     ylab = "SGPV or TOST p-value",
      xlab = "Mean")
@@
 ```
+*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.
 
-When the population mean is 145, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
-Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1`.
+When the population mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
+Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).
 
-One the other hand, if the observed mean is 140, the equivalence test is not surprisingly not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1`.
-Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2`.
+One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1`.
+Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure 1).
 
@@
 
-It is clear the SGPV and the p-value from TOST are closely related.
+It is clear the SGPV and the *p*-value from TOST are closely related.
 We can think of the SGPV as a straight line that will always overlap the *p*-value from an equivalence test in 3 points.
-When the TOST p-value is 0.5, the SGPV is also 0.5.
+When the TOST *p*-value is 0.5, the SGPV is also 0.5.
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
@@
      yaxt = "n",
-     ylab = "",
+     ylab = "SGPV or TOST p-value",
      xlab = "Mean Difference")
@@
 ```
+*Figure 3*: Means, normal distribution, and 95% CI for three example datasets that illustrate the relationship between *p*-values from TOST and SGPV.
 
@@
 high_eqbound = 2 
-alpha = 0.05
+alpha = 0.025 #0.025 for the plot, because we want to show 95% CI.
 
@@
 ```
+*Figure 4*: Means, normal distribution, and 95% CI for data with a sample size of 1000000 and a standard deviation of 500 for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2.
 
+```{r, include=FALSE}
+#For the plot above I wanted 95% CI using the TOST functions, so I adjusted the alpha level.
+But I need to use alpha = 0.05 to calculate the SGPV - so here I quickly recalculate the SGPV for in the text
+m <- 146
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res1 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)
+
+m <- 145.9
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res2 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
+
+m <- 145.8
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res3 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV3 <- TOST_to_SGPV(tost_res = tost_res3)
+
+m <- 145.7
+mu <- 144.5
+sd <- 500
+n <- 1000000
+low_eqbound = -2 
+high_eqbound = 2 
+alpha = 0.05
+
+tost_res4 <- TOSTone.raw(m = m, 
+                   mu = mu,
+                   sd = sd, 
+                   n = n, 
+                   low_eqbound = low_eqbound, 
+                   high_eqbound = high_eqbound, 
+                   alpha = alpha
+)
+SGPV4 <- TOST_to_SGPV(tost_res = tost_res4)
+```
 For example, the SGPV from A to D is `r SGPV1`, `r SGPV2`, `r SGPV3`, and `r SGPV4`.
@@
 
-As we move the means closer to the test value in steps of 0.1 across A to D the p-value calculated for normally distributed data is not uniformly distributed.
+As we move the means closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
 The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r tail1`, `r tail2`, `r tail3`, and `r tail4`.
 As we can see, the difference between A and B (`r tail1-tail2`) is not the same as the difference between C And D (`r tail3-tail4`).
-Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure 1 is the steepest at p = 0.5.
+Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure 1 is the steepest at *p* = 0.5.
 Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
@@
 Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what a SGPV adds to our statistical toolbox.
-First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test).
+First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
+It numerically summarizes the information that is visually present in a plot (such as Figure 3) displaying the equivalence range and the 95% CI around the observed effect.
+
 As a descriptive statistic it is somewhat limited.
-SGPV is 1 for a range of values (see Figure 1) where the p-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1).
+SGPV is 1 for a range of values (see Figure 1) where the *p*-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1).
+Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65).
+Since the SGPV is always directly related to a *p*-value from the TOST procedure, different SGPV can be interpreted in the same manner as different *p*-values.
+From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range.
+From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis while controlling our error rate at a known maximum.
 
-Second, the SGPV
+It seems Blume et a (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values.
+The novelty, it seems to us, mainly lies in its use as a descriptive statistic, but the added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range for practical puroposes remains somewhat unclear.
+Nevertheless, our only goal is to clarify the relationship between a newly proposed statistic and the already existing TOST approach used to test for equivalence, and let researchers make an informed decision about which statistical approach provides the best answer to their question.
 
@@
 (2018).
-Second-generation p-values: Improved rigor, reproducibility, & transparency in statistical analyses.
+Second-generation *p*-values: Improved rigor, reproducibility, & transparency in statistical analyses.
 PLOS ONE, 13(3), e0188299.
 https://doi.org/10.1371/journal.pone.0188299
+Lakens, D.
+(2017).
+Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses.
+Social Psychological and Personality Science, 8(4), 355–362.
+https://doi.org/10.1177/1948550617697177
+Rogers, J.
+L., Howard, K.
+I., & Vessey, J.
+T.
+(1993).
+Using significance tests to evaluate equivalence between two experimental groups.
+Psychological Bulletin, 113(3), 553–565.
+http://dx.doi.org/10.1037/0033-2909.113.3.553

### 2018-07-19 sgpv_vs_TOST.Rmd
add link to Rmd

@@
 ```
+The RMarkdown file with the reproducible code of this text is [here](https://github.com/Lakens/TOST_vs_SGPV/blob/master/sgpv_vs_TOST.Rmd).
 
@@
 From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range.
-From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis while controlling our error rate at a known maximum.
+From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis is true while controlling our error rate at a known maximum.
 

### 2018-07-21 sgpv_vs_TOST.Rmd
clarify sentence

@@
 The SGPV has clear similarities with an already existing approach that compared the data to an equivalence range, known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993).
-In the Two One-Sided Tests (TOST) procedure data is tested against the upper and lower bounds of the equivalence range.
-If both one-sided tests indicate that the presence of effects that fall outside of the equivalence range (or in other words, when a 90% CI falls completely within the equivalence range) an equivalence test can be used to support the abense of a meaningful effect.
+In the Two One-Sided Tests (TOST) procedure data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2.
+If both one-sided tests indicate that effects that fall outside of the equivalence range can be statistically rejected (or in other words, when a 90% CI falls completely within the equivalence range of -2 and +2) an equivalence test can be used to support the abense of a meaningful effect.
 Surprisingly, Blume et al (2018) do not discuss equivalence testing in their article, despite the strong conceptual similarities.
@@
 In other words, the equivalence range in the test contains all means between 143 and 147.
-For clarity, sample sizes consist of 1000000 observations.
-The population standard deviation is set to 500.
+Blume et al (2018) rely on the z-distribution, while to TOST package uses the *t*-distribution (which is more accurate at smaller sample sizes).
+To make sure the SGPV give basically identical results, sample sizes consist of 1000000 observations (for which the t-distribution and z-distribution are basically identical).
+The population standard deviation is set to 500 to still give some variation in responses.
+Our conclusions should hold to the same extend for more realistic numbers (e.g., N = 100, SD = 1).
 

### 2018-07-26 p_tost_converter_onesample.R
add dedicated functions for one sample and indep t-test

@@ -1,0 +1,112 @@
+# Input parameters
+
+# In order to be able to convert p_tost into SGPV, there are many parameters we need to know:
+
+# From which eqbound is computed p_tost?
+# if p_tost = TOST_p1 (= p_tost is computed from the low_eqbound), then bound="low" 
+# else if p_tost = TOST_p2 (= p-tost is computed from the high_eqbound), then bound="high" 
+# n, sd 
+# alpha
+# low_eqbound and high_eqbound
+
+#-----------------------------------------------------------------------------------------------
+library(TOSTER)
+
+pTOSTone_converter=function(p_tost, 
+                         sd, 
+                         n, 
+                         alpha, 
+                         low_eqbound, 
+                         high_eqbound, 
+                         bound){
+
+  #------------------------------------------------------------------------
+  # Computing the SGPV when the CI around I is non-point CI (ie lb != ub)
+  #------------------------------------------------------------------------
+    if (sd!=0){  # data are variable (>< constant)
+
+      # computing t, based on p_tost
+      t <- abs((qt(p_tost, df = n-1))) 
+      
+      # computing I
+      dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+      if (bound=="low") {
+        if (p_tost <= 0.5){I = low_eqbound + dist}
+        if (p_tost > 0.5){I = low_eqbound - dist}} 
+      
+      if (bound=="high") {
+        if (p_tost <= 0.5){I = high_eqbound - dist}
+        if (p_tost > 0.5){I = high_eqbound + dist}}
+      
+      # Computing the CI around I
+      lb <- I - qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+      ub <- I + qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+      
+      qt(1 - alpha/2, df = 8.20001736626575)
+
+      # Computing the SGPV
+      
+      # If H0 is non-point H0
+      if(low_eqbound!=high_eqbound){ 
+        if (p_tost>(1-alpha/2)){SGPV = 0} 
+        else if(p_tost<(alpha/2)){SGPV = 1} 
+        else {SGPV <- (min(ub, high_eqbound) - max(lb, low_eqbound))/min(ub - lb, 2 * (high_eqbound - low_eqbound))}} 
+      
+      # If H0 is point H0
[…]

### 2018-07-26 sgpv_vs_TOST.Rmd
incorporate revisions Marie

@@
 The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis.
-The SGPV is the proportion of the 95% confidence interval (CI) around the observed effect estimate that falls within this equivalence range.
-If the 95% CI falls completely inside the equivalence range the SGPV is 1, or if falls completely outside the SGPV is 0.
+The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range.
+If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence rnge the SGPV is 0.
 
-The SGPV has clear similarities with an already existing approach that compared the data to an equivalence range, known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993).
-In the Two One-Sided Tests (TOST) procedure data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2.
-If both one-sided tests indicate that effects that fall outside of the equivalence range can be statistically rejected (or in other words, when a 90% CI falls completely within the equivalence range of -2 and +2) an equivalence test can be used to support the abense of a meaningful effect.
+The SGPV has strong similarities with an already existing approach known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993).
+In an equivalence test, an equivalence range is based upon a smallest effect size of interest.
+In the Two One-Sided Tests (TOST) approach to equivalence testing data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2).
+If both one-sided tests reject the presence of effects more extreme than the equivalence bounds when can act as if there is no meaningful effect.
+Because two one-sided tests are performed, equivalence can be declared when a 1-2*alpha CI (e.g., when the alpha level is 0.05, a 90% CI)  falls completely within the equivalence range of -2 and +2.
+
 Surprisingly, Blume et al (2018) do not discuss equivalence testing in their article, despite the strong conceptual similarities.
 Here, we aim to examine the similarities and differences between equivalence testing using the TOST procedure and the SGPV.
+Our goal is to allow researchers to choose the statistic that best answers the question they are interested in.
 
@@
 Blume et al (2018) rely on the z-distribution, while to TOST package uses the *t*-distribution (which is more accurate at smaller sample sizes).
-To make sure the SGPV give basically identical results, sample sizes consist of 1000000 observations (for which the t-distribution and z-distribution are basically identical).
+To make sure the SGPV give basically identical results, sample sizes consist of 1000000 observations (for which the *t*-distribution and z-distribution are basically identical).
 The population standard deviation is set to 500 to still give some variation in responses.
@@
 
-One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1`.
+One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1` (or more accuratelty, *p* > .999 as *p*-values are bounded between 0 and 1).
 Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure 1).
@@
 We can think of the SGPV as a straight line that will always overlap the *p*-value from an equivalence test in 3 points.
-When the TOST *p*-value is 0.5, the SGPV is also 0.5.
+When the TOST *p*-value is 0.5, the SGPV is also 0.5 (note that the reverse is not true).
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also so, and thus the *p*-value is 0.5 (situation A).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A).
 ```{r, include=FALSE}
@@
 When the 95% CI falls completely, but only just inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
-When the SGPV changes from 0.9999 to exactly 1 the 95% CI just touches the equivalence bound (see situation B in the plot above, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
+When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in the plot above, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
 The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in the plot above).
@@
 
-##What does SGPV add to Equivalence Testing?
+##What are the Relative Strengths and Weaknesses of Equivalence Testing and SGPV?
 
-Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what a SGPV adds to our statistical toolbox.
+Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what the introduction of SGPV adds to the existing statistical approaches, including equivalence tests, and what the relative strengths and weaknesses of either approach are.
 First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
@@
 
-As a descriptive statistic it is somewhat limited.
-SGPV is 1 for a range of values (see Figure 1) where the *p*-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1).
+The SGPV is 1 for tests where *p*-values for the TOST procedure differ.
+For example,  different equivalence tests with *p* = 0.024 and *p* = 0.0001 have a SGPV of 1.
 Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65).
@@
 
-It seems Blume et a (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values.
-The novelty, it seems to us, mainly lies in its use as a descriptive statistic, but the added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range for practical puroposes remains somewhat unclear.
+[To be extended]
+
+#Discussion
+
+It seems Blume et a (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values to the statistical toolbox.
+The novelty lies in its use as a descriptive statistic.
+The added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range, and using this percentage to describe the data, remains somewhat unclear for practical puroposes.
 Nevertheless, our only goal is to clarify the relationship between a newly proposed statistic and the already existing TOST approach used to test for equivalence, and let researchers make an informed decision about which statistical approach provides the best answer to their question.

### 2018-07-26 sgpv_vs_TOST.Rmd
minor type fix

@@
 author: "Daniël Lakens & Marie Delacre"
-date: "19 juli 2018"
+date: "26 juli 2018"
 output: github_document
@@
 
-It seems Blume et a (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values to the statistical toolbox.
+It seems Blume et al (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values to the statistical toolbox.
 The novelty lies in its use as a descriptive statistic.

### 2018-07-27 sgpv_vs_TOST_small_n_correction.Rmd
explore small sample correction

---
title: "A Closer Look at SGPV's Small Sample Correction"
author: "Daniël Lakens & Marie Delacre"
date: "27 juli 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=99)
```
```{r, include=FALSE}
library(TOSTER)
```

```{r, include=FALSE}
#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R

#' Second Generation P-value
p_delta <- function(lb, ub, delta_lb, delta_ub) {

  # special case: infinite CI and H0 bounds in the same direction
  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
    return(1)
  }

  # usual case: non-point CI & non-point Ho
  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
  if (delta_lb != delta_ub & lb != ub) {
    if (lb > delta_ub | ub < delta_lb) {
      return(0)
    } else if(lb > delta_lb & ub < delta_ub){
      return(1)
    } else {
      return(
        (min(ub, delta_ub) - max(lb, delta_lb)) /
          min(ub - lb, 2 * (delta_ub - delta_lb))
      )
    }
  }

  # special case 1: point CI, w/ or w/out a point H0
  # pdelta = 0 if CI is inside the Ho
  # pdelta = 1 if CI is inside the Ho
  if (lb == ub) {
    if (lb <= delta_ub & lb >= delta_lb){
      return(1)
    } else {
      return(0)
    }
  }

  # special case 2: point H0 & non-point CI
  # pdelta = 1/2 if H0 is inside the CI
  # pdelta = 0 if H0 is outside the CI
  if (delta_lb == delta_ub & lb != ub) {
    if (delta_lb <= ub & delta_lb >= lb) {
      return(1/2)
    } else {
      return(0)
    }
  }
}

#In the code sent by Jeffrey Blume, the code is different than the GitHub code. The inout has different namens (and there are new parameters). But the old code reproduces the shared analyses.

# Create function for Second Generation P-value ----
sgpv <- function(est.lo, est.hi, null.lo, null.hi) {

  # special case: infinite CI and H0 bounds in the same direction
  if ((null.lo == -Inf & est.lo == -Inf) | (null.hi == Inf & est.hi == Inf)) {
    return(1)
  }

  # usual case: non-point CI & non-point Ho
  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
  if (null.lo != null.hi & est.lo != est.hi) {
    if (est.lo > null.hi | est.hi < null.lo) {
      return(0)
    } else if(est.lo > null.lo & est.hi < null.hi){
      return(1)
    } else {
      return(
        (min(est.hi, null.hi) - max(est.lo, null.lo)) /
          min(est.hi - est.lo, 2 * (null.hi - null.lo))
      )
    }
  }

  # special case 1: point CI, w/ or w/out a point H0
  # pdelta = 0 if CI is inside the Ho
  # pdelta = 1 if CI is inside the Ho
  if (est.lo == est.hi) {
    if (est.lo <= null.hi & est.lo >= null.lo){
      return(1)
    } else {
      return(0)
    }
  }

  # special case 2: point H0 & non-point CI
  # pdelta = 1/2 if H0 is inside the CI
  # pdelta = 0 if H0 is outside the CI
  if (null.lo == null.hi & est.lo != est.hi) {
    if (null.lo <= est.hi & null.lo >= est.lo) {
      return(1/2)
    } else {
      return(0)
    }
  }
}

source("TOST_to_SGPV.R")

```

Although the *p*-value from the TOST procedure follows the SGPV closely in the examples we discussed earlier, there is one situation in which the SGPV deviates strongly from the TOST *p*-value. Whenever the CI is more than twice as wide as the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound, the normal calculation of the proportion of overlap is skipped, and the SGPV is set to 0.5 instead. Blume et al. (2018) call this the 'small sample correction factor'. However, it is not a correction in the typical use of the word, since the SGPV is not adjusted to any 'correct' value. When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, when all values in the equivalence range are also supported), the SGPV is set to 0.5 which according to Blume ete a. (2018) signal the SGPV is 'uninformative'. Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) *or* when then equivalence range is narrow. It is therefore not so much a 'small sample correction' as it is an exception to the typical calculation of the SGPV whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.

```{r, include=FALSE}
m <- 0.5
n <- 10
sd <- 1.5
d.lo <- -0.5*0.75
d.hi <- 0.5*0.75

tost_res1 <- TOSTone.raw(m = m, 
                         mu = 0,
                         sd = sd,
                         n = n,
                         low_eqbound = d.lo,
                         high_eqbound = d.hi,
                         alpha = 0.05,
                         plot = F)

SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)

```
```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=4}

plot(NA, 
     ylim = c(0, 1), 
     xlim = c(-2, 2),
     yaxt = "n",
     ylab = "SGPV or TOST p-value",
     xlab = "Mean Difference")
axis(1, at = c(-3,-2,-1,0,1,2,3,4,5), las = 1)
abline(v = tost_res1$high_eqbound, 
       lty = 2)
abline(v = tost_res1$low_eqbound, 
       lty = 2)
abline(v = 0, 
       lty = 2, 
       col = "grey")

points(x = tost_res1$diff, 
       y = 0.5, 
       pch = 15, 
       cex = 2)
segments(tost_res1$LL_CI_TTEST, 
         0.5, 
         tost_res1$UL_CI_TTEST, 
         0.5, 
         lwd = 3)
```
*Figure 1*: Example of a 95% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).

Blume et al. (2018) sent through code that simulates 1000 tests with 6, 10, or 20 subjects, where means are normally distributed with a mean of 0 and a sd of 1, the equivalence range is set from -0.375 to 0.375, and a one-sample t-test is performed against 0. The figure below shows the relationship between the SGPV and the p-value from the TOST procedure. 
```{r, include=FALSE}
#Code by Jeffrey Blume to illustrate where TOST_p and SGPV do not give the same result.
#Note I removed the code "na.constant=1e-5, length.warn=TRUE" from the function because this does not match the code on GitHub and I did not have the same function as used by Jeffrey - but the adjusted code reproduces his result. 
#The code is slow because of verbose output.

n=40
breaks=c(6,10,20)
sims=1000
d.lo=-0.5*0.75
d.hi=0.5*0.75

keep=matrix(-99,nrow=sims,ncol=6)

for (i in 1:sims) {

  z=rnorm(n,mean=0,sd=1)

  to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), 
                        mu=0,
                        sd=sd(z[1:breaks[1]]),
                        n=length(z[1:breaks[1]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.2=TOSTone.raw(m=mean(z[1:breaks[2]]),
                        mu=0,
                        sd=sd(z[1:breaks[2]]),
                        n=length(z[1:breaks[2]]),
                        low_eqbound=d.lo,
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.3=TOSTone.raw(m=mean(z[1:breaks[3]]), 
                        mu=0,
                        sd=sd(z[1:breaks[3]]),
                        n=length(z[1:breaks[3]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
  p.tost.2=max(to.stat.2$TOST_p1,to.stat.2$TOST_p2)
  p.tost.3=max(to.stat.3$TOST_p1,to.stat.3$TOST_p2)

  tt.stat.1=t.test(z[1:breaks[1]])$conf.int
  tt.stat.2=t.test(z[1:breaks[2]])$conf.int
  tt.stat.3=t.test(z[1:breaks[3]])$conf.int

  p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.2=sgpv(est.lo=tt.stat.2[1], est.hi=tt.stat.2[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.3=sgpv(est.lo=tt.stat.3[1], est.hi=tt.stat.3[2], 
                 null.lo=d.lo, null.hi=d.hi)

  keep[i,]=cbind(p.delta.1,p.tost.1,p.delta.2,p.tost.2,p.delta.3,p.tost.3)
}

```

```{r, echo=FALSE, dpi=300, fig.width=7, fig.height=5}
plot(keep[,1],keep[,2],xlim=c(0,1),ylim=c(0,1),type="n",
     xlab="SGPV",ylab="TOST PV")

abline(1,-1,lty=2,col="grey")

points(keep[,1],keep[,2],pch=20,col="dodgerblue")
points(keep[,3],keep[,4],pch=20,col="forestgreen")
points(keep[,5],keep[,6],pch=20,col="firebrick")

legend("topright",bty="n",pch=20,
       col=c("dodgerblue","forestgreen","firebrick"),
       c(paste("n = ",breaks[1],sep=""),
         paste("n = ",breaks[2],sep=""),
         paste("n = ",breaks[3],sep="")))

```
*Figure 2*: Result of simulation showing when p-values from TOST differ from the SGPV.

To understand Figure 2 better, it makes sense to re-run the simulation with slightly larger sample size to distinguish two factors that contribute to the observed pattern, and to better understand the relationship between p-values from the TOST procedure and the SGPV whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1.

```{r, include=FALSE}
#Adapted code.
n=1000
sd <- 10
breaks=c(100,500,1000)
sims=1000
d.lo=-0.5*0.75
d.hi=0.5*0.75

keep=matrix(-99,nrow=sims,ncol=6)

for (i in 1:sims) {

  z=rnorm(n,mean=0,sd=sd)

  to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), mu=0, 
                        sd=sd(z[1:breaks[1]]), n=length(z[1:breaks[1]]), 
                        low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot=F)

  to.stat.2=TOSTone.raw(m=mean(z[1:breaks[2]]), mu=0, 
                        sd=sd(z[1:breaks[2]]), n=length(z[1:breaks[2]]), 
                        low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot=F)

  to.stat.3=TOSTone.raw(m=mean(z[1:breaks[3]]), mu=0, 
                        sd=sd(z[1:breaks[3]]), n=length(z[1:breaks[3]]), 
                        low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot=F)

  p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
  p.tost.2=max(to.stat.2$TOST_p1,to.stat.2$TOST_p2)
  p.tost.3=max(to.stat.3$TOST_p1,to.stat.3$TOST_p2)

  tt.stat.1=t.test(z[1:breaks[1]])$conf.int
  tt.stat.2=t.test(z[1:breaks[2]])$conf.int
  tt.stat.3=t.test(z[1:breaks[3]])$conf.int

  p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.2=sgpv(est.lo=tt.stat.2[1], est.hi=tt.stat.2[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.3=sgpv(est.lo=tt.stat.3[1], est.hi=tt.stat.3[2], 
                 null.lo=d.lo, null.hi=d.hi)

  keep[i,]=cbind(p.delta.1,p.tost.1,p.delta.2,p.tost.2,p.delta.3,p.tost.3)
}

```

```{r, echo=FALSE, dpi=300, fig.width=7, fig.height=5}
plot(keep[,1],keep[,2],xlim=c(0,1),ylim=c(0,1),type="n",
     xlab="SGPV",ylab="TOST PV")

abline(1,-1,lty=2,col="grey")

points(keep[,1],keep[,2],pch=20,col="dodgerblue")
points(keep[,3],keep[,4],pch=20,col="forestgreen")
points(keep[,5],keep[,6],pch=20,col="firebrick")

legend("topright",bty="n",pch=20,
       col=c("dodgerblue","forestgreen","firebrick"),
       c(paste("n = ",breaks[1],sep=""),
         paste("n = ",breaks[2],sep=""),
         paste("n = ",breaks[3],sep="")))

```
*Figure 3*: Reproduced Figure 2, but with larger sample sizes and larger standard deviation.
```{r, include = FALSE}
#Check if power is indeed 0 for equivalence tests
sum(p.tost.1<0.05)
sum(p.tost.2<0.05)
sum(p.tost.3<0.05)
```
First of all, it should be noted that in this simulation the *p*-values for the TOST procedure have a lower bound, and the p-values for the equivalence test are not smaller than 0.05 for sample sizes of 100, 500, and 1000 per group (i.e., they do not get below 0.05 on the y-axis). In other words, we can *never* conclude equivalence based on any of the 1000 studies we simulated. How is this possible? Remember that the TOST procedure consists of two one-sided tests against the upper and lower equivalence bound. The TOST p-value is smaller than 0.05 if the 90% CI falls completely between the upper and lower equivalence bounds. However, we are simulating data where the 90% CI is so wide it never falls completely within the two equivalence bounds. As Lakens (2017) notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” This is the situation in the simulation. None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.

For the SGPV we know that it is set to 0.5 whenever the CI is twice as wide as the equivalence range, and the CI overlaps with the upper and lower equivalence bound. When we start at the left end of the x-axis we see that the SGPV can be 0 (i.e., fall completely outside of the equivalence range). The SGPV becomes smaller as the 95% CI starts to overlap with one of the equivaence bounds. However, where the SGPV would be 0.5 only when the observed mean falls exactly on one of the equivalence bounds, it now is set to 0.5 earlier. The wide 95% CI implies that well before the observed mean has moved close enough to fall on the equivalence bound, the confidence interval overlaps with both of the equivalence bounds (see Figure 1). We see this in Figure 3, where the SGVP increases up until the point where the CI overlaps with the upper and lower equivalence bounds - at which point the SGPV is set to 0.5. The smaller the CI (or the larger the sample size, all else equal) the smaller the TOST *p*-value is before the SGPV is set to 0.5.

Now that we have explained on pattern that leads to the variation in the plot by Jeffrey Blume, we need to turn to the second source of variation. First, we slightly adapt the original code by making the equivalence bound wider (from -1 to 1), adding a constant to the simulated data (from -2 to 2) to simulate data when there is a true effect (this is such that we have data for the entire range of SGPV and TOT p-values), and setting sample sizes to 10, 20 and 40. We see a regular curve as we have seen before.

```{r, include=FALSE}
#
n=40
breaks=c(10,20,40)
sims=1000
d.lo=-1
d.hi=1

keep=matrix(-99,nrow=sims,ncol=6)

for (i in 1:sims) {

  z=rnorm(n,mean=0,sd=1)+runif(1,-2,2)

  to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), 
                        mu=0,
                        sd=sd(z[1:breaks[1]]),
                        n=length(z[1:breaks[1]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.2=TOSTone.raw(m=mean(z[1:breaks[2]]),
                        mu=0,
                        sd=sd(z[1:breaks[2]]),
                        n=length(z[1:breaks[2]]),
                        low_eqbound=d.lo,
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.3=TOSTone.raw(m=mean(z[1:breaks[3]]), 
                        mu=0,
                        sd=sd(z[1:breaks[3]]),
                        n=length(z[1:breaks[3]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
  p.tost.2=max(to.stat.2$TOST_p1,to.stat.2$TOST_p2)
  p.tost.3=max(to.stat.3$TOST_p1,to.stat.3$TOST_p2)

  tt.stat.1=t.test(z[1:breaks[1]])$conf.int
  tt.stat.2=t.test(z[1:breaks[2]])$conf.int
  tt.stat.3=t.test(z[1:breaks[3]])$conf.int

  p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.2=sgpv(est.lo=tt.stat.2[1], est.hi=tt.stat.2[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.3=sgpv(est.lo=tt.stat.3[1], est.hi=tt.stat.3[2], 
                 null.lo=d.lo, null.hi=d.hi)

  keep[i,]=cbind(p.delta.1,p.tost.1,p.delta.2,p.tost.2,p.delta.3,p.tost.3)
}

```
```{r, echo=FALSE, dpi=300, fig.width=7, fig.height=5}
plot(keep[,1],keep[,2],xlim=c(0,1),ylim=c(0,1),type="n",
     xlab="SGPV",ylab="TOST PV")

abline(1,-1,lty=2,col="grey")

points(keep[,1],keep[,2],pch=20,col="dodgerblue")
points(keep[,3],keep[,4],pch=20,col="forestgreen")
points(keep[,5],keep[,6],pch=20,col="firebrick")

legend("topright",bty="n",pch=20,
       col=c("dodgerblue","forestgreen","firebrick"),
       c(paste("n = ",breaks[1],sep=""),
         paste("n = ",breaks[2],sep=""),
         paste("n = ",breaks[3],sep="")))

```
We then repeat the simulation, now setting the equivalence bounds to a more narrow -0.4 to 0.4 range. Everything else is identical to the plot above. 
```{r, include=FALSE}
#
n=40
breaks=c(10,20,40)
sims=1000
d.lo=-0.4
d.hi=0.4

keep=matrix(-99,nrow=sims,ncol=6)

for (i in 1:sims) {

  z=rnorm(n,mean=0,sd=1)+runif(1,-2,2)

  to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), 
                        mu=0,
                        sd=sd(z[1:breaks[1]]),
                        n=length(z[1:breaks[1]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.2=TOSTone.raw(m=mean(z[1:breaks[2]]),
                        mu=0,
                        sd=sd(z[1:breaks[2]]),
                        n=length(z[1:breaks[2]]),
                        low_eqbound=d.lo,
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  to.stat.3=TOSTone.raw(m=mean(z[1:breaks[3]]), 
                        mu=0,
                        sd=sd(z[1:breaks[3]]),
                        n=length(z[1:breaks[3]]),
                        low_eqbound=d.lo, 
                        high_eqbound=d.hi,
                        alpha=0.05,
                        plot="FALSE")

  p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
  p.tost.2=max(to.stat.2$TOST_p1,to.stat.2$TOST_p2)
  p.tost.3=max(to.stat.3$TOST_p1,to.stat.3$TOST_p2)

  tt.stat.1=t.test(z[1:breaks[1]])$conf.int
  tt.stat.2=t.test(z[1:breaks[2]])$conf.int
  tt.stat.3=t.test(z[1:breaks[3]])$conf.int

  p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.2=sgpv(est.lo=tt.stat.2[1], est.hi=tt.stat.2[2], 
                 null.lo=d.lo, null.hi=d.hi)

  p.delta.3=sgpv(est.lo=tt.stat.3[1], est.hi=tt.stat.3[2], 
                 null.lo=d.lo, null.hi=d.hi)

  keep[i,]=cbind(p.delta.1,p.tost.1,p.delta.2,p.tost.2,p.delta.3,p.tost.3)
}

```
```{r, echo=FALSE, dpi=300, fig.width=7, fig.height=5}
plot(keep[,1],keep[,2],xlim=c(0,1),ylim=c(0,1),type="n",
     xlab="SGPV",ylab="TOST PV")

abline(1,-1,lty=2,col="grey")

points(keep[,1],keep[,2],pch=20,col="dodgerblue")
points(keep[,3],keep[,4],pch=20,col="forestgreen")
points(keep[,5],keep[,6],pch=20,col="firebrick")

legend("topright",bty="n",pch=20,
       col=c("dodgerblue","forestgreen","firebrick"),
       c(paste("n = ",breaks[1],sep=""),
         paste("n = ",breaks[2],sep=""),
         paste("n = ",breaks[3],sep="")))

```

### 2018-07-27 Jeffrey/tost.R

@@ -1,0 +1,79 @@
+#######
+
+install.packages("TOSTER")
+library("TOSTER")
+
+n=40
+breaks=c(6,10,20)
+sims=1000
+d.lo=-0.5*0.75
+d.hi=0.5*0.75
+
+keep=matrix(-99,nrow=sims,ncol=6)
+
+for (i in 1:sims) {
+
+z=rnorm(n,mean=0,sd=1)
+
+to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), mu=0, 
+	sd=sd(z[1:breaks[1]]), n=length(z[1:breaks[1]]), 
+	low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot="FALSE")
+
+to.stat.2=TOSTone.raw(m=mean(z[1:breaks[2]]), mu=0, 
+	sd=sd(z[1:breaks[2]]), n=length(z[1:breaks[2]]), 
+	low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot="FALSE")
+
+to.stat.3=TOSTone.raw(m=mean(z[1:breaks[3]]), mu=0, 
+	sd=sd(z[1:breaks[3]]), n=length(z[1:breaks[3]]), 
+	low_eqbound=d.lo, high_eqbound=d.hi, alpha=0.05,plot="FALSE")
+
+p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
+p.tost.2=max(to.stat.2$TOST_p1,to.stat.2$TOST_p2)
+p.tost.3=max(to.stat.3$TOST_p1,to.stat.3$TOST_p2)
+
+tt.stat.1=t.test(z[1:breaks[1]])$conf.int
+tt.stat.2=t.test(z[1:breaks[2]])$conf.int
+tt.stat.3=t.test(z[1:breaks[3]])$conf.int
+	
+p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
+			null.lo=d.lo, null.hi=d.hi, 
+			na.constant=1e-5, length.warn=TRUE)
+
+p.delta.2=sgpv(est.lo=tt.stat.2[1], est.hi=tt.stat.2[2], 
+			null.lo=d.lo, null.hi=d.hi, 
+			na.constant=1e-5, length.warn=TRUE)
+
[…]

### 2018-07-27 Jeffrey/tost_dl.R

@@ -1,0 +1,157 @@
+#######
+## Adjustments to Jeffrey's code by Daniel
+#install.packages("TOSTER")
+
+library("TOSTER")
+
+##########################################################################
+# Create function for Second Generation P-value ----
+sgpv <- function(est.lo, est.hi, null.lo, null.hi) {
+  
+  # special case: infinite CI and H0 bounds in the same direction
+  if ((null.lo == -Inf & est.lo == -Inf) | (null.hi == Inf & est.hi == Inf)) {
+    return(1)
+  }
+  
+  # usual case: non-point CI & non-point Ho
+  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
+  if (null.lo != null.hi & est.lo != est.hi) {
+    if (est.lo > null.hi | est.hi < null.lo) {
+      return(0)
+    } else if(est.lo > null.lo & est.hi < null.hi){
+      return(1)
+    } else {
+      return(
+        (min(est.hi, null.hi) - max(est.lo, null.lo)) /
+          min(est.hi - est.lo, 2 * (null.hi - null.lo))
+      )
+    }
+  }
+  
+  # special case 1: point CI, w/ or w/out a point H0
+  # pdelta = 0 if CI is inside the Ho
+  # pdelta = 1 if CI is inside the Ho
+  if (est.lo == est.hi) {
+    if (est.lo <= null.hi & est.lo >= null.lo){
+      return(1)
+    } else {
+      return(0)
+    }
+  }
+  
+  # special case 2: point H0 & non-point CI
+  # pdelta = 1/2 if H0 is inside the CI
+  # pdelta = 0 if H0 is outside the CI
+  if (null.lo == null.hi & est.lo != est.hi) {
+    if (null.lo <= est.hi & null.lo >= est.lo) {
+      return(1/2)
+    } else {
+      return(0)
+    }
+  }
+}
+################################################################################
+
+#Example 1
+
+n=1000
+sd <- 10
[…]

### 2018-07-27 Marie/TOST_vs_SGPV-patch-3/TOST_to_SGPV.R

@@ -1,0 +1,41 @@
+# Input parameters
+# res = the stored results from the TOST analysis
+# n is the sample size
+# sd is the standard deviation
+#-----------------------------------------------------------------------------------------------
+
+TOST_to_SGPV <- function(tost_res){
+  
+  # computing t, based on p_tost
+  t <- min(tost_res$TOST_t1, tost_res$TOST_t2) 
+  
+  n <- tost_res$TOST_df + 1
+  sd <- (tost_res$diff-tost_res$low_eqbound)/tost_res$TOST_t1 * sqrt(n)
+  
+  # computing I
+  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+  
+  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
+  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
+  if (tost_res$TOST_p1 >= tost_res$TOST_p2) {
+    if (tost_res$TOST_p1 <= 0.5){I = tost_res$low_eqbound + dist}
+    if (tost_res$TOST_p1 >= 0.5){I = tost_res$low_eqbound - dist}} 
+  
+  if (tost_res$TOST_p2 >= tost_res$TOST_p1) {
+    if (tost_res$TOST_p2 <= 0.5){I = tost_res$low_eqbound - dist}
+    if (tost_res$TOST_p2 >= 0.5){I = tost_res$low_eqbound + dist}} 
+  
+  # Computing the CI around I
+  lb <- I - qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+  ub <- I + qt(1 - tost_res$alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+  
+  if (lb > tost_res$high_eqbound | ub < tost_res$low_eqbound){
+    SGPV = 0
+    } 
+  else if(lb > tost_res$low_eqbound & ub < tost_res$high_eqbound){
+    SGPV = 1
+    } 
+  else {SGPV <- (min(ub, tost_res$high_eqbound) - max(lb, tost_res$low_eqbound))/min(ub - lb, 2 * (tost_res$high_eqbound - tost_res$low_eqbound))}
+  
+  return(SGPV)
+}

### 2018-07-27 Marie/TOST_vs_SGPV-patch-3/p_tost_converter.R

@@ -1,0 +1,72 @@
+# Input parameters
+
+# In order to be able to convert p_tost into SGPV, there are many parameters we need to know:
+
+# From which eqbound is computed p_tost?
+	# if p_tost = TOST_p1 (= p_tost is computed from the low_eqbound), then bound="low" 
+      # else if p_tost = TOST_p2 (= p-tost is computed from the high_eqbound), then bound="high" 
+# n, sd 
+# alpha
+# low_eqbound and high_eqbound
+
+#-----------------------------------------------------------------------------------------------
+
+pTOST_converter=function(p_tost, 
+                         sd, 
+                         n, 
+                         alpha, 
+                         low_eqbound, 
+                         high_eqbound, 
+                         bound){
+  
+  # computing t, based on p_tost
+  t <- abs((qt(p_tost, df = n-1))) 
+  
+  # computing I
+  dist <- t * sd/sqrt(n) # how far is I from the closest eqbound?
+  
+  #LAKENS: I I fixed this now - you can't know based on non-sig if bound is left or right from alpha. 
+  #It should be based on whether p is larger or smaller than 0.5. I smaller than 0.5, bound - dist. 
+  # DELACRE: when p_tost = .5, t=0 and therefore dist=0 (as +0 = -0=0, I arbitrary changed "<" into "<=")
+  if (bound=="low") {
+    if (p_tost <= 0.5){I = low_eqbound + dist}
+    if (p_tost > 0.5){I = low_eqbound - dist}} 
+  
+  if (bound=="high") {
+    if (p_tost <= 0.5){I = high_eqbound - dist}
+    if (p_tost > 0.5){I = high_eqbound + dist}}
+  
+  # Computing the CI around I
+  lb <- I - qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # lower bound
+  ub <- I + qt(1 - alpha/2, df = n - 1) * sd/sqrt(n) # upper bound
+  
+  if (lb > high_eqbound | ub < low_eqbound){SGPV = 0} 
+  else if(lb > low_eqbound & ub < high_eqbound){SGPV = 1} 
+  else {SGPV <- (min(ub, high_eqbound) - max(lb, low_eqbound))/min(ub - lb, 2 * (high_eqbound - low_eqbound))}
+  
+  return(SGPV)
+}
+
+
+
+
+m <- 143.9
+mu <- 146
+m-mu
[…]

### 2018-07-27 Marie/TOST_vs_SGPV-patch-3/p_tost_converter_two_indep_samples.R

@@ -1,0 +1,157 @@
+# Input parameters
+
+# In order to be able to convert p_tost into SGPV, there are many parameters we need to know:
+
+# From which eqbound is computed p_tost?
+# if p_tost = TOST_p1 (= p_tost is computed from the low_eqbound), then bound="low" 
+# else if p_tost = TOST_p2 (= p-tost is computed from the high_eqbound), then bound="high" 
+# n, sd 
+# alpha
+# low_eqbound and high_eqbound
+
+#-----------------------------------------------------------------------------------------------
+library(TOSTER)
+
+pTOSTtwo_converter=function(p_tost, 
+                         m1,m2, 
+                         sd1,sd2, 
+                         n1,n2, 
+                         alpha, 
+                         low_eqbound, 
+                         high_eqbound, 
+                         bound,
+                         var.equal){
+
+  # the standard error for the CI won't be computed the same way 
+  # if the homoscedasticity assumption is met or not 
+
+    if(var.equal=="TRUE"){
+    pooled_sd <- sqrt(((n1-1)*sd1^2+(n2-1)*sd2^2)/(n1+n2-2))
+    sd <- pooled_sd*sqrt(1/n1+1/n2)
+  } else {sd<-sqrt(sd1^1/n1+sd2^2/n2)}
+  
+  #------------------------------------------------------------------------
+  # Computing the SGPV when the CI around I is non-point CI (ie lb != ub)
+  #------------------------------------------------------------------------
+
+    if (sd!=0){  # data are variable (>< constant)
+
+      ### Computing the CI around (m1-m2) 
+   
+           
+      # If var.equal=TRUE
+
+       
+      if (var.equal==TRUE){
+        
+       # computing t, based on p_tost and df
+        t <- abs((qt(p_tost, df = n1+n2-2)))
+        dist <- t*pooled_sd*sqrt(1/n1+1/n2) # how far is I from the closest eqbound?
+
+       # computing I
+          if (bound=="low") {
+            if (p_tost <= 0.5){I = low_eqbound + dist}
+            if (p_tost > 0.5){I = low_eqbound - dist}} 
+          if (bound=="high") {
[…]

### 2018-07-27 SGPV_function.R

@@ -1,0 +1,47 @@
+#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
+
+#' Second Generation P-value
+p_delta <- function(lb, ub, delta_lb, delta_ub) {
+  
+  # special case: infinite CI and H0 bounds in the same direction
+  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
+    return(1)
+  }
+  
+  # usual case: non-point CI & non-point Ho
+  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
+  if (delta_lb != delta_ub & lb != ub) {
+    if (lb > delta_ub | ub < delta_lb) {
+      return(0)
+    } else if(lb > delta_lb & ub < delta_ub){
+      return(1)
+    } else {
+      return(
+        (min(ub, delta_ub) - max(lb, delta_lb)) /
+          min(ub - lb, 2 * (delta_ub - delta_lb))
+      )
+    }
+  }
+  
+  # special case 1: point CI, w/ or w/out a point H0
+  # pdelta = 0 if CI is inside the Ho
+  # pdelta = 1 if CI is inside the Ho
+  if (lb == ub) {
+    if (lb <= delta_ub & lb >= delta_lb){
+      return(1)
+    } else {
+      return(0)
+    }
+  }
+  
+  # special case 2: point H0 & non-point CI
+  # pdelta = 1/2 if H0 is inside the CI
+  # pdelta = 0 if H0 is outside the CI
+  if (delta_lb == delta_ub & lb != ub) {
+    if (delta_lb <= ub & delta_lb >= lb) {
+      return(1/2)
+    } else {
+      return(0)
+    }
+  }
+}

### 2018-07-28 sgpv_vs_TOST.Rmd
Update discussing 4 situations when p-values from TOST and SGPV are unrelated

@@
 author: "Daniël Lakens & Marie Delacre"
-date: "26 juli 2018"
+date: "28 juli 2018"
 output: github_document
@@
 ```
-
 ```{r sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
@@
 
+##When are the SGPV and Equivalence Test Unrelated?
+
+There are 4 situations where *p*-values from TOST and SGPV are unrelated.
+The first two situations were discussed earlier, and can be seen in Figure  1.
+When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
+Because p-values approach 0 or 1, but are never exactly 0 or 1, while the SGPV is exactly 0 or 1, the two statistics are completely unrelated.
+The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
+The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical lines at SGPV of 0 and 1.
+```{r, include=FALSE}
+step = 0.01
+
+p_tost_list <- numeric(length(seq(140, 150, step)))
+sgpv_list <- numeric(length(seq(140, 150, step)))
+p_list <- numeric(length(seq(140, 150, step)))
+t_list <- numeric(length(seq(140, 150, step)))
+
+count <- 0
+
+for(i in seq(140, 150, step)){
+  count <- count + 1
+  m <- i
+  mu <- 145
+  sd <- 500
+  n <- 1000000
+  low_eqbound = -2 
+  high_eqbound = 2 
+  alpha = 0.05
+
+  invisible(capture.output(res <- TOSTone.raw(m = m, 
+                                              mu = mu,
+                                              sd = sd, 
+                                              n = n, 
+                                              low_eqbound = low_eqbound, 
+                                              high_eqbound = high_eqbound, 
+                                              alpha = alpha,
+                                              plot = FALSE
+  )))
+  t <- (m - mu)/(sd/sqrt(n))
+  t_list[count] <- t
+  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  p_list[count] <- 2 * pt(-abs(t), df = n-1)
+}
+```
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(sgpv_list, 
+     p_tost_list,
+     type="l",
+     lwd = 3, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1),
+     # yaxt = "n",
+     # xaxt = "n",
+     ylab = "TOST p-value",
+     xlab = "SGPV")
+```
+*Figure 5*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 1.
+
+A third situation in which the SGPV deviates strongly from the TOST *p*-value is whenever the CI is more than twice as wide as the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
+In this situation the normal calculation of the proportion of overlap is skipped, and the SGPV is set to 0.5 instead.
+Blume et al.
+(2018) call this the 'small sample correction factor'.
+However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any 'correct' value.
+When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, when all values in the equivalence range are also supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
+Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) *or* when then equivalence range is narrow.
+It is therefore not so much a 'small sample correction' as it is an exception to the typical calculation of the SGPV whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+
+We can examine this situation be calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range.
+```{r, include=FALSE}
+step = 0.01
+
+p_tost_list <- numeric(length(seq(-3, 3, step)))
+sgpv_list <- numeric(length(seq(-3, 3, step)))
+p_list <- numeric(length(seq(-3, 3, step)))
+t_list <- numeric(length(seq(-3, 3, step)))
+
+count <- 0
+
+for(i in seq(-3, 3, step)){
+  count <- count + 1
+  m <- i
+  mu <- 0
+  sd <- 2
+  n <- 10
+  low_eqbound = -0.4 
+  high_eqbound = 0.4
+  alpha = 0.05
+
+  invisible(capture.output(res <- TOSTone.raw(m = m, 
+                                              mu = mu,
+                                              sd = sd, 
+                                              n = n, 
+                                              low_eqbound = low_eqbound, 
+                                              high_eqbound = high_eqbound, 
+                                              alpha = alpha,
+                                              plot = FALSE
+  )))
+  t <- (m - mu)/(sd/sqrt(n))
+  t_list[count] <- t
+  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  p_list[count] <- 2 * pt(-abs(t), df = n-1)
+}
+```
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, 600),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "",
+     xlab = "Mean")
+axis(1, at = seq(0,600,100), labels = seq(-3,3,1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
+abline(h = 0.5, 
+       lty = 6,
+       col = "lightgrey")
+
+```
+*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis).
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.
+
+We can again plot the two statistics against each other so see where they are unrelated (indicated by staight lines in the curve).
+We see the SGPV is 0.5 for a range of observed means where the p-value from the equivalence test still varies.
+It should be noted that in these calculations the *p*-values for the TOST procedure are *never* smaller than 0.05 (i.e., they do not get below 0.05 on the y-axis).
+In other words, we can't conclude equivalence based on any of the observed means.
+How is this possible?
+Remember that the TOST procedure consists of two one-sided tests against the upper and lower equivalence bound.
+The TOST *p*-value is smaller than 0.05 if the 90% CI falls completely between the upper and lower equivalence bounds.
+However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
+As Lakens (2017) notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(sgpv_list, 
+     p_tost_list,
+     type="l",
+     lwd = 3, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1),
+     # yaxt = "n",
+     # xaxt = "n",
+     ylab = "TOST p-value",
+     xlab = "SGPV")
+```
+*Figure 7*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
+
+There is one last situation where the *p*-value from the TOST procedure and the SGPV are unrelated.
+This is when the CI overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
+This fourth category exists because of the decision by Blume and collagues to set the SGPV to 0.5 whenever the CI is twice as wide as the equivalence range and the CI overlaps with both equivalence bounds.
+This means that there are situations where the CI interval overlaps with both equivalence bounds, while the CI is less than twice as large as the equivalence bound.
+For example, in the example below, we see an example where the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
+```{r, include=FALSE}
+m <- 0.2
+n <- 10
+sd <- 1
+d.lo <- -0.4
+d.hi <- 0.4
+
+tost_res1 <- TOSTone.raw(m = m, 
+                         mu = 0,
+                         sd = sd,
+                         n = n,
+                         low_eqbound = d.lo,
+                         high_eqbound = d.hi,
+                         alpha = 0.05,
+                         plot = F)
+
+#Ratio CI to equivalence bounds
+(tost_res1$UL_CI_TTEST - tost_res1$LL_CI_TTEST) / (d.hi - d.lo)
+
+```
+```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=4}
+
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(-2, 2),
+     yaxt = "n",
+     ylab = "SGPV or TOST p-value",
+     xlab = "Mean Difference")
+axis(1, at = c(-3,-2,-1,0,1,2,3,4,5), las = 1)
+abline(v = tost_res1$high_eqbound, 
+       lty = 2)
+abline(v = tost_res1$low_eqbound, 
+       lty = 2)
+abline(v = 0, 
+       lty = 2, 
+       col = "grey")
+
+points(x = tost_res1$diff, 
+       y = 0.5, 
+       pch = 15, 
+       cex = 2)
+segments(tost_res1$LL_CI_TTEST, 
+         0.5, 
+         tost_res1$UL_CI_TTEST, 
+         0.5, 
+         lwd = 3)
+```
+*Figure 8*: Example of a 95% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).
+
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it ccompletely overlaps with the equivalence range) while the *p*-value for the TOST procedure varies.
+We can see this in Figure 9 below.
+The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
+How high the SGPV will be when the CI overlaps with the lower and upper equivalence bounds, but the CI is not twice as large as the equivalence range, depends on the width of the CI and the equivalence range.
+```{r, include=FALSE}
+step = 0.01
+
+p_tost_list <- numeric(length(seq(-3, 3, step)))
+sgpv_list <- numeric(length(seq(-3, 3, step)))
+p_list <- numeric(length(seq(-3, 3, step)))
+t_list <- numeric(length(seq(-3, 3, step)))
+
+count <- 0
+
+for(i in seq(-3, 3, step)){
+  count <- count + 1
+  m <- i
+  mu <- 0
+  sd <- 1
+  n <- 10
+  low_eqbound = -0.4 
+  high_eqbound = 0.4
+  alpha = 0.05
+
+  invisible(capture.output(res <- TOSTone.raw(m = m, 
+                                              mu = mu,
+                                              sd = sd, 
+                                              n = n, 
+                                              low_eqbound = low_eqbound, 
+                                              high_eqbound = high_eqbound, 
+                                              alpha = alpha,
+                                              plot = FALSE
+  )))
+  t <- (m - mu)/(sd/sqrt(n))
+  t_list[count] <- t
+  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  p_list[count] <- 2 * pt(-abs(t), df = n-1)
+}
+```
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, 600),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "",
+     xlab = "Mean")
+axis(1, at = seq(0,600,100), labels = seq(-3,3,1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
+abline(h = 0.5, 
+       lty = 6,
+       col = "lightgrey")
+```
+*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis).
+The sample size is small (n = 10), but because the sd is half as big as in Figure 7 (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
+The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means.
+
+If we once more plot the two statistics against each other so see where they are unrelated (indicated by staight lines in the curve).
+We see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+plot(sgpv_list, 
+     p_tost_list,
+     type="l",
+     lwd = 3, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1),
+     # yaxt = "n",
+     # xaxt = "n",
+     ylab = "TOST p-value",
+     xlab = "SGPV")
+```
+*Figure 10*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
+
+To conclude this section, there are four situations where the *p*-value from the TOST procedure is unrelated to the SGPV, In all these situation the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
+Therefore, as a purely descriptive statistic, the SGPV is more limited than the *p*value from the TOST procedure.
+The proportion of overlap can be the same value when the observed mean is 0 or when the observed mean falls just inside the equivalence bound, and additional information (e.g., the 95% CI) is required to differentiate these situations.
+One way to mitigate this limitation of the SGPV would be to set the SGPV to 0.5 whenever the CI overlaps with both the upper and lower equivalence bound (irrespective of the width of the CI).
+
 ##What are the Relative Strengths and Weaknesses of Equivalence Testing and SGPV?

### 2018-07-28 sgpv_vs_TOST.Rmd
fix typo

@@
 
-#The relationship between *p*values from TOST and SGPV
+#The relationship between *p*-values from TOST and SGPV
 
@@
 ```
-*Figure 5*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 1.
+*Figure 5*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 1.
 
@@
 ```
-*Figure 7*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
+*Figure 7*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
 
@@
 
-If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it ccompletely overlaps with the equivalence range) while the *p*-value for the TOST procedure varies.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure varies.
 We can see this in Figure 9 below.
@@
 ```
-*Figure 10*: The relationship between *p*values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
+*Figure 10*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
 
 To conclude this section, there are four situations where the *p*-value from the TOST procedure is unrelated to the SGPV, In all these situation the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely descriptive statistic, the SGPV is more limited than the *p*value from the TOST procedure.
+Therefore, as a purely descriptive statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
 The proportion of overlap can be the same value when the observed mean is 0 or when the observed mean falls just inside the equivalence bound, and additional information (e.g., the 95% CI) is required to differentiate these situations.
@@
 
-It seems Blume et al (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*values to the statistical toolbox.
+It seems Blume et al (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
 The novelty lies in its use as a descriptive statistic.

### 2018-07-30 sgpv_vs_TOST.Rmd
updated version

@@
 The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range.
-If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence rnge the SGPV is 0.
+If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence range the SGPV is 0.
 
@@
 In the Two One-Sided Tests (TOST) approach to equivalence testing data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2).
-If both one-sided tests reject the presence of effects more extreme than the equivalence bounds when can act as if there is no meaningful effect.
+If both one-sided tests reject the presence of effects more extreme than the equivalence bounds we can act as if there is no meaningful effect.
 Because two one-sided tests are performed, equivalence can be declared when a 1-2*alpha CI (e.g., when the alpha level is 0.05, a 90% CI)  falls completely within the equivalence range of -2 and +2.
@@
 
-One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1` (or more accuratelty, *p* > .999 as *p*-values are bounded between 0 and 1).
+One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
 Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure 1).
@@
 
-We can examine this situation be calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range.
+We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range.
 ```{r, include=FALSE}
@@
 
-We can again plot the two statistics against each other so see where they are unrelated (indicated by staight lines in the curve).
+We can again plot the two statistics against each other so see where they are unrelated (indicated by straight lines in the curve).
 We see the SGPV is 0.5 for a range of observed means where the p-value from the equivalence test still varies.
@@
 There is one last situation where the *p*-value from the TOST procedure and the SGPV are unrelated.
-This is when the CI overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-This fourth category exists because of the decision by Blume and collagues to set the SGPV to 0.5 whenever the CI is twice as wide as the equivalence range and the CI overlaps with both equivalence bounds.
+This is when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
+This fourth category exists because of the decision by Blume and colleagues to set the SGPV to 0.5 whenever the CI is twice as wide as the equivalence range and the CI overlaps with both equivalence bounds.
 This means that there are situations where the CI interval overlaps with both equivalence bounds, while the CI is less than twice as large as the equivalence bound.
-For example, in the example below, we see an example where the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
+For example, in the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
 ```{r, include=FALSE}
@@
 
-If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure varies.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure can vary between 0 and .025.
 We can see this in Figure 9 below.
@@
 
-If we once more plot the two statistics against each other so see where they are unrelated (indicated by staight lines in the curve).
+If we once more plot the two statistics against each other so see where they are unrelated (indicated by straight lines in the curve).
 We see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 ```
-*Figure 10*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
+*Figure 10*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 9.
 
-To conclude this section, there are four situations where the *p*-value from the TOST procedure is unrelated to the SGPV, In all these situation the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely descriptive statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
+To conclude this section, there are four situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
+In all these situations the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
+Therefore, as a purely descriptive statistic, the SGPV is more limited than the value from the TOST procedure.
 The proportion of overlap can be the same value when the observed mean is 0 or when the observed mean falls just inside the equivalence bound, and additional information (e.g., the 95% CI) is required to differentiate these situations.
@@
 The novelty lies in its use as a descriptive statistic.
-The added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range, and using this percentage to describe the data, remains somewhat unclear for practical puroposes.
+The added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range, and using this percentage to describe the data, remains somewhat unclear for practical purposes.
 Nevertheless, our only goal is to clarify the relationship between a newly proposed statistic and the already existing TOST approach used to test for equivalence, and let researchers make an informed decision about which statistical approach provides the best answer to their question.
@@
 https://doi.org/10.1371/journal.pone.0188299
+
 Lakens, D.
@@
 https://doi.org/10.1177/1948550617697177
+
 Rogers, J.

### 2018-07-30 sgpv_vs_TOST.Rmd

@@
 
-The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, McGowan, Dupont, & Greevy, (2018).
+The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, D'Agostino McGowan, Dupont, & Greevy, (2018).
 The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'.
@@
 Blume, J.
-D., McGowan, L.
-D., Dupont, W.
+D., D'Agostino McGowan, L., Dupont, W.
 D., & Greevy, R.

### 2018-08-02 sgpv_vs_TOST.Rmd
updated example

@@
 ```{r, include=FALSE}
-#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
+source("TOST_to_SGPV.R")
+source("p_delta_function.R")
 
-#' Second Generation P-value
-p_delta <- function(lb, ub, delta_lb, delta_ub) {
-
-  # special case: infinite CI and H0 bounds in the same direction
-  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
-    return(1)
-  }
-
-  # usual case: non-point CI & non-point Ho
-  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
-  if (delta_lb != delta_ub & lb != ub) {
-    if (lb > delta_ub | ub < delta_lb) {
-      return(0)
-    } else if(lb > delta_lb & ub < delta_ub){
-      return(1)
-    } else {
-      return(
-        (min(ub, delta_ub) - max(lb, delta_lb)) /
-          min(ub - lb, 2 * (delta_ub - delta_lb))
-      )
-    }
-  }
-
-  # special case 1: point CI, w/ or w/out a point H0
-  # pdelta = 0 if CI is inside the Ho
-  # pdelta = 1 if CI is inside the Ho
-  if (lb == ub) {
-    if (lb <= delta_ub & lb >= delta_lb){
-      return(1)
-    } else {
-      return(0)
-    }
-  }
-
-  # special case 2: point H0 & non-point CI
-  # pdelta = 1/2 if H0 is inside the CI
-  # pdelta = 0 if H0 is outside the CI
-  if (delta_lb == delta_ub & lb != ub) {
-    if (delta_lb <= ub & delta_lb >= lb) {
-      return(1/2)
-    } else {
-      return(0)
-    }
-  }
-}
-
-source("TOST_to_SGPV.R")
 ```

### 2018-08-02 plot_example_N_100_sd_1.R

@@ -1,0 +1,51 @@
+library(TOSTER)
+source("p_delta_function.R")
+
+step = 0.01
+
+p_tost_list <- numeric(length(seq(140, 150, step)))
+sgpv_list <- numeric(length(seq(140, 150, step)))
+p_list <- numeric(length(seq(140, 150, step)))
+t_list <- numeric(length(seq(140, 150, step)))
+
+count <- 0
+
+for(i in seq(140, 150, step)){
+  count <- count + 1
+  m <- 140
+  mu <- 145
+  sd <- 1
+  n <- 100
+  low_eqbound = -2 
+  high_eqbound = 2 
+  alpha = 0.05
+  
+  invisible(capture.output(res <- TOSTone.raw(m = m, 
+                                              mu = mu,
+                                              sd = sd, 
+                                              n = n, 
+                                              low_eqbound = low_eqbound, 
+                                              high_eqbound = high_eqbound, 
+                                              alpha = alpha,
+                                              plot = FALSE
+  )))
+  t <- (m - mu)/(sd/sqrt(n))
+  t_list[count] <- t
+  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  p_list[count] <- 2 * pt(-abs(t), df = n-1)
+}
+
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, 1001),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "",
+     xlab = "Mean")
+axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+points(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+points(p_tost_list, lwd = 3)
+

### 2018-08-15 sgpv_vs_TOST.Rmd
add asymmetric bounds

@@
 author: "Daniël Lakens & Marie Delacre"
-date: "28 juli 2018"
+date: "15 august 2018"
 output: github_document
@@
 
-  invisible(capture.output(res <- TOSTone.raw(m = m, 
+  res <- TOSTone.raw(m = m, 
                      mu = mu,
@@
                      alpha = alpha,
-                                              plot = FALSE
-  )))
+                     plot = FALSE,
+                     verbose = FALSE
+  )
   t <- (m - mu)/(sd/sqrt(n))
@@
 ```
-```{r sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
 plot(NA, 
@@
 
-lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
 lines(p_tost_list, lwd = 3)
+abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
 ```
@@
 
-lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
 lines(p_tost_list, lwd = 3)
+abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
+
 ```
@@
 
+##The relation between equivalence tests and SGPV when confidence intervals are no symmetrical
+
+So far we have only looked at the relation between equivalence tests and the SGPV when confidence intervals are symmetric (e.g., for confidence intervals around mean differences).
+For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0.
+The confidence interval becomes increasingly asymmetric as the observed correlation nears -1 or 1.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.629 to 0.629, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.992.
+
+The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure 11 below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
+As the observed correlation in the sample moves from 1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
+The pattern is quite similar to that in Figure 2.
+The p-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
+There are two important differences, however.
+First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95% CI.
+Second, and most importantly, the p-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5.
+```{r, include=FALSE}
+n <- 30
+r_pop <- .0
+low_eqbound_r <- -.45
+high_eqbound_r <- .45
+alpha <- .05
+step <- 0.001
+
+p_tost_list <- numeric(length(seq(-0.99, 0.99, step)))
+sgpv_list <- numeric(length(seq(-0.99, 0.99, step)))
+p_list <- numeric(length(seq(-0.99, 0.99, step)))
+t_list <- numeric(length(seq(-0.99, 0.99, step)))
+lowbound_list <- numeric(length(seq(-0.99, 0.99, step)))
+highbound_list <- numeric(length(seq(-0.99, 0.99, step)))
+
+count <- 0
+
+for(i in seq(-0.99, 0.99, step)){
+  count <- count + 1
+  r <- i
+
+  res<-TOSTr(n = n,
+             r = r,
+             low_eqbound_r = low_eqbound_r,
+             high_eqbound_r = high_eqbound_r,
+             alpha = alpha,
+             plot = FALSE,
+             verbose = FALSE)
+
+  t_list[count]=r*sqrt(n-2)/sqrt(1-r^2)
+  p_list[count]=2*(1-pt(abs(t_list[count]),df=n-2))
+  sgpv_list[count] <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  lowbound_list[count]=res$LL_CI_TTEST
+  highbound_list[count]=res$UL_CI_TTEST
+} 
+```
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+par(xpd=F)
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, length(seq(-0.99, 0.99, step))),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "TOST p-value and SGPV",
+     xlab = "Correlation")
+axis(1, at = seq(0,1981,1981/20), labels = seq(-1,1,0.1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
+abline(h = c(0.975, 0.5, 0.025),
+       lty = 2,
+       col = "grey")
+
+```
+*Figure 11*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05.
+```{r, include=FALSE}
+low_eqbound_r = -0.45
+high_eqbound_r = 0.45
+res<-TOSTr(n = 30,
+           r = 0.45,
+           low_eqbound_r = -0.45,
+           high_eqbound_r = 0.45,
+           alpha = .05,
+           plot = FALSE,
+           verbose = FALSE)
+sgpv <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+```
+The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
+If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test indicates that the probability of observing the observed or more extreme data, assuming the equivalence bound is the true effect size, is 50%.
+In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
+However, as can be seen in Figure 12, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to Blume et al.
+(2018) `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+n=30
+low_eqbound_r=-.45
+high_eqbound_r=.45
+r1=-.45
+r2=0
+r3=.45
+
+res1<-TOSTr(n=n,r=r1,low_eqbound_r=low_eqbound_r,high_eqbound_r=high_eqbound_r,alpha=alpha,plot=FALSE, verbose = FALSE)
+res2<-TOSTr(n=n,r=r2,low_eqbound_r=low_eqbound_r,high_eqbound_r=high_eqbound_r,alpha=alpha,plot=FALSE, verbose = FALSE)
+res3<-TOSTr(n=n,r=r3,low_eqbound_r=low_eqbound_r,high_eqbound_r=high_eqbound_r,alpha=alpha,plot=FALSE, verbose = FALSE)
+
+LL95_r1=res1$LL_CI_TTEST
+UL95_r1=res1$UL_CI_TTEST
+LL95_r2=res2$LL_CI_TTEST
+UL95_r2=res2$UL_CI_TTEST
+LL95_r3=res3$LL_CI_TTEST
+UL95_r3=res3$UL_CI_TTEST
+
+par(xpd=F)
+plot(NA, ylim=c(0,.7), xlim=c(-1,1), bty="l", yaxt="n", ylab="",xlab="Correlation")
+abline(v = c(r1, r2, r3),
+       lty = 2,
+       col = "grey")
+
+points(x=r1, y=0.6, pch=15, cex=1.1)
+segments(LL95_r1,0.6,UL95_r1,0.6, lwd=2)
+points(x=r2, y=0.4, pch=15, cex=1.1)
+segments(LL95_r2,0.4,UL95_r2,0.4, lwd=2)
+points(x=r3, y=0.2, pch=15, cex=1.1)
+segments(LL95_r3,0.2,UL95_r3,0.2, lwd=2)
+```
+*Figure 12*: Three 95% confidence intervals for observed effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the confidence interval for r = 0 is symmetric.  
+```{r, include=FALSE}
+#Example illustrating the most extreme case. 
+low_eqbound_r = -0.99
+high_eqbound_r = 0.99
+
+res<-TOSTr(n = 4,
+           r = 0.99,
+           low_eqbound_r = low_eqbound_r,
+           high_eqbound_r = high_eqbound_r,
+           alpha = .05,
+           plot = TRUE,
+           verbose = TRUE)
+sgpv <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+sgpv
+```
+
+This example illustrates the difference between a proportion and a probability.
+There is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
+The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to.
+The conclusion of this in depth look at asymmetric confidence intervals is that, while a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in n equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+Although Blume et al (2018, p.
+3) state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
+When the observed correlation equals an equivalence bound, 50% of the normally distributed data is compatible with the null hypothesis (i.e., falls within the equivalence range), even when the SGPV is larger than 0.5.
+
 ##What are the Relative Strengths and Weaknesses of Equivalence Testing and SGPV?
@@
 
-[To be extended]
+One weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
+Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as Blume et al (2018, p.
+7) seems to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
+Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).
+
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure 13 below.
+In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against against an equivalence range from r = 0.4 to r = 0.8.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of meaningless SGPV in this range.
+This example suggests that the current implementation of the 'small sample correction' could be improved.
+
+```{r, include=FALSE}
+n <- 10
+r_pop <- 0.6
+low_eqbound_r <- 0.4
+high_eqbound_r <- 0.8
+alpha <- .05
+step <- 0.001
+
+p_tost_list <- numeric(length(seq(-0.99, 0.99, step)))
+sgpv_list <- numeric(length(seq(-0.99, 0.99, step)))
+p_list <- numeric(length(seq(-0.99, 0.99, step)))
+t_list <- numeric(length(seq(-0.99, 0.99, step)))
+lowbound_list <- numeric(length(seq(-0.99, 0.99, step)))
+highbound_list <- numeric(length(seq(-0.99, 0.99, step)))
+
+count <- 0
+
+for(i in seq(-0.99, 0.99, step)){
+  count <- count + 1
+  r <- i
+
+  res<-TOSTr(n = n,
+             r = r,
+             low_eqbound_r = low_eqbound_r,
+             high_eqbound_r = high_eqbound_r,
+             alpha = alpha,
+             plot = FALSE,
+             verbose = FALSE)
+
+  t_list[count]=r*sqrt(n-2)/sqrt(1-r^2)
+  p_list[count]=2*(1-pt(abs(t_list[count]),df=n-2))
+  sgpv_list[count] <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
+  lowbound_list[count]=res$LL_CI_TTEST
+  highbound_list[count]=res$UL_CI_TTEST
+} 
+```
+```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+par(xpd=F)
+plot(NA, 
+     ylim = c(0, 1), 
+     xlim = c(0, length(seq(-0.99, 0.99, step))),
+     yaxt = "n",
+     xaxt = "n",
+     ylab = "TOST p-values and 1-SGPV",
+     xlab = "Correlation")
+axis(1, at = seq(0,1981,1981/20), labels = seq(-1,1,0.1), las = 1)
+axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
+
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(p_tost_list, lwd = 3)
+abline(h = c(0.975, 0.5, 0.025),
+       lty = 2,
+       col = "grey")
+```
+*Figure 13*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05.
 

### 2018-08-15 sgpv_vs_TOST_small_n_correction.Rmd
add asymmetric bounds

@@
                          plot = F)
-
-SGPV1 <- TOST_to_SGPV(tost_res = tost_res1)
 
@@
 ```
+Let's look at a single study with diverging p-values to see what is going on.
+
+```{r, include=FALSE}
+#
+n=40
+breaks=c(10,20,40)
+d.lo=-0.4
+d.hi=0.4
+
+z=rnorm(n,mean=0,sd=1)+runif(1,-2,2)
+
+to.stat.1=TOSTone.raw(m=mean(z[1:breaks[1]]), 
+                      mu=0,
+                      sd=sd(z[1:breaks[1]]),
+                      n=length(z[1:breaks[1]]),
+                      low_eqbound=d.lo, 
+                      high_eqbound=d.hi,
+                      alpha=0.05,
+                      plot=TRUE)
+
+p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
+
+tt.stat.1=t.test(z[1:breaks[1]])$conf.int
+
+p.delta.1=sgpv(est.lo=tt.stat.1[1], est.hi=tt.stat.1[2], 
+               null.lo=d.lo, null.hi=d.hi)
+p.delta.1
+p.delta.2=sgpv(est.lo=to.stat.1$LL_CI_TTEST, est.hi=to.stat.1$UL_CI_TTEST, 
+               null.lo=d.lo, null.hi=d.hi)
+p.delta.2
+
+p.tost.1
+p.delta.1
+1-p.delta.1
+
+#Claculate Width of CI
+tt.stat.1[2] - tt.stat.1[1]
+#Calculate Width of equivalence range
+d.hi - d.lo
+#Ratio
+(tt.stat.1[2] - tt.stat.1[1]) / (d.hi - d.lo)
+
+d.lo=-0.4
+d.hi=0.4
+
+to.stat.1=TOSTone.raw(m=0.2, 
+                      mu=0,
+                      sd=1,
+                      n=10,
+                      low_eqbound=d.lo, 
+                      high_eqbound=d.hi,
+                      alpha=0.05,
+                      plot=TRUE)
+
+p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
+
+p.delta.2=sgpv(est.lo=to.stat.1$LL_CI_TTEST, est.hi=to.stat.1$UL_CI_TTEST, 
+               null.lo=d.lo, null.hi=d.hi)
+p.tost.1
+p.delta.2
+
+```

### 2018-08-15 Marie/Confidence interval around r (1).R

@@ -1,0 +1,120 @@
+for (package in c("psych","parallel","smoothmest","fGarch","TOSTER")) {
+  if (!require(package, character.only=T, quietly=T)) {
+    install.packages(package)
+    library(package, character.only=T)
+  }
+}
+
+#--------------------------------------------------------------------------
+
+# The distribution of r is skewed when r!=0
+# when r = 0, the sampling distribution or r is symmetric
+# when r gets closer of +-1, the sampling distribution of r is increasingly skewed.
+# For this reason, a correction for the bias is required.
+# Commonly, reasearchers use the Fisher's z transformation in order to compute CI:
+  # 1) convert r into z: z=log((1+r)/(1-r))/2.    z has a std error of 1/sqrt(n-3)
+  # 2) computing z bounds: bound = z+-qnorm(1-alpha/2)*1/sqrt(n-3)  
+  # 3) convert z bounds into r bounds: rbound= (exp(2*z)-1)/(1+exp(2*z))
+
+#---------------------------------------------------------------------------------
+ 
+# The following section shows that r distribution is skewed, while z distribution is normal
+
+correlDV <- function(n, correlation=.5,nb_DV=4,sd) {
+  # generate nb_DV variables, stored in a matrix
+  X=matrix(0,n,nb_DV)  
+  for(v in 1:nb_DV){
+    X[,v] <- rnorm(n=n,m=0,sd=sd)
+  }
+  # generate the expected correlation matrix    
+  C <- matrix(correlation, nrow = nb_DV, ncol = nb_DV)
+  diag(C) <- 1 
+  L <- chol(C) # Choleski factorization
+  # Return a lower triangular matrix Z such as C=t(Z)%*%Z   
+  # induce correlation, without changing X1 (as long as Z is a lower triangular matrix)
+  DV <- X %*% L
+  return(DV)
+}
+
+samplingcor_plot=function(nSims,n,correlation,sd){
+  
+  count=0
+  cor_list<-rep(0,length(1:nSims))
+  z_list<-rep(0,length(1:nSims))
+  
+  proportion_r<-matrix(0,length(seq(0,.9,.1)),1)
+  colnames(proportion_r)=paste("proportion, when n=",n)
+  rownames(proportion_r)=paste("r >=",seq(0,.9,.1))
+  
[…]

### 2018-08-15 Marie/Correlation SGPV vs TOST (1).R

@@ -1,0 +1,231 @@
+library(TOSTER)
+
+#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
+#' Second Generation P-value
+
+p_delta <- function(lb, ub, delta_lb, delta_ub) {
+  
+  # special case: infinite CI and H0 bounds in the same direction
+  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
+    return(1)
+  }
+  
+  # usual case: non-point CI & non-point Ho
+  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
+  if (delta_lb != delta_ub & lb != ub) {
+    if (lb > delta_ub | ub < delta_lb) {
+      return(0)
+    } else if(lb > delta_lb & ub < delta_ub){
+      return(1)
+    } else {
+      return(
+        (min(ub, delta_ub) - max(lb, delta_lb)) /
+          min(ub - lb, 2 * (delta_ub - delta_lb))
+      )
+    }
+  }
+  # special case 1: point CI, w/ or w/out a point H0
+  # pdelta = 0 if CI is inside the Ho
+  # pdelta = 1 if CI is inside the Ho
+  if (lb == ub) {
+    if (lb <= delta_ub & lb >= delta_lb){
+      return(1)
+    } else {
+      return(0)
+    }
+  }
+  # special case 2: point H0 & non-point CI
+  # pdelta = 1/2 if H0 is inside the CI
+  # pdelta = 0 if H0 is outside the CI
+  if (delta_lb == delta_ub & lb != ub) {
+    if (delta_lb <= ub & delta_lb >= lb) {
+      return(1/2)
+    } else {
+      return(0)
+    }
+  }
+}
+
+###Figure 1, 5 and 6: SGPV vs . TOST
+
+# Figure 1
+#n=120
+#r_pop=.0
+#low_eqbound_r=r_pop-.2
+#high_eqbound_r=r_pop+.2
+#alpha=.05
+#step = 0.001
+
+# Figure 5
+#n=120
+#r_pop=.0
+#low_eqbound_r=r_pop-.1
+#high_eqbound_r=r_pop+.1
+#alpha=.05
[…]

### 2018-08-15 weird_case_sgpv.R

@@ -1,0 +1,20 @@
+d.lo=-0.5
+d.hi=0.5
+
+to.stat.1=TOSTone.raw(m=0.2, 
+                      mu=0,
+                      sd=1.38,
+                      n=10,
+                      low_eqbound=d.lo, 
+                      high_eqbound=d.hi,
+                      alpha=0.05,
+                      plot=TRUE)
+
+p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
+
+p.delta.2=sgpv(est.lo=to.stat.1$LL_CI_TTEST, est.hi=to.stat.1$UL_CI_TTEST, 
+               null.lo=d.lo, null.hi=d.hi)
+p.tost.1
+p.delta.2
+
+(to.stat.1$UL_CI_TTEST - to.stat.1$LL_CI_TTEST) / (d.hi - d.lo)

### 2018-08-16 sgpv_vs_TOST.Rmd
fixed 1 > -1
incorporated changes from google doc, rewrote discussion.

@@
 author: "Daniël Lakens & Marie Delacre"
-date: "15 august 2018"
+date: "16 august 2018"
 output: github_document
@@
 
-The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, D'Agostino McGowan, Dupont, & Greevy, (2018).
-The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'.
-The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis.
-The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range.
-If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence range the SGPV is 0.
-
-The SGPV has strong similarities with an already existing approach known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993).
-In an equivalence test, an equivalence range is based upon a smallest effect size of interest.
-In the Two One-Sided Tests (TOST) approach to equivalence testing data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2).
-If both one-sided tests reject the presence of effects more extreme than the equivalence bounds we can act as if there is no meaningful effect.
-Because two one-sided tests are performed, equivalence can be declared when a 1-2*alpha CI (e.g., when the alpha level is 0.05, a 90% CI)  falls completely within the equivalence range of -2 and +2.
-
-Surprisingly, Blume et al (2018) do not discuss equivalence testing in their article, despite the strong conceptual similarities.
-Here, we aim to examine the similarities and differences between equivalence testing using the TOST procedure and the SGPV.
-Our goal is to allow researchers to choose the statistic that best answers the question they are interested in.
+To test predictions most researchers predominantly rely on null-hypothesis tests. 
+This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect size of zero. 
+Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*.
+When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaninful effect. 
+By specifying a range around the the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).
+
+Second generation p-values (SGPV) were recently proposed to as a descriptive statistic that can loosely be interpreted as ‘the proportion of data-supported hypotheses that are also null hypotheses’ (Blume, D’Agostino McGowan, Dupont, & Greevy, 2018).
+The researcher specifies an equivalence range around a classical simple  null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
+The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis.
+If the estimation interval falls completely within the equivalence range, the SGPV is 1.
+If it lies beyond the equivalence range, the SGPV is 0. Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range. 
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012; Schuirman, 1987) appear to have close ties. 
+Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
+
+The TOST procedure also relies on the confidence interval around the effect. 
+In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test. 
+If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero.
+Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the newly proposed SGPV to equivalence tests.
 
@@
 
-In the plot below *p*-values are calculated for the TOST equivalence testing procedure where a true population mean ranging from 140 to 150 is compared to the test value of 145 in a one-sample equivalence test where equivalence bounds are set to difference of -2 and +2 around the test value of 145.
-In other words, the equivalence range in the test contains all means between 143 and 147.
-Blume et al (2018) rely on the z-distribution, while to TOST package uses the *t*-distribution (which is more accurate at smaller sample sizes).
-To make sure the SGPV give basically identical results, sample sizes consist of 1000000 observations (for which the *t*-distribution and z-distribution are basically identical).
-The population standard deviation is set to 500 to still give some variation in responses.
-Our conclusions should hold to the same extend for more realistic numbers (e.g., N = 100, SD = 1).
+To examine the relation between the TOST p-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
+In Figure 1 *p*-values are plotted for the TOST procedure and the SGPV.
+The statistics are calculated for one-sample *t*-tests where the observed mean in the sample ranges from 140 to 150 (on the x-axis), the equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), a standard deviation of 2 and a sample size of 100.
+Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.
 
@@
   mu <- 145
-  sd <- 500
-  n <- 1000000
+  sd <- 2
+  n <- 30
   low_eqbound = -2 
@@
 
-lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
 lines(p_tost_list, lwd = 3)
-abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
-```
-*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.
+#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
+```
+*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
 
 The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
-For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the two tests more comparable.
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the values more easily comparable.
 We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
@@
 
-lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
 lines(p_tost_list, lwd = 3)
-abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
-
+#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
 ```
@@
 ```
-*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.
-
-When the population mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
+*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
+
+When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 100 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
 Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).
@@
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
-As the observed correlation in the sample moves from 1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
+As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
 The pattern is quite similar to that in Figure 2.
@@
 Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
-When the observed correlation equals an equivalence bound, 50% of the normally distributed data is compatible with the null hypothesis (i.e., falls within the equivalence range), even when the SGPV is larger than 0.5.
+Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.
+a p-value of 0 or 1 are *not* affected by the scale changes."
 
@@
 First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
-It numerically summarizes the information that is visually present in a plot (such as Figure 3) displaying the equivalence range and the 95% CI around the observed effect.
-
-The SGPV is 1 for tests where *p*-values for the TOST procedure differ.
+It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see Figure 3).
+
+One benefit of *p*-values over the SGPV is that the SGPV is 0, 0.5, or 1 for a range of observed effects where *p*-values for the TOST procedure continue to differentiate.
 For example, different equivalence tests with *p* = 0.024 and *p* = 0.0001 have a SGPV of 1.
-Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65).
-Since the SGPV is always directly related to a *p*-value from the TOST procedure, different SGPV can be interpreted in the same manner as different *p*-values.
-From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range.
-From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis is true while controlling our error rate at a known maximum.
+The SGPV provides on average less information than *p*-values.
+
+A possible weakness of the SGPV is that even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive.
+This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (Lakens, Isager, & Scheel, 2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
+Thus, *p*-values can be interpreted in continuous matter, which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcome, while equivalence tests classify results into four possible outcomes.
 
@@
 Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).
+An important benefit of equivalence tests is that is does not need such a correction to prevent misleasing results.
 
@@
 
-#Discussion
-
-It seems Blume et al (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
+#Conclusion
+
+We believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
 The novelty lies in its use as a descriptive statistic.
-The added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range, and using this percentage to describe the data, remains somewhat unclear for practical purposes.
-Nevertheless, our only goal is to clarify the relationship between a newly proposed statistic and the already existing TOST approach used to test for equivalence, and let researchers make an informed decision about which statistical approach provides the best answer to their question.
+There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent.
+We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
 
@@
 Blume, J.
-D., D'Agostino McGowan, L., Dupont, W.
+D., McGowan, L.
+D., Dupont, W.
 D., & Greevy, R.
@@
 (2018).
-Second-generation *p*-values: Improved rigor, reproducibility, & transparency in statistical analyses.
+Second-generation p-values: Improved rigor, reproducibility, & transparency in statistical analyses.
 PLOS ONE, 13(3), e0188299.
 https://doi.org/10.1371/journal.pone.0188299
+
+Hauck, D.
+W.
+W., & Anderson, S.
+(1984).
+A new statistical procedure for testing equivalence in two-group comparative bioavailability trials.
+Journal of Pharmacokinetics and Biopharmaceutics, 12(1), 83–91.
+https://doi.org/10.1007/BF01063612
+
+Kruschke, J.
+K.
+(2018).
+Rejecting or Accepting Parameter Values in Bayesian Estimation.
+Advances in Methods and Practices in Psychological Science, 2515245918771304.
+https://doi.org/10.1177/2515245918771304
 
@@
 https://doi.org/10.1177/1948550617697177
+
+Lakens, D., Scheel, A.
+M., & Isager, P.
+M.
+(2018).
+Equivalence Testing for Psychological Research: A Tutorial.
+Advances in Methods and Practices in Psychological Science, 2515245918770963.
+https://doi.org/10.1177/2515245918770963
+
+Meyners, M. (2012). Equivalence tests – A review. Food Quality and Preference, 26(2), 231–245. https://doi.org/10.1016/j.foodqual.2012.05.003
 
@@
 http://dx.doi.org/10.1037/0033-2909.113.3.553
+
+Schuirmann, D.
+J.
+(1987).
+A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability.
+Journal of Pharmacokinetics and Biopharmaceutics, 15(6), 657–680.
+
+Serlin, R. C., & Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.
+
+Spiegelhalter, D.
+J., Freedman, L.
+S., & Parmar, M.
+K.
+(1994).
+Bayesian approaches to randomized trials.
+Journal of the Royal Statistical Society.
+Series A (Statistics in Society), 357–416.
+https://doi.org/10.2307/2983527
+
+Wellek, S. (2010). Testing statistical hypotheses of equivalence and noninferiority (2nd ed). Boca Raton: CRC Press.
+
+Westlake, W. J. (1972). Use of confidence intervals in analysis of comparative bioavailability trials. Journal of Pharmaceutical Sciences, 61(8), 1340–1341.

### 2018-08-16 sgpv_vs_TOST.Rmd
minor fix

@@
 ```
-*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
+*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
 
@@
 ```
-*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
+*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
 
@@
 ```
-*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis).
+*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
 Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.
@@
 ```
-*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis).
+*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
 The sample size is small (n = 10), but because the sd is half as big as in Figure 7 (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
@@
 
-##The relation between equivalence tests and SGPV when confidence intervals are no symmetrical
+##The relation between equivalence tests and SGPV when confidence intervals are not symmetrical
 

### 2018-08-17 sgpv_vs_TOST.Rmd
new version feedback Marie

@@
 When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaninful effect. 
-By specifying a range around the the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).
+By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).
 
@@
 
-#The relationship between *p*-values from TOST and SGPV
+#The relationship between *p*-values from TOST and SGPV when confidence intervals are symmetrical
 
@@
 In Figure 1 *p*-values are plotted for the TOST procedure and the SGPV.
-The statistics are calculated for one-sample *t*-tests where the observed mean in the sample ranges from 140 to 150 (on the x-axis), the equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), a standard deviation of 2 and a sample size of 100.
+The statistics are calculated for hypothetical one-sample *t*-tests for *all* means that can be observed in studies ranging from 140 to 150 (on the x-axis).
+The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 100.
+For example, for the left-most point in Figure 1 the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
 Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.
@@
      xaxt = "n",
-     ylab = "",
-     xlab = "Mean")
+     ylab = "P-value for TOST and SGPV",
+     xlab = "Observed Mean")
 axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
@@
 ```
-*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
+*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2.
 
@@
      xaxt = "n",
-     ylab = "SGPV or TOST p-value",
-     xlab = "Mean")
+     ylab = "P-value for TOST and 1-SGPV",
+     xlab = "Observed Mean")
 axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
@@
 mu <- 145
-sd <- 500
-n <- 1000000
+sd <- 2
+n <- 30
 low_eqbound = -2 
@@
                    high_eqbound = high_eqbound, 
-                   alpha = alpha
+                   alpha = alpha,
+                   plot = FALSE,
+                   verbose = FALSE
 )
@@
 ```
-*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.
-
-When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 100 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`.
+*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2.
+
+When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* = `r round(tost_res1$TOST_p1, digits =  4)`.
 Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).
 
-One the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r tost_res2$TOST_t1`, *p* = `r tost_res2$TOST_p1` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
+On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
 Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure 1).
@@
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
 ```{r, include=FALSE}
@@
 When the 95% CI falls completely, but only just inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
-When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in the plot above, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in the plot above).
+When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in Figure 3, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in Figure 3).
 When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
 
-The confidence interval width is a uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
+The confidence interval width is uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
 ```{r, include=FALSE}
@@
 ```
-*Figure 4*: Means, normal distribution, and 95% CI for data with a sample size of 1000000 and a standard deviation of 500 for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2.
+*Figure 4*: Means, normal distribution, and 95% CI for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2.
 
@@
 ```
-For example, the SGPV from A to D is `r SGPV1`, `r SGPV2`, `r SGPV3`, and `r SGPV4`.
-The difference in the percentage of overlap between A and B (`r SGPV1-SGPV2`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r SGPV3-SGPV4`).
+For example, the SGPV from A to D is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
+The difference in the percentage of overlap between A and B (`r round(SGPV1-SGPV2, digits = 2)`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r round(SGPV3-SGPV4, digits = 2)`).
 ```{r , echo=FALSE}
@@
 As we move the means closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
-The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r tail1`, `r tail2`, `r tail3`, and `r tail4`.
-As we can see, the difference between A and B (`r tail1-tail2`) is not the same as the difference between C And D (`r tail3-tail4`).
+The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
+As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`).
 Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure 1 is the steepest at *p* = 0.5.
@@
 
-  invisible(capture.output(res <- TOSTone.raw(m = m, 
-                                              mu = mu,
-                                              sd = sd, 
-                                              n = n, 
-                                              low_eqbound = low_eqbound, 
-                                              high_eqbound = high_eqbound, 
-                                              alpha = alpha,
-                                              plot = FALSE
-  )))
+  res <- TOSTone.raw(m = m, 
+                     mu = mu,
+                     sd = sd, 
+                     n = n, 
+                     low_eqbound = low_eqbound, 
+                     high_eqbound = high_eqbound, 
+                     alpha = alpha,
+                     plot = FALSE,
+                     verbose = FALSE
+  )
   t <- (m - mu)/(sd/sqrt(n))
@@
      xaxt = "n",
-     ylab = "",
-     xlab = "Mean")
+     ylab = "P-value for TOST and SGPV",
+     xlab = "Observed Mean")
 axis(1, at = seq(0,600,100), labels = seq(-3,3,1), las = 1)
@@
 
-We can again plot the two statistics against each other so see where they are unrelated (indicated by straight lines in the curve).
+We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve).
 We see the SGPV is 0.5 for a range of observed means where the p-value from the equivalence test still varies.
 It should be noted that in these calculations the *p*-values for the TOST procedure are *never* smaller than 0.05 (i.e., they do not get below 0.05 on the y-axis).
-In other words, we can't conclude equivalence based on any of the observed means.
+In other words, we cannot conclude equivalence based on any of the observed means.
 How is this possible?
@@
 
-If we once more plot the two statistics against each other so see where they are unrelated (indicated by straight lines in the curve).
-We see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
+If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
 ```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
@@
      xaxt = "n",
-     ylab = "TOST p-value and SGPV",
-     xlab = "Correlation")
+     ylab = "P-value for TOST and 1-SGPV",
+     xlab = "Observed Correlation")
 axis(1, at = seq(0,1981,1981/20), labels = seq(-1,1,0.1), las = 1)
@@
 It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to.
-The conclusion of this in depth look at asymmetric confidence intervals is that, while a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in n equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+The conclusion of this in depth look at asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
 Although Blume et al (2018, p.
@@
 This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (Lakens, Isager, & Scheel, 2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, *p*-values can be interpreted in continuous matter, which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcome, while equivalence tests classify results into four possible outcomes.
+Thus, *p*-values can be interpreted in continuous matter [matter?], which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcomes, while equivalence tests classify results into four possible outcomes.
 
@@
 Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as Blume et al (2018, p.
-7) seems to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
+7) seem to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
 Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).
@@
 As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure 13 below.
-In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against against an equivalence range from r = 0.4 to r = 0.8.
+In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
 We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of meaningless SGPV in this range.
@@
      xaxt = "n",
-     ylab = "TOST p-values and 1-SGPV",
-     xlab = "Correlation")
+     ylab = "P-value for TOST and 1-SGPV",
+     xlab = "Observed Correlation")
 axis(1, at = seq(0,1981,1981/20), labels = seq(-1,1,0.1), las = 1)
@@
 Blume, J.
-D., McGowan, L.
+D., D'Agostino McGowan, L.
 D., Dupont, W.

### 2018-08-17 sgpv_vs_TOST.Rmd
fixed typo

@@
 Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*.
-When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaninful effect. 
+When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaningful effect. 
 By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).
@@
 Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).
-An important benefit of equivalence tests is that is does not need such a correction to prevent misleasing results.
+An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
 

### 2018-08-22 manuscript.Rmd
initial version papaja manuscript and .bib

--- 2018-08-17 sgpv_vs_TOST.Rmd
@@
 ---
-title: "Equivalence Testing and the Second Generation P-Value"
-author: "Daniël Lakens & Marie Delacre"
-date: "16 august 2018"
-output: github_document
+title             : "Equivalence Testing and the Second Generation P-Value"
+shorttitle        : "TOST vs. SGPV"
+
+author:
+  - name          : "Dani&euml;l Lakens"
+    affiliation   : "1"
+    corresponding : yes
+    address       : "Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands"
+    email         : "D.Lakens@tue.nl"
+  - name          : "Marie Delacre"
+    affiliation   : "2"
+
+affiliation:
+  - id            : "1"
+    institution   : "Eindhoven University of Technology, Eindhoven, The Netherlands"
+  - id            : "2"
+    institution   : "Service of Analysis of the Data, Université Libre de Bruxelles, Belgium"
+
+author_note: |
+  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV.
+
+abstract: |
+  We aim to compare TOST and SGPV.
+
+keywords          : "equivalence testing, second generation p-values, p-values, hypothesis testing, statistics"
+wordcount         : ""
+
+bibliography      : ["TOST_vs_SGPV.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : yes
+mask              : no
+
+class             : "man"
+output            : papaja::apa6_pdf
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-options(scipen=99)
-```
-```{r, include=FALSE}
-library(TOSTER)
-```
-
+```{r include = FALSE}
+library("TOSTER")
+library("papaja")
+library("citr")
+```
 ```{r, include=FALSE}
@@
 ```
-The RMarkdown file with the reproducible code of this text is [here](https://github.com/Lakens/TOST_vs_SGPV/blob/master/sgpv_vs_TOST.Rmd).
 
@@
 When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaningful effect. 
-By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).
-
-Second generation p-values (SGPV) were recently proposed to as a descriptive statistic that can loosely be interpreted as ‘the proportion of data-supported hypotheses that are also null hypotheses’ (Blume, D’Agostino McGowan, Dupont, & Greevy, 2018).
+By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent [@hauck_new_1984;@kruschke_rejecting_2018;@rogers_using_1993;@serlin_rationality_1985;@spiegelhalter_bayesian_1994;@wellek_testing_2010;@westlake_use_1972].
+
+Second generation p-values (SGPV) were recently proposed to as a descriptive statistic that can loosely be interpreted as ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
 The researcher specifies an equivalence range around a classical simple  null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
@@
 When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
-When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012; Schuirman, 1987) appear to have close ties. 
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties.
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
@@
 To examine the relation between the TOST p-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
-In Figure 1 *p*-values are plotted for the TOST procedure and the SGPV.
+In \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
 The statistics are calculated for hypothetical one-sample *t*-tests for *all* means that can be observed in studies ranging from 140 to 150 (on the x-axis).
 The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 100.
-For example, for the left-most point in Figure 1 the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
+For example, for the left-most point in \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
 Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+
+```{r, TOSTSGPV1, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
 plot(NA, 
@@
 axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
-
 lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
 lines(p_tost_list, lwd = 3)
-#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
-```
-*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2.
+```
 
 The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
-For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the values more easily comparable.
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV in Figure \\ref{fig:TOSTSGPV2}) to make the values more easily comparable.
 We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
-```{r 1-sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+
+```{r, TOSTSGPV2, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
 plot(NA, 
@@
 ```
-*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2.
 
 When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* = `r round(tost_res1$TOST_p1, digits =  4)`.
-Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).
+Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see \ref{fig:TOSTSGPV1}).
 
 On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
-Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure 1).
+Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see \ref{fig:TOSTSGPV1}).
 
@@
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, \ref{fig:TOSTSGPV3}).
 ```{r, include=FALSE}
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=4}
+```{r, TOSTSGPV3, fig.cap="Means, normal distribution, and 95% CI for three example datasets that illustrate the relationship between *p*-values from TOST and SGPV."}
 plot(NA, 
@@
 ```
-*Figure 3*: Means, normal distribution, and 95% CI for three example datasets that illustrate the relationship between *p*-values from TOST and SGPV.
 
@@
 When the 95% CI falls completely, but only just inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
-When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in Figure 3, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in Figure 3).
+When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in \ref{fig:TOSTSGPV3}).
 When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=5}
+```{r, TOSTSGPV4, fig.cap="Means, normal distribution, and 95% CI for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2."}
 plot(NA, 
@@
 ```
-*Figure 4*: Means, normal distribution, and 95% CI for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2.
 
@@
 As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`).
-Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure 1 is the steepest at *p* = 0.5.
+Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
 Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
-
 ##When are the SGPV and Equivalence Test Unrelated?
-
 There are 4 situations where *p*-values from TOST and SGPV are unrelated.
-The first two situations were discussed earlier, and can be seen in Figure  1.
+The first two situations were discussed earlier, and can be seen in \ref{fig:TOSTSGPV1}.
 When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+```{r, TOSTSGPV5, fig.cap="The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure \\ref{fig:TOSTSGPV1}."}
 plot(sgpv_list, 
@@
 ```
-*Figure 5*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 1.
 
@@
 In this situation the normal calculation of the proportion of overlap is skipped, and the SGPV is set to 0.5 instead.
-Blume et al.
-(2018) call this the 'small sample correction factor'.
+@blume_second-generation_2018 call this the 'small sample correction factor'.
 However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any 'correct' value.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+```{r, TOSTSGPV6, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means."}
 plot(NA, 
@@
 ```
-*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
-Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.
-
-We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve).
+
+We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the p-value from the equivalence test still varies.
@@
 However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
-As Lakens (2017) notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
+
+```{r, TOSTSGPV7, fig.cap="The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure \\ref{fig:TOSTSGPV6}."}
 plot(sgpv_list, 
@@
 ```
-*Figure 7*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 6.
 
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=5, fig.height=4}
+```{r, TOSTSGPV8, fig.cap="Example of a 95% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines)."}
 
@@
 ```
-*Figure 8*: Example of a 95% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).
 
 If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure can vary between 0 and .025.
-We can see this in Figure 9 below.
+We can see this in \ref{fig:TOSTSGPV9} below.
 The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+```{r, TOSTSGPV9, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+The sample size is small (n = 10), but because the sd is half as big as in Figure \\ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
+The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means."}
 plot(NA, 
@@
 ```
-*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
-The sample size is small (n = 10), but because the sd is half as big as in Figure 7 (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
-The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means.
 
 If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+
+```{r, TOSTSGPV10, fig.cap="The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure \\ref{fig:TOSTSGPV9}."}
 plot(sgpv_list, 
@@
 ```
-*Figure 10*: The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure 9.
 
@@
 
-The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure 11 below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in \ref{fig:TOSTSGPV11} below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
 As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
-The pattern is quite similar to that in Figure 2.
+The pattern is quite similar to that in \ref{fig:TOSTSGPV2}.
 The p-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
@@
 Second, and most importantly, the p-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5.
+
 ```{r, include=FALSE}
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+
+```{r, TOSTSGPV11, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05."}
 par(xpd=F)
@@
 ```
-*Figure 11*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05.
+
 ```{r, include=FALSE}
@@
 ```
+
 The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
@@
 In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure 12, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
-Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to Blume et al.
-(2018) `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+However, as can be seen in \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
+
+```{r, TOSTSGPV12, fig.cap="Three 95% confidence intervals for observed effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the confidence interval for r = 0 is symmetric."}
 n=30
@@
 ```
-*Figure 12*: Three 95% confidence intervals for observed effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the confidence interval for r = 0 is symmetric.  
+
 ```{r, include=FALSE}
@@
 The conclusion of this in depth look at asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
-Although Blume et al (2018, p.
-3) state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
+Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
 Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
@@
 First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
-It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see Figure 3).
+It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see \ref{fig:TOSTSGPV3}).
 
@@
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive.
-This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (Lakens, Isager, & Scheel, 2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
+This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
 Thus, *p*-values can be interpreted in continuous matter [matter?], which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcomes, while equivalence tests classify results into four possible outcomes.
@@
 This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
-Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as Blume et al (2018, p.
-7) seem to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
-Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).
+Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as @blume_second-generation_2018 seem to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
+Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see \ref{fig:TOSTSGPV6}).
 An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
 
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure 13 below.
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see \ref{fig:TOSTSGPV13} below.
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
@@
 ```
-```{r, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
+```{r, TOSTSGPV13, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05."}
 par(xpd=F)
@@
 ```
-*Figure 13*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05.
 
@@
 
-#References
-
-Blume, J.
-D., D'Agostino McGowan, L.
-D., Dupont, W.
-D., & Greevy, R.
-A.
-(2018).
-Second-generation p-values: Improved rigor, reproducibility, & transparency in statistical analyses.
-PLOS ONE, 13(3), e0188299.
-https://doi.org/10.1371/journal.pone.0188299
-
-Hauck, D.
-W.
-W., & Anderson, S.
-(1984).
-A new statistical procedure for testing equivalence in two-group comparative bioavailability trials.
-Journal of Pharmacokinetics and Biopharmaceutics, 12(1), 83–91.
-https://doi.org/10.1007/BF01063612
-
-Kruschke, J.
-K.
-(2018).
-Rejecting or Accepting Parameter Values in Bayesian Estimation.
-Advances in Methods and Practices in Psychological Science, 2515245918771304.
-https://doi.org/10.1177/2515245918771304
-
-Lakens, D.
-(2017).
-Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses.
-Social Psychological and Personality Science, 8(4), 355–362.
-https://doi.org/10.1177/1948550617697177
-
-Lakens, D., Scheel, A.
-M., & Isager, P.
-M.
-(2018).
-Equivalence Testing for Psychological Research: A Tutorial.
-Advances in Methods and Practices in Psychological Science, 2515245918770963.
-https://doi.org/10.1177/2515245918770963
-
-Meyners, M. (2012). Equivalence tests – A review. Food Quality and Preference, 26(2), 231–245. https://doi.org/10.1016/j.foodqual.2012.05.003
-
-Rogers, J.
-L., Howard, K.
-I., & Vessey, J.
-T.
-(1993).
-Using significance tests to evaluate equivalence between two experimental groups.
-Psychological Bulletin, 113(3), 553–565.
-http://dx.doi.org/10.1037/0033-2909.113.3.553
-
-Schuirmann, D.
-J.
-(1987).
-A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability.
-Journal of Pharmacokinetics and Biopharmaceutics, 15(6), 657–680.
-
-Serlin, R. C., & Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.
-
-Spiegelhalter, D.
-J., Freedman, L.
-S., & Parmar, M.
-K.
-(1994).
-Bayesian approaches to randomized trials.
-Journal of the Royal Statistical Society.
-Series A (Statistics in Society), 357–416.
-https://doi.org/10.2307/2983527
-
-Wellek, S. (2010). Testing statistical hypotheses of equivalence and noninferiority (2nd ed). Boca Raton: CRC Press.
-
-Westlake, W. J. (1972). Use of confidence intervals in analysis of comparative bioavailability trials. Journal of Pharmaceutical Sciences, 61(8), 1340–1341.
+\newpage
+
+# References
+
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}

### 2018-08-22 manuscript.Rmd
added abstract, expanded discussion

@@
 abstract: |
-  We aim to compare TOST and SGPV.
-
-keywords          : "equivalence testing, second generation p-values, p-values, hypothesis testing, statistics"
+  One way to move beyond the limitations of null-hypothesis tests statistical approaches have been developed where the observed data is compared against an range of values that are equivalent to the absence of a meaningful effect.
+We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with equivalence testing using the Two-One-Sided Tests procedure [@schuirmann_comparison_1987].
+We show the two approaches yield almost identical results under optimal circumstances, but under suboptimal circumstances (e.g., when the confidence interval is wider than the equivalence range, or with asymmetric confidence intervals) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
+The second generation is always interpretable in a dichotomous manner when it is 0 or 1, but this can easily be confirmed visually, and does not require calculation.
+Equivalence tests yield more consistent *p*-values and allow for a easy control of Type I and Type II error rates.
+
+keywords          : "equivalence testing, second generation *p*-values, *p*-values, hypothesis testing, statistics"
 wordcount         : ""
@@
 The TOST procedure also relies on the confidence interval around the effect. 
-In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test. 
+In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@Lakens_equivalence_2018].
 If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero.
@@
 
-To examine the relation between the TOST p-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
+The second generation *p*-value (SGPV) is calculated as:
+$$
+  p _ { \delta } = \frac { \left| I \cap H _ { 0 } \right| } { | I | } \times \max \left\{ \frac { | I | } { 2 \left| H _ { 0 } \right| } , 1 \right\}
+$$
+where I is the interval based on the data (e.g., a 95% confidence interval) and H~0~ is the equivalence range.
+The first term of this formula implies that the second generation *p*-value is the width of the confidence interval that overlaps with the equivalence range, divided by the total width of the confidence interval.
+The second term is a 'small sample correction' (see below) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
+
+To examine the relation between the TOST *p*-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
 In \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
@@
 The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
-For ease of comparison we can reverse the SGPV (by calculating 1-SGPV in Figure \\ref{fig:TOSTSGPV2}) to make the values more easily comparable.
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values more easily comparable.
 We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
@@
 
-When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* = `r round(tost_res1$TOST_p1, digits =  4)`.
-Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see \ref{fig:TOSTSGPV1}).
+When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* = `r round(tost_res1$TOST_p1, digits =  5)`.
+Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure \ref{fig:TOSTSGPV1}).
 
 On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
-Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see \ref{fig:TOSTSGPV1}).
+Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure  \ref{fig:TOSTSGPV1}).
 
@@
 It is clear the SGPV and the *p*-value from TOST are closely related.
-We can think of the SGPV as a straight line that will always overlap the *p*-value from an equivalence test in 3 points.
+When confidence intervals are symmatric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values.
 When the TOST *p*-value is 0.5, the SGPV is also 0.5 (note that the reverse is not true).
@@
 When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, \ref{fig:TOSTSGPV3}).
+
 ```{r, include=FALSE}
@@
 ```
+
 ```{r, TOSTSGPV3, fig.cap="Means, normal distribution, and 95% CI for three example datasets that illustrate the relationship between *p*-values from TOST and SGPV."}
@@
 When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value (i.e., 0.0001) to 0 (when the 95% CI completely falls outside of the equivalence bound, see situation C in \ref{fig:TOSTSGPV3}).
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value to 0 (i.e., when the 95% CI falls completely outside of the equivalence bound, see situation C in \ref{fig:TOSTSGPV3}).
 When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
@@
 
-One weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+A final important weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
 This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
@@
 This example suggests that the current implementation of the 'small sample correction' could be improved.
+
+@blume_second-generation_2018 argue that the SGPV has improved eType I rror control.
+However, they mean that the SGPV has a *lower* error rate, not a *more accurate* error rate.
+In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible, but with a decision procedure that yields a desired error rate accurately.
+If a lower Type I error rate is desired, the alpha level can be lowered.
+Equivalence tests also make it straightforward to control the Type 1 error rate by performing an a-priori power analysis.
 

### 2018-08-22 TOST_vs_SGPV_app/app.R
add shiny app

@@ -1,0 +1,198 @@
+library(shiny)
+library(TOSTER)
+
+#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
+
+#' Second Generation P-value
+p_delta <- function(lb, ub, delta_lb, delta_ub) {
+  
+  # special case: infinite CI and H0 bounds in the same direction
+  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
+    return(1)
+  }
+  
+  # usual case: non-point CI & non-point Ho
+  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
+  if (delta_lb != delta_ub & lb != ub) {
+    if (lb > delta_ub | ub < delta_lb) {
+      return(0)
+    } else if(lb > delta_lb & ub < delta_ub){
+      return(1)
+    } else {
+      return(
+        (min(ub, delta_ub) - max(lb, delta_lb)) /
+          min(ub - lb, 2 * (delta_ub - delta_lb))
+      )
+    }
+  }
+  
+  # special case 1: point CI, w/ or w/out a point H0
+  # pdelta = 0 if CI is inside the Ho
+  # pdelta = 1 if CI is inside the Ho
+  if (lb == ub) {
+    if (lb <= delta_ub & lb >= delta_lb){
+      return(1)
+    } else {
+      return(0)
+    }
+  }
+  
+  # special case 2: point H0 & non-point CI
+  # pdelta = 1/2 if H0 is inside the CI
+  # pdelta = 0 if H0 is outside the CI
+  if (delta_lb == delta_ub & lb != ub) {
+    if (delta_lb <= ub & delta_lb >= lb) {
+      return(1/2)
+    } else {
+      return(0)
+    }
+  }
+}
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+   
+   # Application title
+  titlePanel("Plot P-Values for the TOST procedure and Second Generation P-Value"),
+   
+   # Sidebar with a slider input for number of bins 
+  sidebarLayout(
+    sidebarPanel(numericInput("N", "Participants per group:", 30, min = 1, max = 1000),
+                 sliderInput("sd", "Standard Deviation:", min = 0.5, max = 5, value = 2, step= 0.5),
+                 sliderInput("range", "Equivalence Range:", min = -5, max = 5, value = c(-2,2), step= 0.1),              
[…]

### 2018-08-23 Marie/TOST_vs_SGPV-patch-3/sgpv_vs_TOST.R
clean up repo

@@ -1,373 +1,0 @@
-options(scipen = 99)
-
-#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
-
-#' Second Generation P-value
-p_delta <- function(lb, ub, delta_lb, delta_ub) {
-  
-  # special case: infinite CI and H0 bounds in the same direction
-  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
-    return(1)
-  }
-  
-  # usual case: non-point CI & non-point Ho
-  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
-  if (delta_lb != delta_ub & lb != ub) {
-    if (lb > delta_ub | ub < delta_lb) {
-      return(0)
-    } else if(lb > delta_lb & ub < delta_ub){
-      return(1)
-    } else {
-      return(
-        (min(ub, delta_ub) - max(lb, delta_lb)) /
-          min(ub - lb, 2 * (delta_ub - delta_lb))
-      )
-    }
-  }
-  
-  # special case 1: point CI, w/ or w/out a point H0
-  # pdelta = 0 if CI is inside the Ho
-  # pdelta = 1 if CI is inside the Ho
-  if (lb == ub) {
-    if (lb <= delta_ub & lb >= delta_lb){
-      return(1)
-    } else {
-      return(0)
-    }
-  }
-  
-  # special case 2: point H0 & non-point CI
-  # pdelta = 1/2 if H0 is inside the CI
-  # pdelta = 0 if H0 is outside the CI
-  if (delta_lb == delta_ub & lb != ub) {
-    if (delta_lb <= ub & delta_lb >= lb) {
-      return(1/2)
-    } else {
-      return(0)
-    }
-  }
-}
-
-# Recreate examples in Figure 2 just the check that functions work as they should ----
-#1
-res <- TOSTone.raw(m = 146, 
-                   mu = 146,
-                   sd = 500, 
-                   n = 1000000, 
-                   low_eqbound = -2, 
-                   high_eqbound = 2, 
-                   alpha = 0.05
-)
-
-p_delta(146+res$LL_CI_TTEST, 146+res$UL_CI_TTEST, 144, 148)
-
-#2
[…]

### 2018-08-23 plot_example_N_100_sd_1.R

@@ -1,51 +1,0 @@
-library(TOSTER)
-source("p_delta_function.R")
-
-step = 0.01
-
-p_tost_list <- numeric(length(seq(140, 150, step)))
-sgpv_list <- numeric(length(seq(140, 150, step)))
-p_list <- numeric(length(seq(140, 150, step)))
-t_list <- numeric(length(seq(140, 150, step)))
-
-count <- 0
-
-for(i in seq(140, 150, step)){
-  count <- count + 1
-  m <- 140
-  mu <- 145
-  sd <- 1
-  n <- 100
-  low_eqbound = -2 
-  high_eqbound = 2 
-  alpha = 0.05
-  
-  invisible(capture.output(res <- TOSTone.raw(m = m, 
-                                              mu = mu,
-                                              sd = sd, 
-                                              n = n, 
-                                              low_eqbound = low_eqbound, 
-                                              high_eqbound = high_eqbound, 
-                                              alpha = alpha,
-                                              plot = FALSE
-  )))
-  t <- (m - mu)/(sd/sqrt(n))
-  t_list[count] <- t
-  sgpv_list[count] <- p_delta(mu+res$LL_CI_TTEST, mu+res$UL_CI_TTEST, mu+low_eqbound, mu+high_eqbound)
-  p_tost_list[count] <- max(res$TOST_p1, res$TOST_p2)
-  p_list[count] <- 2 * pt(-abs(t), df = n-1)
-}
-
-plot(NA, 
-     ylim = c(0, 1), 
-     xlim = c(0, 1001),
-     yaxt = "n",
-     xaxt = "n",
-     ylab = "",
-     xlab = "Mean")
-axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
-axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
-
-points(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
-points(p_tost_list, lwd = 3)
-

### 2018-08-23 weird_case_sgpv.R

@@ -1,20 +1,0 @@
-d.lo=-0.5
-d.hi=0.5
-
-to.stat.1=TOSTone.raw(m=0.2, 
-                      mu=0,
-                      sd=1.38,
-                      n=10,
-                      low_eqbound=d.lo, 
-                      high_eqbound=d.hi,
-                      alpha=0.05,
-                      plot=TRUE)
-
-p.tost.1=max(to.stat.1$TOST_p1,to.stat.1$TOST_p2)
-
-p.delta.2=sgpv(est.lo=to.stat.1$LL_CI_TTEST, est.hi=to.stat.1$UL_CI_TTEST, 
-               null.lo=d.lo, null.hi=d.hi)
-p.tost.1
-p.delta.2
-
-(to.stat.1$UL_CI_TTEST - to.stat.1$LL_CI_TTEST) / (d.hi - d.lo)

### 2018-08-23 manuscript.Rmd
clean up repo
update manuscript

@@
 abstract: |
-  One way to move beyond the limitations of null-hypothesis tests statistical approaches have been developed where the observed data is compared against an range of values that are equivalent to the absence of a meaningful effect.
-We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with equivalence testing using the Two-One-Sided Tests procedure [@schuirmann_comparison_1987].
-We show the two approaches yield almost identical results under optimal circumstances, but under suboptimal circumstances (e.g., when the confidence interval is wider than the equivalence range, or with asymmetric confidence intervals) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
-The second generation is always interpretable in a dichotomous manner when it is 0 or 1, but this can easily be confirmed visually, and does not require calculation.
-Equivalence tests yield more consistent *p*-values and allow for a easy control of Type I and Type II error rates.
+  To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
+We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the Two-One-Sided Tests equivalence testing procedure [@schuirmann_comparison_1987].
+We show that the two approaches yield almost identical results under optimal circumstances, but under suboptimal circumstances (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
+The second generation is interpretable in a dichotomous manner when it is 0 or 1 (and lies completely within or outside of the equivalence range), but these cases can be observed visually and do not require calculation.
+Equivalence tests yield more consistent *p*-values, distinguish between datsets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
 
@@
 library("papaja")
-library("citr")
-```
-```{r, include=FALSE}
-source("TOST_to_SGPV.R")
-source("p_delta_function.R")
-
+```
+```{r, include=FALSE}
+source("functions/TOST_to_SGPV.R")
+source("functions/p_delta_function.R")
 ```
@@
 
-Second generation p-values (SGPV) were recently proposed to as a descriptive statistic that can loosely be interpreted as ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
+Second generation *p*-values (SGPV) were recently proposed to as a descriptive statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
 The researcher specifies an equivalence range around a classical simple null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
@@
 If the estimation interval falls completely within the equivalence range, the SGPV is 1.
-If it lies beyond the equivalence range, the SGPV is 0. Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range. 
+If the confidence interval falls completely outside of the equivalence range, the SGPV is 0.
+Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
 When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
@@
 The TOST procedure also relies on the confidence interval around the effect. 
-In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@Lakens_equivalence_2018].
+In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
 If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero.
 Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
-Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the newly proposed SGPV to equivalence tests.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the behavior of the newly proposed SGPV to equivalence tests.
 
@@
 The first term of this formula implies that the second generation *p*-value is the width of the confidence interval that overlaps with the equivalence range, divided by the total width of the confidence interval.
-The second term is a 'small sample correction' (see below) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
+The second term is a 'small sample correction' (which will be discussed later) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
 
@@
 In \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
-The statistics are calculated for hypothetical one-sample *t*-tests for *all* means that can be observed in studies ranging from 140 to 150 (on the x-axis).
+The statistics are calculated for hypothetical one-sample *t*-tests for observed means ranging from 140 to 150 (on the x-axis).
 The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 100.
@@
 
-When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* = `r round(tost_res1$TOST_p1, digits =  5)`.
+When the observed sample mean is 145, the sample size is 30, and the standard deviation is 2, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* < .001.
 Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure \ref{fig:TOSTSGPV1}).
@@
 It is clear the SGPV and the *p*-value from TOST are closely related.
-When confidence intervals are symmatric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values.
+When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values.
 When the TOST *p*-value is 0.5, the SGPV is also 0.5 (note that the reverse is not true).
-The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound.
+The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
 When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, \ref{fig:TOSTSGPV3}).
@@
 Two other points always have to overlap.
-When the 95% CI falls completely, but only just inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
-When the SGPV changes from <1 to 1 the 95% CI is exactly equal to one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) the TOST *p*-value is 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value to 0 (i.e., when the 95% CI falls completely outside of the equivalence bound, see situation C in \ref{fig:TOSTSGPV3}).
+When the 95% CI falls completely (but only just) inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
+When the SGPV changes from <1 to 1 the 95% CI touches one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) and the TOST *p*-value is always 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value to 0 (i.e., when the 95% CI falls completely outside of the equivalence range, but touches one of the equivalence bounds, see situation C in \ref{fig:TOSTSGPV3}).
 When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
 
-The confidence interval width is uniformly distributed across the mean differences, in the sense that as the true mean in a one-sample t-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
+The confidence interval width is uniformly distributed across the mean differences.
+As the observed mean in a one-sample *t*-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
 ```{r, include=FALSE}
@@
 ```
-```{r, TOSTSGPV4, fig.cap="Means, normal distribution, and 95% CI for samples where the true population mean is 1.5, 1.4, 1.3, and 1.2."}
+```{r, TOSTSGPV4, fig.cap="Means, normal distribution, and 95% CI for samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2."}
 plot(NA, 
@@
 
-As we move the means closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
+As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
 The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
@@
 When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
-Because p-values approach 0 or 1, but are never exactly 0 or 1, while the SGPV is exactly 0 or 1, the two statistics are completely unrelated.
+Because *p*-values approach 0 or 1, but are never exactly 0 or 1, while the SGPV is exactly 0 or 1, the two statistics are completely unrelated.
 The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
@@
 We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see \ref{fig:TOSTSGPV7}).
-We see the SGPV is 0.5 for a range of observed means where the p-value from the equivalence test still varies.
+We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
 It should be noted that in these calculations the *p*-values for the TOST procedure are *never* smaller than 0.05 (i.e., they do not get below 0.05 on the y-axis).
@@
 
-The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in \ref{fig:TOSTSGPV11} below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
@@
 The pattern is quite similar to that in \ref{fig:TOSTSGPV2}.
-The p-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
+The *p*-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
 There are two important differences, however.
 First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95% CI.
-Second, and most importantly, the p-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5.
+Second, and most importantly, the *p*-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5.
 
@@
 However definitive findings, i.e.
-a p-value of 0 or 1 are *not* affected by the scale changes."
+a *p*-value of 0 or 1 are *not* affected by the scale changes."
 
@@
 
-One benefit of *p*-values over the SGPV is that the SGPV is 0, 0.5, or 1 for a range of observed effects where *p*-values for the TOST procedure continue to differentiate.
-For example, different equivalence tests with *p* = 0.024 and *p* = 0.0001 have a SGPV of 1.
-The SGPV provides on average less information than *p*-values.
-
 A possible weakness of the SGPV is that even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive.
-This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, *p*-values can be interpreted in continuous matter [matter?], which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcomes, while equivalence tests classify results into four possible outcomes.
-
-A final important weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018).
+The difference is that where a SGPV of 1 can be interpreted as *p* < .05, and equivalence test provides an exact *p*-value, and continues to differentiate between for example p = 0.048 and p = 0.002.
+*P*-values continue to differentiate for situations where the SGPV are identical.
+For example, different equivalence tests with *p* = 0.048 and *p* = 0.002 have a SGPV of 1.
+Whether this is desireable depends on the perspecitve that is used.
+From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
+At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how surprising the data is under the null model.
+Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
+Thus, the SGPV is used to classify results into one of three possible outcomes (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible outcomes.
+
+An important issue when calculating the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
 This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
-Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as @blume_second-generation_2018 seem to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range.
-Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see \ref{fig:TOSTSGPV6}).
+Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV.
+@blume_second-generation_2018 suggest that under such a scenario 'the data favor alternative hypotheses', even when a better interpretation would be that there is not enough data to accurately estimate the true effect compared to the width of the equivalence range.
+Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example \ref{fig:TOSTSGPV6}).
 An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
@@
 This example suggests that the current implementation of the 'small sample correction' could be improved.
-
-@blume_second-generation_2018 argue that the SGPV has improved eType I rror control.
-However, they mean that the SGPV has a *lower* error rate, not a *more accurate* error rate.
-In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible, but with a decision procedure that yields a desired error rate accurately.
-If a lower Type I error rate is desired, the alpha level can be lowered.
-Equivalence tests also make it straightforward to control the Type 1 error rate by performing an a-priori power analysis.
+If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the 'small sample correction'.
+
+@blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
+However, the SGPV has a *lower* error rate, not a *more accurate* error rate.
+In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
+Traditional frequentist tests such as equivalence tests, null-hypothesis tests, and minimal effect tests (which have the same goal as the SGPV to test whether a confidence interval falls completely outside the equivalence range) make it straightforward to control the Type 1 error rate, as well as the Type II error rate by performing an a-priori power analysis.
+Note that the TOST procedure uses a 90% confidence interval (because it is based on two one-sided tests, the confidence interval is 1-2*$\alpha$, but because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed).
+Therefore, the TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval.
+
+@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
+15) and that "second-generation p-values provide a proper scientific adjustment for multiple comparisons".
+However, this is not correct.
+Even when for a single test the probability of concluding there is a meaningful effect (where the confidence interval falls outside of the equivalence range) is lower than the probability that there is any effect, with a sufficient number of looks and narrow confidence intervals error rates can rise above the nominal alpha level.
+More importantly, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for null-hypothesis testing.
+To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
+Equivalence tests provide and easier and more formal way to control error rates.
 
@@
 ```
+
 ```{r, TOSTSGPV13, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05."}
@@
 We believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
-The novelty lies in its use as a descriptive statistic.
-There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent.
+The novelty lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical, or wider than the equivalence range.
+There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent, and easier to interpret.
 We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
+Our comparisons shows that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
+We believe equivalence tests achieve the goals of the second generation *p*-value while allowing users to more easily control error rates, and while yielding more consistent statistical outcomes.
 

### 2018-08-23 manuscript.Rmd
add shiny app to doc

@@
 For example, for the left-most point in \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
-Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.
+Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
 

### 2018-08-23 TOST_vs_SGPV_app/server.R

@@ -1,85 +1,50 @@
-library(shiny)
-library(TOSTER)
-
-#Create SGPV funtion from https://github.com/LucyMcGowan/sgpvalue/blob/master/R/p_delta.R
-
-#' Second Generation P-value
-p_delta <- function(lb, ub, delta_lb, delta_ub) {
-  
-  # special case: infinite CI and H0 bounds in the same direction
-  if ((delta_lb == -Inf & lb == -Inf) | (delta_ub == Inf & ub == Inf)) {
-    return(1)
-  }
-  
-  # usual case: non-point CI & non-point Ho
-  # pdelta = |CI intersect Ho| / min{ |CI|, 2|Ho| }
-  if (delta_lb != delta_ub & lb != ub) {
-    if (lb > delta_ub | ub < delta_lb) {
-      return(0)
-    } else if(lb > delta_lb & ub < delta_ub){
-      return(1)
-    } else {
-      return(
-        (min(ub, delta_ub) - max(lb, delta_lb)) /
-          min(ub - lb, 2 * (delta_ub - delta_lb))
-      )
-    }
-  }
-  
-  # special case 1: point CI, w/ or w/out a point H0
-  # pdelta = 0 if CI is inside the Ho
-  # pdelta = 1 if CI is inside the Ho
-  if (lb == ub) {
-    if (lb <= delta_ub & lb >= delta_lb){
-      return(1)
-    } else {
-      return(0)
-    }
-  }
-  
-  # special case 2: point H0 & non-point CI
-  # pdelta = 1/2 if H0 is inside the CI
-  # pdelta = 0 if H0 is outside the CI
-  if (delta_lb == delta_ub & lb != ub) {
-    if (delta_lb <= ub & delta_lb >= lb) {
-      return(1/2)
-    } else {
-      return(0)
-    }
-  }
-}
-
-# Define UI for application that draws a histogram
-ui <- fluidPage(
-   
-   # Application title
-  titlePanel("Plot P-Values for the TOST procedure and Second Generation P-Value"),
-   
-   # Sidebar with a slider input for number of bins 
-  sidebarLayout(
-    sidebarPanel(numericInput("N", "Participants per group:", 30, min = 1, max = 1000),
-                 sliderInput("sd", "Standard Deviation:", min = 0.5, max = 5, value = 2, step= 0.5),
-                 sliderInput("range", "Equivalence Range:", min = -5, max = 5, value = c(-2,2), step= 0.1),              
[…]

### 2018-08-24 manuscript.Rmd
re-writes towards final version

@@
   To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
-We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the Two-One-Sided Tests equivalence testing procedure [@schuirmann_comparison_1987].
-We show that the two approaches yield almost identical results under optimal circumstances, but under suboptimal circumstances (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
-The second generation is interpretable in a dichotomous manner when it is 0 or 1 (and lies completely within or outside of the equivalence range), but these cases can be observed visually and do not require calculation.
-Equivalence tests yield more consistent *p*-values, distinguish between datsets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
-
-keywords          : "equivalence testing, second generation *p*-values, *p*-values, hypothesis testing, statistics"
+Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interepreted as a statistically significant difference.
+We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the more established Two One-Sided Tests (TOST) equivalence testing procedure [@schuirmann_comparison_1987].
+We show that the two approaches yield almost identical results under optimal conditions.
+Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
+The second generation *p*-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
+We conclude that equivalence tests yield more consistent *p*-values, distinguish between datsets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
+
+keywords          : "equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference"
 wordcount         : ""
@@
 
-To test predictions most researchers predominantly rely on null-hypothesis tests. 
-This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect size of zero. 
+To test predictions researchers predominantly rely on null-hypothesis tests. 
+This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero. 
 Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*.
-When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaningful effect. 
+When testing for equivalence researchers aim to examine whether an observed effect is too small to be considered meaningful, and therefore is practically equivalent to zero. 
 By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent [@hauck_new_1984;@kruschke_rejecting_2018;@rogers_using_1993;@serlin_rationality_1985;@spiegelhalter_bayesian_1994;@wellek_testing_2010;@westlake_use_1972].
@@
 Second generation *p*-values (SGPV) were recently proposed to as a descriptive statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
-The researcher specifies an equivalence range around a classical simple null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
+The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis. 
 The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis. 
@@
 Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
-When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
-When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties.
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although other one could also choose to use credible intervals or Likelihood support intervals (SI).
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties, because both tests conpare a confidence interval against an equivalence range.
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
@@
 In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
-If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero.
+If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
 Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
-Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the behavior of the newly proposed SGPV to equivalence tests.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
 
@@
 To examine the relation between the TOST *p*-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
-In \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
+In Figure \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
 The statistics are calculated for hypothetical one-sample *t*-tests for observed means ranging from 140 to 150 (on the x-axis).
-The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 100.
-For example, for the left-most point in \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
+The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 30.
+For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
 Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
@@
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, \ref{fig:TOSTSGPV3}).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure \ref{fig:TOSTSGPV3}).
 
@@
 Two other points always have to overlap.
-When the 95% CI falls completely (but only just) inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
-When the SGPV changes from <1 to 1 the 95% CI touches one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) and the TOST *p*-value is always 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value to 0 (i.e., when the 95% CI falls completely outside of the equivalence range, but touches one of the equivalence bounds, see situation C in \ref{fig:TOSTSGPV3}).
-When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
-
-The confidence interval width is uniformly distributed across the mean differences.
-As the observed mean in a one-sample *t*-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
+When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST *p*-value (which relies on a one-sided test) is always 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975.
+
+As the observed mean in a one-sample *t*-test lies closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
 ```{r, include=FALSE}
@@
 As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`).
-Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
+Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
 Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
@@
 There are 4 situations where *p*-values from TOST and SGPV are unrelated.
-The first two situations were discussed earlier, and can be seen in \ref{fig:TOSTSGPV1}.
+The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
 When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
-Because *p*-values approach 0 or 1, but are never exactly 0 or 1, while the SGPV is exactly 0 or 1, the two statistics are completely unrelated.
+Because *p*-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges.
 The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
-The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical lines at SGPV of 0 and 1.
+The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
 ```{r, include=FALSE}
@@
 
-A third situation in which the SGPV deviates strongly from the TOST *p*-value is whenever the CI is more than twice as wide as the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
-In this situation the normal calculation of the proportion of overlap is skipped, and the SGPV is set to 0.5 instead.
+A third situation in which the SGPV deviates from the TOST *p*-value is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
+When the confidence interval is more than twice as wide as the equivalence range the SGPV is set to 0.5.
 @blume_second-generation_2018 call this the 'small sample correction factor'.
 However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any 'correct' value.
-When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, when all values in the equivalence range are also supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
+When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
 Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) *or* when then equivalence range is narrow.
@@
 
-We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see \ref{fig:TOSTSGPV7}).
+We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 In other words, we cannot conclude equivalence based on any of the observed means.
-How is this possible?
-Remember that the TOST procedure consists of two one-sided tests against the upper and lower equivalence bound.
-The TOST *p*-value is smaller than 0.05 if the 90% CI falls completely between the upper and lower equivalence bounds.
-However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
+This happens because the TOST *p*-value is smaller than 0.05 only when the 90% CI falls completely between the upper and lower equivalence bounds.
+However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds, and thus the equivalence test is never significant.
 As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
@@
 
-There is one last situation where the *p*-value from the TOST procedure and the SGPV are unrelated.
-This is when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-This fourth category exists because of the decision by Blume and colleagues to set the SGPV to 0.5 whenever the CI is twice as wide as the equivalence range and the CI overlaps with both equivalence bounds.
-This means that there are situations where the CI interval overlaps with both equivalence bounds, while the CI is less than twice as large as the equivalence bound.
+The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
 For example, in the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
+This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
 ```{r, include=FALSE}
@@
 
-If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure can vary between 0 and .025.
-We can see this in \ref{fig:TOSTSGPV9} below.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV remains constant (the CI width does not change, and it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure does vary.
+We can see this in Figure \ref{fig:TOSTSGPV9} below.
 The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
-How high the SGPV will be when the CI overlaps with the lower and upper equivalence bounds, but the CI is not twice as large as the equivalence range, depends on the width of the CI and the equivalence range.
+How high the SGPV will be for a CI that is not twice as wide as the equivalence range, but overlaps with the lower and upper equivalence bounds, depends on the width of the CI and the equivalence range.
 ```{r, include=FALSE}
@@
 In all these situations the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely descriptive statistic, the SGPV is more limited than the value from the TOST procedure.
-The proportion of overlap can be the same value when the observed mean is 0 or when the observed mean falls just inside the equivalence bound, and additional information (e.g., the 95% CI) is required to differentiate these situations.
-One way to mitigate this limitation of the SGPV would be to set the SGPV to 0.5 whenever the CI overlaps with both the upper and lower equivalence bound (irrespective of the width of the CI).
+Therefore, as a purely continuous descriptive statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
 
@@
 
-The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
 As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
-The pattern is quite similar to that in \ref{fig:TOSTSGPV2}.
+The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
 The *p*-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
@@
 In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
+However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
 Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
@@
 In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
-It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to.
-The conclusion of this in depth look at asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answer, and the question a *p*-value answers.
+The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
 Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
@@
 
-##What are the Relative Strengths and Weaknesses of Equivalence Testing and SGPV?
-
-Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what the introduction of SGPV adds to the existing statistical approaches, including equivalence tests, and what the relative strengths and weaknesses of either approach are.
-First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
-It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see \ref{fig:TOSTSGPV3}).
-
-A possible weakness of the SGPV is that even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
-This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive.
+##What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
+
+When introducing a new statistical method, it is important to compare it to existing approaches and specify it's relative strengths and weaknesses.
+First of all, the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
+
+Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+In one sense, they are what they are (the proportion of overlap), but in any specific case it can be unclear what this number tells us about the data we have collected.
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0, 1, or inconclusive.
 This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018).
-The difference is that where a SGPV of 1 can be interpreted as *p* < .05, and equivalence test provides an exact *p*-value, and continues to differentiate between for example p = 0.048 and p = 0.002.
-*P*-values continue to differentiate for situations where the SGPV are identical.
-For example, different equivalence tests with *p* = 0.048 and *p* = 0.002 have a SGPV of 1.
-Whether this is desireable depends on the perspecitve that is used.
+The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example p = 0.048 and p = 0.002.
+Whether this is desireable depends on the perspective that is used.
 From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
-At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how surprising the data is under the null model.
+At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how precisely how surprising the data is under the null model.
 Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, the SGPV is used to classify results into one of three possible outcomes (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible outcomes.
+Thus, the SGPV is used to classify results into one of three possible cateogies (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories
 
@@
 @blume_second-generation_2018 suggest that under such a scenario 'the data favor alternative hypotheses', even when a better interpretation would be that there is not enough data to accurately estimate the true effect compared to the width of the equivalence range.
-Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example \ref{fig:TOSTSGPV6}).
+Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example Figure \ref{fig:TOSTSGPV6}).
 An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
 
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see \ref{fig:TOSTSGPV13} below.
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of meaningless SGPV in this range.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range.
 This example suggests that the current implementation of the 'small sample correction' could be improved.
@@
 @blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
-However, the SGPV has a *lower* error rate, not a *more accurate* error rate.
+However, the SGPV has a *lower* error rate than a null-hypothesis test, not a *more accurate* error rate.
 In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
-Traditional frequentist tests such as equivalence tests, null-hypothesis tests, and minimal effect tests (which have the same goal as the SGPV to test whether a confidence interval falls completely outside the equivalence range) make it straightforward to control the Type 1 error rate, as well as the Type II error rate by performing an a-priori power analysis.
-Note that the TOST procedure uses a 90% confidence interval (because it is based on two one-sided tests, the confidence interval is 1-2*$\alpha$, but because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed).
-Therefore, the TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval.
+We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
+The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2*$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
+The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
 
 @blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
-15) and that "second-generation p-values provide a proper scientific adjustment for multiple comparisons".
+15) and that "second-generation *p*-values provide a proper scientific adjustment for multiple comparisons".
 However, this is not correct.
-Even when for a single test the probability of concluding there is a meaningful effect (where the confidence interval falls outside of the equivalence range) is lower than the probability that there is any effect, with a sufficient number of looks and narrow confidence intervals error rates can rise above the nominal alpha level.
-More importantly, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for null-hypothesis testing.
+With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
+When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
 To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
-Equivalence tests provide and easier and more formal way to control error rates.
+Equivalence tests provide and easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
 
@@
 
-We believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
-The novelty lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical, or wider than the equivalence range.
-There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent, and easier to interpret.
+We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation *p*-values to the statistical toolbox.
+The novelty of te SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
+There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent and easier to interpret.
 We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.

### 2018-08-24 manuscript.Rmd
Typo

@@
 The second generation *p*-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
-We conclude that equivalence tests yield more consistent *p*-values, distinguish between datsets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
+We conclude that equivalence tests yield more consistent *p*-values, distinguish between datasets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
 

### 2018-08-24 manuscript.Rmd
typo's

@@
 ---
-title             : "Equivalence Testing and the Second Generation P-Value"
+title             : "Equivalence Testing and the Second Generation *P*-Value"
 shorttitle        : "TOST vs. SGPV"
@@
 When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although other one could also choose to use credible intervals or Likelihood support intervals (SI).
-When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties, because both tests conpare a confidence interval against an equivalence range.
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties, because both tests compare a confidence interval against an equivalence range.
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.

### 2018-08-24 manuscript.Rmd
Typo's and details

@@
 
-On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
+On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
 Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure  \ref{fig:TOSTSGPV1}).
@@
 
-As the observed mean in a one-sample *t*-test lies closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
+As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure 4, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
 ```{r, include=FALSE}
@@
 The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
-As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`).
+As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C and D (`r round(tail3-tail4, digits = 3)`).
 Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
 Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
+
 ##When are the SGPV and Equivalence Test Unrelated?
+
 There are 4 situations where *p*-values from TOST and SGPV are unrelated.
@@
 The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-For example, in the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
+In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
 This means the SGPV is not set to 0.5, but it is constant across a range of observed means.

### 2018-08-24 manuscript.Rmd
Last typo's and rounding mistakes

@@
 
-There are 4 situations where *p*-values from TOST and SGPV are unrelated.
+There are three situations where *p*-values from TOST and SGPV are unrelated.
 The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
@@
 
-To conclude this section, there are four situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
+To conclude this section, there are three situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
 In all these situations the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
@@
 The confidence interval becomes increasingly asymmetric as the observed correlation nears -1 or 1.
-For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.629 to 0.629, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.992.
-
-The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.993.
+
+The effect of asymmetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
@@
 n <- 30
-r_pop <- .0
+r_pop <- 0
 low_eqbound_r <- -.45
@@
 In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
-It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answer, and the question a *p*-value answers.
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a *p*-value answers.
 The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
@@
 Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
-In one sense, they are what they are (the proportion of overlap), but in any specific case it can be unclear what this number tells us about the data we have collected.
+In one sense, they are what they are (the proportion of overlap), but in any specific cases it can be unclear what this number tells us about the data we have collected.
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0, 1, or inconclusive.
@@
 The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example p = 0.048 and p = 0.002.
-Whether this is desireable depends on the perspective that is used.
+Whether this is desirable depends on the perspective that is used.
 From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
@@
 Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, the SGPV is used to classify results into one of three possible cateogies (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories
+Thus, the SGPV is used to classify results into one of three possible categories (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories.
 
@@
 To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
-Equivalence tests provide and easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
+Equivalence tests provide an easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
 

### 2018-08-24 manuscript.Rmd
feedback Marie

@@
   All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV.
+This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
 
@@
 Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
-When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although other one could also choose to use credible intervals or Likelihood support intervals (SI).
-When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties, because both tests compare a confidence interval against an equivalence range.
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although one could also choose to use credible intervals or Likelihood support intervals (SI).
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@quertemont_how_2011;@schuirmann_comparison_1987] appear to have close ties, because both tests compare a confidence interval against an equivalence range.
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
@@
 The second term is a 'small sample correction' (which will be discussed later) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
-
 To examine the relation between the TOST *p*-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
@@
 Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
-
 ```{r, include=FALSE}
@@
 ```
-
 ```{r, TOSTSGPV1, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
@@
 ```
-
 When the observed sample mean is 145, the sample size is 30, and the standard deviation is 2, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* < .001.
 Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure \ref{fig:TOSTSGPV1}).
-
 On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
@@
 
-As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure 4, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
 ```{r, include=FALSE}
@@
 ```
-
 ```{r, include=FALSE}
@@
 ```
-For example, the SGPV from A to D is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
-The difference in the percentage of overlap between A and B (`r round(SGPV1-SGPV2, digits = 2)`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r round(SGPV3-SGPV4, digits = 2)`).
 ```{r , echo=FALSE}
@@
 ```
-
+For example, the SGPV from A to D is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
+The difference in the percentage of overlap between A and B (`r round(SGPV1-SGPV2, digits = 2)`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r round(SGPV3-SGPV4, digits = 2)`).
+As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
 As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
@@
 
-We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range.
+We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
 ```{r, include=FALSE}
@@
 The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
+In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
 This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
@@
 
-If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies.
+If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
-The effect of asymmetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The effect of asymmetric confidence intervals is most noticable at smaller sample sizes.
+In Figure \ref{fig:TOSTSGPV11} we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
@@
 In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
-Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
+However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
 
@@
 First of all, the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
-
 Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
@@
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0, 1, or inconclusive.
-This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018).
-The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example p = 0.048 and p = 0.002.
+This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test [@lakens_equivalence_2018].
+The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example *p* = 0.048 and *p* = 0.002.
 Whether this is desirable depends on the perspective that is used.
@@
 We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation *p*-values to the statistical toolbox.
-The novelty of te SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
+The novelty of the SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
 There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent and easier to interpret.

### 2018-08-28 archive/sgpv_vs_TOST.Rmd

--- 2018-08-24 manuscript.Rmd
@@
 ---
-title             : "Equivalence Testing and the Second Generation *P*-Value"
-shorttitle        : "TOST vs. SGPV"
-
-author:
-  - name          : "Dani&euml;l Lakens"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands"
-    email         : "D.Lakens@tue.nl"
-  - name          : "Marie Delacre"
-    affiliation   : "2"
-
-affiliation:
-  - id            : "1"
-    institution   : "Eindhoven University of Technology, Eindhoven, The Netherlands"
-  - id            : "2"
-    institution   : "Service of Analysis of the Data, Université Libre de Bruxelles, Belgium"
-
-author_note: |
-  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV.
-
-abstract: |
-  To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
-Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interepreted as a statistically significant difference.
-We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the more established Two One-Sided Tests (TOST) equivalence testing procedure [@schuirmann_comparison_1987].
-We show that the two approaches yield almost identical results under optimal conditions.
-Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
-The second generation *p*-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
-We conclude that equivalence tests yield more consistent *p*-values, distinguish between datasets that yield the same second generation *p*-value, and allow for easier control of Type I and Type II error rates.
-
-keywords          : "equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference"
-wordcount         : ""
-
-bibliography      : ["TOST_vs_SGPV.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : yes
-mask              : no
-
-class             : "man"
-output            : papaja::apa6_pdf
+title: "Equivalence Testing and the Second Generation P-Value"
+author: "Daniël Lakens & Marie Delacre"
+output: github_document
 ---
 
-```{r include = FALSE}
-library("TOSTER")
-library("papaja")
-```
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+options(scipen=99)
+```
+```{r, include=FALSE}
+library(TOSTER)
+```
+
 ```{r, include=FALSE}
@@
 source("functions/p_delta_function.R")
-```
-
-To test predictions researchers predominantly rely on null-hypothesis tests. 
-This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero. 
+
+```
+To test predictions most researchers predominantly rely on null-hypothesis tests. 
+This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect size of zero. 
 Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*.
-When testing for equivalence researchers aim to examine whether an observed effect is too small to be considered meaningful, and therefore is practically equivalent to zero. 
+When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaningful effect. 
 By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent [@hauck_new_1984;@kruschke_rejecting_2018;@rogers_using_1993;@serlin_rationality_1985;@spiegelhalter_bayesian_1994;@wellek_testing_2010;@westlake_use_1972].
@@
 Second generation *p*-values (SGPV) were recently proposed to as a descriptive statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
-The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis. 
+The researcher specifies an equivalence range around a classical simple null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
 The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis.
@@
 Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
-When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although other one could also choose to use credible intervals or Likelihood support intervals (SI).
-When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties, because both tests compare a confidence interval against an equivalence range.
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure [@lakens_equivalence_2017;@meyners_equivalence_2012;@schuirmann_comparison_1987] appear to have close ties.
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
@@
 In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
-If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
+If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero.
 Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
-Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the behavior of the newly proposed SGPV to equivalence tests.
 
@@
 To examine the relation between the TOST *p*-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
-In Figure \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
+In \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
 The statistics are calculated for hypothetical one-sample *t*-tests for observed means ranging from 140 to 150 (on the x-axis).
-The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 30.
-For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
-Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
+The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 100.
+For example, for the left-most point in \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 100, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
+Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.
 
@@
 
-On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
+On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1).
 Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure  \ref{fig:TOSTSGPV1}).
@@
 The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure \ref{fig:TOSTSGPV3}).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, \ref{fig:TOSTSGPV3}).
 
@@
 Two other points always have to overlap.
-When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST *p*-value (which relies on a one-sided test) is always 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975.
-
-As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure 4, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
+When the 95% CI falls completely (but only just) inside the equivalence region, the TOST (which relies on a one-sided test) should be significant at an alpha level of 0.025.
+When the SGPV changes from <1 to 1 the 95% CI touches one of the equivalence bounds (see situation B in \ref{fig:TOSTSGPV3}, where the 95% CI falls completely inside the equivalence bounds) and the TOST *p*-value is always 0.025.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the SGPV  changes from a positive value to 0 (i.e., when the 95% CI falls completely outside of the equivalence range, but touches one of the equivalence bounds, see situation C in \ref{fig:TOSTSGPV3}).
+When the 95% CI touches the outside of the equivalence bound and the TOST *p*-value will be 0.975.
+
+The confidence interval width is uniformly distributed across the mean differences.
+As the observed mean in a one-sample *t*-test gets closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap is stable.
 ```{r, include=FALSE}
@@
 The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
-As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C and D (`r round(tail3-tail4, digits = 3)`).
-Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
+As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`).
+Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
 Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
-
 ##When are the SGPV and Equivalence Test Unrelated?
-
 There are 4 situations where *p*-values from TOST and SGPV are unrelated.
-The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
+The first two situations were discussed earlier, and can be seen in \ref{fig:TOSTSGPV1}.
 When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
-Because *p*-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges.
+Because *p*-values approach 0 or 1, but are never exactly 0 or 1, while the SGPV is exactly 0 or 1, the two statistics are completely unrelated.
 The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
-The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
+The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical lines at SGPV of 0 and 1.
 ```{r, include=FALSE}
@@
 
-A third situation in which the SGPV deviates from the TOST *p*-value is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
-When the confidence interval is more than twice as wide as the equivalence range the SGPV is set to 0.5.
+A third situation in which the SGPV deviates strongly from the TOST *p*-value is whenever the CI is more than twice as wide as the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
+In this situation the normal calculation of the proportion of overlap is skipped, and the SGPV is set to 0.5 instead.
 @blume_second-generation_2018 call this the 'small sample correction factor'.
 However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any 'correct' value.
-When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
+When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, when all values in the equivalence range are also supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
 Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) *or* when then equivalence range is narrow.
@@
 
-We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 In other words, we cannot conclude equivalence based on any of the observed means.
-This happens because the TOST *p*-value is smaller than 0.05 only when the 90% CI falls completely between the upper and lower equivalence bounds.
-However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds, and thus the equivalence test is never significant.
+How is this possible?
+Remember that the TOST procedure consists of two one-sided tests against the upper and lower equivalence bound.
+The TOST *p*-value is smaller than 0.05 if the 90% CI falls completely between the upper and lower equivalence bounds.
+However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
 As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
@@
 
-The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
-This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
+There is one last situation where the *p*-value from the TOST procedure and the SGPV are unrelated.
+This is when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
+This fourth category exists because of the decision by Blume and colleagues to set the SGPV to 0.5 whenever the CI is twice as wide as the equivalence range and the CI overlaps with both equivalence bounds.
+This means that there are situations where the CI interval overlaps with both equivalence bounds, while the CI is less than twice as large as the equivalence bound.
+For example, in the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds.
 ```{r, include=FALSE}
@@
 
-If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV remains constant (the CI width does not change, and it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure does vary.
-We can see this in Figure \ref{fig:TOSTSGPV9} below.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV would remain constant (the CI width does not change, it completely overlaps with the equivalence range) while the *p*-value for the TOST procedure can vary between 0 and .025.
+We can see this in \ref{fig:TOSTSGPV9} below.
 The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
-How high the SGPV will be for a CI that is not twice as wide as the equivalence range, but overlaps with the lower and upper equivalence bounds, depends on the width of the CI and the equivalence range.
+How high the SGPV will be when the CI overlaps with the lower and upper equivalence bounds, but the CI is not twice as large as the equivalence range, depends on the width of the CI and the equivalence range.
 ```{r, include=FALSE}
@@
 In all these situations the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely continuous descriptive statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
+Therefore, as a purely descriptive statistic, the SGPV is more limited than the value from the TOST procedure.
+The proportion of overlap can be the same value when the observed mean is 0 or when the observed mean falls just inside the equivalence bound, and additional information (e.g., the 95% CI) is required to differentiate these situations.
+One way to mitigate this limitation of the SGPV would be to set the SGPV to 0.5 whenever the CI overlaps with both the upper and lower equivalence bound (irrespective of the width of the CI).
 
@@
 
-The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in \ref{fig:TOSTSGPV11} below we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
 As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
-The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
+The pattern is quite similar to that in \ref{fig:TOSTSGPV2}.
 The *p*-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
@@
 In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
+However, as can be seen in \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are `r round(sgpv,3)`.
 Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv,3)*100`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
@@
 In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
-It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answer, and the question a *p*-value answers.
-The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to.
+The conclusion of this in depth look at asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
 Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
@@
 
-##What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
-
-When introducing a new statistical method, it is important to compare it to existing approaches and specify it's relative strengths and weaknesses.
-First of all, the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
-
-Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
-In one sense, they are what they are (the proportion of overlap), but in any specific case it can be unclear what this number tells us about the data we have collected.
-This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0, 1, or inconclusive.
+##What are the Relative Strengths and Weaknesses of Equivalence Testing and SGPV?
+
+Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what the introduction of SGPV adds to the existing statistical approaches, including equivalence tests, and what the relative strengths and weaknesses of either approach are.
+First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic).
+It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see \ref{fig:TOSTSGPV3}).
+
+A possible weakness of the SGPV is that even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive.
 This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (@lakens_equivalence_2018).
-The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example p = 0.048 and p = 0.002.
-Whether this is desireable depends on the perspective that is used.
+The difference is that where a SGPV of 1 can be interpreted as *p* < .05, and equivalence test provides an exact *p*-value, and continues to differentiate between for example p = 0.048 and p = 0.002.
+*P*-values continue to differentiate for situations where the SGPV are identical.
+For example, different equivalence tests with *p* = 0.048 and *p* = 0.002 have a SGPV of 1.
+Whether this is desireable depends on the perspecitve that is used.
 From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
-At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how precisely how surprising the data is under the null model.
+At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how surprising the data is under the null model.
 Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, the SGPV is used to classify results into one of three possible cateogies (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories
+Thus, the SGPV is used to classify results into one of three possible outcomes (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible outcomes.
 
@@
 @blume_second-generation_2018 suggest that under such a scenario 'the data favor alternative hypotheses', even when a better interpretation would be that there is not enough data to accurately estimate the true effect compared to the width of the equivalence range.
-Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example Figure \ref{fig:TOSTSGPV6}).
+Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example \ref{fig:TOSTSGPV6}).
 An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
 
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see \ref{fig:TOSTSGPV13} below.
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of meaningless SGPV in this range.
 This example suggests that the current implementation of the 'small sample correction' could be improved.
@@
 @blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
-However, the SGPV has a *lower* error rate than a null-hypothesis test, not a *more accurate* error rate.
+However, the SGPV has a *lower* error rate, not a *more accurate* error rate.
 In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
-We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
-The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2*$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
-The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
+Traditional frequentist tests such as equivalence tests, null-hypothesis tests, and minimal effect tests (which have the same goal as the SGPV to test whether a confidence interval falls completely outside the equivalence range) make it straightforward to control the Type 1 error rate, as well as the Type II error rate by performing an a-priori power analysis.
+Note that the TOST procedure uses a 90% confidence interval (because it is based on two one-sided tests, the confidence interval is 1-2*$\alpha$, but because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed).
+Therefore, the TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval.
 
 @blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
-15) and that "second-generation *p*-values provide a proper scientific adjustment for multiple comparisons".
+15) and that "second-generation p-values provide a proper scientific adjustment for multiple comparisons".
 However, this is not correct.
-With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
-When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
+Even when for a single test the probability of concluding there is a meaningful effect (where the confidence interval falls outside of the equivalence range) is lower than the probability that there is any effect, with a sufficient number of looks and narrow confidence intervals error rates can rise above the nominal alpha level.
+More importantly, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for null-hypothesis testing.
 To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
-Equivalence tests provide and easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
+Equivalence tests provide and easier and more formal way to control error rates.
 
@@
 
-We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation *p*-values to the statistical toolbox.
-The novelty of te SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
-There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent and easier to interpret.
+We believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox.
+The novelty lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical, or wider than the equivalence range.
+There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent, and easier to interpret.
 We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
@@
 We believe equivalence tests achieve the goals of the second generation *p*-value while allowing users to more easily control error rates, and while yielding more consistent statistical outcomes.
-
-\newpage
-
-# References
-
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}

### 2018-08-28 manuscript.Rmd

@@
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of "misleading" values in this range.
 This example suggests that the current implementation of the 'small sample correction' could be improved.

### 2018-08-28 manuscript.Rmd
Update manuscript.Rmd

--- 2018-08-24 manuscript.Rmd
@@
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of 'misleading' values in this range.
 This example suggests that the current implementation of the 'small sample correction' could be improved.

### 2018-08-28 manuscript.Rmd
submission

--- 2018-08-24 manuscript.Rmd
@@
 footnotelist      : no
-lineno            : yes
+lineno            : no
 mask              : no
@@
 If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
-Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
+Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2$\times$alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
 Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
@@
 The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975.
+Note that this situation is in essence a *minimum-effect test* [@murphy_statistical_2014].
+The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
+The SGPV summarizes the information from an equivalence test and a minimum-effect test.
+These can be two relevant questions to ask, although it often makes sense to combine an equivalence test and a null-hypothesis test instead [@lakens_equivalence_2018].
 
@@
 However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any 'correct' value.
-When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signal the SGPV is 'uninformative'.
+When the normal calculation would be 'misleading' (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signals that the SGPV is 'uninformative'.
 Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) *or* when then equivalence range is narrow.
@@
 
-We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
 ```{r, include=FALSE}
@@
 
-We can again plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
+When the two statistics are plotted against each other we can seewhere they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 
-If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
-
 ```{r, TOSTSGPV10, fig.cap="The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure \\ref{fig:TOSTSGPV9}."}
@@
 
+If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 To conclude this section, there are three situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
@@
 lines(p_tost_list, lwd = 3)
-abline(h = c(0.975, 0.5, 0.025),
-       lty = 2,
-       col = "grey")
+# abline(h = c(0.975, 0.5, 0.025),
+#        lty = 2,
+#        col = "grey")
 
@@
 Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
-In one sense, they are what they are (the proportion of overlap), but in any specific cases it can be unclear what this number tells us about the data we have collected.
-This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0, 1, or inconclusive.
+In one sense, they are what they are (the proportion of overlap), but it can be unclear what this number tells us about the data we have collected.
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) seems to be to examine whether the SGPV is 0, 1, or inconclusive.
 This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test [@lakens_equivalence_2018].
@@
 An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
-
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
-In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range.
-This example suggests that the current implementation of the 'small sample correction' could be improved.
-If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the 'small sample correction'.
-
-@blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
-However, the SGPV has a *lower* error rate than a null-hypothesis test, not a *more accurate* error rate.
-In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
-We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
-The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2*$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
-The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
-
-@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
-15) and that "second-generation *p*-values provide a proper scientific adjustment for multiple comparisons".
-However, this is not correct.
-With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
-When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
-To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
-Equivalence tests provide an easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
 
@@
 lines(p_tost_list, lwd = 3)
-abline(h = c(0.975, 0.5, 0.025),
-       lty = 2,
-       col = "grey")
-```
+#abline(h = c(0.975, 0.5, 0.025),
+#       lty = 2,
+#       col = "grey")
+```
+
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
+In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a misleading SGPV in this range.
+This example suggests that the current implementation of the 'small sample correction' could be improved.
+If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the 'small sample correction'.
+
+@blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
+However, the SGPV has a *lower* error rate than a null-hypothesis test, not a *more accurate* error rate.
+In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
+We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
+The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2*$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
+The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
+
+@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
+15) and that "second-generation *p*-values provide a proper scientific adjustment for multiple comparisons".
+However, this is not correct.
+With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
+When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
+To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
+Equivalence tests provide an easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
 
@@
 We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
-Our comparisons shows that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
+Our comparisons show that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
 We believe equivalence tests achieve the goals of the second generation *p*-value while allowing users to more easily control error rates, and while yielding more consistent statistical outcomes.

### 2018-08-28 manuscript.tex
submission

\documentclass[floatsintext,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Equivalence Testing and the Second Generation P-Value},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Equivalence Testing and the Second Generation \emph{P}-Value}

  \shorttitle{TOST vs.~SGPV}

  \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}

  \def\affdep{{"", ""}}%
  \def\affcity{{"", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\
          \textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium  }

  \authornote{
    \newcounter{author}
    All code associated with this article, including the reproducible
    manuscript, is available from
    \url{https://github.com/Lakens/TOST_vs_SGPV}. This work was supported by
    the Netherlands Organization for Scientific Research (NWO) VIDI grant
    452-17-013.

                      Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}
                          }

  \abstract{To move beyond the limitations of null-hypothesis tests, statistical
approaches have been developed where the observed data is compared
against a range of values that are equivalent to the absence of a
meaningful effect. Specifying a range of values around zero allows
researchers to statistically reject the presence of effects large enough
to matter, and prevents practically insignificant effects from being
interepreted as a statistically significant difference. We compare the
behavior of the recently proposed second generation \emph{p}-value
(Blume, D'Agostino McGowan, Dupont, \& Greevy, 2018) with the more
established Two One-Sided Tests (TOST) equivalence testing procedure
(Schuirmann, 1987). We show that the two approaches yield almost
identical results under optimal conditions. Under suboptimal conditions
(e.g., when the confidence interval is wider than the equivalence range,
or when confidence intervals are asymmetric) the second generation
\emph{p}-value becomes difficult to interpret as a descriptive
statistic. The second generation \emph{p}-value is interpretable in a
dichotomous manner (i.e., when the SGPV equals 0 or 1 because the
confidence intervals lies completely within or outside of the
equivalence range), but this dichotomous interpretation does not require
calculations. We conclude that equivalence tests yield more consistent
\emph{p}-values, distinguish between datasets that yield the same second
generation \emph{p}-value, and allow for easier control of Type I and
Type II error rates.}
  \keywords{equivalence testing, second generation \emph{p}-values, hypothesis
testing, TOST, statistical inference \\

  }

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

To test predictions researchers predominantly rely on null-hypothesis
tests. This statistical approach can be used to examine whether observed
data is sufficiently surprising under the null hypothesis to reject an
effect that equals exactly zero. Null-hypothesis tests have an important
limitation, in that this procedure can only reject the hypothesis that
there is no effect, while scientists should also be able to provide
statistical support for \emph{equivalence}. When testing for equivalence
researchers aim to examine whether an observed effect is too small to be
considered meaningful, and therefore is practically equivalent to zero.
By specifying a range around the null hypothesis of values that are
deemed practically equivalent to the absence of an effect (i.e., 0 ±
0.3) the observed data can be compared against an \emph{equivalence
range} and researchers can test if a meaningful effect is absent (Hauck
\& Anderson, 1984; Kruschke, 2018; Rogers, Howard, \& Vessey, 1993;
Serlin \& Lapsley, 1985; Spiegelhalter, Freedman, \& Parmar, 1994;
Wellek, 2010; Westlake, 1972).

Second generation \emph{p}-values (SGPV) were recently proposed to as a
descriptive statistic that represents \enquote{the proportion of
data-supported hypotheses that are also null hypotheses} (Blume et al.,
2018). The researcher specifies an equivalence range around a null
hypothesis of values that are considered practically equivalent to the
null hypothesis. The SGPV measures the degree to which a set of
data-supported parameter values falls within the interval null
hypothesis. If the estimation interval falls completely within the
equivalence range, the SGPV is 1. If the confidence interval falls
completely outside of the equivalence range, the SGPV is 0. Otherwise
the SGPV is a value between 0 and 1 that expresses the overlap of
data-supported hypotheses and the equivalence range. When calculating
the SGPV the set of data-supported parameter values can be represented
by a confidence interval (CI), although one could also choose to use
credible intervals or Likelihood support intervals (SI). When a
confidence interval is used, the SGPV and equivalence tests such as the
Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012;
Quertemont, 2011; Schuirmann, 1987) appear to have close ties, because
both tests compare a confidence interval against an equivalence range.
Here, we aim to examine the similarities and differences between the
TOST procedure and the SGPV.

The TOST procedure also relies on the confidence interval around the
effect. In the TOST procedure the data is tested against the lower
equivalence bound in the first one-sided test, and against the upper
equivalence bound in the second one-sided test (Lakens, Scheel, \&
Isager, 2018). If both tests statistically reject an effect as extreme
or more extreme than the equivalence bound, you can conclude the
observed effect is practically equivalent to zero from a Neyman-Pearson
approach to statistical inferences. Because one-sided tests are
performed, one can also conclude equivalence by checking whether the
1-2\(\times\)alpha confidence interval (e.g., when the alpha level is
0.05, a 90\% CI) falls completely within the equivalence bounds. Because
both equivalence tests as the SGPV are based on whether and how much a
confidence interval overlaps with equivalence bounds, it seems
worthwhile to compare the behavior of the newly proposed SGPV to
equivalence tests to examine the unique contribution of the SGPV to the
statistical toolbox.

\section{\texorpdfstring{The relationship between \emph{p}-values from
TOST and SGPV when confidence intervals are
symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}

The second generation \emph{p}-value (SGPV) is calculated as: \[
  p _ { \delta } = \frac { \left| I \cap H _ { 0 } \right| } { | I | } \times \max \left\{ \frac { | I | } { 2 \left| H _ { 0 } \right| } , 1 \right\}
\] where I is the interval based on the data (e.g., a 95\% confidence
interval) and H\textsubscript{0} is the equivalence range. The first
term of this formula implies that the second generation \emph{p}-value
is the width of the confidence interval that overlaps with the
equivalence range, divided by the total width of the confidence
interval. The second term is a \enquote{small sample correction} (which
will be discussed later) that comes into play whenever the confidence
interval is more than twice as wide as the equivalence range. To examine
the relation between the TOST \emph{p}-value and the SGPV we can
calculate both statistics across a range of observed effect sizes. In
Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST
procedure and the SGPV. The statistics are calculated for hypothetical
one-sample \emph{t}-tests for observed means ranging from 140 to 150 (on
the x-axis). The equivalence range is set to 145 ± 2 (i.e., an
equivalence range from 143 to 147), the observed standard deviation is
assumed to be 2, and the sample size is 30. For example, for the
left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST
\emph{p}-value is calculated for a hypothetical study with a sample size
of 30, an observed standard deviation of 2, and an observed mean of 140,
where the \emph{p}-value for the equivalence test is 1, and the SGPV is
0. Our conclusions about the relationship between TOST \emph{p}-values
and SGPV in this article are not dependent upon any specific example, as
readers can explore for themselves in an online Shiny app:
\url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV1-1.pdf}
\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
line) and SGPV (dotted grey line) across a range of observed sample
means (x-axis) tested against a mean of 145 in a one-sample
\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
\end{figure}

The SGPV treats the equivalence range as the null-hypothesis, while the
TOST procedure treats the values outside of the equivalence range as the
null-hypothesis. For ease of comparison we can reverse the SGPV (by
calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values
more easily comparable. We see that the \emph{p}-value from the TOST
procedure and the SGPV follow each other closely.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV2-1.pdf}
\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
line) and 1-SGPV (dotted grey line) across a range of observed sample
means (x-axis) tested against a mean of 145 in a one-sample
\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
\end{figure}

When the observed sample mean is 145, the sample size is 30, and the
standard deviation is 2, and we are testing against equivalence bounds
of 143 and 147 using the TOST procedure for a one-sample \emph{t}-test,
the equivalence test is significant, \emph{t}(29) = 5.48, \emph{p}
\textless{} .001. Because the 95\% CI falls completely within the
equivalence bounds, the SGPV is 1 (see Figure \ref{fig:TOSTSGPV1}). On
the other hand, when the observed mean is 140, the equivalence test is
not significant (the observed mean is far outside the equivalence range
of 143 to 147), \emph{t}(29) = -8.22, \emph{p} = 1 (or more accurately,
\emph{p} \textgreater{} .999 as \emph{p}-values are bounded between 0
and 1). Because the 95\% CI falls completely outside the equivalence
bounds, the SGPV is 0 (see Figure \ref{fig:TOSTSGPV1}).

\subsection{SGPV as a uniform measure of
overlap}\label{sgpv-as-a-uniform-measure-of-overlap}

It is clear the SGPV and the \emph{p}-value from TOST are closely
related. When confidence intervals are symmetric we can think of the
SGPV as a straight line that is directly related to the \emph{p}-value
from an equivalence test for three values. When the TOST \emph{p}-value
is 0.5, the SGPV is also 0.5 (note that the reverse is not true). The
SGPV is 50\% when the observed mean falls exactly on the lower or upper
equivalence bound, because 50\% of the symmetrical confidence interval
overlaps with the equivalence range. When the observed mean equals the
equivalence bound, the difference between the mean in the data and the
equivalence bound is 0, the \emph{t}-value for the equivalence test is
also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure
\ref{fig:TOSTSGPV3}).

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV3-1.pdf}
\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for
three example datasets that illustrate the relationship between
\emph{p}-values from TOST and SGPV.}
\end{figure}

Two other points always have to overlap. When the 95\% CI falls
completely inside the equivalence region, and one endpoint of the
confidence interval is exactly equal to one of the equivalence bounds
(see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value
(which relies on a one-sided test) is always 0.025. The third point
where the SGPV and the \emph{p}-value from the TOST procedure should
overlap is where the 95\% CI falls completely outside of the equivalence
range, but one endpoint of the confidence interval is equal to the
equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when
the \emph{p}-value will always be 0.975. Note that this situation is in
essence a \emph{minimum-effect test} (Murphy, Myors, \& Wolach, 2014).
The goal of a minimum-effect is not just to reject a difference of zero,
but to reject the smallest effect size of interest (i.e., the
equivalence bounds). The SGPV summarizes the information from an
equivalence test and a minimum-effect test. These can be two relevant
questions to ask, although it often makes sense to combine an
equivalence test and a null-hypothesis test instead (Lakens et al.,
2018).

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV4-1.pdf}
\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for
samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
\end{figure}

For example, the SGPV from A to D is 0.76, 0.81, 0.86, and 0.91. The
difference in the percentage of overlap between A and B (-0.05) is
identical to the difference in the percentage of overlap between C and D
as the mean gets 0.1 closer to the test value (-0.05). As the observed
mean in a one-sample \emph{t}-test lies closer to the test value (in
Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer
to the test value by 0.1) the difference in the overlap changes
uniformly. As we move the observed mean closer to the test value in
steps of 0.1 across A to D the \emph{p}-value calculated for normally
distributed data is not uniformly distributed. The probability of
observing data more extreme than the upper bound of 2 is (from A to D)
0.16, 0.12, 0.08, and 0.06. As we can see, the difference between A and
B (0.04) is not the same as the difference between C and D (0.03).
Indeed, the difference in \emph{p}-values is the largest as you start at
\emph{p} = 0.5 (when the observed mean falls on the test value), which
is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at
\emph{p} = 0.5. Note that where the SGPV reaches 1 or 0, \emph{p}-values
closely approximate 0 and 1, but never reach these values.

\subsection{When are the SGPV and Equivalence Test
Unrelated?}\label{when-are-the-sgpv-and-equivalence-test-unrelated}

There are three situations where \emph{p}-values from TOST and SGPV are
unrelated. The first two situations were discussed before and can be
seen in Figure \ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1
\emph{p}-values from the equivalence test fall between 0.975 and 1 or
between 0 and 0.025. Because \emph{p}-values approach 0 or 1, but are
never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics
are completely unrelated within these ranges. The easiest way to see
this is by plotting the SGPV against the \emph{p}-value from the TOST
procedure. The situations where the SPGV and \emph{p}-values from the
TOST procedure are unrelated are indicated by the parts of the curve
where there are vertical straight lines at second generation
\emph{p}-values of 0 and 1.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV5-1.pdf}
\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV1}.}
\end{figure}

A third situation in which the SGPV deviates from the TOST
\emph{p}-value is whenever the CI is wider than the equivalence range,
and the CI overlaps with the upper \emph{and} lower equivalence bound.
When the confidence interval is more than twice as wide as the
equivalence range the SGPV is set to 0.5. Blume et al. (2018) call this
the \enquote{small sample correction factor}. However, it is not a
correction in the typical sense of the word, since the SGPV is not
adjusted to any \enquote{correct} value. When the normal calculation
would be \enquote{misleading} (i.e., the SGPV would be small, which
normally would suggest support for the alternative hypothesis, but at
the same time all values in the equivalence range are supported), the
SGPV is set to 0.5 which according to Blume and colleagues signals that
the SGPV is \enquote{uninformative}. Note that the CI can be twice as
wide as the equivalence range whenever the sample size is small (and the
confidence interval width is large) \emph{or} when then equivalence
range is narrow. It is therefore not so much a \enquote{small sample
correction} as it is an exception to the typical calculation of the SGPV
whenever the ratio of the confidence interval width to the equivalence
range exceeds 2:1 and the CI overlaps with the upper and lower bounds.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV6-1.pdf}
\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
line) and SGPV (dotted grey line) across a range of observed sample
means (x-axis). Because the sample size is small (n = 10) and the CI is
more than twice as wide as the equivalence range (set to -0.4 to 0.4),
the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
observed means.}
\end{figure}

We can examine this situation by calculating the SGPV and performing the
TOST for a situation where sample sizes are small and the equivalence
range is narrow, such that the CI is more than twice as large as the
equivalence range (see Figure \ref{fig:TOSTSGPV6}). When the two
statistics are plotted against each other we can seewhere they are
unrelated (indicated by straight lines in the curve, see Figure
\ref{fig:TOSTSGPV7}). We see the SGPV is 0.5 for a range of observed
means where the \emph{p}-value from the equivalence test still varies.
It should be noted that in these calculations the \emph{p}-values for
the TOST procedure are \emph{never} smaller than 0.05 (i.e., they do not
get below 0.05 on the y-axis). In other words, we cannot conclude
equivalence based on any of the observed means. This happens because the
TOST \emph{p}-value is smaller than 0.05 only when the 90\% CI falls
completely between the upper and lower equivalence bounds. However, we
are examining a scenario where the 90\% CI is so wide that it never
falls completely within the two equivalence bounds, and thus the
equivalence test is never significant. As Lakens (2017) notes:
\enquote{in small samples (where CIs are wide), a study might have no
statistical power (i.e., the CI will always be so wide that it is
necessarily wider than the equivalence bounds).} None of the
\emph{p}-values based on the TOST procedure are below 0.05, and thus, in
the long run we have 0\% power.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV7-1.pdf}
\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV6}.}
\end{figure}

The \emph{p}-value from the TOST procedure and the SGPV are also
unrelated when the CI is wider than the equivalence range (so the
precision is low) and overlaps with the upper and lower equivalence
bound, but the CI is \emph{not} twice as wide as the equivalence range.
In the example below, we see that the CI is only 1.79 times as wide as
the equivalence bounds, but the CI overlaps with the lower and upper
equivalence bounds (Figure \ref{fig:TOSTSGPV8}). This means the SGPV is
not set to 0.5, but it is constant across a range of observed means.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV8-1.pdf}
\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the
lower and upper equivalence bound (indicated by the vertical dotted
lines).}
\end{figure}

If the observed mean would be somewhat closer to 0, or further away from
0, the SGPV remains constant (the CI width does not change, and it
completely overlaps with the equivalence range) while the \emph{p}-value
for the TOST procedure does vary. We can see this in Figure
\ref{fig:TOSTSGPV9} below. The SGPV is not set to 0.5, but is slightly
higher than 0.5 across a range of means. How high the SGPV will be for a
CI that is not twice as wide as the equivalence range, but overlaps with
the lower and upper equivalence bounds, depends on the width of the CI
and the equivalence range.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV9-1.pdf}
\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
line) and SGPV (dotted grey line) across a range of observed sample
means (x-axis). The sample size is small (n = 10), but because the sd is
half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is
less than twice as wide as the equivalence range (set to -0.4 to 0.4).
The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a
maximum slightly above 0.5 across a range of observed means.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV10-1.pdf}
\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV9}.}
\end{figure}

If we once more plot the two statistics against each other to see where
they are unrelated (indicated by straight lines in the curve), we see
the SGPV is 0.56 for a range of observed means where the \emph{p}-value
from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}). To
conclude this section, there are three situations where the
\emph{p}-value from the TOST procedure is unrelated to the SGPV. In all
these situations the \emph{p}-value for the equivalence test
differentiates tests with different means, but the SGPV does not.
Therefore, as a purely continuous descriptive statistic, the SGPV is
more limited than the \emph{p}-value from the TOST procedure.

\subsection{The relation between equivalence tests and SGPV when
confidence intervals are not
symmetrical}\label{the-relation-between-equivalence-tests-and-sgpv-when-confidence-intervals-are-not-symmetrical}

So far we have only looked at the relation between equivalence tests and
the SGPV when confidence intervals are symmetric (e.g., for confidence
intervals around mean differences). For correlations, which are bound
between -1 and 1, confidence intervals are only symmetric for a
correlation of exactly 0. The confidence interval becomes increasingly
asymmetric as the observed correlation nears -1 or 1. For example, with
ten observations, an observed correlation of 0 has a symmetric 95\%
confidence interval ranging from -0.630 to 0.630, while and observed
correlation of 0.7 has an asymmetric 95\% confidence interval ranging
from 0.126 to 0.993.

The effect of asymmetric confidence intervals is most noticable at
smaller sample sizes. In Figure \ref{fig:TOSTSGPV11} we plot the
\emph{p}-values from equivalence tests and the SGPV (again plotted as
1-SGPV for ease of comparison) for correlations. The sample size is 30
pairs of observations, and the lower and upper equivalence bounds are
set to -0.45 and 0.45, with an alpha of 0.05. As the observed
correlation in the sample moves from -1 to 0 the \emph{p}-value from the
equivalence test becomes smaller, as does 1-SGPV. The pattern is quite
similar to that in Figure \ref{fig:TOSTSGPV2}. The \emph{p}-value for
the TOST procedure and 1-SGPV are still identical when \emph{p}-values
are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted
lines). There are two important differences, however. First of all, the
SGPV is no longer a straight line, but a curve, due to the asymmetry in
the 95\% CI. Second, and most importantly, the \emph{p}-value for the
equivalence test and the SGPV do no longer overlap at \emph{p} = 0.5.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV11-1.pdf}
\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
(black line) and 1-SGPV (dotted grey curve) across a range of observed
sample correlations (x-axis) tested against equivalence bounds of r =
-0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
\end{figure}

The reason that the equivalence test and SGPV no longer overlap is also
because of asymmetric confidence intervals. If the observed correlation
falls exactly on the equivalence bound the \emph{p}-value for the
equivalence test indicates that the probability of observing the
observed or more extreme data, assuming the equivalence bound is the
true effect size, is 50\%. In other words, if the true effect size is
the same as the equivalence bound, it is equally likely to find an
effect more extreme than the equivalence bound, as it is to observe an
effect that is less extreme than the equivalence bound. However, as can
be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation
\emph{p}-values associated with the observed correlations at r = -0.45
and r = 0.45 are larger than 50\%. Because the confidence intervals are
asymmetric around the observed effect size of 0.45 (ranging from 0.11 to
0.70) according to Blume et al. (2018) 58.11\% of the data-supported
hypotheses are null hypotheses, and therefore 58.10\% of the
data-supported hypotheses are compatible with the null premise.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV12-1.pdf}
\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the
confidence interval for r = 0 is symmetric.}
\end{figure}

This example illustrates the difference between a proportion and a
probability. There is always a 50\% probability of observing a
correlation smaller or larger than the true correlation, but the SGPV
for this situation depends on how far away the observed correlation is
from 0. The further away from 0, the larger the SGPV when the observed
mean falls on the equivalence bound. The SGPV is the proportion of
values in a 95\% confidence interval that overlap with the equivalence
range, but not the probability that these values will be observed. In
the most extreme case (i.e., a sample size of 4, and equivalence bounds
set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\%
of the confidence interval overlaps with the equivalence range, even
though in the long run only 50\% of the correlations observed in the
future will fall in this range. It should be noted that in larger sample
sizes the SGPV is closer to 0.5 whenever the observed correlation falls
on the equivalence bound, but this extreme example nevertheless clearly
illustrates the difference between question the SGPV answers, and the
question a \emph{p}-value answers. The conclusion of this section on
asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
TOST procedure are always directly related at these values. Although
Blume et al. (2018) state that \enquote{the degree of overlap conveys
how compatible the data are with the null premise} this definition of
what the SGPV provides does not hold for asymmetric confidence
intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV
between 0 and 1 is not interpretable as \enquote{compatibility with the
null hypothesis}. Indeed, Blume and colleagues write in the supplemental
material that \enquote{The magnitude of an inconclusive
second-generation \emph{p}-value can vary slightly when the effect size
scale is transformed. However definitive findings, i.e.~a \emph{p}-value
of 0 or 1 are \emph{not} affected by the scale changes.}

\subsection{What are the Relative Strengths and Weaknesses of
Equivalence Testing and the
SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}

When introducing a new statistical method, it is important to compare it
to existing approaches and specify it's relative strengths and
weaknesses. First of all, the SGPV is a descriptive statistic (unlike
the \emph{p}-value that is calculated for an equivalence test, which is
an inferential statistic) that provides the proportion of overlap of the
confidence interval and the equivalence range. Even though a SGPV of 1
or 0 has a clear interpretation (we can reject effects outside or inside
the equivalence range), intermediate values are not as easy to interpret
(especially for effects that have asymmetric confidence intervals). In
one sense, they are what they are (the proportion of overlap), but it
can be unclear what this number tells us about the data we have
collected. This is not too problematic, since the main use of the SGPV
(e.g., in all examples provided by Blume and colleagues) seems to be to
examine whether the SGPV is 0, 1, or inconclusive. This interpretation
of a SGPV as allowing researchers to reject the null, reject the
presence of a meaningful effect, or remaining inconclusive is very
similar to the Neyman-Pearson interpretation of combining a
null-hypothesis test and an equivalence test (Lakens et al., 2018). The
difference is that where a SGPV of 1 can be interpreted as \emph{p}
\textless{} .025, equivalence tests provide exact \emph{p}-values, and
they continue to differentiate between for example \emph{p} = 0.048 and
\emph{p} = 0.002. Whether this is desirable depends on the perspective
that is used. From a Neyman-Pearson perspective on statistical
inferences the main conclusion is based on whether or not
\(p < \alpha\), and thus an equivalence test and SGPV can be performed
by simply checking whether the confidence interval falls within the
equivalence range, just as a null-hypothesis test can be performed by
checking whether the confidence interval contains zero or not. At the
same time, it is recommended to report exact \emph{p}-values (American
Psychological Association, 2010), and exact \emph{p}-values might
provide information of interest to readers about how precisely how
surprising the data is under the null model. Equivalence tests combined
with null-hypothesis significance tests also allow researchers to
conclude an effect is significant \emph{and} equivalent (i.e.,
statistically different from zero, but also too small to be considered
meaningful). Thus, the SGPV is used to classify results into one of
three possible categories (with the data falling inside or outside the
equivalence range, or being inconclusive), while equivalence tests
combined with null-hypothesis tests classify results into four possible
categories.

An important issue when calculating the SGPV is its reliance on the
\enquote{small sample correction}, where the SGPV is set to 0.5 whenever
the ratio of the confidence interval width to the equivalence range
exceeds 2:1 and the CI overlaps with the upper and lower bounds. This
exception to the normal calculation of the SGPV is introduced to prevent
misleading values. Without this correction it is possible that a
confidence interval is extremely wide, and an equivalence range is
extremely narrow, which without the correction would lead to a very low
value for the SGPV. Blume et al. (2018) suggest that under such a
scenario \enquote{the data favor alternative hypotheses}, even when a
better interpretation would be that there is not enough data to
accurately estimate the true effect compared to the width of the
equivalence range. Although it is necessary to set the SGPV to 0.5
whenever the ratio of the confidence interval width to the equivalence
range exceeds 2:1, it leads to a range of situations where the SGPV is
set to 0.5, while the \emph{p}-value from the TOST procedure continues
to differentiate (see for example Figure \ref{fig:TOSTSGPV6}). An
important benefit of equivalence tests is that is does not need such a
correction to prevent misleading results.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV13-1.pdf}
\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
(black line) and 1-SGPV (dotted grey curve) across a range of observed
sample correlations (x-axis) tested against equivalence bounds of r =
0.4 and r = 0.8 with n = 10 and an alpha of 0.05.}
\end{figure}

As a more extreme example of the peculiar behavior of the \enquote{small
sample correction} as currently implemented in the calculation of the
SGPV see Figure \ref{fig:TOSTSGPV13} below. In this figure observed
correlations (from a sample size of 10) from -1 to 1 are tested against
an equivalence range from r = 0.4 to r = 0.8. We can see the SGPV has a
peculiar shape because it is set to 0.5 for certain observed
correlations, even though there is no risk of a misleading SGPV in this
range. This example suggests that the current implementation of the
\enquote{small sample correction} could be improved. If, on the other
hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it
might be preferable to simply never apply the \enquote{small sample
correction}.

Blume et al. (2018) argue that the SGPV has improved error control, in
that the conclusion that the 95\% confidence interval lies completely
outside the equivalence range around zero will necessarily occur less
frequently than a Type I error in a null-hypothesis test (where the 95\%
confidence interval only needs to not overlap with zero). However, the
SGPV has a \emph{lower} error rate than a null-hypothesis test, not a
\emph{more accurate} error rate. In a Neyman-Pearson perspective (which
forms the basis of equivalence tests) the goal is not to end up with an
error rate that is as low as possible (to achieve that, one simply
adjusts the alpha level), but with a decision procedure that, when
applied, yields a desired error rate with high accuracy. We show here
that the SGPV and equivalence tests are directly related, and so are
their error rates. The TOST procedure uses a 90\% confidence interval
because it is based on two \emph{one-sided} tests, and thus the
confidence interval is 1-2*\(\alpha\), and because both tests need to be
significant to conclude equivalence, no adjustment for multiple
comparisons is needed. The TOST procedure always has higher power to
declare equivalence than the SGPV, which relies on a 95\% confidence
interval (but note that there is no reason to always set the alpha level
to 0.05).

Blume et al. (2018) claim that \enquote{Adjustments for multiple
comparisons are obviated} (p.~15) and that \enquote{second-generation
\emph{p}-values provide a proper scientific adjustment for multiple
comparisons}. However, this is not correct. With a sufficient number of
looks error rates can rise above the nominal alpha level (both when
compared to equivalence and minimal effect tests, but even when compared
to a null-hypothesis test). When directly comparing equivalence tests
and the SGPV, multiple comparisons inflate the probability that one
erronously concludes there is \emph{no} effect, where there \emph{is} a
true effect size that equals the equivalence bound, just as quickly for
the SGPV as for equivalence tests, because they are directly related. To
conclude, the idea that the SGPV improves error rates does not hold up
under closer scrutiny, and the recommendation to ignore adjustments for
multiple comparisons has the potential to increase false positives in
the literature. Equivalence tests provide an easier and more formal way
to control both Type I error rates (by setting the alpha level) and the
Type II error rate (by performing an a-priori power analysis).

\section{Conclusion}\label{conclusion}

We believe that our explanation of the similarities between the TOST
procedure and the SGPV provides context to interpret the contribution of
second generation \emph{p}-values to the statistical toolbox. The
novelty of the SGPV lies in its use as a descriptive statistic, but this
use can be limited when confidence intervals are asymmetrical or wider
than the equivalence range. There are strong similarities with
\emph{p}-values from the TOST procedure, and in all situations where the
statistics yield different results, the behavior of the \emph{p}-value
from the TOST procedure is more consistent and easier to interpret. We
hope this overview of the relationship between the SGPV and equivalence
tests will help researchers to make an informed decision about which
statistical approach provides the best answer to their question. Our
comparisons show that when proposing alternatives to null-hypothesis
tests, it is important to compare new proposals to already existing
procedures. We believe equivalence tests achieve the goals of the second
generation \emph{p}-value while allowing users to more easily control
error rates, and while yielding more consistent statistical outcomes.

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-american_psychological_association_publication_2010}{}
American Psychological Association (Ed.). (2010). \emph{Publication
manual of the American Psychological Association} (6th ed.). Washington,
DC: American Psychological Association.

\hypertarget{ref-blume_second-generation_2018}{}
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
(2018). Second-generation p-values: Improved rigor, reproducibility, \&
transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
e0188299.
doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\hypertarget{ref-hauck_new_1984}{}
Hauck, D. W. W., \& Anderson, S. (1984). A new statistical procedure for
testing equivalence in two-group comparative bioavailability trials.
\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1),
83--91.
doi:\href{https://doi.org/10.1007/BF01063612}{10.1007/BF01063612}

\hypertarget{ref-kruschke_rejecting_2018}{}
Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in
Bayesian Estimation. \emph{Advances in Methods and Practices in
Psychological Science}, 2515245918771304.
doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}

\hypertarget{ref-lakens_equivalence_2017}{}
Lakens, D. (2017). Equivalence Tests: A Practical Primer for t Tests,
Correlations, and Meta-Analyses. \emph{Social Psychological and
Personality Science}, \emph{8}(4), 355--362.
doi:\href{https://doi.org/10.1177/1948550617697177}{10.1177/1948550617697177}

\hypertarget{ref-lakens_equivalence_2018}{}
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing
for Psychological Research: A Tutorial. \emph{Advances in Methods and
Practices in Psychological Science}, 2515245918770963.
doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}

\hypertarget{ref-meyners_equivalence_2012}{}
Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and
Preference}, \emph{26}(2), 231--245.
doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}

\hypertarget{ref-murphy_statistical_2014}{}
Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
power analysis: A simple and general model for traditional and modern
hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
Francis Group.

\hypertarget{ref-quertemont_how_2011}{}
Quertemont, E. (2011). How to Statistically Show the Absence of an
Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127.
doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}

\hypertarget{ref-rogers_using_1993}{}
Rogers, J. L., Howard, K. I., \& Vessey, J. T. (1993). Using
significance tests to evaluate equivalence between two experimental
groups. \emph{Psychological Bulletin}, \emph{113}(3), 553--565.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/0033-2909.113.3.553}{http://dx.doi.org/10.1037/0033-2909.113.3.553}

\hypertarget{ref-schuirmann_comparison_1987}{}
Schuirmann, D. J. (1987). A comparison of the two one-sided tests
procedure and the power approach for assessing the equivalence of
average bioavailability. \emph{Journal of Pharmacokinetics and
Biopharmaceutics}, \emph{15}(6), 657--680.

\hypertarget{ref-serlin_rationality_1985}{}
Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological
research: The good-enough principle.

\hypertarget{ref-spiegelhalter_bayesian_1994}{}
Spiegelhalter, D. J., Freedman, L. S., \& Parmar, M. K. (1994). Bayesian
approaches to randomized trials. \emph{Journal of the Royal Statistical
Society. Series A (Statistics in Society)}, 357--416.
doi:\href{https://doi.org/10.2307/2983527}{10.2307/2983527}

\hypertarget{ref-wellek_testing_2010}{}
Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence
and noninferiority} (2nd ed.). Boca Raton: CRC Press.

\hypertarget{ref-westlake_use_1972}{}
Westlake, W. J. (1972). Use of Confidence Intervals in Analysis of
Comparative Bioavailability Trials. \emph{Journal of Pharmaceutical
Sciences}, \emph{61}(8), 1340--1341.
doi:\href{https://doi.org/10.1002/JPS.2600610845}{10.1002/JPS.2600610845}

\end{document}

### 2018-08-28 manuscript.tex
submission

@@
 
+ % Line numbering
+  \usepackage{lineno}
+  \linenumbers
+
 \usepackage{tikz} % Variable definition to generate author note
@@
 To test predictions researchers predominantly rely on null-hypothesis
-tests. This statistical approach can be used to examine whether observed
-data is sufficiently surprising under the null hypothesis to reject an
-effect that equals exactly zero. Null-hypothesis tests have an important
+tests.\\
+This statistical approach can be used to examine whether observed data
+is sufficiently surprising under the null hypothesis to reject an effect
+that equals exactly zero. Null-hypothesis tests have an important
 limitation, in that this procedure can only reject the hypothesis that
@@
 performed, one can also conclude equivalence by checking whether the
-1-2\(\times\)alpha confidence interval (e.g., when the alpha level is
-0.05, a 90\% CI) falls completely within the equivalence bounds. Because
-both equivalence tests as the SGPV are based on whether and how much a
-confidence interval overlaps with equivalence bounds, it seems
+1-2\(\times\)\(\alpha\) confidence interval (e.g., when the alpha level
+is 0.05, a 90\% CI) falls completely within the equivalence bounds.
+Because both equivalence tests as the SGPV are based on whether and how
+much a confidence interval overlaps with equivalence bounds, it seems
 worthwhile to compare the behavior of the newly proposed SGPV to
@@
 the \emph{p}-value will always be 0.975. Note that this situation is in
-essence a \emph{minimum-effect test} (Murphy, Myors, \& Wolach, 2014).
-The goal of a minimum-effect is not just to reject a difference of zero,
-but to reject the smallest effect size of interest (i.e., the
-equivalence bounds). The SGPV summarizes the information from an
-equivalence test and a minimum-effect test. These can be two relevant
-questions to ask, although it often makes sense to combine an
-equivalence test and a null-hypothesis test instead (Lakens et al.,
-2018).
+essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal
+of a minimum-effect is not just to reject a difference of zero, but to
+reject the smallest effect size of interest (i.e., the equivalence
+bounds). The SGPV summarizes the information from an equivalence test
+and a minimum-effect test. These can be two relevant questions to ask,
+although it often makes sense to combine an equivalence test and a
+null-hypothesis test instead (Lakens et al., 2018).
 
@@
 equivalence range (see Figure \ref{fig:TOSTSGPV6}). When the two
-statistics are plotted against each other we can seewhere they are
+statistics are plotted against each other we can see where they are
 unrelated (indicated by straight lines in the curve, see Figure
@@
 less than twice as wide as the equivalence range (set to -0.4 to 0.4).
-The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a
+The SGPV is not set to 0.5 (horizontal light grey line) but reaches a
 maximum slightly above 0.5 across a range of observed means.}
 \end{figure}
+
+If we once more plot the two statistics against each other to see where
+they are unrelated (indicated by straight lines in the curve), we see
+the SGPV is 0.56 for a range of observed means where the \emph{p}-value
+from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
-If we once more plot the two statistics against each other to see where
-they are unrelated (indicated by straight lines in the curve), we see
-the SGPV is 0.56 for a range of observed means where the \emph{p}-value
-from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}). To
-conclude this section, there are three situations where the
+To conclude this section, there are three situations where the
 \emph{p}-value from the TOST procedure is unrelated to the SGPV. In all
@@
 the most extreme case (i.e., a sample size of 4, and equivalence bounds
-set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\%
+set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
 of the confidence interval overlaps with the equivalence range, even
@@
 When introducing a new statistical method, it is important to compare it
-to existing approaches and specify it's relative strengths and
+to existing approaches and specify its relative strengths and
 weaknesses. First of all, the SGPV is a descriptive statistic (unlike
@@
 peculiar shape because it is set to 0.5 for certain observed
-correlations, even though there is no risk of a misleading SGPV in this
-range. This example suggests that the current implementation of the
-\enquote{small sample correction} could be improved. If, on the other
-hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it
-might be preferable to simply never apply the \enquote{small sample
-correction}.
+correlations, even though there is no risk of a \enquote{misleading}
+SGPV in this range. This example suggests that the current
+implementation of the \enquote{small sample correction} could be
+improved. If, on the other hand, the SGPV is mainly meant to be
+interpreted when it is 0 or 1, it might be preferable to simply never
+apply the \enquote{small sample correction}.
 
@@
 because it is based on two \emph{one-sided} tests, and thus the
-confidence interval is 1-2*\(\alpha\), and because both tests need to be
-significant to conclude equivalence, no adjustment for multiple
-comparisons is needed. The TOST procedure always has higher power to
-declare equivalence than the SGPV, which relies on a 95\% confidence
-interval (but note that there is no reason to always set the alpha level
-to 0.05).
+confidence interval is 1-2\(\times\)\(\alpha\), and because both tests
+need to be significant to conclude equivalence, no adjustment for
+multiple comparisons is needed. The TOST procedure always has higher
+power to declare equivalence than the SGPV, which relies on a 95\%
+confidence interval (but note that there is no reason to always set the
+alpha level to 0.05).
 

### 2018-08-28 manuscript.Rmd
submission

@@
   To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
-Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interepreted as a statistically significant difference.
+Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interpreted as a statistically significant difference.
 We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the more established Two One-Sided Tests (TOST) equivalence testing procedure [@schuirmann_comparison_1987].
@@
 If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
-Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2$\times$alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
+Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2$\times$$\alpha$ confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds.
 Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
@@
 Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
+
 ```{r, include=FALSE}
@@
 ```
+
 When the observed sample mean is 145, the sample size is 30, and the standard deviation is 2, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r round(tost_res1$TOST_t1, digits = 2)`, *p* < .001.
@@
 The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975.
-Note that this situation is in essence a *minimum-effect test* [@murphy_statistical_2014].
+Note that this situation is in essence a minimum-effect test [@murphy_statistical_2014].
 The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
@@
 ```
+
 For example, the SGPV from A to D is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
@@
 The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
+
 ```{r, include=FALSE}
@@
 ```
+
 ```{r, TOSTSGPV5, fig.cap="The relationship between *p*-values from the TOST procedure and the SGPV for the same scenario as in Figure \\ref{fig:TOSTSGPV1}."}
@@
 ```
+
 ```{r, TOSTSGPV6, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
-Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means."}
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal light grey line) across a range of observed means."}
 plot(NA, 
@@
 We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
-When the two statistics are plotted against each other we can seewhere they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+When the two statistics are plotted against each other we can see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
+
 ```{r, include=FALSE}
@@
 ```
+
 ```{r, TOSTSGPV8, fig.cap="Example of a 95% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines)."}
@@
 How high the SGPV will be for a CI that is not twice as wide as the equivalence range, but overlaps with the lower and upper equivalence bounds, depends on the width of the CI and the equivalence range.
+
 ```{r, include=FALSE}
@@
 ```
+
 ```{r, TOSTSGPV9, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
 The sample size is small (n = 10), but because the sd is half as big as in Figure \\ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
-The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means."}
+The SGPV is not set to 0.5 (horizontal light grey line) but reaches a maximum slightly above 0.5 across a range of observed means."}
 plot(NA, 
@@
 ```
+
+If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
-If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 To conclude this section, there are three situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
@@
 
-The effect of asymmetric confidence intervals is most noticable at smaller sample sizes.
+The effect of asymmetric confidence intervals is most noticeable at smaller sample sizes.
 In Figure \ref{fig:TOSTSGPV11} we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
@@
 lines(p_tost_list, lwd = 3)
-# abline(h = c(0.975, 0.5, 0.025),
-#        lty = 2,
-#        col = "grey")
+abline(h = c(0.975, 0.5, 0.025),
+       lty = 2,
+       col = "grey")
 
@@
 segments(LL95_r3,0.2,UL95_r3,0.2, lwd=2)
-```
-
-```{r, include=FALSE}
-#Example illustrating the most extreme case. 
-low_eqbound_r = -0.99
-high_eqbound_r = 0.99
-
-res<-TOSTr(n = 4,
-           r = 0.99,
-           low_eqbound_r = low_eqbound_r,
-           high_eqbound_r = high_eqbound_r,
-           alpha = .05,
-           plot = TRUE,
-           verbose = TRUE)
-sgpv <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
-sgpv
 ```
@@
 
+```{r, include=FALSE}
+#Example illustrating the most extreme case. 
+low_eqbound_r = -0.99
+high_eqbound_r = 0.99
+
+res<-TOSTr(n = 4,
+           r = 0.99,
+           low_eqbound_r = low_eqbound_r,
+           high_eqbound_r = high_eqbound_r,
+           alpha = .05,
+           plot = TRUE,
+           verbose = TRUE)
+sgpv <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+sgpv
+```
+
 ##What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
 
-When introducing a new statistical method, it is important to compare it to existing approaches and specify it's relative strengths and weaknesses.
+When introducing a new statistical method, it is important to compare it to existing approaches and specify its relative strengths and weaknesses.
 First of all, the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
@@
 lines(p_tost_list, lwd = 3)
-#abline(h = c(0.975, 0.5, 0.025),
-#       lty = 2,
-#       col = "grey")
+abline(h = c(0.975, 0.5, 0.025),
+       lty = 2,
+       col = "grey")
 ```
@@
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
-We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a misleading SGPV in this range.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a 'misleading' SGPV in this range.
 This example suggests that the current implementation of the 'small sample correction' could be improved.
@@
 We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
-The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2*$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
+The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2$\times$$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
 The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).

### 2018-08-28 manuscript.tex
submission

@@
 
- % Line numbering
-  \usepackage{lineno}
-  \linenumbers
-
 \usepackage{tikz} % Variable definition to generate author note
@@
 to matter, and prevents practically insignificant effects from being
-interepreted as a statistically significant difference. We compare the
+interpreted as a statistically significant difference. We compare the
 behavior of the recently proposed second generation \emph{p}-value
@@
 more than twice as wide as the equivalence range (set to -0.4 to 0.4),
-the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
+the SGPV is set to 0.5 (horizontal light grey line) across a range of
 observed means.}
@@
 
-The effect of asymmetric confidence intervals is most noticable at
+The effect of asymmetric confidence intervals is most noticeable at
 smaller sample sizes. In Figure \ref{fig:TOSTSGPV11} we plot the

### 2018-08-28 manuscript.Rmd

@@
   To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
-Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interpreted as a statistically significant difference.
+Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interepreted as a statistically significant difference.
 We compare the behavior of the recently proposed second generation *p*-value [@blume_second-generation_2018] with the more established Two One-Sided Tests (TOST) equivalence testing procedure [@schuirmann_comparison_1987].
@@
 footnotelist      : no
-lineno            : no
+lineno            : yes
 mask              : no
@@
 ```{r, TOSTSGPV6, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
-Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal light grey line) across a range of observed means."}
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means."}
 plot(NA, 
@@
 
-The effect of asymmetric confidence intervals is most noticeable at smaller sample sizes.
+The effect of asymmetric confidence intervals is most noticable at smaller sample sizes.
 In Figure \ref{fig:TOSTSGPV11} we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.

### 2018-08-28 manuscript.tex
pre-print submission

@@
 more than twice as wide as the equivalence range (set to -0.4 to 0.4),
-the SGPV is set to 0.5 (horizontal light grey line) across a range of
+the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
 observed means.}

### 2019-03-08 reply_to_reviews.R1.Rmd
First complete reply to review DL.

---
title             : "Reply to Reviews"
shorttitle        : "Reply R1"

author:
  - name          : "Dani&euml;l Lakens"
    affiliation   : "1"
    corresponding : yes
    address       : "Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
  - name          : "Marie Delacre"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology, Eindhoven, The Netherlands"
  - id            : "2"
    institution   : "Service of Analysis of the Data, Université Libre de Bruxelles, Belgium"

abstract: |
  We respond to all the comments raised by the two reviewers and the editors. We would like to thank the editor and reviewers for their suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct. We feel we were able to accomodate all suggestions, and we hope you think our submission is ready to be accepted for publication in Meta-Psychology.

bibliography      : ["TOST_vs_SGPV.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("TOSTER")
library("papaja")
```

```{r load code, include=FALSE}
#source("functions/TOST_to_SGPV.R")
#source("functions/p_delta_function.R")
```

Dear editor,

Thank you for your comments on our submitted manuscript. We have incorporated your three comments:

1. We moved the first sentence on page 3 into the next paragraph (well spotted).
2. The code for the Shiny app was on GitHub, and the GitHub repository is linked to the OSF project page, but we have added a component to the OSF page and also directly added the Shiny App code there to make it easier to find: https://osf.io/7f8uq/
3. We now immediately refer to Figure 4 in the beginning of the paragraph in which the Figure is described.

We will respond to the points raised by both reviewers in turn.

# Reply to Reviewer 1

1. We have changed the part of the sentence "Our conclusions about the relationship between TOST p-values and SGPV in this article are not dependent upon any specific example" into "Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.". We mainly intended to refer to our conclusion that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values" namely p = 0.5 for TOST when the SGPV will be 0.5, and the p-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1). We have now made it clearer that when we talk about 'correspondence between TOST *p*-values and the SGPV', we mean that there is a direct relation between three points.

2. We appreciate correcting our use of the term 'unrelated' and teaching us the word 'bijective'. We used the word 'unrelated' somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST *p*-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST p-value differs across this range of means. We now just directly say what we originally meant, and no longer use the word 'unrelated'. For example, "There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate." and "While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value)." and similarly "A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound."

3. Please do not feel like you ever need to apologize for having formal training we lack, that allows you to point out whenever we make formally incorrect statements. This is exactly why we submit our work for peer review - to be able to improve it based on feedback from experts. We now preface the sentence with "As long as data is normally distributed,". We follow your recommendation throughout to not generalize beyond the scenarios we study. In the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." See also point 5 below.

4. After making the change at point 2 above, we now think the sentence "The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p < 0:025 or p > 0:975 in an equivalence test, since the SGPV and p-value for the TOST
procedure are always directly related at these values." should no longer be confusing. To make the sentence clearer, we have changed "these values" into "at the values p = 0.025 and p = 0.975" It should now be clear the sections are not contradictory - TOST differentiates below p < 0.025, when the SGPV is 1 for all p < 0.025.

5. We agree that is unclear whether the original statement by Blume et al that "the degree of overlap conveys how compatible the data are with the null premise" holds in general. We have now amended the sentence to read: "Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data requires further examination."

6. We have removed our earlier statements that the SGPV only works as a descriptive statistic. We deleted the sentence "the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range." and deleted "The novelty of the SGPV lies in its use as a descriptive statistic" from the conclusion. Indeed, we acknowledge that "Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as “compatibility with the null hypothesis”." So the SGPV is an inferential statistic when interpreted dichotomously. We will leave our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should be interpreted to future researchers, and we do not make any statements about whether such values are descriptive our inferential.

7. We agree that using TOST for small samples (e.g., N = 4) will not be useful. Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.

8. With our recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions. An additional change not mentioned above is that we renamed the section on asymmetric confidence intervals to the more specific "The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations" instead of the more general "The relation between equivalence tests and SGPV when confidence intervals are not symmetrical". We appreciate the very positive evaluation of our manuscript, but even more so the criticism which allowed us to improve the manuscript.

# Reply to Reviewer 2

Before listing major points, the reviewer raises the point that we compare SGPV with p-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:

"Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant and equivalent (i.e., statistically different from zero, but also too small to be considered meaningful). Thus, the SGPV is used to classify results into one of three possible categories (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories."

The reviewer says that "the authors suddenly switch the premise; now the SGPV should be replaced by two p-values, one from an equivalence test and one from a NHST". However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all. In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7):

"The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975. Note that this
situation is in essence a minimum-effect test (Murphy, Myors, & Wolach, 2014). The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds). The SGPV summarizes the information from an equivalence test and a minimum-effect test."

One might argue that we suggest to replace the SGPV with two tests. However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound. When the TOST *p*-value is 0.975, the 95% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range. This is mathematically identical to a statistically significant minimum effect test at p < 0.05. We didn't make this explicit, but we clearly should have. We have added the sentence (on page 7):

"An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test."

One might wonder why then, on page 20, why we introduce the idea to perform both a null-hypothesis significance test and an equivalence test. We were not clear enough. And indeed, the sentence "This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test" was simply confusing. We have deleted this sentence and replaced it with "As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary)."

Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test. Part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests. But that is not what we propose. Werewrote the paragraph:

"Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test. This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected. Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant and equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see (Lakens et al., 2018))."

We hope this makes it clear we are not pulling a bait and switch. The SGPV is strongly related to an equivalence test (or it's complement, a minimum effect test). Describing the relation between the SGPV and TOST is our main contribution. We just wanted to mention that researchers might want to combine an equivalence test with a NHST, because in the literature, this is a question we see many psychologists ask.

We will now discuss the major points in turn.

1. In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." After all, p-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior. Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals). We look forward to future papers that illustrate the SGPV with other interval estimates and are happy to add the limitation to continuous normally distributed data in our article. Note that we did not add that the correspondence only holds for situations where the SE's are small compared to the width of the equivalence range, as the reviewer suggests.

2. The reviewer repeats that the correspondence only holds when SE's are small compared to the width of the equivalence range. The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9). We clearly state that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the p-value from an equivalence test for three values." This correspondence is not dependent upon the SE's. It will always hold for continuous normal data. The reviewer says that "The paper does not provide theoretical justification for this connection nor any proofs." We are unsure which proof is needed for the overlap between the three points, since it is rather trivial and we believe the explanation in the paper is very clear.

For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range. When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the p-value is 0.5 (situation A, Figure 3). Two other points always have to overlap. When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST p-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1. The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975, and the SGPV is 0.

We do not think we can provide any other proof for this. A confidence interval and a p-value are directly related. The TOST procedure is a test using the confidence interval, and the SGPV (now that we clearly limited our discussion to a SGPV based on a confidence interval calculated from continuous normal data) compared against the same equivalence bounds will be related as we describe. But we believe our article might not have been clear enough about that we limit our discussion about the correspondence of the curves to these 3 points. Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9, 13). Nevertheless, in these graphs, we still have the correspondence between these 3 points (or at leas tthe 2 points if the CI is too wide compared to the equivalence bounds to ever observe a *p* = 0.025). To make it clearer that we talk about the overlap in these 3 critical points, we have added:

"When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1. These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5). These three points of overlap are indicated by the horizontal dotted lines in Figure 2."

We believe this satisfactorily addresses the point by the reviewer that "Because of this
lack of discussion, the reader can easily miss that the close correspondence only occurs when
the sample size is large enough that the standard error is very small relative to the width of the
equivalence zone." Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a p-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.

3. We are aware of the Beger and Hsu (1996) article. But if the reviewer reads more closely, it should be clear that we never say the TOST is UMP. We say that TOST is a test procedure that aims to control error rates - our use of the term 'Neyman-Pearson perspective' refers to the classic difference between significance tests (Fisher) and hypothesis tests (Neyman-Pearson). We do not imply that any test that fixes an error rate is a NP test. Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of p-values, we are simply adding a 'Neyman-Pearson' approach in the text to explain that "From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not." We believe this is a correct use of the term 'Neyman-Pearson perspective on statistical inferences'.

4. We tried to find the passage the reviewer refers to when he writes "In light of this, the assertion without proof that classical p-values provide more or better assessments of the “evidence” appear out of place." but we could not. We do not use the word 'evidence' in the text (because neither the p-value from TOST nor the SGPV are measures of 'evidence' - we fully agree with BLume et al., 2018, in this respect). We also do not say the p-value is 'naturally informative'. Indeed, related to point 3 above, we tried to be consistent in interpreting the TOST procedure from a Neyman-Pearson perspective, and focus on error control. So we regrettably do not know how to incorporate this point.

5. We fully agree with the reviewer on point 5 that "The maximum Type I Error rate for the SGPV over the null
interval is 5%, exactly like the TOST test." Indeed, given the direct overlap between the TOST *p*-value and the SGPV at *p* = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical. This is why we were so surprised when Blume et al (2018) write "They control the Type I error naturally, forcing it to zero as the sample size grows. This, in turn, offsets Type I Error inflation that results from multiple comparisons or multiple examinations of accumulating data. Findings identified by second-generation p-values are less likely to be false discoveries than findings identified by classical p-values. Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons." Clearly, it can not both be true that the the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.

The editor asks us to better substantiate the frequency claims for the comparison of TOST and SGPV, but since the SGPV and TOST *p*-value are directly related (a TOST *p* < 0.025 = a SGPV of 1) we do not think any additional substantiation is possible, especially since the reviewer agrees that (as long as confidence intervals are used to calculate the SGPV, which we now clearly limit our conclusions to) "The maximum Type I Error rate for the SGPV over the null interval is 5%, exactly like the TOST test".

Nevertheless, we agree this discussion was a bit too extensive. Given my own fondness of error control in statistical inferences, I get worried if researchers suggest we can ignore it, especially when making multiple comparisons. Imagine people start to use the SGPV instead of the TOST procedure whenever they perform 20 tests, and then argue they do not need to correct for multiple comparison - I think we can all agree this is undesireable! We have reduced the two paragraphs to one hopefully clear statement about the need to control error rates, also when using the SGPV. We hope this addresses the concerns by the editor as well as the reviewer, while still making an important point in the literature about the need to control error rates (if one cares about drawing incorrect conclusions).

@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p. 15). However, this is not correct. Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests. Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.

6. We have removed this section while addressing point 5 above, and thus incorporated the reviewers'suggestion to remove these statements.

7. We have not removed the paragraph about multiple comparisons, as the reviewer asks, but we have simplified our treatment of it. We do not need any other argument to make our claims about multiple comparisons that fact, noted by the reviewer, that "The maximum Type I Error rate for the SGPV over the null interval is 5%, exactly like the TOST test." This is true, and it logically follows (hence, no mathematical proof is needed) that error rates need to be controlled when using SGPV to conclude support for the null-hypothesis. We blieve error control is important enough to include this paragraph in the paper, as we believe that lack of error control was one of the  causes of the replication crisis in psychology.

8. We thank the reviewer for this comment. Indeed, to calculate confidence intervals around a correlation, the Fisher's z-transformation is used, which is approximately normally distributed, and symmatric CI are calculated. When transforming these confidence intervals back to correlations, they become asymmetric. We have added to the text: "Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally distributed, which allows one to compute symmetric confidence intervals, which are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero." This is simply one example of a general effect mentioned in Blume et al (2018), which we already cited in the main text: "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e. a *p*-value of 0 or 1 are *not* affected by the scale changes."

Minor Concerns:

1. We added ",or more extreme data,"

2. This text was deleted (see major point 5 above)

3. We see how "reverse the SGPV" might have been confusing. We did not mean to imply to reverse the null and alternative. We now just say that we plot 1-SGPV (which is what we incorrectly tried to express with "reverse").

4. The issue of the SGPV needing a 'correction' by setting it to 0.5 is not related to the fact that large *p*-values are not evidence for the null. The *p*-value is behaving as it is intended to, without any correction. A high p-value is not a 'misleading result' - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing). We therefore did not incorporate this point.

5. In line with comments by reviewer 1, we removed statemetns about SGPV not being inferential, thereby solving the issue reviewer 2 raised.

6. In line with major point 8, we added information that asymmetric condifence intervals around a correlation are symmetric when Fisher z-transformed. This is just an example of what Blume et al (2018) refer to when they write "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e. a *p*-value of 0 or 1 are *not* affected by the scale changes." We beieve this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that "The asymmetric CI case is very interesting"). We have made our point less general, now only talking about correlations, by changing the title of this section into "The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations". The reviewer is correct confidence intervals can be created in many difference ways (e.g., with holes in the middle), but for this paper, we just focus on one specific case now, which we believe might be closest to what researchers would use in real life, the confidence interval around a correlation.

7. It is a well-known fact that the TOST can have 0 power (and indeed, this is one of the main issues in the Perlman and Wu (1999) paper the reviewer cited). As explained in Lakens (2017): "It is important to take statistical power into account when determining the equivalence bounds because, in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds)." We agree with the reviewer it is not interesting to do a test if you have 0 power. People should design informative experiments by doing an a-priori power analysis. Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study. Not that the exact same issue applies to the SGPV. It is also possible to have 0 power for the SGPV - so we do not understand why the reviewer is so surprised about this. The question "Why use the TOST test then?" equally applies to "Why use the SGPV then?" if you, from the outset, know that the 'small sample correction' will lead to a SGPV of 0.5.

8. We do not see how setting the SGPV to 0.5 'shrinks' an estimate to some value. Regardless of how correction factors are applied in statistics, we are trying to educate our readers about what the 'small sample correction' does. We believe our readers will associate 'correction' with 'correcting', and want to explain that the SGPV is not set to a 'correct' value. We are not talking about statistical terms here - we are warning the reader to not interpret 'correction' in terms of normal language use. This is similar to warning readers that 'significant' does not have the normal language connotation of 'important'. We have therefore kept our original sentence.

As a final comment, altough not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an "outright ban of TOST". The best summary of this discussion (of which Perlman & Wu is one contribution) can be found in Meyners (2012), which we cited. The discussion has different arguments, and Meyners draws the conclusion that there is no universially preferred approach. The power benefits of alternative approaches are typically modest, or only noticeable in situations where all alternatives are underpowered. The power issue is not that important - the main discussion is about whether equivalence tests should have a bounded rejection region, ike TOST, or an unbounded rejection region. It might be useful to note that TOST and SGPV are similar in this respect - both have bounded rejection regions, and if the reviewer agrees with Perlman and Wu (1999) in the criticism against TOST, the same criticism applies to the SGPV. If the reviewer reads Perlman and Wu (1999) as an argument to ban TOST, it is at the same time an argument to ban the SGPV. We agree with Meyners, who writes: "The debate has been quite heated in times; this section intends to give a brief overview of the debate. We would like to emphasize again that the differences between the approaches are minor and to a large extent of academic interest only, as is this debate." and concludes: "To summarize, there is no right or wrong in most of the arguments; the two opposing parties rather apply different criteria to select the most appropriate test, one group focusing rather on mathematical/statistical criteria, the other one more on interpretability and reasonability." We have added a reference to this discussion for the interested reader, and added "For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see Meyners, 2012."

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-03-08 reply_to_reviews.R1.tex
First complete reply to review DL.

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Reply to Reviews},
            pdfauthor={Daniël Lakens~\& Marie Delacre},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Reply to Reviews}
    \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}
    \date{}

\shorttitle{Reply R1}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\\textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{

Correspondence concerning this article should be addressed to Daniël
Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
E-mail:
\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}

\abstract{
We respond to all the comments raised by the two reviewers and the
editors. We would like to thank the editor and reviewers for their
suggestions for improvements, which we believe made our main argument
much clearer, focussed, and formally correct. We feel we were able to
accomodate all suggestions, and we hope you think our submission is
ready to be accepted for publication in Meta-Psychology.

}

\begin{document}
\maketitle

Dear editor,

Thank you for your comments on our submitted manuscript. We have
incorporated your three comments:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  We moved the first sentence on page 3 into the next paragraph (well
  spotted).
\item
  The code for the Shiny app was on GitHub, and the GitHub repository is
  linked to the OSF project page, but we have added a component to the
  OSF page and also directly added the Shiny App code there to make it
  easier to find: \url{https://osf.io/7f8uq/}
\item
  We now immediately refer to Figure 4 in the beginning of the paragraph
  in which the Figure is described.
\end{enumerate}

We will respond to the points raised by both reviewers in turn.

\section{Reply to Reviewer 1}\label{reply-to-reviewer-1}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We have changed the part of the sentence \enquote{Our conclusions
  about the relationship between TOST p-values and SGPV in this article
  are not dependent upon any specific example} into \enquote{Our
  conclusions about the relationship between TOST \emph{p}-values and
  SGPV hold for an SGPV calculated from confidence intervals, and
  assuming continuous normally distributed data.}. We mainly intended to
  refer to our conclusion that: \enquote{When confidence intervals are
  symmetric we can think of the SGPV as a straight line that is directly
  related to the \emph{p}-value from an equivalence test for three
  values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
  p-values for TOST of 0.025 and 0.975 (corresponding to the largest
  observed mean where the SGPV is 0 and the smallest observed mean where
  the SGPV is 1). We have now made it clearer that when we talk about
  \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we
  mean that there is a direct relation between three points.
\item
  We appreciate correcting our use of the term \enquote{unrelated} and
  teaching us the word \enquote{bijective}. We used the word
  \enquote{unrelated} somewhat naievely, looking at the Figures and
  wanting to express that across the three identified situations, a
  different TOST \emph{p}-value does not imply a different SGPV - the
  SGPV across these ranges of means is aways the same (either 0, 0.5, or
  1) while the TOST p-value differs across this range of means. We now
  just directly say what we originally meant, and no longer use the word
  \enquote{unrelated}. For example, \enquote{There are three situations
  where \emph{p}-values for TOST differentiate between observed results,
  while the SGPV does not differentiate.} and \enquote{While the SGPV is
  1 as long as the confidence interval falls completely within the
  equivalence bounds, the \emph{p}-value for the TOST continues to
  differentiate between results as a function of how far the confidence
  interval lies within the equivalence bounds (the further the
  confidence interval is from both bounds, the lower the
  \emph{p}-value).} and similarly \enquote{A third situation in which
  the SGPV remains stable across a range of observed effects, while the
  TOST \emph{p}-value continues to differentiate, is whenever the CI is
  wider than the equivalence range, and the CI overlaps with the upper
  \emph{and} lower equivalence bound.}
\item
  Please do not feel like you ever need to apologize for having formal
  training we lack, that allows you to point out whenever we make
  formally incorrect statements. This is exactly why we submit our work
  for peer review - to be able to improve it based on feedback from
  experts. We now preface the sentence with \enquote{As long as data is
  normally distributed,}. We follow your recommendation throughout to
  not generalize beyond the scenarios we study. In the second paragraph
  of the manuscript we now clearly state: \enquote{We limit our analysis
  to normally distributed continuous data.} See also point 5 below.
\item
  After making the change at point 2 above, we now think the sentence
  \enquote{The conclusion of this section on asymmetric confidence
  intervals is that a SGPV of 1 or 0 can still be interpreted as a p
  \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test,
  since the SGPV and p-value for the TOST procedure are always directly
  related at these values.} should no longer be confusing. To make the
  sentence clearer, we have changed \enquote{these values} into
  \enquote{at the values p = 0.025 and p = 0.975} It should now be clear
  the sections are not contradictory - TOST differentiates below p
  \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
\item
  We agree that is unclear whether the original statement by Blume et al
  that \enquote{the degree of overlap conveys how compatible the data
  are with the null premise} holds in general. We have now amended the
  sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly
  interpreted, a SGPV between 0 and 1 is not interpretable as
  \enquote{compatibility with the null hypothesis} under the assumption
  of normally distributed data, and the generalizability of this
  statement needs to be examined beyond normally distributed data
  requires further examination.}
\item
  We have removed our earlier statements that the SGPV only works as a
  descriptive statistic. We deleted the sentence \enquote{the SGPV is a
  descriptive statistic (unlike the \emph{p}-value that is calculated
  for an equivalence test, which is an inferential statistic) that
  provides the proportion of overlap of the confidence interval and the
  equivalence range.} and deleted \enquote{The novelty of the SGPV lies
  in its use as a descriptive statistic} from the conclusion. Indeed, we
  acknowledge that \enquote{Although a SGPV of 1 or 0 can be directly
  interpreted, a SGPV between 0 and 1 is not interpretable as
  \enquote{compatibility with the null hypothesis}.} So the SGPV is an
  inferential statistic when interpreted dichotomously. We will leave
  our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should
  be interpreted to future researchers, and we do not make any
  statements about whether such values are descriptive our inferential.
\item
  We agree that using TOST for small samples (e.g., N = 4) will not be
  useful. Indeed, an a-priori power analysis for equivalence tests would
  prevent anyone from planning such a study, since the result will be
  that such a study has 0 power - the CI will never fit withing the
  equivalence bounds.
\item
  With our recommendations, we have limited our conclusions to the
  specific cases we have examined, and noted the possibility for future
  research to examine a wider set of assumptions. An additional change
  not mentioned above is that we renamed the section on asymmetric
  confidence intervals to the more specific \enquote{The relation
  between equivalence tests and SGPV for asymmetrical confidence
  intervals around correlations} instead of the more general
  \enquote{The relation between equivalence tests and SGPV when
  confidence intervals are not symmetrical}. We appreciate the very
  positive evaluation of our manuscript, but even more so the criticism
  which allowed us to improve the manuscript.
\end{enumerate}

\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}

Before listing major points, the reviewer raises the point that we
compare SGPV with p-values from TOST throughout our paper, and in all
figures, but then at the end, in page 20, we write:

\enquote{Equivalence tests combined with null-hypothesis significance
tests also allow researchers to conclude an effect is significant and
equivalent (i.e., statistically different from zero, but also too small
to be considered meaningful). Thus, the SGPV is used to classify results
into one of three possible categories (with the data falling inside or
outside the equivalence range, or being inconclusive), while equivalence
tests combined with null-hypothesis tests classify results into four
possible categories.}

The reviewer says that \enquote{the authors suddenly switch the premise;
now the SGPV should be replaced by two p-values, one from an equivalence
test and one from a NHST}. However, we do not suggest to replace the
SGPV with an equivalence test and a NHST at all. In our manuscript, we
already pointed out how the SGPV is basically the same as an equivalence
test and a minimum effect test (on page 7):

\enquote{The third point where the SGPV and the p-value from the TOST
procedure should overlap is where the 95\% CI falls completely outside
of the equivalence range, but one endpoint of the confidence interval is
equal to the equivalence bound (see situation C in Figure 3), when the
p-value will always be 0.975. Note that this situation is in essence a
minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal of a
minimum-effect is not just to reject a difference of zero, but to reject
the smallest effect size of interest (i.e., the equivalence bounds). The
SGPV summarizes the information from an equivalence test and a
minimum-effect test.}

One might argue that we suggest to replace the SGPV with two tests.
However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives
away that the equivalence test can be interpreted as a minimum effect
test against the equivalence bound. When the TOST \emph{p}-value is
0.975, the 95\% CI touches either the upper or lower equivalence bound,
and fall complately outside of the equivalence range. This is
mathematically identical to a statistically significant minimum effect
test at p \textless{} 0.05. We didn't make this explicit, but we clearly
should have. We have added the sentence (on page 7):

\enquote{An equivalence test and minimum effect test against the same
equivalence bound are complementary, and when a TOST \emph{p}-value is
larger than 0.975, the \emph{p}-value for the minimum effect test is
smaller than 0.05, and the minimum effect test provides no additional
information that can not be derived from the \emph{p}-value from the
equivalence test.}

One might wonder why then, on page 20, why we introduce the idea to
perform both a null-hypothesis significance test and an equivalence
test. We were not clear enough. And indeed, the sentence \enquote{This
interpretation of a SGPV as allowing researchers to reject the null,
reject the presence of a meaningful effect, or remaining inconclusive is
very similar to the Neyman-Pearson interpretation of combining a
null-hypothesis test and an equivalence test} was simply confusing. We
have deleted this sentence and replaced it with \enquote{As already
mentioned, this interpretation of a SGPV as is very similar to the
Neyman-Pearson interpretation of an equivalence test and a minimum
effect tests (which are complementary).}

Furthermore, to prevent the apparent confusion about why we suggested to
perform a null-hypothesis test and equivalence test. Part of this
confusion was our original sentence comparing the SGPV and a combination
of NHST and an equivalence test which was not needed, and we understand
it made it seem as if SGPV needs to be replaced by a combination of
other tests. But that is not what we propose. Werewrote the paragraph:

\enquote{Some researchers might be interested in combining an
equivalence tests with a null-hypothesis significance test. This allows
a researcher to ask whether there is an effect that is statistically
different from zero, and whether effect sizes that are considered
meaningful can be rejected. Equivalence tests combined with
null-hypothesis tests classify results into four possible categories,
and for example allow researchers to conclude an effect is significant
and equivalent (i.e., statistically different from zero, but also too
small to be considered meaningful, see (Lakens et al., 2018)).}

We hope this makes it clear we are not pulling a bait and switch. The
SGPV is strongly related to an equivalence test (or it's complement, a
minimum effect test). Describing the relation between the SGPV and TOST
is our main contribution. We just wanted to mention that researchers
might want to combine an equivalence test with a NHST, because in the
literature, this is a question we see many psychologists ask.

We will now discuss the major points in turn.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In line with the comments by reviewer 1, in the second paragraph of
  the manuscript we now clearly state: \enquote{We limit our analysis to
  normally distributed continuous data.} After all, p-values and
  confidence are directly related, but Bayesian credible intervals would
  not necessarily be, depending on the prior. Blume et al (2018) limit
  their examples to confidence intervals, but explicitly acknowledge
  other possibilities (such as Bayesian intervals). We look forward to
  future papers that illustrate the SGPV with other interval estimates
  and are happy to add the limitation to continuous normally distributed
  data in our article. Note that we did not add that the correspondence
  only holds for situations where the SE's are small compared to the
  width of the equivalence range, as the reviewer suggests.
\item
  The reviewer repeats that the correspondence only holds when SE's are
  small compared to the width of the equivalence range. The
  correspondence is not in the shape of the curve (which clearly differs
  across Figures 2, 6, and 9). We clearly state that: \enquote{When
  confidence intervals are symmetric we can think of the SGPV as a
  straight line that is directly related to the p-value from an
  equivalence test for three values.} This correspondence is not
  dependent upon the SE's. It will always hold for continuous normal
  data. The reviewer says that \enquote{The paper does not provide
  theoretical justification for this connection nor any proofs.} We are
  unsure which proof is needed for the overlap between the three points,
  since it is rather trivial and we believe the explanation in the paper
  is very clear.
\end{enumerate}

For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and
SGPV = 1, and TOST p = 0.975 and SGPV = 1: ``The SGPV is 50\% when the
observed mean falls exactly on the lower or upper equivalence bound,
because 50\% of the symmetrical confidence interval overlaps with the
equivalence range. When the observed mean equals the equivalence bound,
the difference between the mean in the data and the equivalence bound is
0, the t-value for the equivalence test is also 0, and thus the p-value
is 0.5 (situation A, Figure 3). Two other points always have to overlap.
When the 95\% CI falls completely inside the equivalence region, and one
endpoint of the confidence interval is exactly equal to one of the
equivalence bounds (see situation B in Figure 3) the TOST p-value (which
relies on a one-sided test) is always 0.025, and the SGPV is 1. The
third point where the SGPV and the p-value from the TOST procedure
should overlap is where the 95\% CI falls completely outside of the
equivalence range, but one endpoint of the confidence interval is equal
to the equivalence bound (see situation C in Figure 3), when the p-value
will always be 0.975, and the SGPV is 0.

We do not think we can provide any other proof for this. A confidence
interval and a p-value are directly related. The TOST procedure is a
test using the confidence interval, and the SGPV (now that we clearly
limited our discussion to a SGPV based on a confidence interval
calculated from continuous normal data) compared against the same
equivalence bounds will be related as we describe. But we believe our
article might not have been clear enough about that we limit our
discussion about the correspondence of the curves to these 3 points.
Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
13). Nevertheless, in these graphs, we still have the correspondence
between these 3 points (or at leas tthe 2 points if the CI is too wide
compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
To make it clearer that we talk about the overlap in these 3 critical
points, we have added:

\enquote{When we discuss the relationship between the p-values from TOST
and the SGPV, we focus on their correspondence at three values, namely
where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} =
0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
These three values are important for the SGPV because they indicate the
values at which the SGPV indicates the data should be interpreted as
compatible with the null hypothesis (SGPV = 1), or with the alternative
hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV
= 0.5). These three points of overlap are indicated by the horizontal
dotted lines in Figure 2.}

We believe this satisfactorily addresses the point by the reviewer that
\enquote{Because of this lack of discussion, the reader can easily miss
that the close correspondence only occurs when the sample size is large
enough that the standard error is very small relative to the width of
the equivalence zone.} Indeed, the correspondence between the TOST and
SGPV at these 3 points should be obvious to anyone who understands the
relationship between a p-value and a confidence interval, so we do not
provide any further proof, but we hope that clarifying we talk about the
correspondence of these 3 points, and not the entire curve, is
sufficient to address point 2.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  We are aware of the Beger and Hsu (1996) article. But if the reviewer
  reads more closely, it should be clear that we never say the TOST is
  UMP. We say that TOST is a test procedure that aims to control error
  rates - our use of the term \enquote{Neyman-Pearson perspective}
  refers to the classic difference between significance tests (Fisher)
  and hypothesis tests (Neyman-Pearson). We do not imply that any test
  that fixes an error rate is a NP test. Because many psychologists are
  not trained in the difference between a Fisherian approach and a
  Neyman Pearson approach to the use of p-values, we are simply adding a
  \enquote{Neyman-Pearson} approach in the text to explain that
  \enquote{From a Neyman-Pearson perspective on statistical inferences
  the main conclusion is based on whether or not \(p < \alpha\), and
  thus an equivalence test and SGPV can be performed by simply checking
  whether the confidence interval falls within the equivalence range,
  just as a null-hypothesis test can be performed by checking whether
  the confidence interval contains zero or not.} We believe this is a
  correct use of the term \enquote{Neyman-Pearson perspective on
  statistical inferences}.
\item
  We tried to find the passage the reviewer refers to when he writes
  \enquote{In light of this, the assertion without proof that classical
  p-values provide more or better assessments of the \enquote{evidence}
  appear out of place.} but we could not. We do not use the word
  \enquote{evidence} in the text (because neither the p-value from TOST
  nor the SGPV are measures of \enquote{evidence} - we fully agree with
  BLume et al., 2018, in this respect). We also do not say the p-value
  is \enquote{naturally informative}. Indeed, related to point 3 above,
  we tried to be consistent in interpreting the TOST procedure from a
  Neyman-Pearson perspective, and focus on error control. So we
  regrettably do not know how to incorporate this point.
\item
  We fully agree with the reviewer on point 5 that \enquote{The maximum
  Type I Error rate for the SGPV over the null interval is 5\%, exactly
  like the TOST test.} Indeed, given the direct overlap between the TOST
  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
  1 and 0, any error rates (when concluding support for the null or
  alternative when the SGPV is either 1 or 0) must be identical. This is
  why we were so surprised when Blume et al (2018) write \enquote{They
  control the Type I error naturally, forcing it to zero as the sample
  size grows. This, in turn, offsets Type I Error inflation that results
  from multiple comparisons or multiple examinations of accumulating
  data. Findings identified by second-generation p-values are less
  likely to be false discoveries than findings identified by classical
  p-values. Consequently, second-generation p-values do not require
  ad-hoc adjustments to provide strict error control and this improves
  power in studies with massive multiple comparisons.} Clearly, it can
  not both be true that the the error rate of SGPV and TOST is
  identical, TOST requires adjusting for multiple comparisons, but the
  SGPV does not.
\end{enumerate}

The editor asks us to better substantiate the frequency claims for the
comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value
are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1)
we do not think any additional substantiation is possible, especially
since the reviewer agrees that (as long as confidence intervals are used
to calculate the SGPV, which we now clearly limit our conclusions to)
\enquote{The maximum Type I Error rate for the SGPV over the null
interval is 5\%, exactly like the TOST test}.

Nevertheless, we agree this discussion was a bit too extensive. Given my
own fondness of error control in statistical inferences, I get worried
if researchers suggest we can ignore it, especially when making multiple
comparisons. Imagine people start to use the SGPV instead of the TOST
procedure whenever they perform 20 tests, and then argue they do not
need to correct for multiple comparison - I think we can all agree this
is undesireable! We have reduced the two paragraphs to one hopefully
clear statement about the need to control error rates, also when using
the SGPV. We hope this addresses the concerns by the editor as well as
the reviewer, while still making an important point in the literature
about the need to control error rates (if one cares about drawing
incorrect conclusions).

Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
\enquote{Adjustments for multiple comparisons are obviated} (p.~15).
However, this is not correct. Given the direct relationship between TOST
and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025
equals SGPV = 1, as long as the SGPV is calculated based on confidence
intervals, and assuming continuous and normally distributed data), not
correcting for multiple comparisons will inflate the probability of
concluding the absence of a meaningful effect based on the SGPV in
exactly the same way as for equivalence tests. Whenever statistical
tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or
SGPV =1), it is possible do so erroneously, and if researchers want to
control error rates, they need to correct for multiple comparisons.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\item
  We have removed this section while addressing point 5 above, and thus
  incorporated the reviewers'suggestion to remove these statements.
\item
  We have not removed the paragraph about multiple comparisons, as the
  reviewer asks, but we have simplified our treatment of it. We do not
  need any other argument to make our claims about multiple comparisons
  that fact, noted by the reviewer, that \enquote{The maximum Type I
  Error rate for the SGPV over the null interval is 5\%, exactly like
  the TOST test.} This is true, and it logically follows (hence, no
  mathematical proof is needed) that error rates need to be controlled
  when using SGPV to conclude support for the null-hypothesis. We blieve
  error control is important enough to include this paragraph in the
  paper, as we believe that lack of error control was one of the causes
  of the replication crisis in psychology.
\item
  We thank the reviewer for this comment. Indeed, to calculate
  confidence intervals around a correlation, the Fisher's
  z-transformation is used, which is approximately normally distributed,
  and symmatric CI are calculated. When transforming these confidence
  intervals back to correlations, they become asymmetric. We have added
  to the text: \enquote{Note that calculating confidence intervals for a
  correlation involves a Fisher's z-transformation, which transforms
  values such that they are approximately normally distributed, which
  allows one to compute symmetric confidence intervals, which are then
  retransformed into a correlation, where the confidence intervals are
  asymmetric if the correlation is not exactly zero.} This is simply one
  example of a general effect mentioned in Blume et al (2018), which we
  already cited in the main text: \enquote{The magnitude of an
  inconclusive second-generation \emph{p}-value can vary slightly when
  the effect size scale is transformed. However definitive findings,
  i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.}
\end{enumerate}

Minor Concerns:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We added \enquote{,or more extreme data,}
\item
  This text was deleted (see major point 5 above)
\item
  We see how \enquote{reverse the SGPV} might have been confusing. We
  did not mean to imply to reverse the null and alternative. We now just
  say that we plot 1-SGPV (which is what we incorrectly tried to express
  with \enquote{reverse}).
\item
  The issue of the SGPV needing a \enquote{correction} by setting it to
  0.5 is not related to the fact that large \emph{p}-values are not
  evidence for the null. The \emph{p}-value is behaving as it is
  intended to, without any correction. A high p-value is not a
  \enquote{misleading result} - although it can be misinterpreted (which
  is exactly what we try to prevent with our work on equivalence
  testing). We therefore did not incorporate this point.
\item
  In line with comments by reviewer 1, we removed statemetns about SGPV
  not being inferential, thereby solving the issue reviewer 2 raised.
\item
  In line with major point 8, we added information that asymmetric
  condifence intervals around a correlation are symmetric when Fisher
  z-transformed. This is just an example of what Blume et al (2018)
  refer to when they write \enquote{The magnitude of an inconclusive
  second-generation \emph{p}-value can vary slightly when the effect
  size scale is transformed. However definitive findings, i.e.~a
  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.} We beieve this section, although the most detailed, is
  interesting, even only for more expert readers (indeed, Reviewer 1
  notes that \enquote{The asymmetric CI case is very interesting}). We
  have made our point less general, now only talking about correlations,
  by changing the title of this section into \enquote{The relation
  between equivalence tests and SGPV for asymmetrical confidence
  intervals around correlations}. The reviewer is correct confidence
  intervals can be created in many difference ways (e.g., with holes in
  the middle), but for this paper, we just focus on one specific case
  now, which we believe might be closest to what researchers would use
  in real life, the confidence interval around a correlation.
\item
  It is a well-known fact that the TOST can have 0 power (and indeed,
  this is one of the main issues in the Perlman and Wu (1999) paper the
  reviewer cited). As explained in Lakens (2017): \enquote{It is
  important to take statistical power into account when determining the
  equivalence bounds because, in small samples (where CIs are wide), a
  study might have no statistical power (i.e., the CI will always be so
  wide that it is necessarily wider than the equivalence bounds).} We
  agree with the reviewer it is not interesting to do a test if you have
  0 power. People should design informative experiments by doing an
  a-priori power analysis. Any problem in this respect is not a problem
  with equivalence tests, but a problem with designing a bad study. Not
  that the exact same issue applies to the SGPV. It is also possible to
  have 0 power for the SGPV - so we do not understand why the reviewer
  is so surprised about this. The question \enquote{Why use the TOST
  test then?} equally applies to \enquote{Why use the SGPV then?} if
  you, from the outset, know that the \enquote{small sample correction}
  will lead to a SGPV of 0.5.
\item
  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an
  estimate to some value. Regardless of how correction factors are
  applied in statistics, we are trying to educate our readers about what
  the \enquote{small sample correction} does. We believe our readers
  will associate \enquote{correction} with \enquote{correcting}, and
  want to explain that the SGPV is not set to a \enquote{correct} value.
  We are not talking about statistical terms here - we are warning the
  reader to not interpret \enquote{correction} in terms of normal
  language use. This is similar to warning readers that
  \enquote{significant} does not have the normal language connotation of
  \enquote{important}. We have therefore kept our original sentence.
\end{enumerate}

As a final comment, altough not explicitly listed as a major point of
minor point, we are happy to respond to the reviewers' suggestion that
Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
best summary of this discussion (of which Perlman \& Wu is one
contribution) can be found in Meyners (2012), which we cited. The
discussion has different arguments, and Meyners draws the conclusion
that there is no universially preferred approach. The power benefits of
alternative approaches are typically modest, or only noticeable in
situations where all alternatives are underpowered. The power issue is
not that important - the main discussion is about whether equivalence
tests should have a bounded rejection region, ike TOST, or an unbounded
rejection region. It might be useful to note that TOST and SGPV are
similar in this respect - both have bounded rejection regions, and if
the reviewer agrees with Perlman and Wu (1999) in the criticism against
TOST, the same criticism applies to the SGPV. If the reviewer reads
Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
an argument to ban the SGPV. We agree with Meyners, who writes:
\enquote{The debate has been quite heated in times; this section intends
to give a brief overview of the debate. We would like to emphasize again
that the differences between the approaches are minor and to a large
extent of academic interest only, as is this debate.} and concludes:
\enquote{To summarize, there is no right or wrong in most of the
arguments; the two opposing parties rather apply different criteria to
select the most appropriate test, one group focusing rather on
mathematical/statistical criteria, the other one more on
interpretability and reasonability.} We have added a reference to this
discussion for the interested reader, and added \enquote{For an
excellent discussion of the strengths and weaknesses of different
frequentist equivalence tests, including alternatives to the TOST
procedure, see Meyners, 2012.}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-blume_second-generation_2018}{}
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
(2018). Second-generation p-values: Improved rigor, reproducibility, \&
transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
e0188299.
doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\endgroup

\end{document}

### 2019-03-08 manuscript.R1.Rmd
First complete reply to review DL.

--- 2018-08-28 manuscript.Rmd
@@
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV. 
+We limit our analysis to normally distributed continuous data.
 
@@
 In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
+For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see [@meyners_equivalence_2012].
 If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
@@
 For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
-Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
+Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.
+Readers can explore the relationship between TOST *p*-values and SGPV for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
 
@@
 The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
-For ease of comparison we can reverse the SGPV (by calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values more easily comparable.
+For ease of comparison we can plot 1-SGPV (see Figure \ref{fig:TOSTSGPV2}) to make the values more easily comparable.
 We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
+When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
+These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
+These three points of overlap are indicated by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2}.
 
@@
 lines(p_tost_list, lwd = 3)
-#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
+abline(h = c(0.975, 0.5, 0.025),
+       lty = 2,
+       col = "grey")
 ```
@@
 Two other points always have to overlap.
-When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST *p*-value (which relies on a one-sided test) is always 0.025.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975.
+When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST *p*-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975, and the SGPV is 0.
 Note that this situation is in essence a minimum-effect test [@murphy_statistical_2014].
 The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
+An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test.
 The SGPV summarizes the information from an equivalence test and a minimum-effect test.
@@
 
-For example, the SGPV from A to D is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
+For example, in Figure \ref{fig:TOSTSGPV4} we have plotted four SGPV's.
+From A to D the SGPV is `r round(SGPV1, digits = 2)`, `r round(SGPV2, digits = 2)`, `r round(SGPV3, digits = 2)`, and `r round(SGPV4, digits = 2)`.
 The difference in the percentage of overlap between A and B (`r round(SGPV1-SGPV2, digits = 2)`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r round(SGPV3-SGPV4, digits = 2)`).
-As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
+As the observed mean in a one-sample *t*-test lies closer to the test value, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly. 
 As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
@@
 
-##When are the SGPV and Equivalence Test Unrelated?
-
-There are three situations where *p*-values from TOST and SGPV are unrelated.
+##When different *p*-values for equivalence tests yield the same SGPV
+
+There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate.
 The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
-When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
-Because *p*-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges.
+When the SGPV is either 0 or 1, *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
+While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value).
 The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
-The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
+The situations where the *p*-values from the TOST procedure continue to differentiate based on how extreme the results are, but the SGPV is a fixed value are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
 
@@
 
-A third situation in which the SGPV deviates from the TOST *p*-value is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
+A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound.
 When the confidence interval is more than twice as wide as the equivalence range the SGPV is set to 0.5.
@@
 
-##The relation between equivalence tests and SGPV when confidence intervals are not symmetrical
+##The relation between equivalence tests and SGPV when for asymmetrical confidence intervals around correlations
 
@@
 For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0.
-The confidence interval becomes increasingly asymmetric as the observed correlation nears -1 or 1.
+The confidence interval for a correaltion becomes increasingly asymmetric as the observed correlation nears -1 or 1.
 For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.993.
-
-The effect of asymmetric confidence intervals is most noticeable at smaller sample sizes.
+Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally distributed, which allows one to compute symmetric confidence intervals, which are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.
+
+The effect of asymmetric confidence intervals around correlations is most noticeable at smaller sample sizes.
 In Figure \ref{fig:TOSTSGPV11} we plot the *p*-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
@@
 This example illustrates the difference between a proportion and a probability.
-There is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+As long as data is normally distributed, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
 The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
@@
 It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a *p*-value answers.
-The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at the values *p* = 0.025 and *p* = 0.975.
 Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
-Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data.
 Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
@@
 When introducing a new statistical method, it is important to compare it to existing approaches and specify its relative strengths and weaknesses.
-First of all, the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
-Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+First of all, even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
 In one sense, they are what they are (the proportion of overlap), but it can be unclear what this number tells us about the data we have collected.
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) seems to be to examine whether the SGPV is 0, 1, or inconclusive.
-This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test [@lakens_equivalence_2018].
+As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).
 The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example *p* = 0.048 and *p* = 0.002.
@@
 From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
-At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how precisely how surprising the data is under the null model.
-Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
-Thus, the SGPV is used to classify results into one of three possible categories (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories.
+At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how precisely how surprising the data, or more extreme data, is under the null model.
+Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test.
+This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see [@lakens_equivalence_2018]).
 
@@
 Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see for example Figure \ref{fig:TOSTSGPV6}).
-An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
+An important benefit of equivalence tests is that it does not need such a correction to prevent misleading results.
 
@@
 
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13}.
 In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
@@
 
-@blume_second-generation_2018 argue that the SGPV has improved error control, in that the conclusion that the 95% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95% confidence interval only needs to not overlap with zero).
-However, the SGPV has a *lower* error rate than a null-hypothesis test, not a *more accurate* error rate.
-In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
-We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
-The TOST procedure uses a 90% confidence interval because it is based on two *one-sided* tests, and thus the confidence interval is 1-2$\times$$\alpha$, and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
-The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
-
 @blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
-15) and that "second-generation *p*-values provide a proper scientific adjustment for multiple comparisons".
+15).
 However, this is not correct.
-With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
-When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is *no* effect, where there *is* a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
-To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
-Equivalence tests provide an easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 
@@
 We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation *p*-values to the statistical toolbox.
-The novelty of the SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
+The novelty of the SGPV can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
 There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent and easier to interpret.
@@
 Our comparisons show that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
-We believe equivalence tests achieve the goals of the second generation *p*-value while allowing users to more easily control error rates, and while yielding more consistent statistical outcomes.
+We believe equivalence tests achieve the goals of the second generation *p*-value while allowing users to easily control error rates, and while yielding more consistent statistical outcomes.
 

### 2019-03-08 manuscript.R1.tex
First complete reply to review DL.

--- 2018-08-28 manuscript.tex
@@
-\documentclass[floatsintext,man]{apa6}
-
+\documentclass[,man,floatsintext]{apa6}
+\usepackage{lmodern}
 \usepackage{amssymb,amsmath}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-
-% Table formatting
-\usepackage{longtable, booktabs}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-
-\newenvironment{lltable}
-  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
-  {\end{ThreePartTable}\end{center}\end{landscape}}
-
-% The following enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand\getlongtablewidth{%
- \begingroup
-  \ifcsname LT@\roman{LT@tables}\endcsname
-  \global\longtablewidth=0pt
-  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
-  \@nameuse{LT@\roman{LT@tables}}%
-  \fi
-\endgroup}
-
-  \usepackage{graphicx}
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Equivalence Testing and the Second Generation P-Value},
+            pdfauthor={Daniël Lakens~\& Marie Delacre},
+            pdfkeywords={equivalence testing, second generation \emph{p}-values, hypothesis
+testing, TOST, statistical inference},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
 \fi
-\hypersetup{breaklinks=true,
-            pdfauthor={},
-            pdftitle={Equivalence Testing and the Second Generation P-Value},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\setlength{\parindent}{0pt}
-%\setlength{\parskip}{0pt plus 0pt minus 0pt}
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
+  \title{Equivalence Testing and the Second Generation \emph{P}-Value}
+    \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}
+    \date{}
 
-% Manuscript styling
-\captionsetup{font=singlespacing,justification=justified}
+\shorttitle{TOST vs. SGPV}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\\textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium}
+\keywords{equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference\newline\indent Word count: }
 \usepackage{csquotes}
 \usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-\usepackage{tikz} % Variable definition to generate author note
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
 
-% fix for \tightlist problem in pandoc 1.14
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
-% Essential manuscript parts
-  \title{Equivalence Testing and the Second Generation \emph{P}-Value}
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 
-  \shorttitle{TOST vs.~SGPV}
+\usepackage{lineno}
 
-  \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}
+\linenumbers
 
-  \def\affdep{{"", ""}}%
-  \def\affcity{{"", ""}}%
-
-  \affiliation{
-    \vspace{0.5cm}
-          \textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\
-          \textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium  }
-
-  \authornote{
-    \newcounter{author}
-    All code associated with this article, including the reproducible
-    manuscript, is available from
+\authornote{All code associated with this article, including
+the reproducible manuscript, is available from
 \url{https://github.com/Lakens/TOST_vs_SGPV}. This work was supported by
@@
 
-                      Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
-E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}
-                          }
+Correspondence concerning this article should be addressed to Daniël
+Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
+E-mail:
+\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
-  \abstract{To move beyond the limitations of null-hypothesis tests, statistical
+\abstract{
+To move beyond the limitations of null-hypothesis tests, statistical
 approaches have been developed where the observed data is compared
@@
 generation \emph{p}-value, and allow for easier control of Type I and
-Type II error rates.}
-  \keywords{equivalence testing, second generation \emph{p}-values, hypothesis
-testing, TOST, statistical inference \\
+Type II error rates.
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
-
 \maketitle
 
-\setcounter{secnumdepth}{0}
-
 To test predictions researchers predominantly rely on null-hypothesis
-tests.\\
-This statistical approach can be used to examine whether observed data
-is sufficiently surprising under the null hypothesis to reject an effect
-that equals exactly zero. Null-hypothesis tests have an important
+tests. This statistical approach can be used to examine whether observed
+data is sufficiently surprising under the null hypothesis to reject an
+effect that equals exactly zero. Null-hypothesis tests have an important
 limitation, in that this procedure can only reject the hypothesis that
@@
 Here, we aim to examine the similarities and differences between the
-TOST procedure and the SGPV.
+TOST procedure and the SGPV. We limit our analysis to normally
+distributed continuous data.
 
@@
 equivalence bound in the second one-sided test (Lakens, Scheel, \&
-Isager, 2018). If both tests statistically reject an effect as extreme
-or more extreme than the equivalence bound, you can conclude the
-observed effect is practically equivalent to zero from a Neyman-Pearson
-approach to statistical inferences. Because one-sided tests are
-performed, one can also conclude equivalence by checking whether the
-1-2\(\times\)\(\alpha\) confidence interval (e.g., when the alpha level
-is 0.05, a 90\% CI) falls completely within the equivalence bounds.
-Because both equivalence tests as the SGPV are based on whether and how
-much a confidence interval overlaps with equivalence bounds, it seems
-worthwhile to compare the behavior of the newly proposed SGPV to
-equivalence tests to examine the unique contribution of the SGPV to the
-statistical toolbox.
+Isager, 2018). For an excellent discussion of the strengths and
+weaknesses of different frequentist equivalence tests, including
+alternatives to the TOST procedure, see (Meyners, 2012). If both tests
+statistically reject an effect as extreme or more extreme than the
+equivalence bound, you can conclude the observed effect is practically
+equivalent to zero from a Neyman-Pearson approach to statistical
+inferences. Because one-sided tests are performed, one can also conclude
+equivalence by checking whether the 1-2\(\times\)\(\alpha\) confidence
+interval (e.g., when the alpha level is 0.05, a 90\% CI) falls
+completely within the equivalence bounds. Because both equivalence tests
+as the SGPV are based on whether and how much a confidence interval
+overlaps with equivalence bounds, it seems worthwhile to compare the
+behavior of the newly proposed SGPV to equivalence tests to examine the
+unique contribution of the SGPV to the statistical toolbox.
 
@@
 0. Our conclusions about the relationship between TOST \emph{p}-values
-and SGPV in this article are not dependent upon any specific example, as
-readers can explore for themselves in an online Shiny app:
-\url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
+and SGPV hold for an SGPV calculated from confidence intervals, and
+assuming continuous normally distributed data. Readers can explore the
+relationship between TOST \emph{p}-values and SGPV for themselves in an
+online Shiny app: \url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV1-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV1-1.pdf}
 \caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
@@
 TOST procedure treats the values outside of the equivalence range as the
-null-hypothesis. For ease of comparison we can reverse the SGPV (by
-calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values
-more easily comparable. We see that the \emph{p}-value from the TOST
-procedure and the SGPV follow each other closely.
+null-hypothesis. For ease of comparison we can plot 1-SGPV (see Figure
+\ref{fig:TOSTSGPV2}) to make the values more easily comparable. We see
+that the \emph{p}-value from the TOST procedure and the SGPV follow each
+other closely. When we discuss the relationship between the p-values
+from TOST and the SGPV, we focus on their correspondence at three
+values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
+TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
+and SGPV = 1. These three values are important for the SGPV because they
+indicate the values at which the SGPV indicates the data should be
+interpreted as compatible with the null hypothesis (SGPV = 1), or with
+the alternative hypothesis (SGPV = 0), or when the data are strictly
+inconclusive (SGPV = 0.5). These three points of overlap are indicated
+by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2}.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV2-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV2-1.pdf}
 \caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV3-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV3-1.pdf}
 \caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for
@@
 (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value
-(which relies on a one-sided test) is always 0.025. The third point
-where the SGPV and the \emph{p}-value from the TOST procedure should
-overlap is where the 95\% CI falls completely outside of the equivalence
-range, but one endpoint of the confidence interval is equal to the
-equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when
-the \emph{p}-value will always be 0.975. Note that this situation is in
-essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal
-of a minimum-effect is not just to reject a difference of zero, but to
-reject the smallest effect size of interest (i.e., the equivalence
-bounds). The SGPV summarizes the information from an equivalence test
-and a minimum-effect test. These can be two relevant questions to ask,
-although it often makes sense to combine an equivalence test and a
-null-hypothesis test instead (Lakens et al., 2018).
+(which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+The third point where the SGPV and the \emph{p}-value from the TOST
+procedure should overlap is where the 95\% CI falls completely outside
+of the equivalence range, but one endpoint of the confidence interval is
+equal to the equivalence bound (see situation C in Figure
+\ref{fig:TOSTSGPV3}), when the \emph{p}-value will always be 0.975, and
+the SGPV is 0. Note that this situation is in essence a minimum-effect
+test (Murphy, Myors, \& Wolach, 2014). The goal of a minimum-effect is
+not just to reject a difference of zero, but to reject the smallest
+effect size of interest (i.e., the equivalence bounds). An equivalence
+test and minimum effect test against the same equivalence bound are
+complementary, and when a TOST \emph{p}-value is larger than 0.975, the
+\emph{p}-value for the minimum effect test is smaller than 0.05, and the
+minimum effect test provides no additional information that can not be
+derived from the \emph{p}-value from the equivalence test. The SGPV
+summarizes the information from an equivalence test and a minimum-effect
+test. These can be two relevant questions to ask, although it often
+makes sense to combine an equivalence test and a null-hypothesis test
+instead (Lakens et al., 2018).
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV4-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV4-1.pdf}
 \caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for
@@
 
-For example, the SGPV from A to D is 0.76, 0.81, 0.86, and 0.91. The
-difference in the percentage of overlap between A and B (-0.05) is
-identical to the difference in the percentage of overlap between C and D
-as the mean gets 0.1 closer to the test value (-0.05). As the observed
-mean in a one-sample \emph{t}-test lies closer to the test value (in
-Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer
-to the test value by 0.1) the difference in the overlap changes
-uniformly. As we move the observed mean closer to the test value in
-steps of 0.1 across A to D the \emph{p}-value calculated for normally
-distributed data is not uniformly distributed. The probability of
-observing data more extreme than the upper bound of 2 is (from A to D)
-0.16, 0.12, 0.08, and 0.06. As we can see, the difference between A and
-B (0.04) is not the same as the difference between C and D (0.03).
-Indeed, the difference in \emph{p}-values is the largest as you start at
-\emph{p} = 0.5 (when the observed mean falls on the test value), which
-is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at
-\emph{p} = 0.5. Note that where the SGPV reaches 1 or 0, \emph{p}-values
-closely approximate 0 and 1, but never reach these values.
+For example, in Figure \ref{fig:TOSTSGPV4} we have plotted four SGPV's.
+From A to D the SGPV is 0.76, 0.81, 0.86, and 0.91. The difference in
+the percentage of overlap between A and B (-0.05) is identical to the
+difference in the percentage of overlap between C and D as the mean gets
+0.1 closer to the test value (-0.05). As the observed mean in a
+one-sample \emph{t}-test lies closer to the test value, from situation A
+to D, the mean gets closer to the test value by 0.1) the difference in
+the overlap changes uniformly. As we move the observed mean closer to
+the test value in steps of 0.1 across A to D the \emph{p}-value
+calculated for normally distributed data is not uniformly distributed.
+The probability of observing data more extreme than the upper bound of 2
+is (from A to D) 0.16, 0.12, 0.08, and 0.06. As we can see, the
+difference between A and B (0.04) is not the same as the difference
+between C and D (0.03). Indeed, the difference in \emph{p}-values is the
+largest as you start at \emph{p} = 0.5 (when the observed mean falls on
+the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is
+the steepest at \emph{p} = 0.5. Note that where the SGPV reaches 1 or 0,
+\emph{p}-values closely approximate 0 and 1, but never reach these
+values.
 
-\subsection{When are the SGPV and Equivalence Test
-Unrelated?}\label{when-are-the-sgpv-and-equivalence-test-unrelated}
+\subsection{\texorpdfstring{When different \emph{p}-values for
+equivalence tests yield the same
+SGPV}{When different p-values for equivalence tests yield the same SGPV}}\label{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}
 
-There are three situations where \emph{p}-values from TOST and SGPV are
-unrelated. The first two situations were discussed before and can be
-seen in Figure \ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1
-\emph{p}-values from the equivalence test fall between 0.975 and 1 or
-between 0 and 0.025. Because \emph{p}-values approach 0 or 1, but are
-never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics
-are completely unrelated within these ranges. The easiest way to see
-this is by plotting the SGPV against the \emph{p}-value from the TOST
-procedure. The situations where the SPGV and \emph{p}-values from the
-TOST procedure are unrelated are indicated by the parts of the curve
-where there are vertical straight lines at second generation
-\emph{p}-values of 0 and 1.
+There are three situations where \emph{p}-values for TOST differentiate
+between observed results, while the SGPV does not differentiate. The
+first two situations were discussed before and can be seen in Figure
+\ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1, \emph{p}-values
+from the equivalence test fall between 0.975 and 1 or between 0 and
+0.025. While the SGPV is 1 as long as the confidence interval falls
+completely within the equivalence bounds, the \emph{p}-value for the
+TOST continues to differentiate between results as a function of how far
+the confidence interval lies within the equivalence bounds (the further
+the confidence interval is from both bounds, the lower the
+\emph{p}-value). The easiest way to see this is by plotting the SGPV
+against the \emph{p}-value from the TOST procedure. The situations where
+the \emph{p}-values from the TOST procedure continue to differentiate
+based on how extreme the results are, but the SGPV is a fixed value are
+indicated by the parts of the curve where there are vertical straight
+lines at second generation \emph{p}-values of 0 and 1.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV5-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV5-1.pdf}
 \caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from
@@
 
-A third situation in which the SGPV deviates from the TOST
-\emph{p}-value is whenever the CI is wider than the equivalence range,
+A third situation in which the SGPV remains stable across a range of
+observed effects, while the TOST \emph{p}-value continues to
+differentiate, is whenever the CI is wider than the equivalence range,
 and the CI overlaps with the upper \emph{and} lower equivalence bound.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV6-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV6-1.pdf}
 \caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV7-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV7-1.pdf}
 \caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV8-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV8-1.pdf}
 \caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV9-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV9-1.pdf}
 \caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV10-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV10-1.pdf}
 \caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from
@@
 
-\subsection{The relation between equivalence tests and SGPV when
-confidence intervals are not
-symmetrical}\label{the-relation-between-equivalence-tests-and-sgpv-when-confidence-intervals-are-not-symmetrical}
+\subsection{The relation between equivalence tests and SGPV when for
+asymmetrical confidence intervals around
+correlations}\label{the-relation-between-equivalence-tests-and-sgpv-when-for-asymmetrical-confidence-intervals-around-correlations}
 
@@
 between -1 and 1, confidence intervals are only symmetric for a
-correlation of exactly 0. The confidence interval becomes increasingly
-asymmetric as the observed correlation nears -1 or 1. For example, with
-ten observations, an observed correlation of 0 has a symmetric 95\%
-confidence interval ranging from -0.630 to 0.630, while and observed
-correlation of 0.7 has an asymmetric 95\% confidence interval ranging
-from 0.126 to 0.993.
+correlation of exactly 0. The confidence interval for a correaltion
+becomes increasingly asymmetric as the observed correlation nears -1 or
+1. For example, with ten observations, an observed correlation of 0 has
+a symmetric 95\% confidence interval ranging from -0.630 to 0.630, while
+and observed correlation of 0.7 has an asymmetric 95\% confidence
+interval ranging from 0.126 to 0.993. Note that calculating confidence
+intervals for a correlation involves a Fisher's z-transformation, which
+transforms values such that they are approximately normally distributed,
+which allows one to compute symmetric confidence intervals, which are
+then retransformed into a correlation, where the confidence intervals
+are asymmetric if the correlation is not exactly zero.
 
-The effect of asymmetric confidence intervals is most noticeable at
-smaller sample sizes. In Figure \ref{fig:TOSTSGPV11} we plot the
-\emph{p}-values from equivalence tests and the SGPV (again plotted as
-1-SGPV for ease of comparison) for correlations. The sample size is 30
-pairs of observations, and the lower and upper equivalence bounds are
-set to -0.45 and 0.45, with an alpha of 0.05. As the observed
+The effect of asymmetric confidence intervals around correlations is
+most noticeable at smaller sample sizes. In Figure \ref{fig:TOSTSGPV11}
+we plot the \emph{p}-values from equivalence tests and the SGPV (again
+plotted as 1-SGPV for ease of comparison) for correlations. The sample
+size is 30 pairs of observations, and the lower and upper equivalence
+bounds are set to -0.45 and 0.45, with an alpha of 0.05. As the observed
 correlation in the sample moves from -1 to 0 the \emph{p}-value from the
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV11-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV11-1.pdf}
 \caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV12-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV12-1.pdf}
 \caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
@@
 This example illustrates the difference between a proportion and a
-probability. There is always a 50\% probability of observing a
-correlation smaller or larger than the true correlation, but the SGPV
-for this situation depends on how far away the observed correlation is
-from 0. The further away from 0, the larger the SGPV when the observed
-mean falls on the equivalence bound. The SGPV is the proportion of
-values in a 95\% confidence interval that overlap with the equivalence
-range, but not the probability that these values will be observed. In
-the most extreme case (i.e., a sample size of 4, and equivalence bounds
-set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
-of the confidence interval overlaps with the equivalence range, even
-though in the long run only 50\% of the correlations observed in the
-future will fall in this range. It should be noted that in larger sample
-sizes the SGPV is closer to 0.5 whenever the observed correlation falls
-on the equivalence bound, but this extreme example nevertheless clearly
-illustrates the difference between question the SGPV answers, and the
-question a \emph{p}-value answers. The conclusion of this section on
-asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
-interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
-0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
-TOST procedure are always directly related at these values. Although
+probability. As long as data is normally distributed, there is always a
+50\% probability of observing a correlation smaller or larger than the
+true correlation, but the SGPV for this situation depends on how far
+away the observed correlation is from 0. The further away from 0, the
+larger the SGPV when the observed mean falls on the equivalence bound.
+The SGPV is the proportion of values in a 95\% confidence interval that
+overlap with the equivalence range, but not the probability that these
+values will be observed. In the most extreme case (i.e., a sample size
+of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed
+correlation of 0.99) 58.10\% of the confidence interval overlaps with
+the equivalence range, even though in the long run only 50\% of the
+correlations observed in the future will fall in this range. It should
+be noted that in larger sample sizes the SGPV is closer to 0.5 whenever
+the observed correlation falls on the equivalence bound, but this
+extreme example nevertheless clearly illustrates the difference between
+question the SGPV answers, and the question a \emph{p}-value answers.
+The conclusion of this section on asymmetric confidence intervals is
+that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{}
+0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the
+SGPV and \emph{p}-value for the TOST procedure are always directly
+related at the values \emph{p} = 0.025 and \emph{p} = 0.975. Although
 Blume et al. (2018) state that \enquote{the degree of overlap conveys
@@
 between 0 and 1 is not interpretable as \enquote{compatibility with the
-null hypothesis}. Indeed, Blume and colleagues write in the supplemental
-material that \enquote{The magnitude of an inconclusive
+null hypothesis} under the assumption of normally distributed data, and
+the generalizability of this statement needs to be examined beyond
+normally distributed data. Indeed, Blume and colleagues write in the
+supplemental material that \enquote{The magnitude of an inconclusive
 second-generation \emph{p}-value can vary slightly when the effect size
@@
 to existing approaches and specify its relative strengths and
-weaknesses. First of all, the SGPV is a descriptive statistic (unlike
-the \emph{p}-value that is calculated for an equivalence test, which is
-an inferential statistic) that provides the proportion of overlap of the
-confidence interval and the equivalence range. Even though a SGPV of 1
-or 0 has a clear interpretation (we can reject effects outside or inside
-the equivalence range), intermediate values are not as easy to interpret
-(especially for effects that have asymmetric confidence intervals). In
-one sense, they are what they are (the proportion of overlap), but it
-can be unclear what this number tells us about the data we have
-collected. This is not too problematic, since the main use of the SGPV
-(e.g., in all examples provided by Blume and colleagues) seems to be to
-examine whether the SGPV is 0, 1, or inconclusive. This interpretation
-of a SGPV as allowing researchers to reject the null, reject the
-presence of a meaningful effect, or remaining inconclusive is very
-similar to the Neyman-Pearson interpretation of combining a
-null-hypothesis test and an equivalence test (Lakens et al., 2018). The
-difference is that where a SGPV of 1 can be interpreted as \emph{p}
+weaknesses. First of all, even though a SGPV of 1 or 0 has a clear
+interpretation (we can reject effects outside or inside the equivalence
+range), intermediate values are not as easy to interpret (especially for
+effects that have asymmetric confidence intervals). In one sense, they
+are what they are (the proportion of overlap), but it can be unclear
+what this number tells us about the data we have collected. This is not
+too problematic, since the main use of the SGPV (e.g., in all examples
+provided by Blume and colleagues) seems to be to examine whether the
+SGPV is 0, 1, or inconclusive. As already mentioned, this interpretation
+of a SGPV as is very similar to the Neyman-Pearson interpretation of an
+equivalence test and a minimum effect tests (which are complementary).
+The difference is that where a SGPV of 1 can be interpreted as \emph{p}
 \textless{} .025, equivalence tests provide exact \emph{p}-values, and
@@
 provide information of interest to readers about how precisely how
-surprising the data is under the null model. Equivalence tests combined
-with null-hypothesis significance tests also allow researchers to
+surprising the data, or more extreme data, is under the null model. Some
+researchers might be interested in combining an equivalence tests with a
+null-hypothesis significance test. This allows a researcher to ask
+whether there is an effect that is statistically different from zero,
+and whether effect sizes that are considered meaningful can be rejected.
+Equivalence tests combined with null-hypothesis tests classify results
+into four possible categories, and for example allow researchers to
 conclude an effect is significant \emph{and} equivalent (i.e.,
 statistically different from zero, but also too small to be considered
-meaningful). Thus, the SGPV is used to classify results into one of
-three possible categories (with the data falling inside or outside the
-equivalence range, or being inconclusive), while equivalence tests
-combined with null-hypothesis tests classify results into four possible
-categories.
+meaningful, see (Lakens et al., 2018)).
 
@@
 to differentiate (see for example Figure \ref{fig:TOSTSGPV6}). An
-important benefit of equivalence tests is that is does not need such a
+important benefit of equivalence tests is that it does not need such a
 correction to prevent misleading results.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/TOSTSGPV13-1.pdf}
+\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV13-1.pdf}
 \caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
@@
 sample correction} as currently implemented in the calculation of the
-SGPV see Figure \ref{fig:TOSTSGPV13} below. In this figure observed
+SGPV see Figure \ref{fig:TOSTSGPV13}. In this figure observed
 correlations (from a sample size of 10) from -1 to 1 are tested against
@@
 
-Blume et al. (2018) argue that the SGPV has improved error control, in
-that the conclusion that the 95\% confidence interval lies completely
-outside the equivalence range around zero will necessarily occur less
-frequently than a Type I error in a null-hypothesis test (where the 95\%
-confidence interval only needs to not overlap with zero). However, the
-SGPV has a \emph{lower} error rate than a null-hypothesis test, not a
-\emph{more accurate} error rate. In a Neyman-Pearson perspective (which
-forms the basis of equivalence tests) the goal is not to end up with an
-error rate that is as low as possible (to achieve that, one simply
-adjusts the alpha level), but with a decision procedure that, when
-applied, yields a desired error rate with high accuracy. We show here
-that the SGPV and equivalence tests are directly related, and so are
-their error rates. The TOST procedure uses a 90\% confidence interval
-because it is based on two \emph{one-sided} tests, and thus the
-confidence interval is 1-2\(\times\)\(\alpha\), and because both tests
-need to be significant to conclude equivalence, no adjustment for
-multiple comparisons is needed. The TOST procedure always has higher
-power to declare equivalence than the SGPV, which relies on a 95\%
-confidence interval (but note that there is no reason to always set the
-alpha level to 0.05).
-
 Blume et al. (2018) claim that \enquote{Adjustments for multiple
-comparisons are obviated} (p.~15) and that \enquote{second-generation
-\emph{p}-values provide a proper scientific adjustment for multiple
-comparisons}. However, this is not correct. With a sufficient number of
-looks error rates can rise above the nominal alpha level (both when
-compared to equivalence and minimal effect tests, but even when compared
-to a null-hypothesis test). When directly comparing equivalence tests
-and the SGPV, multiple comparisons inflate the probability that one
-erronously concludes there is \emph{no} effect, where there \emph{is} a
-true effect size that equals the equivalence bound, just as quickly for
-the SGPV as for equivalence tests, because they are directly related. To
-conclude, the idea that the SGPV improves error rates does not hold up
-under closer scrutiny, and the recommendation to ignore adjustments for
-multiple comparisons has the potential to increase false positives in
-the literature. Equivalence tests provide an easier and more formal way
-to control both Type I error rates (by setting the alpha level) and the
-Type II error rate (by performing an a-priori power analysis).
+comparisons are obviated} (p.~15). However, this is not correct. Given
+the direct relationship between TOST and SGPV highlighted in this
+manuscript (where to TOST \emph{p} = 0.025 equals SGPV = 1, as long as
+the SGPV is calculated based on confidence intervals, and assuming
+continuous and normally distributed data), not correcting for multiple
+comparisons will inflate the probability of concluding the absence of a
+meaningful effect based on the SGPV in exactly the same way as for
+equivalence tests. Whenever statistical tests are interpreted as support
+for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so
+erroneously, and if researchers want to control error rates, they need
+to correct for multiple comparisons.
 
@@
 second generation \emph{p}-values to the statistical toolbox. The
-novelty of the SGPV lies in its use as a descriptive statistic, but this
-use can be limited when confidence intervals are asymmetrical or wider
-than the equivalence range. There are strong similarities with
-\emph{p}-values from the TOST procedure, and in all situations where the
-statistics yield different results, the behavior of the \emph{p}-value
-from the TOST procedure is more consistent and easier to interpret. We
-hope this overview of the relationship between the SGPV and equivalence
-tests will help researchers to make an informed decision about which
-statistical approach provides the best answer to their question. Our
-comparisons show that when proposing alternatives to null-hypothesis
-tests, it is important to compare new proposals to already existing
-procedures. We believe equivalence tests achieve the goals of the second
-generation \emph{p}-value while allowing users to more easily control
-error rates, and while yielding more consistent statistical outcomes.
+novelty of the SGPV can be limited when confidence intervals are
+asymmetrical or wider than the equivalence range. There are strong
+similarities with \emph{p}-values from the TOST procedure, and in all
+situations where the statistics yield different results, the behavior of
+the \emph{p}-value from the TOST procedure is more consistent and easier
+to interpret. We hope this overview of the relationship between the SGPV
+and equivalence tests will help researchers to make an informed decision
+about which statistical approach provides the best answer to their
+question. Our comparisons show that when proposing alternatives to
+null-hypothesis tests, it is important to compare new proposals to
+already existing procedures. We believe equivalence tests achieve the
+goals of the second generation \emph{p}-value while allowing users to
+easily control error rates, and while yielding more consistent
+statistical outcomes.
 

### 2019-03-09 manuscript.R1.Rmd
Few typos and minor changes

@@
 abstract: |
-  To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
+  To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data are compared against a range of values that are equivalent to the absence of a meaningful effect.
 Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interpreted as a statistically significant difference.
@@
 To test predictions researchers predominantly rely on null-hypothesis tests. 
-This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero. 
+This statistical approach can be used to examine whether observed data are sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero. 
 Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*.
@@
 The TOST procedure also relies on the confidence interval around the effect. 
-In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
-For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see [@meyners_equivalence_2012].
+In the TOST procedure the data are tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test [@lakens_equivalence_2018].
+For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see @meyners_equivalence_2012.
 If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
@@
 As the observed mean in a one-sample *t*-test lies closer to the test value, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly. 
-As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed.
+As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data are not uniformly distributed.
 The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
@@
 
-##The relation between equivalence tests and SGPV when for asymmetrical confidence intervals around correlations
+##The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations
 
@@
 For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0.
-The confidence interval for a correaltion becomes increasingly asymmetric as the observed correlation nears -1 or 1.
+The confidence interval for a correlation becomes increasingly asymmetric as the observed correlation nears -1 or 1.
 For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.993.
@@
 This example illustrates the difference between a proportion and a probability.
-As long as data is normally distributed, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+As long as data are normally distributed, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
 The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
@@
 This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) seems to be to examine whether the SGPV is 0, 1, or inconclusive.
-As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).
+As already mentioned, this interpretation of a SGPV is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).
 The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example *p* = 0.048 and *p* = 0.002.
@@
 This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
-Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see [@lakens_equivalence_2018]).
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see @lakens_equivalence_2018).
 

### 2019-03-09 reply_to_reviews.R1.Rmd
typos

@@
 Indeed, we acknowledge that "Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as “compatibility with the null hypothesis”." So the SGPV is an inferential statistic when interpreted dichotomously.
-We will leave our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should be interpreted to future researchers, and we do not make any statements about whether such values are descriptive our inferential.
+We will leave our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should be interpreted to future researchers, and we do not make any statements about whether such values are descriptive or inferential.
 
@@
 Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9, 13).
-Nevertheless, in these graphs, we still have the correspondence between these 3 points (or at leas tthe 2 points if the CI is too wide compared to the equivalence bounds to ever observe a *p* = 0.025).
+Nevertheless, in these graphs, we still have the correspondence between these 3 points (or at least the 2 points if the CI is too wide compared to the equivalence bounds to ever observe a *p* = 0.025).
 To make it clearer that we talk about the overlap in these 3 critical points, we have added:
@@
 Findings identified by second-generation p-values are less likely to be false discoveries than findings identified by classical p-values.
-Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons." Clearly, it can not both be true that the the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
+Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons." Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
 
@@
 We do not need any other argument to make our claims about multiple comparisons that fact, noted by the reviewer, that "The maximum Type I Error rate for the SGPV over the null interval is 5%, exactly like the TOST test." This is true, and it logically follows (hence, no mathematical proof is needed) that error rates need to be controlled when using SGPV to conclude support for the null-hypothesis.
-We blieve error control is important enough to include this paragraph in the paper, as we believe that lack of error control was one of the  causes of the replication crisis in psychology.
+We believe error control is important enough to include this paragraph in the paper, as we believe that lack of error control was one of the  causes of the replication crisis in psychology.
 

### 2019-03-09 reply_to_reviews.R1.tex
typos

@@
 
-Correspondence concerning this article should be addressed to Daniël
-Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
-E-mail:
-\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
+E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
 \abstract{
-We respond to all the comments raised by the two reviewers and the
-editors. We would like to thank the editor and reviewers for their
-suggestions for improvements, which we believe made our main argument
-much clearer, focussed, and formally correct. We feel we were able to
-accomodate all suggestions, and we hope you think our submission is
-ready to be accepted for publication in Meta-Psychology.
+We respond to all the comments raised by the two reviewers and the editors.
+We would like to thank the editor and reviewers for their suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct.
+We feel we were able to accomodate all suggestions, and we hope you think our submission is ready to be accepted for publication in Meta-Psychology.
 
@@
 
-Thank you for your comments on our submitted manuscript. We have
-incorporated your three comments:
+Thank you for your comments on our submitted manuscript. We have incorporated your three comments:
 
@@
 \item
-  We moved the first sentence on page 3 into the next paragraph (well
-  spotted).
+  We moved the first sentence on page 3 into the next paragraph (well spotted).
 \item
-  The code for the Shiny app was on GitHub, and the GitHub repository is
-  linked to the OSF project page, but we have added a component to the
-  OSF page and also directly added the Shiny App code there to make it
-  easier to find: \url{https://osf.io/7f8uq/}
+  The code for the Shiny app was on GitHub, and the GitHub repository is linked to the OSF project page, but we have added a component to the OSF page and also directly added the Shiny App code there to make it easier to find: \url{https://osf.io/7f8uq/}
 \item
-  We now immediately refer to Figure 4 in the beginning of the paragraph
-  in which the Figure is described.
+  We now immediately refer to Figure 4 in the beginning of the paragraph in which the Figure is described.
 \end{enumerate}
@@
 
-\section{Reply to Reviewer 1}\label{reply-to-reviewer-1}
+\hypertarget{reply-to-reviewer-1}{%
+\section{Reply to Reviewer 1}\label{reply-to-reviewer-1}}
 
@@
 \item
-  We have changed the part of the sentence \enquote{Our conclusions
-  about the relationship between TOST p-values and SGPV in this article
-  are not dependent upon any specific example} into \enquote{Our
-  conclusions about the relationship between TOST \emph{p}-values and
-  SGPV hold for an SGPV calculated from confidence intervals, and
-  assuming continuous normally distributed data.}. We mainly intended to
-  refer to our conclusion that: \enquote{When confidence intervals are
-  symmetric we can think of the SGPV as a straight line that is directly
-  related to the \emph{p}-value from an equivalence test for three
-  values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
-  p-values for TOST of 0.025 and 0.975 (corresponding to the largest
-  observed mean where the SGPV is 0 and the smallest observed mean where
-  the SGPV is 1). We have now made it clearer that when we talk about
-  \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we
-  mean that there is a direct relation between three points.
+  We have changed the part of the sentence \enquote{Our conclusions about the relationship between TOST p-values and SGPV in this article are not dependent upon any specific example} into \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.}.
+We mainly intended to refer to our conclusion that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the p-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
+We have now made it clearer that when we talk about \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we mean that there is a direct relation between three points.
 \item
-  We appreciate correcting our use of the term \enquote{unrelated} and
-  teaching us the word \enquote{bijective}. We used the word
-  \enquote{unrelated} somewhat naievely, looking at the Figures and
-  wanting to express that across the three identified situations, a
-  different TOST \emph{p}-value does not imply a different SGPV - the
-  SGPV across these ranges of means is aways the same (either 0, 0.5, or
-  1) while the TOST p-value differs across this range of means. We now
-  just directly say what we originally meant, and no longer use the word
-  \enquote{unrelated}. For example, \enquote{There are three situations
-  where \emph{p}-values for TOST differentiate between observed results,
-  while the SGPV does not differentiate.} and \enquote{While the SGPV is
-  1 as long as the confidence interval falls completely within the
-  equivalence bounds, the \emph{p}-value for the TOST continues to
-  differentiate between results as a function of how far the confidence
-  interval lies within the equivalence bounds (the further the
-  confidence interval is from both bounds, the lower the
-  \emph{p}-value).} and similarly \enquote{A third situation in which
-  the SGPV remains stable across a range of observed effects, while the
-  TOST \emph{p}-value continues to differentiate, is whenever the CI is
-  wider than the equivalence range, and the CI overlaps with the upper
-  \emph{and} lower equivalence bound.}
+  We appreciate correcting our use of the term \enquote{unrelated} and teaching us the word \enquote{bijective}.
+We used the word \enquote{unrelated} somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST \emph{p}-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST p-value differs across this range of means.
+We now just directly say what we originally meant, and no longer use the word \enquote{unrelated}.
+For example, \enquote{There are three situations where \emph{p}-values for TOST differentiate between observed results, while the SGPV does not differentiate.} and \enquote{While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the \emph{p}-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the \emph{p}-value).} and similarly \enquote{A third situation in which the SGPV remains stable across a range of observed effects, while the TOST \emph{p}-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper \emph{and} lower equivalence bound.}
 \item
-  Please do not feel like you ever need to apologize for having formal
-  training we lack, that allows you to point out whenever we make
-  formally incorrect statements. This is exactly why we submit our work
-  for peer review - to be able to improve it based on feedback from
-  experts. We now preface the sentence with \enquote{As long as data is
-  normally distributed,}. We follow your recommendation throughout to
-  not generalize beyond the scenarios we study. In the second paragraph
-  of the manuscript we now clearly state: \enquote{We limit our analysis
-  to normally distributed continuous data.} See also point 5 below.
+  Please do not feel like you ever need to apologize for having formal training we lack, that allows you to point out whenever we make formally incorrect statements.
+This is exactly why we submit our work for peer review - to be able to improve it based on feedback from experts.
+We now preface the sentence with \enquote{As long as data is normally distributed,}.
+We follow your recommendation throughout to not generalize beyond the scenarios we study.
+In the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} See also point 5 below.
 \item
-  After making the change at point 2 above, we now think the sentence
-  \enquote{The conclusion of this section on asymmetric confidence
-  intervals is that a SGPV of 1 or 0 can still be interpreted as a p
-  \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test,
-  since the SGPV and p-value for the TOST procedure are always directly
-  related at these values.} should no longer be confusing. To make the
-  sentence clearer, we have changed \enquote{these values} into
-  \enquote{at the values p = 0.025 and p = 0.975} It should now be clear
-  the sections are not contradictory - TOST differentiates below p
-  \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
+  After making the change at point 2 above, we now think the sentence \enquote{The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test, since the SGPV and p-value for the TOST
+  procedure are always directly related at these values.} should no longer be confusing.
+To make the sentence clearer, we have changed \enquote{these values} into \enquote{at the values p = 0.025 and p = 0.975} It should now be clear the sections are not contradictory - TOST differentiates below p \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
 \item
-  We agree that is unclear whether the original statement by Blume et al
-  that \enquote{the degree of overlap conveys how compatible the data
-  are with the null premise} holds in general. We have now amended the
-  sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly
-  interpreted, a SGPV between 0 and 1 is not interpretable as
-  \enquote{compatibility with the null hypothesis} under the assumption
-  of normally distributed data, and the generalizability of this
-  statement needs to be examined beyond normally distributed data
-  requires further examination.}
+  We agree that is unclear whether the original statement by Blume et al that \enquote{the degree of overlap conveys how compatible the data are with the null premise} holds in general.
+We have now amended the sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis} under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data requires further examination.}
 \item
-  We have removed our earlier statements that the SGPV only works as a
-  descriptive statistic. We deleted the sentence \enquote{the SGPV is a
-  descriptive statistic (unlike the \emph{p}-value that is calculated
-  for an equivalence test, which is an inferential statistic) that
-  provides the proportion of overlap of the confidence interval and the
-  equivalence range.} and deleted \enquote{The novelty of the SGPV lies
-  in its use as a descriptive statistic} from the conclusion. Indeed, we
-  acknowledge that \enquote{Although a SGPV of 1 or 0 can be directly
-  interpreted, a SGPV between 0 and 1 is not interpretable as
-  \enquote{compatibility with the null hypothesis}.} So the SGPV is an
-  inferential statistic when interpreted dichotomously. We will leave
-  our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should
-  be interpreted to future researchers, and we do not make any
-  statements about whether such values are descriptive our inferential.
+  We have removed our earlier statements that the SGPV only works as a descriptive statistic.
+We deleted the sentence \enquote{the SGPV is a descriptive statistic (unlike the \emph{p}-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.} and deleted \enquote{The novelty of the SGPV lies in its use as a descriptive statistic} from the conclusion.
+Indeed, we acknowledge that \enquote{Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as ``compatibility with the null hypothesis}." So the SGPV is an inferential statistic when interpreted dichotomously.
+We will leave our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should be interpreted to future researchers, and we do not make any statements about whether such values are descriptive or inferential.
 \item
-  We agree that using TOST for small samples (e.g., N = 4) will not be
-  useful. Indeed, an a-priori power analysis for equivalence tests would
-  prevent anyone from planning such a study, since the result will be
-  that such a study has 0 power - the CI will never fit withing the
-  equivalence bounds.
+  We agree that using TOST for small samples (e.g., N = 4) will not be useful.
+Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.
 \item
-  With our recommendations, we have limited our conclusions to the
-  specific cases we have examined, and noted the possibility for future
-  research to examine a wider set of assumptions. An additional change
-  not mentioned above is that we renamed the section on asymmetric
-  confidence intervals to the more specific \enquote{The relation
-  between equivalence tests and SGPV for asymmetrical confidence
-  intervals around correlations} instead of the more general
-  \enquote{The relation between equivalence tests and SGPV when
-  confidence intervals are not symmetrical}. We appreciate the very
-  positive evaluation of our manuscript, but even more so the criticism
-  which allowed us to improve the manuscript.
+  With our recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions.
+An additional change not mentioned above is that we renamed the section on asymmetric confidence intervals to the more specific \enquote{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations} instead of the more general \enquote{The relation between equivalence tests and SGPV when confidence intervals are not symmetrical}.
+We appreciate the very positive evaluation of our manuscript, but even more so the criticism which allowed us to improve the manuscript.
 \end{enumerate}
 
-\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}
+\hypertarget{reply-to-reviewer-2}{%
+\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}}
 
-Before listing major points, the reviewer raises the point that we
-compare SGPV with p-values from TOST throughout our paper, and in all
-figures, but then at the end, in page 20, we write:
+Before listing major points, the reviewer raises the point that we compare SGPV with p-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
 
-\enquote{Equivalence tests combined with null-hypothesis significance
-tests also allow researchers to conclude an effect is significant and
-equivalent (i.e., statistically different from zero, but also too small
-to be considered meaningful). Thus, the SGPV is used to classify results
-into one of three possible categories (with the data falling inside or
-outside the equivalence range, or being inconclusive), while equivalence
-tests combined with null-hypothesis tests classify results into four
-possible categories.}
+\enquote{Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant and equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
+Thus, the SGPV is used to classify results into one of three possible categories (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories.}
 
-The reviewer says that \enquote{the authors suddenly switch the premise;
-now the SGPV should be replaced by two p-values, one from an equivalence
-test and one from a NHST}. However, we do not suggest to replace the
-SGPV with an equivalence test and a NHST at all. In our manuscript, we
-already pointed out how the SGPV is basically the same as an equivalence
-test and a minimum effect test (on page 7):
+The reviewer says that \enquote{the authors suddenly switch the premise; now the SGPV should be replaced by two p-values, one from an equivalence test and one from a NHST}.
+However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all.
+In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7):
 
-\enquote{The third point where the SGPV and the p-value from the TOST
-procedure should overlap is where the 95\% CI falls completely outside
-of the equivalence range, but one endpoint of the confidence interval is
-equal to the equivalence bound (see situation C in Figure 3), when the
-p-value will always be 0.975. Note that this situation is in essence a
-minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal of a
-minimum-effect is not just to reject a difference of zero, but to reject
-the smallest effect size of interest (i.e., the equivalence bounds). The
-SGPV summarizes the information from an equivalence test and a
-minimum-effect test.}
+\enquote{The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975.
+Note that this
+situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014).
+The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
+The SGPV summarizes the information from an equivalence test and a minimum-effect test.}
 
 One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives
-away that the equivalence test can be interpreted as a minimum effect
-test against the equivalence bound. When the TOST \emph{p}-value is
-0.975, the 95\% CI touches either the upper or lower equivalence bound,
-and fall complately outside of the equivalence range. This is
-mathematically identical to a statistically significant minimum effect
-test at p \textless{} 0.05. We didn't make this explicit, but we clearly
-should have. We have added the sentence (on page 7):
+However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
+When the TOST \emph{p}-value is 0.975, the 95\% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range.
+This is mathematically identical to a statistically significant minimum effect test at p \textless{} 0.05.
+We didn't make this explicit, but we clearly should have.
+We have added the sentence (on page 7):
 
-\enquote{An equivalence test and minimum effect test against the same
-equivalence bound are complementary, and when a TOST \emph{p}-value is
-larger than 0.975, the \emph{p}-value for the minimum effect test is
-smaller than 0.05, and the minimum effect test provides no additional
-information that can not be derived from the \emph{p}-value from the
-equivalence test.}
+\enquote{An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST \emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the \emph{p}-value from the equivalence test.}
 
-One might wonder why then, on page 20, why we introduce the idea to
-perform both a null-hypothesis significance test and an equivalence
-test. We were not clear enough. And indeed, the sentence \enquote{This
-interpretation of a SGPV as allowing researchers to reject the null,
-reject the presence of a meaningful effect, or remaining inconclusive is
-very similar to the Neyman-Pearson interpretation of combining a
-null-hypothesis test and an equivalence test} was simply confusing. We
-have deleted this sentence and replaced it with \enquote{As already
-mentioned, this interpretation of a SGPV as is very similar to the
-Neyman-Pearson interpretation of an equivalence test and a minimum
-effect tests (which are complementary).}
+One might wonder why then, on page 20, why we introduce the idea to perform both a null-hypothesis significance test and an equivalence test.
+We were not clear enough.
+And indeed, the sentence \enquote{This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test} was simply confusing.
+We have deleted this sentence and replaced it with \enquote{As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).}
 
-Furthermore, to prevent the apparent confusion about why we suggested to
-perform a null-hypothesis test and equivalence test. Part of this
-confusion was our original sentence comparing the SGPV and a combination
-of NHST and an equivalence test which was not needed, and we understand
-it made it seem as if SGPV needs to be replaced by a combination of
-other tests. But that is not what we propose. Werewrote the paragraph:
+Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test.
+Part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
+But that is not what we propose.
+Werewrote the paragraph:
 
-\enquote{Some researchers might be interested in combining an
-equivalence tests with a null-hypothesis significance test. This allows
-a researcher to ask whether there is an effect that is statistically
-different from zero, and whether effect sizes that are considered
-meaningful can be rejected. Equivalence tests combined with
-null-hypothesis tests classify results into four possible categories,
-and for example allow researchers to conclude an effect is significant
-and equivalent (i.e., statistically different from zero, but also too
-small to be considered meaningful, see (Lakens et al., 2018)).}
+\enquote{Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test.
+This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant and equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see (Lakens et al., 2018)).}
 
-We hope this makes it clear we are not pulling a bait and switch. The
-SGPV is strongly related to an equivalence test (or it's complement, a
-minimum effect test). Describing the relation between the SGPV and TOST
-is our main contribution. We just wanted to mention that researchers
-might want to combine an equivalence test with a NHST, because in the
-literature, this is a question we see many psychologists ask.
+We hope this makes it clear we are not pulling a bait and switch.
+The SGPV is strongly related to an equivalence test (or it's complement, a minimum effect test).
+Describing the relation between the SGPV and TOST is our main contribution.
+We just wanted to mention that researchers might want to combine an equivalence test with a NHST, because in the literature, this is a question we see many psychologists ask.
 
@@
 \item
-  In line with the comments by reviewer 1, in the second paragraph of
-  the manuscript we now clearly state: \enquote{We limit our analysis to
-  normally distributed continuous data.} After all, p-values and
-  confidence are directly related, but Bayesian credible intervals would
-  not necessarily be, depending on the prior. Blume et al (2018) limit
-  their examples to confidence intervals, but explicitly acknowledge
-  other possibilities (such as Bayesian intervals). We look forward to
-  future papers that illustrate the SGPV with other interval estimates
-  and are happy to add the limitation to continuous normally distributed
-  data in our article. Note that we did not add that the correspondence
-  only holds for situations where the SE's are small compared to the
-  width of the equivalence range, as the reviewer suggests.
+  In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} After all, p-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
+Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals).
+We look forward to future papers that illustrate the SGPV with other interval estimates and are happy to add the limitation to continuous normally distributed data in our article.
+Note that we did not add that the correspondence only holds for situations where the SE's are small compared to the width of the equivalence range, as the reviewer suggests.
 \item
-  The reviewer repeats that the correspondence only holds when SE's are
-  small compared to the width of the equivalence range. The
-  correspondence is not in the shape of the curve (which clearly differs
-  across Figures 2, 6, and 9). We clearly state that: \enquote{When
-  confidence intervals are symmetric we can think of the SGPV as a
-  straight line that is directly related to the p-value from an
-  equivalence test for three values.} This correspondence is not
-  dependent upon the SE's. It will always hold for continuous normal
-  data. The reviewer says that \enquote{The paper does not provide
-  theoretical justification for this connection nor any proofs.} We are
-  unsure which proof is needed for the overlap between the three points,
-  since it is rather trivial and we believe the explanation in the paper
-  is very clear.
+  The reviewer repeats that the correspondence only holds when SE's are small compared to the width of the equivalence range.
+The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
+We clearly state that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the p-value from an equivalence test for three values.} This correspondence is not dependent upon the SE's.
+It will always hold for continuous normal data.
+The reviewer says that \enquote{The paper does not provide theoretical justification for this connection nor any proofs.} We are unsure which proof is needed for the overlap between the three points, since it is rather trivial and we believe the explanation in the paper is very clear.
 \end{enumerate}
 
-For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and
-SGPV = 1, and TOST p = 0.975 and SGPV = 1: ``The SGPV is 50\% when the
-observed mean falls exactly on the lower or upper equivalence bound,
-because 50\% of the symmetrical confidence interval overlaps with the
-equivalence range. When the observed mean equals the equivalence bound,
-the difference between the mean in the data and the equivalence bound is
-0, the t-value for the equivalence test is also 0, and thus the p-value
-is 0.5 (situation A, Figure 3). Two other points always have to overlap.
-When the 95\% CI falls completely inside the equivalence region, and one
-endpoint of the confidence interval is exactly equal to one of the
-equivalence bounds (see situation B in Figure 3) the TOST p-value (which
-relies on a one-sided test) is always 0.025, and the SGPV is 1. The
-third point where the SGPV and the p-value from the TOST procedure
-should overlap is where the 95\% CI falls completely outside of the
-equivalence range, but one endpoint of the confidence interval is equal
-to the equivalence bound (see situation C in Figure 3), when the p-value
-will always be 0.975, and the SGPV is 0.
+For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50\% when the observed mean falls exactly on the lower or upper equivalence bound, because 50\% of the symmetrical confidence interval overlaps with the equivalence range.
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the p-value is 0.5 (situation A, Figure 3).
+Two other points always have to overlap.
+When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST p-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975, and the SGPV is 0.
 
-We do not think we can provide any other proof for this. A confidence
-interval and a p-value are directly related. The TOST procedure is a
-test using the confidence interval, and the SGPV (now that we clearly
-limited our discussion to a SGPV based on a confidence interval
-calculated from continuous normal data) compared against the same
-equivalence bounds will be related as we describe. But we believe our
-article might not have been clear enough about that we limit our
-discussion about the correspondence of the curves to these 3 points.
-Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
-13). Nevertheless, in these graphs, we still have the correspondence
-between these 3 points (or at leas tthe 2 points if the CI is too wide
-compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
-To make it clearer that we talk about the overlap in these 3 critical
-points, we have added:
+We do not think we can provide any other proof for this.
+A confidence interval and a p-value are directly related.
+The TOST procedure is a test using the confidence interval, and the SGPV (now that we clearly limited our discussion to a SGPV based on a confidence interval calculated from continuous normal data) compared against the same equivalence bounds will be related as we describe.
+But we believe our article might not have been clear enough about that we limit our discussion about the correspondence of the curves to these 3 points.
+Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9, 13).
+Nevertheless, in these graphs, we still have the correspondence between these 3 points (or at least the 2 points if the CI is too wide compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
+To make it clearer that we talk about the overlap in these 3 critical points, we have added:
 
-\enquote{When we discuss the relationship between the p-values from TOST
-and the SGPV, we focus on their correspondence at three values, namely
-where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} =
-0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
-These three values are important for the SGPV because they indicate the
-values at which the SGPV indicates the data should be interpreted as
-compatible with the null hypothesis (SGPV = 1), or with the alternative
-hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV
-= 0.5). These three points of overlap are indicated by the horizontal
-dotted lines in Figure 2.}
+\enquote{When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
+These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
+These three points of overlap are indicated by the horizontal dotted lines in Figure 2.}
 
-We believe this satisfactorily addresses the point by the reviewer that
-\enquote{Because of this lack of discussion, the reader can easily miss
-that the close correspondence only occurs when the sample size is large
-enough that the standard error is very small relative to the width of
-the equivalence zone.} Indeed, the correspondence between the TOST and
-SGPV at these 3 points should be obvious to anyone who understands the
-relationship between a p-value and a confidence interval, so we do not
-provide any further proof, but we hope that clarifying we talk about the
-correspondence of these 3 points, and not the entire curve, is
-sufficient to address point 2.
+We believe this satisfactorily addresses the point by the reviewer that \enquote{Because of this
+lack of discussion, the reader can easily miss that the close correspondence only occurs when
+the sample size is large enough that the standard error is very small relative to the width of the
+equivalence zone.} Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a p-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
 
@@
 \item
-  We are aware of the Beger and Hsu (1996) article. But if the reviewer
-  reads more closely, it should be clear that we never say the TOST is
-  UMP. We say that TOST is a test procedure that aims to control error
-  rates - our use of the term \enquote{Neyman-Pearson perspective}
-  refers to the classic difference between significance tests (Fisher)
-  and hypothesis tests (Neyman-Pearson). We do not imply that any test
-  that fixes an error rate is a NP test. Because many psychologists are
-  not trained in the difference between a Fisherian approach and a
-  Neyman Pearson approach to the use of p-values, we are simply adding a
-  \enquote{Neyman-Pearson} approach in the text to explain that
-  \enquote{From a Neyman-Pearson perspective on statistical inferences
-  the main conclusion is based on whether or not \(p < \alpha\), and
-  thus an equivalence test and SGPV can be performed by simply checking
-  whether the confidence interval falls within the equivalence range,
-  just as a null-hypothesis test can be performed by checking whether
-  the confidence interval contains zero or not.} We believe this is a
-  correct use of the term \enquote{Neyman-Pearson perspective on
-  statistical inferences}.
+  We are aware of the Beger and Hsu (1996) article.
+But if the reviewer reads more closely, it should be clear that we never say the TOST is UMP.
+We say that TOST is a test procedure that aims to control error rates - our use of the term \enquote{Neyman-Pearson perspective} refers to the classic difference between significance tests (Fisher) and hypothesis tests (Neyman-Pearson).
+We do not imply that any test that fixes an error rate is a NP test.
+Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of p-values, we are simply adding a \enquote{Neyman-Pearson} approach in the text to explain that \enquote{From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not \(p < \alpha\), and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.} We believe this is a correct use of the term \enquote{Neyman-Pearson perspective on statistical inferences}.
 \item
-  We tried to find the passage the reviewer refers to when he writes
-  \enquote{In light of this, the assertion without proof that classical
-  p-values provide more or better assessments of the \enquote{evidence}
-  appear out of place.} but we could not. We do not use the word
-  \enquote{evidence} in the text (because neither the p-value from TOST
-  nor the SGPV are measures of \enquote{evidence} - we fully agree with
-  BLume et al., 2018, in this respect). We also do not say the p-value
-  is \enquote{naturally informative}. Indeed, related to point 3 above,
-  we tried to be consistent in interpreting the TOST procedure from a
-  Neyman-Pearson perspective, and focus on error control. So we
-  regrettably do not know how to incorporate this point.
+  We tried to find the passage the reviewer refers to when he writes \enquote{In light of this, the assertion without proof that classical p-values provide more or better assessments of the ``evidence} appear out of place." but we could not.
+We do not use the word \enquote{evidence} in the text (because neither the p-value from TOST nor the SGPV are measures of \enquote{evidence} - we fully agree with BLume et al., 2018, in this respect).
+We also do not say the p-value is \enquote{naturally informative}.
+Indeed, related to point 3 above, we tried to be consistent in interpreting the TOST procedure from a Neyman-Pearson perspective, and focus on error control.
+So we regrettably do not know how to incorporate this point.
 \item
-  We fully agree with the reviewer on point 5 that \enquote{The maximum
-  Type I Error rate for the SGPV over the null interval is 5\%, exactly
-  like the TOST test.} Indeed, given the direct overlap between the TOST
-  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
-  1 and 0, any error rates (when concluding support for the null or
-  alternative when the SGPV is either 1 or 0) must be identical. This is
-  why we were so surprised when Blume et al (2018) write \enquote{They
-  control the Type I error naturally, forcing it to zero as the sample
-  size grows. This, in turn, offsets Type I Error inflation that results
-  from multiple comparisons or multiple examinations of accumulating
-  data. Findings identified by second-generation p-values are less
-  likely to be false discoveries than findings identified by classical
-  p-values. Consequently, second-generation p-values do not require
-  ad-hoc adjustments to provide strict error control and this improves
-  power in studies with massive multiple comparisons.} Clearly, it can
-  not both be true that the the error rate of SGPV and TOST is
-  identical, TOST requires adjusting for multiple comparisons, but the
-  SGPV does not.
+  We fully agree with the reviewer on point 5 that \enquote{The maximum Type I Error rate for the SGPV over the null
+  interval is 5\%, exactly like the TOST test.} Indeed, given the direct overlap between the TOST \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical.
+This is why we were so surprised when Blume et al (2018) write \enquote{They control the Type I error naturally, forcing it to zero as the sample size grows.
+This, in turn, offsets Type I Error inflation that results from multiple comparisons or multiple examinations of accumulating data.
+Findings identified by second-generation p-values are less likely to be false discoveries than findings identified by classical p-values.
+Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons.} Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
 \end{enumerate}
 
-The editor asks us to better substantiate the frequency claims for the
-comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value
-are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1)
-we do not think any additional substantiation is possible, especially
-since the reviewer agrees that (as long as confidence intervals are used
-to calculate the SGPV, which we now clearly limit our conclusions to)
-\enquote{The maximum Type I Error rate for the SGPV over the null
-interval is 5\%, exactly like the TOST test}.
+The editor asks us to better substantiate the frequency claims for the comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1) we do not think any additional substantiation is possible, especially since the reviewer agrees that (as long as confidence intervals are used to calculate the SGPV, which we now clearly limit our conclusions to) \enquote{The maximum Type I Error rate for the SGPV over the null interval is 5\%, exactly like the TOST test}.
 
-Nevertheless, we agree this discussion was a bit too extensive. Given my
-own fondness of error control in statistical inferences, I get worried
-if researchers suggest we can ignore it, especially when making multiple
-comparisons. Imagine people start to use the SGPV instead of the TOST
-procedure whenever they perform 20 tests, and then argue they do not
-need to correct for multiple comparison - I think we can all agree this
-is undesireable! We have reduced the two paragraphs to one hopefully
-clear statement about the need to control error rates, also when using
-the SGPV. We hope this addresses the concerns by the editor as well as
-the reviewer, while still making an important point in the literature
-about the need to control error rates (if one cares about drawing
-incorrect conclusions).
+Nevertheless, we agree this discussion was a bit too extensive.
+Given my own fondness of error control in statistical inferences, I get worried if researchers suggest we can ignore it, especially when making multiple comparisons.
+Imagine people start to use the SGPV instead of the TOST procedure whenever they perform 20 tests, and then argue they do not need to correct for multiple comparison - I think we can all agree this is undesireable!
+We have reduced the two paragraphs to one hopefully clear statement about the need to control error rates, also when using the SGPV.
+We hope this addresses the concerns by the editor as well as the reviewer, while still making an important point in the literature about the need to control error rates (if one cares about drawing incorrect conclusions).
 
-Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
-\enquote{Adjustments for multiple comparisons are obviated} (p.~15).
-However, this is not correct. Given the direct relationship between TOST
-and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025
-equals SGPV = 1, as long as the SGPV is calculated based on confidence
-intervals, and assuming continuous and normally distributed data), not
-correcting for multiple comparisons will inflate the probability of
-concluding the absence of a meaningful effect based on the SGPV in
-exactly the same way as for equivalence tests. Whenever statistical
-tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or
-SGPV =1), it is possible do so erroneously, and if researchers want to
-control error rates, they need to correct for multiple comparisons.
+Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that \enquote{Adjustments for multiple comparisons are obviated} (p.~15).
+However, this is not correct.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 
@@
 \item
-  We have removed this section while addressing point 5 above, and thus
-  incorporated the reviewers'suggestion to remove these statements.
+  We have removed this section while addressing point 5 above, and thus incorporated the reviewers'suggestion to remove these statements.
 \item
-  We have not removed the paragraph about multiple comparisons, as the
-  reviewer asks, but we have simplified our treatment of it. We do not
-  need any other argument to make our claims about multiple comparisons
-  that fact, noted by the reviewer, that \enquote{The maximum Type I
-  Error rate for the SGPV over the null interval is 5\%, exactly like
-  the TOST test.} This is true, and it logically follows (hence, no
-  mathematical proof is needed) that error rates need to be controlled
-  when using SGPV to conclude support for the null-hypothesis. We blieve
-  error control is important enough to include this paragraph in the
-  paper, as we believe that lack of error control was one of the causes
-  of the replication crisis in psychology.
+  We have not removed the paragraph about multiple comparisons, as the reviewer asks, but we have simplified our treatment of it.
+We do not need any other argument to make our claims about multiple comparisons that fact, noted by the reviewer, that \enquote{The maximum Type I Error rate for the SGPV over the null interval is 5\%, exactly like the TOST test.} This is true, and it logically follows (hence, no mathematical proof is needed) that error rates need to be controlled when using SGPV to conclude support for the null-hypothesis.
+We believe error control is important enough to include this paragraph in the paper, as we believe that lack of error control was one of the causes of the replication crisis in psychology.
 \item
-  We thank the reviewer for this comment. Indeed, to calculate
-  confidence intervals around a correlation, the Fisher's
-  z-transformation is used, which is approximately normally distributed,
-  and symmatric CI are calculated. When transforming these confidence
-  intervals back to correlations, they become asymmetric. We have added
-  to the text: \enquote{Note that calculating confidence intervals for a
-  correlation involves a Fisher's z-transformation, which transforms
-  values such that they are approximately normally distributed, which
-  allows one to compute symmetric confidence intervals, which are then
-  retransformed into a correlation, where the confidence intervals are
-  asymmetric if the correlation is not exactly zero.} This is simply one
-  example of a general effect mentioned in Blume et al (2018), which we
-  already cited in the main text: \enquote{The magnitude of an
-  inconclusive second-generation \emph{p}-value can vary slightly when
-  the effect size scale is transformed. However definitive findings,
-  i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
-  changes.}
+  We thank the reviewer for this comment.
+Indeed, to calculate confidence intervals around a correlation, the Fisher's z-transformation is used, which is approximately normally distributed, and symmatric CI are calculated.
+When transforming these confidence intervals back to correlations, they become asymmetric.
+We have added to the text: \enquote{Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally distributed, which allows one to compute symmetric confidence intervals, which are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.} This is simply one example of a general effect mentioned in Blume et al (2018), which we already cited in the main text: \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}
 \end{enumerate}
@@
 \item
-  We see how \enquote{reverse the SGPV} might have been confusing. We
-  did not mean to imply to reverse the null and alternative. We now just
-  say that we plot 1-SGPV (which is what we incorrectly tried to express
-  with \enquote{reverse}).
+  We see how \enquote{reverse the SGPV} might have been confusing.
+We did not mean to imply to reverse the null and alternative.
+We now just say that we plot 1-SGPV (which is what we incorrectly tried to express with \enquote{reverse}).
 \item
-  The issue of the SGPV needing a \enquote{correction} by setting it to
-  0.5 is not related to the fact that large \emph{p}-values are not
-  evidence for the null. The \emph{p}-value is behaving as it is
-  intended to, without any correction. A high p-value is not a
-  \enquote{misleading result} - although it can be misinterpreted (which
-  is exactly what we try to prevent with our work on equivalence
-  testing). We therefore did not incorporate this point.
+  The issue of the SGPV needing a \enquote{correction} by setting it to 0.5 is not related to the fact that large \emph{p}-values are not evidence for the null.
+The \emph{p}-value is behaving as it is intended to, without any correction.
+A high p-value is not a \enquote{misleading result} - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing).
+We therefore did not incorporate this point.
 \item
-  In line with comments by reviewer 1, we removed statemetns about SGPV
-  not being inferential, thereby solving the issue reviewer 2 raised.
+  In line with comments by reviewer 1, we removed statemetns about SGPV not being inferential, thereby solving the issue reviewer 2 raised.
 \item
-  In line with major point 8, we added information that asymmetric
-  condifence intervals around a correlation are symmetric when Fisher
-  z-transformed. This is just an example of what Blume et al (2018)
-  refer to when they write \enquote{The magnitude of an inconclusive
-  second-generation \emph{p}-value can vary slightly when the effect
-  size scale is transformed. However definitive findings, i.e.~a
-  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
-  changes.} We beieve this section, although the most detailed, is
-  interesting, even only for more expert readers (indeed, Reviewer 1
-  notes that \enquote{The asymmetric CI case is very interesting}). We
-  have made our point less general, now only talking about correlations,
-  by changing the title of this section into \enquote{The relation
-  between equivalence tests and SGPV for asymmetrical confidence
-  intervals around correlations}. The reviewer is correct confidence
-  intervals can be created in many difference ways (e.g., with holes in
-  the middle), but for this paper, we just focus on one specific case
-  now, which we believe might be closest to what researchers would use
-  in real life, the confidence interval around a correlation.
+  In line with major point 8, we added information that asymmetric condifence intervals around a correlation are symmetric when Fisher z-transformed.
+This is just an example of what Blume et al (2018) refer to when they write \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.} We beieve this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that \enquote{The asymmetric CI case is very interesting}).
+We have made our point less general, now only talking about correlations, by changing the title of this section into \enquote{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations}.
+The reviewer is correct confidence intervals can be created in many difference ways (e.g., with holes in the middle), but for this paper, we just focus on one specific case now, which we believe might be closest to what researchers would use in real life, the confidence interval around a correlation.
 \item
-  It is a well-known fact that the TOST can have 0 power (and indeed,
-  this is one of the main issues in the Perlman and Wu (1999) paper the
-  reviewer cited). As explained in Lakens (2017): \enquote{It is
-  important to take statistical power into account when determining the
-  equivalence bounds because, in small samples (where CIs are wide), a
-  study might have no statistical power (i.e., the CI will always be so
-  wide that it is necessarily wider than the equivalence bounds).} We
-  agree with the reviewer it is not interesting to do a test if you have
-  0 power. People should design informative experiments by doing an
-  a-priori power analysis. Any problem in this respect is not a problem
-  with equivalence tests, but a problem with designing a bad study. Not
-  that the exact same issue applies to the SGPV. It is also possible to
-  have 0 power for the SGPV - so we do not understand why the reviewer
-  is so surprised about this. The question \enquote{Why use the TOST
-  test then?} equally applies to \enquote{Why use the SGPV then?} if
-  you, from the outset, know that the \enquote{small sample correction}
-  will lead to a SGPV of 0.5.
+  It is a well-known fact that the TOST can have 0 power (and indeed, this is one of the main issues in the Perlman and Wu (1999) paper the reviewer cited).
+As explained in Lakens (2017): \enquote{It is important to take statistical power into account when determining the equivalence bounds because, in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).} We agree with the reviewer it is not interesting to do a test if you have 0 power.
+People should design informative experiments by doing an a-priori power analysis.
+Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study.
+Not that the exact same issue applies to the SGPV.
+It is also possible to have 0 power for the SGPV - so we do not understand why the reviewer is so surprised about this.
+The question \enquote{Why use the TOST test then?} equally applies to \enquote{Why use the SGPV then?} if you, from the outset, know that the \enquote{small sample correction} will lead to a SGPV of 0.5.
 \item
-  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an
-  estimate to some value. Regardless of how correction factors are
-  applied in statistics, we are trying to educate our readers about what
-  the \enquote{small sample correction} does. We believe our readers
-  will associate \enquote{correction} with \enquote{correcting}, and
-  want to explain that the SGPV is not set to a \enquote{correct} value.
-  We are not talking about statistical terms here - we are warning the
-  reader to not interpret \enquote{correction} in terms of normal
-  language use. This is similar to warning readers that
-  \enquote{significant} does not have the normal language connotation of
-  \enquote{important}. We have therefore kept our original sentence.
+  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an estimate to some value.
+Regardless of how correction factors are applied in statistics, we are trying to educate our readers about what the \enquote{small sample correction} does.
+We believe our readers will associate \enquote{correction} with \enquote{correcting}, and want to explain that the SGPV is not set to a \enquote{correct} value.
+We are not talking about statistical terms here - we are warning the reader to not interpret \enquote{correction} in terms of normal language use.
+This is similar to warning readers that \enquote{significant} does not have the normal language connotation of \enquote{important}.
+We have therefore kept our original sentence.
 \end{enumerate}
 
-As a final comment, altough not explicitly listed as a major point of
-minor point, we are happy to respond to the reviewers' suggestion that
-Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
-best summary of this discussion (of which Perlman \& Wu is one
-contribution) can be found in Meyners (2012), which we cited. The
-discussion has different arguments, and Meyners draws the conclusion
-that there is no universially preferred approach. The power benefits of
-alternative approaches are typically modest, or only noticeable in
-situations where all alternatives are underpowered. The power issue is
-not that important - the main discussion is about whether equivalence
-tests should have a bounded rejection region, ike TOST, or an unbounded
-rejection region. It might be useful to note that TOST and SGPV are
-similar in this respect - both have bounded rejection regions, and if
-the reviewer agrees with Perlman and Wu (1999) in the criticism against
-TOST, the same criticism applies to the SGPV. If the reviewer reads
-Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
-an argument to ban the SGPV. We agree with Meyners, who writes:
-\enquote{The debate has been quite heated in times; this section intends
-to give a brief overview of the debate. We would like to emphasize again
-that the differences between the approaches are minor and to a large
-extent of academic interest only, as is this debate.} and concludes:
-\enquote{To summarize, there is no right or wrong in most of the
-arguments; the two opposing parties rather apply different criteria to
-select the most appropriate test, one group focusing rather on
-mathematical/statistical criteria, the other one more on
-interpretability and reasonability.} We have added a reference to this
-discussion for the interested reader, and added \enquote{For an
-excellent discussion of the strengths and weaknesses of different
-frequentist equivalence tests, including alternatives to the TOST
-procedure, see Meyners, 2012.}
+As a final comment, altough not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an \enquote{outright ban of TOST}.
+The best summary of this discussion (of which Perlman \& Wu is one contribution) can be found in Meyners (2012), which we cited.
+The discussion has different arguments, and Meyners draws the conclusion that there is no universially preferred approach.
+The power benefits of alternative approaches are typically modest, or only noticeable in situations where all alternatives are underpowered.
+The power issue is not that important - the main discussion is about whether equivalence tests should have a bounded rejection region, ike TOST, or an unbounded rejection region.
+It might be useful to note that TOST and SGPV are similar in this respect - both have bounded rejection regions, and if the reviewer agrees with Perlman and Wu (1999) in the criticism against TOST, the same criticism applies to the SGPV.
+If the reviewer reads Perlman and Wu (1999) as an argument to ban TOST, it is at the same time an argument to ban the SGPV.
+We agree with Meyners, who writes: \enquote{The debate has been quite heated in times; this section intends to give a brief overview of the debate.
+We would like to emphasize again that the differences between the approaches are minor and to a large extent of academic interest only, as is this debate.} and concludes: \enquote{To summarize, there is no right or wrong in most of the arguments; the two opposing parties rather apply different criteria to select the most appropriate test, one group focusing rather on mathematical/statistical criteria, the other one more on interpretability and reasonability.} We have added a reference to this discussion for the interested reader, and added \enquote{For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see Meyners, 2012.}
 
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-blume_second-generation_2018}{}
-Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
-(2018). Second-generation p-values: Improved rigor, reproducibility, \&
-transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
-e0188299.
+\leavevmode\hypertarget{ref-blume_second-generation_2018}{}%
+Blume, J.
+D., D'Agostino McGowan, L., Dupont, W.
+D., \& Greevy, R.
+A.
+(2018).
+Second-generation p-values: Improved rigor, reproducibility, \& transparency in statistical analyses.
+\emph{PLOS ONE}, \emph{13}(3), e0188299.
 doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

### 2019-03-09 reply_to_reviews.R1.Rmd
change p-value into *p*-value

@@
 1.
-We have changed the part of the sentence "Our conclusions about the relationship between TOST p-values and SGPV in this article are not dependent upon any specific example" into "Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.".
-We mainly intended to refer to our conclusion that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values" namely p = 0.5 for TOST when the SGPV will be 0.5, and the p-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
+We have changed the part of the sentence "Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example" into "Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.".
+We mainly intended to refer to our conclusion that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values" namely p = 0.5 for TOST when the SGPV will be 0.5, and the *p*-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
 We have now made it clearer that when we talk about 'correspondence between TOST *p*-values and the SGPV', we mean that there is a direct relation between three points.
@@
 We appreciate correcting our use of the term 'unrelated' and teaching us the word 'bijective'.
-We used the word 'unrelated' somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST *p*-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST p-value differs across this range of means.
+We used the word 'unrelated' somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST *p*-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST *p*-value differs across this range of means.
 We now just directly say what we originally meant, and no longer use the word 'unrelated'.
@@
 4.
-After making the change at point 2 above, we now think the sentence "The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p < 0:025 or p > 0:975 in an equivalence test, since the SGPV and p-value for the TOST
+After making the change at point 2 above, we now think the sentence "The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p < 0:025 or p > 0:975 in an equivalence test, since the SGPV and *p*-value for the TOST
 procedure are always directly related at these values." should no longer be confusing.
@@
 
-Before listing major points, the reviewer raises the point that we compare SGPV with p-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
+Before listing major points, the reviewer raises the point that we compare SGPV with *p*-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
 
@@
 
-The reviewer says that "the authors suddenly switch the premise; now the SGPV should be replaced by two p-values, one from an equivalence test and one from a NHST".
+The reviewer says that "the authors suddenly switch the premise; now the SGPV should be replaced by two *p*-values, one from an equivalence test and one from a NHST".
 However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all.
@@
 
-"The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975.
+"The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the *p*-value will always be 0.975.
 Note that this
@@
 One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
+However, the overlap of the TOST *p*-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
 When the TOST *p*-value is 0.975, the 95% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range.
@@
 1.
-In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." After all, p-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
+In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." After all, *p*-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
 Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals).
@@
 The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
-We clearly state that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the p-value from an equivalence test for three values." This correspondence is not dependent upon the SE's.
+We clearly state that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values." This correspondence is not dependent upon the SE's.
 It will always hold for continuous normal data.
@@
 For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the p-value is 0.5 (situation A, Figure 3).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
 Two other points always have to overlap.
-When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST p-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975, and the SGPV is 0.
+When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST *p*-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the *p*-value will always be 0.975, and the SGPV is 0.
 
 We do not think we can provide any other proof for this.
-A confidence interval and a p-value are directly related.
+A confidence interval and a *p*-value are directly related.
 The TOST procedure is a test using the confidence interval, and the SGPV (now that we clearly limited our discussion to a SGPV based on a confidence interval calculated from continuous normal data) compared against the same equivalence bounds will be related as we describe.
@@
 
-"When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
+"When we discuss the relationship between the *p*-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
 These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
@@
 the sample size is large enough that the standard error is very small relative to the width of the
-equivalence zone." Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a p-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+equivalence zone." Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a *p*-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
 
@@
 We do not imply that any test that fixes an error rate is a NP test.
-Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of p-values, we are simply adding a 'Neyman-Pearson' approach in the text to explain that "From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not." We believe this is a correct use of the term 'Neyman-Pearson perspective on statistical inferences'.
+Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of *p*-values, we are simply adding a 'Neyman-Pearson' approach in the text to explain that "From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not $p < \alpha$, and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not." We believe this is a correct use of the term 'Neyman-Pearson perspective on statistical inferences'.
 
 4.
-We tried to find the passage the reviewer refers to when he writes "In light of this, the assertion without proof that classical p-values provide more or better assessments of the “evidence” appear out of place." but we could not.
-We do not use the word 'evidence' in the text (because neither the p-value from TOST nor the SGPV are measures of 'evidence' - we fully agree with BLume et al., 2018, in this respect).
-We also do not say the p-value is 'naturally informative'.
+We tried to find the passage the reviewer refers to when he writes "In light of this, the assertion without proof that classical *p*-values provide more or better assessments of the “evidence” appear out of place." but we could not.
+We do not use the word 'evidence' in the text (because neither the *p*-value from TOST nor the SGPV are measures of 'evidence' - we fully agree with BLume et al., 2018, in this respect).
+We also do not say the *p*-value is 'naturally informative'.
 Indeed, related to point 3 above, we tried to be consistent in interpreting the TOST procedure from a Neyman-Pearson perspective, and focus on error control.
@@
 This, in turn, offsets Type I Error inflation that results from multiple comparisons or multiple examinations of accumulating data.
-Findings identified by second-generation p-values are less likely to be false discoveries than findings identified by classical p-values.
-Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons." Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
+Findings identified by second-generation *p*-values are less likely to be false discoveries than findings identified by classical *p*-values.
+Consequently, second-generation *p*-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons." Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
 
@@
 The *p*-value is behaving as it is intended to, without any correction.
-A high p-value is not a 'misleading result' - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing).
+A high *p*-value is not a 'misleading result' - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing).
 We therefore did not incorporate this point.

### 2019-03-09 reply_to_reviews.R1.tex
change p-value into *p*-value

@@
 \item
-  We have changed the part of the sentence \enquote{Our conclusions about the relationship between TOST p-values and SGPV in this article are not dependent upon any specific example} into \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.}.
-We mainly intended to refer to our conclusion that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the p-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
+  We have changed the part of the sentence \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV in this article are not dependent upon any specific example} into \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.}.
+We mainly intended to refer to our conclusion that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
 We have now made it clearer that when we talk about \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we mean that there is a direct relation between three points.
@@
   We appreciate correcting our use of the term \enquote{unrelated} and teaching us the word \enquote{bijective}.
-We used the word \enquote{unrelated} somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST \emph{p}-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST p-value differs across this range of means.
+We used the word \enquote{unrelated} somewhat naievely, looking at the Figures and wanting to express that across the three identified situations, a different TOST \emph{p}-value does not imply a different SGPV - the SGPV across these ranges of means is aways the same (either 0, 0.5, or 1) while the TOST \emph{p}-value differs across this range of means.
 We now just directly say what we originally meant, and no longer use the word \enquote{unrelated}.
@@
 \item
-  After making the change at point 2 above, we now think the sentence \enquote{The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test, since the SGPV and p-value for the TOST
+  After making the change at point 2 above, we now think the sentence \enquote{The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST
   procedure are always directly related at these values.} should no longer be confusing.
@@
 
-Before listing major points, the reviewer raises the point that we compare SGPV with p-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
+Before listing major points, the reviewer raises the point that we compare SGPV with \emph{p}-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
 
@@
 
-The reviewer says that \enquote{the authors suddenly switch the premise; now the SGPV should be replaced by two p-values, one from an equivalence test and one from a NHST}.
+The reviewer says that \enquote{the authors suddenly switch the premise; now the SGPV should be replaced by two \emph{p}-values, one from an equivalence test and one from a NHST}.
 However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all.
@@
 
-\enquote{The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975.
+\enquote{The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the \emph{p}-value will always be 0.975.
 Note that this
@@
 One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
+However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
 When the TOST \emph{p}-value is 0.975, the 95\% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range.
@@
 \item
-  In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} After all, p-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
+  In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} After all, \emph{p}-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
 Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals).
@@
 The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
-We clearly state that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the p-value from an equivalence test for three values.} This correspondence is not dependent upon the SE's.
+We clearly state that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values.} This correspondence is not dependent upon the SE's.
 It will always hold for continuous normal data.
@@
 For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50\% when the observed mean falls exactly on the lower or upper equivalence bound, because 50\% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the p-value is 0.5 (situation A, Figure 3).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure 3).
 Two other points always have to overlap.
-When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST p-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-The third point where the SGPV and the p-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the p-value will always be 0.975, and the SGPV is 0.
+When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the \emph{p}-value will always be 0.975, and the SGPV is 0.
 
 We do not think we can provide any other proof for this.
-A confidence interval and a p-value are directly related.
+A confidence interval and a \emph{p}-value are directly related.
 The TOST procedure is a test using the confidence interval, and the SGPV (now that we clearly limited our discussion to a SGPV based on a confidence interval calculated from continuous normal data) compared against the same equivalence bounds will be related as we describe.
@@
 
-\enquote{When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
+\enquote{When we discuss the relationship between the \emph{p}-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
 These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
@@
 the sample size is large enough that the standard error is very small relative to the width of the
-equivalence zone.} Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a p-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+equivalence zone.} Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a \emph{p}-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
 
@@
 We do not imply that any test that fixes an error rate is a NP test.
-Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of p-values, we are simply adding a \enquote{Neyman-Pearson} approach in the text to explain that \enquote{From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not \(p < \alpha\), and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.} We believe this is a correct use of the term \enquote{Neyman-Pearson perspective on statistical inferences}.
+Because many psychologists are not trained in the difference between a Fisherian approach and a Neyman Pearson approach to the use of \emph{p}-values, we are simply adding a \enquote{Neyman-Pearson} approach in the text to explain that \enquote{From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not \(p < \alpha\), and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.} We believe this is a correct use of the term \enquote{Neyman-Pearson perspective on statistical inferences}.
 \item
-  We tried to find the passage the reviewer refers to when he writes \enquote{In light of this, the assertion without proof that classical p-values provide more or better assessments of the ``evidence} appear out of place." but we could not.
-We do not use the word \enquote{evidence} in the text (because neither the p-value from TOST nor the SGPV are measures of \enquote{evidence} - we fully agree with BLume et al., 2018, in this respect).
-We also do not say the p-value is \enquote{naturally informative}.
+  We tried to find the passage the reviewer refers to when he writes \enquote{In light of this, the assertion without proof that classical \emph{p}-values provide more or better assessments of the ``evidence} appear out of place." but we could not.
+We do not use the word \enquote{evidence} in the text (because neither the \emph{p}-value from TOST nor the SGPV are measures of \enquote{evidence} - we fully agree with BLume et al., 2018, in this respect).
+We also do not say the \emph{p}-value is \enquote{naturally informative}.
 Indeed, related to point 3 above, we tried to be consistent in interpreting the TOST procedure from a Neyman-Pearson perspective, and focus on error control.
@@
 This, in turn, offsets Type I Error inflation that results from multiple comparisons or multiple examinations of accumulating data.
-Findings identified by second-generation p-values are less likely to be false discoveries than findings identified by classical p-values.
-Consequently, second-generation p-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons.} Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
+Findings identified by second-generation \emph{p}-values are less likely to be false discoveries than findings identified by classical \emph{p}-values.
+Consequently, second-generation \emph{p}-values do not require ad-hoc adjustments to provide strict error control and this improves power in studies with massive multiple comparisons.} Clearly, it can not both be true that the error rate of SGPV and TOST is identical, TOST requires adjusting for multiple comparisons, but the SGPV does not.
 \end{enumerate}
@@
 The \emph{p}-value is behaving as it is intended to, without any correction.
-A high p-value is not a \enquote{misleading result} - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing).
+A high \emph{p}-value is not a \enquote{misleading result} - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing).
 We therefore did not incorporate this point.

### 2019-03-09 reply_to_reviews.R1.Rmd
typos

@@
 However, the overlap of the TOST *p*-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
-When the TOST *p*-value is 0.975, the 95% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range.
+When the TOST *p*-value is 0.975, the 95% CI touches either the upper or lower equivalence bound, and fall completely outside of the equivalence range.
 This is mathematically identical to a statistically significant minimum effect test at p < 0.05.
@@
 We have deleted this sentence and replaced it with "As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary)."
-
-Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test.
-Part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
+Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test: part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
 But that is not what we propose.
-Werewrote the paragraph:
+We rewrote the paragraph:
 
@@
 For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
 Two other points always have to overlap.
@@
 6.
-In line with major point 8, we added information that asymmetric condifence intervals around a correlation are symmetric when Fisher z-transformed.
+In line with major point 8, we added information that asymmetric confidence intervals around a correlation are symmetric when Fisher z-transformed.
 This is just an example of what Blume et al (2018) refer to when they write "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
 However definitive findings, i.e.
-a *p*-value of 0 or 1 are *not* affected by the scale changes." We beieve this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that "The asymmetric CI case is very interesting").
+a *p*-value of 0 or 1 are *not* affected by the scale changes." We believe this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that "The asymmetric CI case is very interesting").
 We have made our point less general, now only talking about correlations, by changing the title of this section into "The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations".
@@
 Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study.
-Not that the exact same issue applies to the SGPV.
+Note that the exact same issue applies to the SGPV.
 It is also possible to have 0 power for the SGPV - so we do not understand why the reviewer is so surprised about this.
@@
 The power benefits of alternative approaches are typically modest, or only noticeable in situations where all alternatives are underpowered.
-The power issue is not that important - the main discussion is about whether equivalence tests should have a bounded rejection region, ike TOST, or an unbounded rejection region.
+The power issue is not that important - the main discussion is about whether equivalence tests should have a bounded rejection region, like TOST, or an unbounded rejection region.
 It might be useful to note that TOST and SGPV are similar in this respect - both have bounded rejection regions, and if the reviewer agrees with Perlman and Wu (1999) in the criticism against TOST, the same criticism applies to the SGPV.

### 2019-03-09 reply_to_reviews.R1.Rmd
R1

@@
 We will respond to the points raised by both reviewers in turn.
+Our points below detail 1) that we limit ourselves to a comparison of SGPV and TOST, and do not require researchers to perform both an equivalence test and a NHST (and therefore we did not add these curves to the Figures), 2) we rewrote the frequency claims, 3) we provide more detail about confidence intervals around correlations, and 4) removed all statements about the SGPV being a descriptive statistic.
 
@@
 We now just directly say what we originally meant, and no longer use the word 'unrelated'.
-For example, "There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate." and "While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value)." and similarly "A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound."
+For example, "There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate." and "While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value)." and similarly "A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound." We have removed the word 'unrelated' throughout the manuscript.
 
@@
 6.
-We have removed our earlier statements that the SGPV only works as a descriptive statistic.
+We have removed all our earlier statements that the SGPV only works as a descriptive statistic.
 We deleted the sentence "the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range." and deleted "The novelty of the SGPV lies in its use as a descriptive statistic" from the conclusion.

### 2019-03-09 reply_to_reviews.R1.tex
R1

--- 2019-03-08 reply_to_reviews.R1.tex
@@
 
-We will respond to the points raised by both reviewers in turn.
+We will respond to the points raised by both reviewers in turn. Our
+points below detail 1) that we limit ourselves to a comparison of SGPV
+and TOST, and do not require researchers to perform both an equivalence
+test and a NHST (and therefore we did not add these curves to the
+Figures), 2) we rewrote the frequency claims, 3) we provide more detail
+about confidence intervals around correlations, and 4) removed all
+statements about the SGPV being a descriptive statistic.
 
@@
   We have changed the part of the sentence \enquote{Our conclusions
-  about the relationship between TOST p-values and SGPV in this article
-  are not dependent upon any specific example} into \enquote{Our
+  about the relationship between TOST \emph{p}-values and SGPV in this
+  article are not dependent upon any specific example} into \enquote{Our
   conclusions about the relationship between TOST \emph{p}-values and
@@
   values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
-  p-values for TOST of 0.025 and 0.975 (corresponding to the largest
-  observed mean where the SGPV is 0 and the smallest observed mean where
-  the SGPV is 1). We have now made it clearer that when we talk about
-  \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we
-  mean that there is a direct relation between three points.
+  \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the
+  largest observed mean where the SGPV is 0 and the smallest observed
+  mean where the SGPV is 1). We have now made it clearer that when we
+  talk about \enquote{correspondence between TOST \emph{p}-values and
+  the SGPV}, we mean that there is a direct relation between three
+  points.
 \item
@@
   SGPV across these ranges of means is aways the same (either 0, 0.5, or
-  1) while the TOST p-value differs across this range of means. We now
-  just directly say what we originally meant, and no longer use the word
-  \enquote{unrelated}. For example, \enquote{There are three situations
-  where \emph{p}-values for TOST differentiate between observed results,
-  while the SGPV does not differentiate.} and \enquote{While the SGPV is
-  1 as long as the confidence interval falls completely within the
-  equivalence bounds, the \emph{p}-value for the TOST continues to
-  differentiate between results as a function of how far the confidence
-  interval lies within the equivalence bounds (the further the
-  confidence interval is from both bounds, the lower the
+  1) while the TOST \emph{p}-value differs across this range of means.
+  We now just directly say what we originally meant, and no longer use
+  the word \enquote{unrelated}. For example, \enquote{There are three
+  situations where \emph{p}-values for TOST differentiate between
+  observed results, while the SGPV does not differentiate.} and
+  \enquote{While the SGPV is 1 as long as the confidence interval falls
+  completely within the equivalence bounds, the \emph{p}-value for the
+  TOST continues to differentiate between results as a function of how
+  far the confidence interval lies within the equivalence bounds (the
+  further the confidence interval is from both bounds, the lower the
   \emph{p}-value).} and similarly \enquote{A third situation in which
@@
   wider than the equivalence range, and the CI overlaps with the upper
-  \emph{and} lower equivalence bound.}
+  \emph{and} lower equivalence bound.} We have removed the word
+  \enquote{unrelated} throughout the manuscript.
 \item
@@
   \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test,
-  since the SGPV and p-value for the TOST procedure are always directly
-  related at these values.} should no longer be confusing. To make the
-  sentence clearer, we have changed \enquote{these values} into
+  since the SGPV and \emph{p}-value for the TOST procedure are always
+  directly related at these values.} should no longer be confusing. To
+  make the sentence clearer, we have changed \enquote{these values} into
   \enquote{at the values p = 0.025 and p = 0.975} It should now be clear
@@
 \item
-  We have removed our earlier statements that the SGPV only works as a
-  descriptive statistic. We deleted the sentence \enquote{the SGPV is a
-  descriptive statistic (unlike the \emph{p}-value that is calculated
+  We have removed all our earlier statements that the SGPV only works as
+  a descriptive statistic. We deleted the sentence \enquote{the SGPV is
+  a descriptive statistic (unlike the \emph{p}-value that is calculated
   for an equivalence test, which is an inferential statistic) that
@@
   be interpreted to future researchers, and we do not make any
-  statements about whether such values are descriptive our inferential.
+  statements about whether such values are descriptive or inferential.
 \item
@@
 Before listing major points, the reviewer raises the point that we
-compare SGPV with p-values from TOST throughout our paper, and in all
-figures, but then at the end, in page 20, we write:
+compare SGPV with \emph{p}-values from TOST throughout our paper, and in
+all figures, but then at the end, in page 20, we write:
 
@@
 The reviewer says that \enquote{the authors suddenly switch the premise;
-now the SGPV should be replaced by two p-values, one from an equivalence
-test and one from a NHST}. However, we do not suggest to replace the
-SGPV with an equivalence test and a NHST at all. In our manuscript, we
-already pointed out how the SGPV is basically the same as an equivalence
-test and a minimum effect test (on page 7):
+now the SGPV should be replaced by two \emph{p}-values, one from an
+equivalence test and one from a NHST}. However, we do not suggest to
+replace the SGPV with an equivalence test and a NHST at all. In our
+manuscript, we already pointed out how the SGPV is basically the same as
+an equivalence test and a minimum effect test (on page 7):
 
-\enquote{The third point where the SGPV and the p-value from the TOST
-procedure should overlap is where the 95\% CI falls completely outside
-of the equivalence range, but one endpoint of the confidence interval is
-equal to the equivalence bound (see situation C in Figure 3), when the
-p-value will always be 0.975. Note that this situation is in essence a
-minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal of a
-minimum-effect is not just to reject a difference of zero, but to reject
-the smallest effect size of interest (i.e., the equivalence bounds). The
-SGPV summarizes the information from an equivalence test and a
-minimum-effect test.}
+\enquote{The third point where the SGPV and the \emph{p}-value from the
+TOST procedure should overlap is where the 95\% CI falls completely
+outside of the equivalence range, but one endpoint of the confidence
+interval is equal to the equivalence bound (see situation C in Figure
+3), when the \emph{p}-value will always be 0.975. Note that this
+situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
+2014). The goal of a minimum-effect is not just to reject a difference
+of zero, but to reject the smallest effect size of interest (i.e., the
+equivalence bounds). The SGPV summarizes the information from an
+equivalence test and a minimum-effect test.}
 
 One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST p-value at 0.975 when SGPV = 0 gives
-away that the equivalence test can be interpreted as a minimum effect
-test against the equivalence bound. When the TOST \emph{p}-value is
-0.975, the 95\% CI touches either the upper or lower equivalence bound,
-and fall complately outside of the equivalence range. This is
+However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0
+gives away that the equivalence test can be interpreted as a minimum
+effect test against the equivalence bound. When the TOST \emph{p}-value
+is 0.975, the 95\% CI touches either the upper or lower equivalence
+bound, and fall completely outside of the equivalence range. This is
 mathematically identical to a statistically significant minimum effect
@@
 Neyman-Pearson interpretation of an equivalence test and a minimum
-effect tests (which are complementary).}
-
-Furthermore, to prevent the apparent confusion about why we suggested to
-perform a null-hypothesis test and equivalence test. Part of this
-confusion was our original sentence comparing the SGPV and a combination
-of NHST and an equivalence test which was not needed, and we understand
-it made it seem as if SGPV needs to be replaced by a combination of
-other tests. But that is not what we propose. Werewrote the paragraph:
+effect tests (which are complementary).} Furthermore, to prevent the
+apparent confusion about why we suggested to perform a null-hypothesis
+test and equivalence test: part of this confusion was our original
+sentence comparing the SGPV and a combination of NHST and an equivalence
+test which was not needed, and we understand it made it seem as if SGPV
+needs to be replaced by a combination of other tests. But that is not
+what we propose. We rewrote the paragraph:
 
@@
   the manuscript we now clearly state: \enquote{We limit our analysis to
-  normally distributed continuous data.} After all, p-values and
+  normally distributed continuous data.} After all, \emph{p}-values and
   confidence are directly related, but Bayesian credible intervals would
@@
   confidence intervals are symmetric we can think of the SGPV as a
-  straight line that is directly related to the p-value from an
+  straight line that is directly related to the \emph{p}-value from an
   equivalence test for three values.} This correspondence is not
@@
 the difference between the mean in the data and the equivalence bound is
-0, the t-value for the equivalence test is also 0, and thus the p-value
-is 0.5 (situation A, Figure 3). Two other points always have to overlap.
-When the 95\% CI falls completely inside the equivalence region, and one
-endpoint of the confidence interval is exactly equal to one of the
-equivalence bounds (see situation B in Figure 3) the TOST p-value (which
-relies on a one-sided test) is always 0.025, and the SGPV is 1. The
-third point where the SGPV and the p-value from the TOST procedure
-should overlap is where the 95\% CI falls completely outside of the
-equivalence range, but one endpoint of the confidence interval is equal
-to the equivalence bound (see situation C in Figure 3), when the p-value
-will always be 0.975, and the SGPV is 0.
+0, the \emph{t}-value for the equivalence test is also 0, and thus the
+\emph{p}-value is 0.5 (situation A, Figure 3). Two other points always
+have to overlap. When the 95\% CI falls completely inside the
+equivalence region, and one endpoint of the confidence interval is
+exactly equal to one of the equivalence bounds (see situation B in
+Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is
+always 0.025, and the SGPV is 1. The third point where the SGPV and the
+\emph{p}-value from the TOST procedure should overlap is where the 95\%
+CI falls completely outside of the equivalence range, but one endpoint
+of the confidence interval is equal to the equivalence bound (see
+situation C in Figure 3), when the \emph{p}-value will always be 0.975,
+and the SGPV is 0.
 
 We do not think we can provide any other proof for this. A confidence
-interval and a p-value are directly related. The TOST procedure is a
-test using the confidence interval, and the SGPV (now that we clearly
-limited our discussion to a SGPV based on a confidence interval
+interval and a \emph{p}-value are directly related. The TOST procedure
+is a test using the confidence interval, and the SGPV (now that we
+clearly limited our discussion to a SGPV based on a confidence interval
 calculated from continuous normal data) compared against the same
@@
 13). Nevertheless, in these graphs, we still have the correspondence
-between these 3 points (or at leas tthe 2 points if the CI is too wide
+between these 3 points (or at least the 2 points if the CI is too wide
 compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
@@
 
-\enquote{When we discuss the relationship between the p-values from TOST
-and the SGPV, we focus on their correspondence at three values, namely
-where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} =
-0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
-These three values are important for the SGPV because they indicate the
-values at which the SGPV indicates the data should be interpreted as
-compatible with the null hypothesis (SGPV = 1), or with the alternative
-hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV
-= 0.5). These three points of overlap are indicated by the horizontal
-dotted lines in Figure 2.}
+\enquote{When we discuss the relationship between the \emph{p}-values
+from TOST and the SGPV, we focus on their correspondence at three
+values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
+TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
+and SGPV = 1. These three values are important for the SGPV because they
+indicate the values at which the SGPV indicates the data should be
+interpreted as compatible with the null hypothesis (SGPV = 1), or with
+the alternative hypothesis (SGPV = 0), or when the data are strictly
+inconclusive (SGPV = 0.5). These three points of overlap are indicated
+by the horizontal dotted lines in Figure 2.}
 
@@
 SGPV at these 3 points should be obvious to anyone who understands the
-relationship between a p-value and a confidence interval, so we do not
-provide any further proof, but we hope that clarifying we talk about the
-correspondence of these 3 points, and not the entire curve, is
+relationship between a \emph{p}-value and a confidence interval, so we
+do not provide any further proof, but we hope that clarifying we talk
+about the correspondence of these 3 points, and not the entire curve, is
 sufficient to address point 2.
@@
   not trained in the difference between a Fisherian approach and a
-  Neyman Pearson approach to the use of p-values, we are simply adding a
-  \enquote{Neyman-Pearson} approach in the text to explain that
+  Neyman Pearson approach to the use of \emph{p}-values, we are simply
+  adding a \enquote{Neyman-Pearson} approach in the text to explain that
   \enquote{From a Neyman-Pearson perspective on statistical inferences
@@
   \enquote{In light of this, the assertion without proof that classical
-  p-values provide more or better assessments of the \enquote{evidence}
-  appear out of place.} but we could not. We do not use the word
-  \enquote{evidence} in the text (because neither the p-value from TOST
-  nor the SGPV are measures of \enquote{evidence} - we fully agree with
-  BLume et al., 2018, in this respect). We also do not say the p-value
-  is \enquote{naturally informative}. Indeed, related to point 3 above,
-  we tried to be consistent in interpreting the TOST procedure from a
-  Neyman-Pearson perspective, and focus on error control. So we
-  regrettably do not know how to incorporate this point.
+  \emph{p}-values provide more or better assessments of the
+  \enquote{evidence} appear out of place.} but we could not. We do not
+  use the word \enquote{evidence} in the text (because neither the
+  \emph{p}-value from TOST nor the SGPV are measures of
+  \enquote{evidence} - we fully agree with BLume et al., 2018, in this
+  respect). We also do not say the \emph{p}-value is \enquote{naturally
+  informative}. Indeed, related to point 3 above, we tried to be
+  consistent in interpreting the TOST procedure from a Neyman-Pearson
+  perspective, and focus on error control. So we regrettably do not know
+  how to incorporate this point.
 \item
@@
   from multiple comparisons or multiple examinations of accumulating
-  data. Findings identified by second-generation p-values are less
-  likely to be false discoveries than findings identified by classical
-  p-values. Consequently, second-generation p-values do not require
-  ad-hoc adjustments to provide strict error control and this improves
-  power in studies with massive multiple comparisons.} Clearly, it can
-  not both be true that the the error rate of SGPV and TOST is
-  identical, TOST requires adjusting for multiple comparisons, but the
-  SGPV does not.
+  data. Findings identified by second-generation \emph{p}-values are
+  less likely to be false discoveries than findings identified by
+  classical \emph{p}-values. Consequently, second-generation
+  \emph{p}-values do not require ad-hoc adjustments to provide strict
+  error control and this improves power in studies with massive multiple
+  comparisons.} Clearly, it can not both be true that the error rate of
+  SGPV and TOST is identical, TOST requires adjusting for multiple
+  comparisons, but the SGPV does not.
 \end{enumerate}
@@
   mathematical proof is needed) that error rates need to be controlled
-  when using SGPV to conclude support for the null-hypothesis. We blieve
-  error control is important enough to include this paragraph in the
-  paper, as we believe that lack of error control was one of the causes
-  of the replication crisis in psychology.
+  when using SGPV to conclude support for the null-hypothesis. We
+  believe error control is important enough to include this paragraph in
+  the paper, as we believe that lack of error control was one of the
+  causes of the replication crisis in psychology.
 \item
@@
   evidence for the null. The \emph{p}-value is behaving as it is
-  intended to, without any correction. A high p-value is not a
+  intended to, without any correction. A high \emph{p}-value is not a
   \enquote{misleading result} - although it can be misinterpreted (which
@@
   In line with major point 8, we added information that asymmetric
-  condifence intervals around a correlation are symmetric when Fisher
+  confidence intervals around a correlation are symmetric when Fisher
   z-transformed. This is just an example of what Blume et al (2018)
@@
   \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
-  changes.} We beieve this section, although the most detailed, is
+  changes.} We believe this section, although the most detailed, is
   interesting, even only for more expert readers (indeed, Reviewer 1
@@
   a-priori power analysis. Any problem in this respect is not a problem
-  with equivalence tests, but a problem with designing a bad study. Not
+  with equivalence tests, but a problem with designing a bad study. Note
   that the exact same issue applies to the SGPV. It is also possible to
@@
 not that important - the main discussion is about whether equivalence
-tests should have a bounded rejection region, ike TOST, or an unbounded
+tests should have a bounded rejection region, like TOST, or an unbounded
 rejection region. It might be useful to note that TOST and SGPV are

### 2019-03-09 manuscript.R1.Rmd
R1

@@
 We show that the two approaches yield almost identical results under optimal conditions.
-Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret as a descriptive statistic.
+Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation *p*-value becomes difficult to interpret.
 The second generation *p*-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
@@
 
-keywords          : "equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference" 
-wordcount         : ""
+keywords          : "equivalence testing, second generation p-values, hypothesis testing, TOST, statistical inference"
 
@@
 
-Second generation *p*-values (SGPV) were recently proposed to as a descriptive statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
+Second generation *p*-values (SGPV) were recently proposed to as a statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
 The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis. 
@@
 Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV. 
-We limit our analysis to normally distributed continuous data.
+We limit our analysis to continuous data sampled from a bivariate normal distribution.
 
@@
 We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
-When the two statistics are plotted against each other we can see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+When the two statistics are plotted against each other we can see where the SGPV is the same while the TOST *p*-value still differentiates different observed means (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
 We see the SGPV is 0.5 for a range of observed means where the *p*-value from the equivalence test still varies.
@@
 
-The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
+The *p*-value from the TOST procedure still differentiates observed means, while the  SGPV does not, when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
 In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
-This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
+This means the SGPV is not set to 0.5, but it is constant across a range of observed means, while the TOST *p*-value is not constant across this range.
 
@@
 
-If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
+If we once more plot the two statistics against each other we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies, as indicated by the straight section of the line (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
-To conclude this section, there are three situations where the *p*-value from the TOST procedure is unrelated to the SGPV.
-In all these situations the *p*-value for the equivalence test differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely continuous descriptive statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
+To conclude this section, there are situations where the *p*-value from the TOST procedure continues to differentiate, while the SGPV does not.
+Therefore, interpreted as a continuous statistic, the SGPV is more limited than the *p*-value from the TOST procedure.
 
@@
 This example illustrates the difference between a proportion and a probability.
-As long as data are normally distributed, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+As long as data are sampled from a bivariate normal distribution, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
 The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
@@
 Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
-Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of a bivariate normal distribution, and the generalizability of this statement needs to be examined beyond normal bivariate distributions.
 Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
@@
 However, this is not correct.
-Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
 Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.

### 2019-03-09 manuscript.R1.tex
R1

@@
             pdfauthor={Daniël Lakens~\& Marie Delacre},
-            pdfkeywords={equivalence testing, second generation \emph{p}-values, hypothesis
-testing, TOST, statistical inference},
+            pdfkeywords={equivalence testing, second generation p-values, hypothesis testing,
+TOST, statistical inference},
             pdfborder={0 0 0},
@@
 \textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\\textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium}
-\keywords{equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference\newline\indent Word count: }
+\keywords{equivalence testing, second generation p-values, hypothesis testing, TOST, statistical inference}
 \usepackage{csquotes}
@@
 To move beyond the limitations of null-hypothesis tests, statistical
-approaches have been developed where the observed data is compared
+approaches have been developed where the observed data are compared
 against a range of values that are equivalent to the absence of a
@@
 or when confidence intervals are asymmetric) the second generation
-\emph{p}-value becomes difficult to interpret as a descriptive
-statistic. The second generation \emph{p}-value is interpretable in a
-dichotomous manner (i.e., when the SGPV equals 0 or 1 because the
-confidence intervals lies completely within or outside of the
-equivalence range), but this dichotomous interpretation does not require
-calculations. We conclude that equivalence tests yield more consistent
-\emph{p}-values, distinguish between datasets that yield the same second
-generation \emph{p}-value, and allow for easier control of Type I and
-Type II error rates.
+\emph{p}-value becomes difficult to interpret. The second generation
+\emph{p}-value is interpretable in a dichotomous manner (i.e., when the
+SGPV equals 0 or 1 because the confidence intervals lies completely
+within or outside of the equivalence range), but this dichotomous
+interpretation does not require calculations. We conclude that
+equivalence tests yield more consistent \emph{p}-values, distinguish
+between datasets that yield the same second generation \emph{p}-value,
+and allow for easier control of Type I and Type II error rates.
 
@@
 tests. This statistical approach can be used to examine whether observed
-data is sufficiently surprising under the null hypothesis to reject an
+data are sufficiently surprising under the null hypothesis to reject an
 effect that equals exactly zero. Null-hypothesis tests have an important
@@
 Second generation \emph{p}-values (SGPV) were recently proposed to as a
-descriptive statistic that represents \enquote{the proportion of
-data-supported hypotheses that are also null hypotheses} (Blume et al.,
-2018). The researcher specifies an equivalence range around a null
-hypothesis of values that are considered practically equivalent to the
-null hypothesis. The SGPV measures the degree to which a set of
+statistic that represents \enquote{the proportion of data-supported
+hypotheses that are also null hypotheses} (Blume et al., 2018). The
+researcher specifies an equivalence range around a null hypothesis of
+values that are considered practically equivalent to the null
+hypothesis. The SGPV measures the degree to which a set of
 data-supported parameter values falls within the interval null
@@
 Here, we aim to examine the similarities and differences between the
-TOST procedure and the SGPV. We limit our analysis to normally
-distributed continuous data.
+TOST procedure and the SGPV. We limit our analysis to continuous data
+sampled from a bivariate normal distribution.
 
 The TOST procedure also relies on the confidence interval around the
-effect. In the TOST procedure the data is tested against the lower
+effect. In the TOST procedure the data are tested against the lower
 equivalence bound in the first one-sided test, and against the upper
@@
 weaknesses of different frequentist equivalence tests, including
-alternatives to the TOST procedure, see (Meyners, 2012). If both tests
+alternatives to the TOST procedure, see Meyners (2012). If both tests
 statistically reject an effect as extreme or more extreme than the
@@
 the test value in steps of 0.1 across A to D the \emph{p}-value
-calculated for normally distributed data is not uniformly distributed.
+calculated for normally distributed data are not uniformly distributed.
 The probability of observing data more extreme than the upper bound of 2
@@
 equivalence range (see Figure \ref{fig:TOSTSGPV6}). When the two
-statistics are plotted against each other we can see where they are
-unrelated (indicated by straight lines in the curve, see Figure
+statistics are plotted against each other we can see where the SGPV is
+the same while the TOST \emph{p}-value still differentiates different
+observed means (indicated by straight lines in the curve, see Figure
 \ref{fig:TOSTSGPV7}). We see the SGPV is 0.5 for a range of observed
@@
 
-The \emph{p}-value from the TOST procedure and the SGPV are also
-unrelated when the CI is wider than the equivalence range (so the
-precision is low) and overlaps with the upper and lower equivalence
-bound, but the CI is \emph{not} twice as wide as the equivalence range.
-In the example below, we see that the CI is only 1.79 times as wide as
-the equivalence bounds, but the CI overlaps with the lower and upper
-equivalence bounds (Figure \ref{fig:TOSTSGPV8}). This means the SGPV is
-not set to 0.5, but it is constant across a range of observed means.
+The \emph{p}-value from the TOST procedure still differentiates observed
+means, while the SGPV does not, when the CI is wider than the
+equivalence range (so the precision is low) and overlaps with the upper
+and lower equivalence bound, but the CI is \emph{not} twice as wide as
+the equivalence range. In the example below, we see that the CI is only
+1.79 times as wide as the equivalence bounds, but the CI overlaps with
+the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
+This means the SGPV is not set to 0.5, but it is constant across a range
+of observed means, while the TOST \emph{p}-value is not constant across
+this range.
 
@@
 
-If we once more plot the two statistics against each other to see where
-they are unrelated (indicated by straight lines in the curve), we see
-the SGPV is 0.56 for a range of observed means where the \emph{p}-value
-from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
+If we once more plot the two statistics against each other we see the
+SGPV is 0.56 for a range of observed means where the \emph{p}-value from
+the equivalence test still varies, as indicated by the straight section
+of the line (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
-To conclude this section, there are three situations where the
-\emph{p}-value from the TOST procedure is unrelated to the SGPV. In all
-these situations the \emph{p}-value for the equivalence test
-differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely continuous descriptive statistic, the SGPV is
-more limited than the \emph{p}-value from the TOST procedure.
+To conclude this section, there are situations where the \emph{p}-value
+from the TOST procedure continues to differentiate, while the SGPV does
+not. Therefore, interpreted as a continuous statistic, the SGPV is more
+limited than the \emph{p}-value from the TOST procedure.
 
-\subsection{The relation between equivalence tests and SGPV when for
+\subsection{The relation between equivalence tests and SGPV for
 asymmetrical confidence intervals around
-correlations}\label{the-relation-between-equivalence-tests-and-sgpv-when-for-asymmetrical-confidence-intervals-around-correlations}
+correlations}\label{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}
 
@@
 between -1 and 1, confidence intervals are only symmetric for a
-correlation of exactly 0. The confidence interval for a correaltion
+correlation of exactly 0. The confidence interval for a correlation
 becomes increasingly asymmetric as the observed correlation nears -1 or
@@
 This example illustrates the difference between a proportion and a
-probability. As long as data is normally distributed, there is always a
-50\% probability of observing a correlation smaller or larger than the
-true correlation, but the SGPV for this situation depends on how far
-away the observed correlation is from 0. The further away from 0, the
-larger the SGPV when the observed mean falls on the equivalence bound.
-The SGPV is the proportion of values in a 95\% confidence interval that
-overlap with the equivalence range, but not the probability that these
-values will be observed. In the most extreme case (i.e., a sample size
-of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed
-correlation of 0.99) 58.10\% of the confidence interval overlaps with
-the equivalence range, even though in the long run only 50\% of the
-correlations observed in the future will fall in this range. It should
-be noted that in larger sample sizes the SGPV is closer to 0.5 whenever
-the observed correlation falls on the equivalence bound, but this
-extreme example nevertheless clearly illustrates the difference between
-question the SGPV answers, and the question a \emph{p}-value answers.
-The conclusion of this section on asymmetric confidence intervals is
-that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{}
-0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the
-SGPV and \emph{p}-value for the TOST procedure are always directly
-related at the values \emph{p} = 0.025 and \emph{p} = 0.975. Although
-Blume et al. (2018) state that \enquote{the degree of overlap conveys
-how compatible the data are with the null premise} this definition of
-what the SGPV provides does not hold for asymmetric confidence
-intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV
-between 0 and 1 is not interpretable as \enquote{compatibility with the
-null hypothesis} under the assumption of normally distributed data, and
-the generalizability of this statement needs to be examined beyond
-normally distributed data. Indeed, Blume and colleagues write in the
-supplemental material that \enquote{The magnitude of an inconclusive
-second-generation \emph{p}-value can vary slightly when the effect size
-scale is transformed. However definitive findings, i.e.~a \emph{p}-value
-of 0 or 1 are \emph{not} affected by the scale changes.}
+probability. As long as data are sampled from a bivariate normal
+distribution, there is always a 50\% probability of observing a
+correlation smaller or larger than the true correlation, but the SGPV
+for this situation depends on how far away the observed correlation is
+from 0. The further away from 0, the larger the SGPV when the observed
+mean falls on the equivalence bound. The SGPV is the proportion of
+values in a 95\% confidence interval that overlap with the equivalence
+range, but not the probability that these values will be observed. In
+the most extreme case (i.e., a sample size of 4, and equivalence bounds
+set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
+of the confidence interval overlaps with the equivalence range, even
+though in the long run only 50\% of the correlations observed in the
+future will fall in this range. It should be noted that in larger sample
+sizes the SGPV is closer to 0.5 whenever the observed correlation falls
+on the equivalence bound, but this extreme example nevertheless clearly
+illustrates the difference between question the SGPV answers, and the
+question a \emph{p}-value answers. The conclusion of this section on
+asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
+interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
+0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
+TOST procedure are always directly related at the values \emph{p} =
+0.025 and \emph{p} = 0.975. Although Blume et al. (2018) state that
+\enquote{the degree of overlap conveys how compatible the data are with
+the null premise} this definition of what the SGPV provides does not
+hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can
+be directly interpreted, a SGPV between 0 and 1 is not interpretable as
+\enquote{compatibility with the null hypothesis} under the assumption of
+a bivariate normal distribution, and the generalizability of this
+statement needs to be examined beyond normal bivariate distributions.
+Indeed, Blume and colleagues write in the supplemental material that
+\enquote{The magnitude of an inconclusive second-generation
+\emph{p}-value can vary slightly when the effect size scale is
+transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or
+1 are \emph{not} affected by the scale changes.}
 
@@
 SGPV is 0, 1, or inconclusive. As already mentioned, this interpretation
-of a SGPV as is very similar to the Neyman-Pearson interpretation of an
+of a SGPV is very similar to the Neyman-Pearson interpretation of an
 equivalence test and a minimum effect tests (which are complementary).
@@
 statistically different from zero, but also too small to be considered
-meaningful, see (Lakens et al., 2018)).
+meaningful, see Lakens et al. (2018)).
 
@@
 manuscript (where to TOST \emph{p} = 0.025 equals SGPV = 1, as long as
-the SGPV is calculated based on confidence intervals, and assuming
-continuous and normally distributed data), not correcting for multiple
-comparisons will inflate the probability of concluding the absence of a
-meaningful effect based on the SGPV in exactly the same way as for
-equivalence tests. Whenever statistical tests are interpreted as support
-for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so
-erroneously, and if researchers want to control error rates, they need
-to correct for multiple comparisons.
+the SGPV is calculated based on confidence intervals, and assuming data
+sampled from a continuous bivariate normal distribution), not correcting
+for multiple comparisons will inflate the probability of concluding the
+absence of a meaningful effect based on the SGPV in exactly the same way
+as for equivalence tests. Whenever statistical tests are interpreted as
+support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do
+so erroneously, and if researchers want to control error rates, they
+need to correct for multiple comparisons.
 

### 2019-03-10 reply_to_reviews.R1.Rmd
R1 final

--- 2019-03-09 reply_to_reviews.R1.Rmd
@@
 abstract: |
-  We respond to all the comments raised by the two reviewers and the editors.
-We would like to thank the editor and reviewers for their suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct.
+  We respond to all the comments on our submission that were raised by the two reviewers, as well as the comments you highlighted as editor.
+We would like to thank you and reviewers for suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct.
 We feel we were able to accomodate all suggestions, and we hope you think our submission is ready to be accepted for publication in Meta-Psychology.
@@
 
-Thank you for your comments on our submitted manuscript. We have incorporated your three comments:
+Thank you for your comments on our submitted manuscript. We have incorporated your three small suggestions:
 
@@
 We will respond to the points raised by both reviewers in turn.
+Our points below detail the main issues you highlighted in your editorial letter, namely 1) that we limit ourselves to a comparison of SGPV and TOST, and do not require researchers to perform both an equivalence test and a NHST (and therefore we did not add these curves to the Figures), 2) we rewrote the frequency claims, 3) we provide more detail about confidence intervals around correlations, and 4) removed all statements about the SGPV being a descriptive statistic.
 
@@
 1.
-We have changed the part of the sentence "Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example" into "Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.".
-We mainly intended to refer to our conclusion that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values" namely p = 0.5 for TOST when the SGPV will be 0.5, and the *p*-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
+We have changed the part of the sentence "Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example" into "Our conclusions about the relationship between TOST *p*-values and SGPV hold for second generation *p*-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution".
+We mainly intended to refer to our conclusion that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values" namely *p* = 0.5 for TOST when the SGPV will be 0.5, and the *p*-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
 We have now made it clearer that when we talk about 'correspondence between TOST *p*-values and the SGPV', we mean that there is a direct relation between three points.
+We have added the explanation: "When we discuss the relationship between the *p*-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
+These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5)."
 
@@
 We now just directly say what we originally meant, and no longer use the word 'unrelated'.
-For example, "There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate." and "While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value)." and similarly "A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound."
+For example, "There are three situations where *p*-values for TOST differentiate between observed results, while the SGPV does not differentiate" and "Where the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds" and similarly "A third situation in which the SGPV remains stable across a range of observed effects, while the TOST *p*-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper *and* lower equivalence bound".
+We have removed the word 'unrelated' throughout the manuscript.
 
@@
 This is exactly why we submit our work for peer review - to be able to improve it based on feedback from experts.
-We now preface the sentence with "As long as data is normally distributed,".
+We now preface the sentence with "As long as data are sampled from a bivariate normal distribution,".
 We follow your recommendation throughout to not generalize beyond the scenarios we study.
-In the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." See also point 5 below.
+In the second paragraph of the manuscript we now clearly state: "We limit our analysis to continuous data sampled from a bivariate normal distribution." See also point 5 below.
 
 4.
-After making the change at point 2 above, we now think the sentence "The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p < 0:025 or p > 0:975 in an equivalence test, since the SGPV and *p*-value for the TOST
-procedure are always directly related at these values." should no longer be confusing.
-To make the sentence clearer, we have changed "these values" into "at the values p = 0.025 and p = 0.975" It should now be clear the sections are not contradictory - TOST differentiates below p < 0.025, when the SGPV is 1 for all p < 0.025.
+After making the change at point 2 above, we now think the sentence "The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p < 0:025 or p > 0:975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values." should no longer be confusing.
+To make the sentence clearer, we have changed "these values" into "at the values *p* = 0.025 and *p* = 0.975" It should now be clear the sections are not contradictory - TOST differentiates below *p* < 0.025, when the SGPV is 1 for all *p* < 0.025.
 
@@
 We agree that is unclear whether the original statement by Blume et al that "the degree of overlap conveys how compatible the data are with the null premise" holds in general.
-We have now amended the sentence to read: "Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data requires further examination."
+We have now amended the sentence to read: "Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis' under the assumption of a bivariate normal distribution, and the generalizability of this statement needs to be examined beyond normal bivariate distributions."
 
 6.
-We have removed our earlier statements that the SGPV only works as a descriptive statistic.
+We have removed all our earlier statements that the SGPV only works as a descriptive statistic.
 We deleted the sentence "the SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range." and deleted "The novelty of the SGPV lies in its use as a descriptive statistic" from the conclusion.
@@
 
-7.
-We agree that using TOST for small samples (e.g., N = 4) will not be useful.
-Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.
-
-8.
-With our recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions.
+Based on your recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions.
 An additional change not mentioned above is that we renamed the section on asymmetric confidence intervals to the more specific "The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations" instead of the more general "The relation between equivalence tests and SGPV when confidence intervals are not symmetrical".
@@
 
-Before listing major points, the reviewer raises the point that we compare SGPV with *p*-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
+Before listing major points, the reviewer raises the point that we compare SGPV with *p*-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we wrote:
 
@@
 However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all.
-In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7):
+In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7), and we have expanded this text to clarify that a minimum effects test and TOST are complementary:
 
 "The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the *p*-value will always be 0.975.
-Note that this
-situation is in essence a minimum-effect test (Murphy, Myors, & Wolach, 2014).
+Note that this situation is in essence a minimum-effect test [@murphy_statistical_2014].
 The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
-The SGPV summarizes the information from an equivalence test and a minimum-effect test."
+An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05 (and therefore the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test).
+The SGPV summarizes the information from an equivalence test (and the complementary minimum-effect test)."
 
-One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST *p*-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
+The overlap of the TOST *p*-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
 When the TOST *p*-value is 0.975, the 95% CI touches either the upper or lower equivalence bound, and fall completely outside of the equivalence range.
-This is mathematically identical to a statistically significant minimum effect test at p < 0.05.
-We didn't make this explicit, but we clearly should have.
-We have added the sentence (on page 7):
-
-"An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test."
+This is mathematically identical to a statistically significant minimum effect test at *p* < 0.05.
+We clearly should have made this more explicit, and hope the additional text clarifies the statistical relationship between TOST, a minimum effect test, and the SGPV
 
@@
 And indeed, the sentence "This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test" was simply confusing.
-We have deleted this sentence and replaced it with "As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary)."
-Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test: part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
+We have deleted this sentence and replaced it with "As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary)." Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test: part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
 But that is not what we propose.
@@
 Describing the relation between the SGPV and TOST is our main contribution.
-We just wanted to mention that researchers might want to combine an equivalence test with a NHST, because in the literature, this is a question we see many psychologists ask.
+We just wanted to mention that researchers might want to combine an equivalence test with a NHST, because in the literature, this is a question we see many psychologists ask when they use TOST.
 
@@
 1.
-In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: "We limit our analysis to normally distributed continuous data." After all, *p*-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
+In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: "We limit our analysis to continuous data sampled from a bivariate normal distribution." and  "Our conclusions about the relationship between TOST *p*-values and SGPV hold for second generation *p*-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution.".
+After all, *p*-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
 Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals).
 We look forward to future papers that illustrate the SGPV with other interval estimates and are happy to add the limitation to continuous normally distributed data in our article.
-Note that we did not add that the correspondence only holds for situations where the SE's are small compared to the width of the equivalence range, as the reviewer suggests.
 
 2.
-The reviewer repeats that the correspondence only holds when SE's are small compared to the width of the equivalence range.
-The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
+The reviewer notes that the correspondence only holds when SE's are small compared to the width of the equivalence range.
+The correspondence we refer to is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
 We clearly state that: "When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the *p*-value from an equivalence test for three values." This correspondence is not dependent upon the SE's.
-It will always hold for continuous normal data.
-The reviewer says that "The paper does not provide theoretical justification for this connection nor any proofs." We are unsure which proof is needed for the overlap between the three points, since it is rather trivial and we believe the explanation in the paper is very clear.
-
-For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50% when the observed mean falls exactly on the lower or upper equivalence bound, because 50% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the *t*-value for the equivalence test is also 0, and thus the *p*-value is 0.5 (situation A, Figure 3).
-Two other points always have to overlap.
-When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST *p*-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the *p*-value will always be 0.975, and the SGPV is 0.
-
-We do not think we can provide any other proof for this.
+It will always hold for CI based on bivariate continuous normally distributed data.
+The reviewer says that "The paper does not provide theoretical justification for this connection nor any proofs." We do not think proof is needed (the 'proof' is that the SGPV and the TOST both use the same confidence interval) and we believe the explanation in the paper of why this overlap must be so is very clear.
 A confidence interval and a *p*-value are directly related.
@@
 
-We believe this satisfactorily addresses the point by the reviewer that "Because of this
-lack of discussion, the reader can easily miss that the close correspondence only occurs when
-the sample size is large enough that the standard error is very small relative to the width of the
-equivalence zone." Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a *p*-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+We believe this satisfactorily addresses the point by the reviewer that "Because of this lack of discussion, the reader can easily miss that the close correspondence only occurs when the sample size is large enough that the standard error is very small relative to the width of the equivalence zone." Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a *p*-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+We have also changed the figures, making the SGPV a solid line, to make the relationship more clearly visible compared to the previous dotted curve.
 
@@
 We tried to find the passage the reviewer refers to when he writes "In light of this, the assertion without proof that classical *p*-values provide more or better assessments of the “evidence” appear out of place." but we could not.
-We do not use the word 'evidence' in the text (because neither the *p*-value from TOST nor the SGPV are measures of 'evidence' - we fully agree with BLume et al., 2018, in this respect).
+We do not use the word 'evidence' in the text (because neither the *p*-value from TOST nor the SGPV are measures of 'evidence' - we fully agree with Bume et al., 2018, in this respect).
 We also do not say the *p*-value is 'naturally informative'.
@@
 
-5. We fully agree with the reviewer on point 5 that "The maximum Type I Error rate for the SGPV over the null
-interval is 5%, exactly like the TOST test." Indeed, given the direct overlap between the TOST *p*-value and the SGPV at *p* = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical.
+5.
+We fully agree with the reviewer on point 5 that "The maximum Type I Error rate for the SGPV over the null interval is 5%, exactly like the TOST test." Indeed, given the direct overlap between the TOST *p*-value and the SGPV at *p* = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical.
 This is why we were so surprised when Blume et al (2018) write "They control the Type I error naturally, forcing it to zero as the sample size grows.
@@
 Given my own fondness of error control in statistical inferences, I get worried if researchers suggest we can ignore it, especially when making multiple comparisons.
-Imagine people start to use the SGPV instead of the TOST procedure whenever they perform 20 tests, and then argue they do not need to correct for multiple comparison - I think we can all agree this is undesireable!
+Imagine people start to use the SGPV instead of the TOST procedure whenever they perform 20 tests, and then argue they do not need to correct for multiple comparisons - I think we can all agree this is undesireable, given that we are trying to fix the replicability crisis in psychology!
 We have reduced the two paragraphs to one hopefully clear statement about the need to control error rates, also when using the SGPV.
@@
 
-@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
+"@blume_second-generation_2018 claim that when using the SGPV "Adjustments for multiple comparisons are obviated" (p.
 15).
 However, this is not correct.
-Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons."
 
@@
 
-5. In line with comments by reviewer 1, we removed statemetns about SGPV not being inferential, thereby solving the issue reviewer 2 raised.
+5. In line with comments by reviewer 1, we removed statements about SGPV not being inferential, thereby solving the issue reviewer 2 raised.
 
@@
 7.
+We agree that using TOST for small samples (e.g., N = 4) will not be useful.
+Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.
 It is a well-known fact that the TOST can have 0 power (and indeed, this is one of the main issues in the Perlman and Wu (1999) paper the reviewer cited).
@@
 Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study.
+The paper already contained a section explaining this ("This happens because the we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
+As Lakens (2017) notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power").
+
 Note that the exact same issue applies to the SGPV.
@@
 The question "Why use the TOST test then?" equally applies to "Why use the SGPV then?" if you, from the outset, know that the 'small sample correction' will lead to a SGPV of 0.5.
+Note that, following Reviewer 1's caution in using words ike 'always', we have added a comment about the overlap between the 3 points of TOST and SGPV where we say: "Two other points always have to overlap." which we now follow with: "Note that when sample sizes are small or equivalence bounds are narrow, small *p*-values for the TOST or a SGPV = 1 might not be observed in practice if too few observations are collected."
 
@@
 
-As a final comment, altough not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an "outright ban of TOST".
+As a final comment, although not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an "outright ban of TOST".
 The best summary of this discussion (of which Perlman & Wu is one contribution) can be found in Meyners (2012), which we cited.
@@
 
+\newpage
+# References
+
 \begingroup

### 2019-03-10 reply_to_reviews.R1.tex
R1 final

@@
 \abstract{
-We respond to all the comments raised by the two reviewers and the
-editors. We would like to thank the editor and reviewers for their
-suggestions for improvements, which we believe made our main argument
-much clearer, focussed, and formally correct. We feel we were able to
-accomodate all suggestions, and we hope you think our submission is
-ready to be accepted for publication in Meta-Psychology.
+We respond to all the comments on our submission that were raised by the
+two reviewers, as well as the comments you highlighted as editor. We
+would like to thank you and reviewers for suggestions for improvements,
+which we believe made our main argument much clearer, focussed, and
+formally correct. We feel we were able to accomodate all suggestions,
+and we hope you think our submission is ready to be accepted for
+publication in Meta-Psychology.
 
@@
 Thank you for your comments on our submitted manuscript. We have
-incorporated your three comments:
+incorporated your three small suggestions:
 
@@
 We will respond to the points raised by both reviewers in turn. Our
-points below detail 1) that we limit ourselves to a comparison of SGPV
-and TOST, and do not require researchers to perform both an equivalence
-test and a NHST (and therefore we did not add these curves to the
-Figures), 2) we rewrote the frequency claims, 3) we provide more detail
-about confidence intervals around correlations, and 4) removed all
-statements about the SGPV being a descriptive statistic.
+points below detail the main issues you highlighted in your editorial
+letter, namely 1) that we limit ourselves to a comparison of SGPV and
+TOST, and do not require researchers to perform both an equivalence test
+and a NHST (and therefore we did not add these curves to the Figures),
+2) we rewrote the frequency claims, 3) we provide more detail about
+confidence intervals around correlations, and 4) removed all statements
+about the SGPV being a descriptive statistic.
 
@@
   conclusions about the relationship between TOST \emph{p}-values and
-  SGPV hold for an SGPV calculated from confidence intervals, and
-  assuming continuous normally distributed data.}. We mainly intended to
-  refer to our conclusion that: \enquote{When confidence intervals are
-  symmetric we can think of the SGPV as a straight line that is directly
-  related to the \emph{p}-value from an equivalence test for three
-  values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
+  SGPV hold for second generation \emph{p}-values calculated from
+  confidence intervals, and assuming data is sampled from a bivariate
+  normal distribution}. We mainly intended to refer to our conclusion
+  that: \enquote{When confidence intervals are symmetric we can think of
+  the SGPV as a straight line that is directly related to the
+  \emph{p}-value from an equivalence test for three values} namely
+  \emph{p} = 0.5 for TOST when the SGPV will be 0.5, and the
   \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the
@@
   the SGPV}, we mean that there is a direct relation between three
-  points.
+  points. We have added the explanation: \enquote{When we discuss the
+  relationship between the \emph{p}-values from TOST and the SGPV, we
+  focus on their correspondence at three values, namely where the TOST
+  \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV
+  = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1. These three
+  values are important for the SGPV because they indicate the values at
+  which the SGPV indicates the data should be interpreted as compatible
+  with the null hypothesis (SGPV = 1), or with the alternative
+  hypothesis (SGPV = 0), or when the data are strictly inconclusive
+  (SGPV = 0.5).}
 \item
@@
   situations where \emph{p}-values for TOST differentiate between
-  observed results, while the SGPV does not differentiate.} and
-  \enquote{While the SGPV is 1 as long as the confidence interval falls
+  observed results, while the SGPV does not differentiate} and
+  \enquote{Where the SGPV is 1 as long as the confidence interval falls
   completely within the equivalence bounds, the \emph{p}-value for the
   TOST continues to differentiate between results as a function of how
-  far the confidence interval lies within the equivalence bounds (the
-  further the confidence interval is from both bounds, the lower the
-  \emph{p}-value).} and similarly \enquote{A third situation in which
-  the SGPV remains stable across a range of observed effects, while the
-  TOST \emph{p}-value continues to differentiate, is whenever the CI is
-  wider than the equivalence range, and the CI overlaps with the upper
-  \emph{and} lower equivalence bound.} We have removed the word
-  \enquote{unrelated} throughout the manuscript.
+  far the confidence interval lies within the equivalence bounds} and
+  similarly \enquote{A third situation in which the SGPV remains stable
+  across a range of observed effects, while the TOST \emph{p}-value
+  continues to differentiate, is whenever the CI is wider than the
+  equivalence range, and the CI overlaps with the upper \emph{and} lower
+  equivalence bound}. We have removed the word \enquote{unrelated}
+  throughout the manuscript.
 \item
@@
   for peer review - to be able to improve it based on feedback from
-  experts. We now preface the sentence with \enquote{As long as data is
-  normally distributed,}. We follow your recommendation throughout to
-  not generalize beyond the scenarios we study. In the second paragraph
-  of the manuscript we now clearly state: \enquote{We limit our analysis
-  to normally distributed continuous data.} See also point 5 below.
+  experts. We now preface the sentence with \enquote{As long as data are
+  sampled from a bivariate normal distribution,}. We follow your
+  recommendation throughout to not generalize beyond the scenarios we
+  study. In the second paragraph of the manuscript we now clearly state:
+  \enquote{We limit our analysis to continuous data sampled from a
+  bivariate normal distribution.} See also point 5 below.
 \item
@@
   make the sentence clearer, we have changed \enquote{these values} into
-  \enquote{at the values p = 0.025 and p = 0.975} It should now be clear
-  the sections are not contradictory - TOST differentiates below p
-  \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
+  \enquote{at the values \emph{p} = 0.025 and \emph{p} = 0.975} It
+  should now be clear the sections are not contradictory - TOST
+  differentiates below \emph{p} \textless{} 0.025, when the SGPV is 1
+  for all \emph{p} \textless{} 0.025.
 \item
@@
   \enquote{compatibility with the null hypothesis} under the assumption
-  of normally distributed data, and the generalizability of this
-  statement needs to be examined beyond normally distributed data
-  requires further examination.}
+  of a bivariate normal distribution, and the generalizability of this
+  statement needs to be examined beyond normal bivariate distributions.}
 \item
@@
   statements about whether such values are descriptive or inferential.
-\item
-  We agree that using TOST for small samples (e.g., N = 4) will not be
-  useful. Indeed, an a-priori power analysis for equivalence tests would
-  prevent anyone from planning such a study, since the result will be
-  that such a study has 0 power - the CI will never fit withing the
-  equivalence bounds.
-\item
-  With our recommendations, we have limited our conclusions to the
+\end{enumerate}
+
+Based on your recommendations, we have limited our conclusions to the
 specific cases we have examined, and noted the possibility for future
-  research to examine a wider set of assumptions. An additional change
-  not mentioned above is that we renamed the section on asymmetric
-  confidence intervals to the more specific \enquote{The relation
-  between equivalence tests and SGPV for asymmetrical confidence
-  intervals around correlations} instead of the more general
-  \enquote{The relation between equivalence tests and SGPV when
-  confidence intervals are not symmetrical}. We appreciate the very
-  positive evaluation of our manuscript, but even more so the criticism
-  which allowed us to improve the manuscript.
-\end{enumerate}
+research to examine a wider set of assumptions. An additional change not
+mentioned above is that we renamed the section on asymmetric confidence
+intervals to the more specific \enquote{The relation between equivalence
+tests and SGPV for asymmetrical confidence intervals around
+correlations} instead of the more general \enquote{The relation between
+equivalence tests and SGPV when confidence intervals are not
+symmetrical}. We appreciate the very positive evaluation of our
+manuscript, but even more so the criticism which allowed us to improve
+the manuscript.
 
@@
 compare SGPV with \emph{p}-values from TOST throughout our paper, and in
-all figures, but then at the end, in page 20, we write:
+all figures, but then at the end, in page 20, we wrote:
 
@@
 manuscript, we already pointed out how the SGPV is basically the same as
-an equivalence test and a minimum effect test (on page 7):
+an equivalence test and a minimum effect test (on page 7), and we have
+expanded this text to clarify that a minimum effects test and TOST are
+complementary:
 
@@
 of zero, but to reject the smallest effect size of interest (i.e., the
-equivalence bounds). The SGPV summarizes the information from an
-equivalence test and a minimum-effect test.}
+equivalence bounds). An equivalence test and minimum effect test against
+the same equivalence bound are complementary, and when a TOST
+\emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum
+effect test is smaller than 0.05 (and therefore the minimum effect test
+provides no additional information that can not be derived from the
+\emph{p}-value from the equivalence test). The SGPV summarizes the
+information from an equivalence test (and the complementary
+minimum-effect test).}
 
-One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0
-gives away that the equivalence test can be interpreted as a minimum
-effect test against the equivalence bound. When the TOST \emph{p}-value
-is 0.975, the 95\% CI touches either the upper or lower equivalence
-bound, and fall completely outside of the equivalence range. This is
-mathematically identical to a statistically significant minimum effect
-test at p \textless{} 0.05. We didn't make this explicit, but we clearly
-should have. We have added the sentence (on page 7):
-
-\enquote{An equivalence test and minimum effect test against the same
-equivalence bound are complementary, and when a TOST \emph{p}-value is
-larger than 0.975, the \emph{p}-value for the minimum effect test is
-smaller than 0.05, and the minimum effect test provides no additional
-information that can not be derived from the \emph{p}-value from the
-equivalence test.}
+The overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0 gives away
+that the equivalence test can be interpreted as a minimum effect test
+against the equivalence bound. When the TOST \emph{p}-value is 0.975,
+the 95\% CI touches either the upper or lower equivalence bound, and
+fall completely outside of the equivalence range. This is mathematically
+identical to a statistically significant minimum effect test at \emph{p}
+\textless{} 0.05. We clearly should have made this more explicit, and
+hope the additional text clarifies the statistical relationship between
+TOST, a minimum effect test, and the SGPV
 
@@
 might want to combine an equivalence test with a NHST, because in the
-literature, this is a question we see many psychologists ask.
+literature, this is a question we see many psychologists ask when they
+use TOST.
 
@@
   the manuscript we now clearly state: \enquote{We limit our analysis to
-  normally distributed continuous data.} After all, \emph{p}-values and
+  continuous data sampled from a bivariate normal distribution.} and
+  \enquote{Our conclusions about the relationship between TOST
+  \emph{p}-values and SGPV hold for second generation \emph{p}-values
+  calculated from confidence intervals, and assuming data is sampled
+  from a bivariate normal distribution.}. After all, \emph{p}-values and
   confidence are directly related, but Bayesian credible intervals would
@@
   and are happy to add the limitation to continuous normally distributed
-  data in our article. Note that we did not add that the correspondence
-  only holds for situations where the SE's are small compared to the
-  width of the equivalence range, as the reviewer suggests.
+  data in our article.
 \item
-  The reviewer repeats that the correspondence only holds when SE's are
+  The reviewer notes that the correspondence only holds when SE's are
   small compared to the width of the equivalence range. The
-  correspondence is not in the shape of the curve (which clearly differs
-  across Figures 2, 6, and 9). We clearly state that: \enquote{When
-  confidence intervals are symmetric we can think of the SGPV as a
-  straight line that is directly related to the \emph{p}-value from an
-  equivalence test for three values.} This correspondence is not
-  dependent upon the SE's. It will always hold for continuous normal
-  data. The reviewer says that \enquote{The paper does not provide
-  theoretical justification for this connection nor any proofs.} We are
-  unsure which proof is needed for the overlap between the three points,
-  since it is rather trivial and we believe the explanation in the paper
-  is very clear.
-\end{enumerate}
-
-For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and
-SGPV = 1, and TOST p = 0.975 and SGPV = 1: ``The SGPV is 50\% when the
-observed mean falls exactly on the lower or upper equivalence bound,
-because 50\% of the symmetrical confidence interval overlaps with the
-equivalence range. When the observed mean equals the equivalence bound,
-the difference between the mean in the data and the equivalence bound is
-0, the \emph{t}-value for the equivalence test is also 0, and thus the
-\emph{p}-value is 0.5 (situation A, Figure 3). Two other points always
-have to overlap. When the 95\% CI falls completely inside the
-equivalence region, and one endpoint of the confidence interval is
-exactly equal to one of the equivalence bounds (see situation B in
-Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is
-always 0.025, and the SGPV is 1. The third point where the SGPV and the
-\emph{p}-value from the TOST procedure should overlap is where the 95\%
-CI falls completely outside of the equivalence range, but one endpoint
-of the confidence interval is equal to the equivalence bound (see
-situation C in Figure 3), when the \emph{p}-value will always be 0.975,
-and the SGPV is 0.
-
-We do not think we can provide any other proof for this. A confidence
-interval and a \emph{p}-value are directly related. The TOST procedure
-is a test using the confidence interval, and the SGPV (now that we
-clearly limited our discussion to a SGPV based on a confidence interval
+  correspondence we refer to is not in the shape of the curve (which
+  clearly differs across Figures 2, 6, and 9). We clearly state that:
+  \enquote{When confidence intervals are symmetric we can think of the
+  SGPV as a straight line that is directly related to the \emph{p}-value
+  from an equivalence test for three values.} This correspondence is not
+  dependent upon the SE's. It will always hold for CI based on bivariate
+  continuous normally distributed data. The reviewer says that
+  \enquote{The paper does not provide theoretical justification for this
+  connection nor any proofs.} We do not think proof is needed (the
+  \enquote{proof} is that the SGPV and the TOST both use the same
+  confidence interval) and we believe the explanation in the paper of
+  why this overlap must be so is very clear. A confidence interval and a
+  \emph{p}-value are directly related. The TOST procedure is a test
+  using the confidence interval, and the SGPV (now that we clearly
+  limited our discussion to a SGPV based on a confidence interval
   calculated from continuous normal data) compared against the same
@@
   discussion about the correspondence of the curves to these 3 points.
-Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
-13). Nevertheless, in these graphs, we still have the correspondence
-between these 3 points (or at least the 2 points if the CI is too wide
-compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
-To make it clearer that we talk about the overlap in these 3 critical
-points, we have added:
+  Indeed, in some figures, the curves are less similar (e.g., Figure 6,
+  9, 13). Nevertheless, in these graphs, we still have the
+  correspondence between these 3 points (or at least the 2 points if the
+  CI is too wide compared to the equivalence bounds to ever observe a
+  \emph{p} = 0.025). To make it clearer that we talk about the overlap
+  in these 3 critical points, we have added:
+\end{enumerate}
 
@@
 about the correspondence of these 3 points, and not the entire curve, is
-sufficient to address point 2.
+sufficient to address point 2. We have also changed the figures, making
+the SGPV a solid line, to make the relationship more clearly visible
+compared to the previous dotted curve.
 
@@
   \emph{p}-value from TOST nor the SGPV are measures of
-  \enquote{evidence} - we fully agree with BLume et al., 2018, in this
+  \enquote{evidence} - we fully agree with Bume et al., 2018, in this
   respect). We also do not say the \emph{p}-value is \enquote{naturally
@@
 procedure whenever they perform 20 tests, and then argue they do not
-need to correct for multiple comparison - I think we can all agree this
-is undesireable! We have reduced the two paragraphs to one hopefully
-clear statement about the need to control error rates, also when using
-the SGPV. We hope this addresses the concerns by the editor as well as
-the reviewer, while still making an important point in the literature
-about the need to control error rates (if one cares about drawing
-incorrect conclusions).
+need to correct for multiple comparisons - I think we can all agree this
+is undesireable, given that we are trying to fix the replicability
+crisis in psychology! We have reduced the two paragraphs to one
+hopefully clear statement about the need to control error rates, also
+when using the SGPV. We hope this addresses the concerns by the editor
+as well as the reviewer, while still making an important point in the
+literature about the need to control error rates (if one cares about
+drawing incorrect conclusions).
 
-Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
-\enquote{Adjustments for multiple comparisons are obviated} (p.~15).
-However, this is not correct. Given the direct relationship between TOST
-and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025
-equals SGPV = 1, as long as the SGPV is calculated based on confidence
-intervals, and assuming continuous and normally distributed data), not
-correcting for multiple comparisons will inflate the probability of
-concluding the absence of a meaningful effect based on the SGPV in
-exactly the same way as for equivalence tests. Whenever statistical
-tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or
-SGPV =1), it is possible do so erroneously, and if researchers want to
-control error rates, they need to correct for multiple comparisons.
+\enquote{Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
+when using the SGPV}Adjustments for multiple comparisons are obviated"
+(p.~15). However, this is not correct. Given the direct relationship
+between TOST and SGPV highlighted in this manuscript (where a TOST
+\emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated
+based on confidence intervals, and assuming data are sampled from a
+continuous bivariate normal distribution), not correcting for multiple
+comparisons will inflate the probability of concluding the absence of a
+meaningful effect based on the SGPV in exactly the same way as it will
+for equivalence tests. Whenever statistical tests are interpreted as
+support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do
+so erroneously, and if researchers want to control error rates, they
+need to correct for multiple comparisons."
 
@@
 \item
-  In line with comments by reviewer 1, we removed statemetns about SGPV
+  In line with comments by reviewer 1, we removed statements about SGPV
   not being inferential, thereby solving the issue reviewer 2 raised.
@@
 \item
-  It is a well-known fact that the TOST can have 0 power (and indeed,
-  this is one of the main issues in the Perlman and Wu (1999) paper the
-  reviewer cited). As explained in Lakens (2017): \enquote{It is
-  important to take statistical power into account when determining the
-  equivalence bounds because, in small samples (where CIs are wide), a
-  study might have no statistical power (i.e., the CI will always be so
-  wide that it is necessarily wider than the equivalence bounds).} We
-  agree with the reviewer it is not interesting to do a test if you have
-  0 power. People should design informative experiments by doing an
-  a-priori power analysis. Any problem in this respect is not a problem
-  with equivalence tests, but a problem with designing a bad study. Note
-  that the exact same issue applies to the SGPV. It is also possible to
-  have 0 power for the SGPV - so we do not understand why the reviewer
-  is so surprised about this. The question \enquote{Why use the TOST
-  test then?} equally applies to \enquote{Why use the SGPV then?} if
-  you, from the outset, know that the \enquote{small sample correction}
-  will lead to a SGPV of 0.5.
+  We agree that using TOST for small samples (e.g., N = 4) will not be
+  useful. Indeed, an a-priori power analysis for equivalence tests would
+  prevent anyone from planning such a study, since the result will be
+  that such a study has 0 power - the CI will never fit withing the
+  equivalence bounds. It is a well-known fact that the TOST can have 0
+  power (and indeed, this is one of the main issues in the Perlman and
+  Wu (1999) paper the reviewer cited). As explained in Lakens (2017):
+  \enquote{It is important to take statistical power into account when
+  determining the equivalence bounds because, in small samples (where
+  CIs are wide), a study might have no statistical power (i.e., the CI
+  will always be so wide that it is necessarily wider than the
+  equivalence bounds).} We agree with the reviewer it is not interesting
+  to do a test if you have 0 power. People should design informative
+  experiments by doing an a-priori power analysis. Any problem in this
+  respect is not a problem with equivalence tests, but a problem with
+  designing a bad study. The paper already contained a section
+  explaining this (\enquote{This happens because the we are examining a
+  scenario where the 90\% CI is so wide that it never falls completely
+  within the two equivalence bounds. As Lakens (2017) notes: \enquote{in
+  small samples (where CIs are wide), a study might have no statistical
+  power (i.e., the CI will always be so wide that it is necessarily
+  wider than the equivalence bounds).} None of the \emph{p}-values based
+  on the TOST procedure are below 0.05, and thus, in the long run we
+  have 0\% power}).
+\end{enumerate}
+
+Note that the exact same issue applies to the SGPV. It is also possible
+to have 0 power for the SGPV - so we do not understand why the reviewer
+is so surprised about this. The question \enquote{Why use the TOST test
+then?} equally applies to \enquote{Why use the SGPV then?} if you, from
+the outset, know that the \enquote{small sample correction} will lead to
+a SGPV of 0.5. Note that, following Reviewer 1's caution in using words
+ike \enquote{always}, we have added a comment about the overlap between
+the 3 points of TOST and SGPV where we say: \enquote{Two other points
+always have to overlap.} which we now follow with: \enquote{Note that
+when sample sizes are small or equivalence bounds are narrow, small
+\emph{p}-values for the TOST or a SGPV = 1 might not be observed in
+practice if too few observations are collected.}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{7}
+\tightlist
 \item
@@
 
-As a final comment, altough not explicitly listed as a major point of
+As a final comment, although not explicitly listed as a major point of
 minor point, we are happy to respond to the reviewers' suggestion that
@@
 
+\newpage
+
+\section{References}\label{references}
+
 \begingroup
@@
 
+\hypertarget{ref-murphy_statistical_2014}{}
+Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
+power analysis: A simple and general model for traditional and modern
+hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
+Francis Group.
+
 \endgroup

### 2019-03-10 manuscript.R1.Rmd
R1 final

@@
 
-Second generation *p*-values (SGPV) were recently proposed to as a statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018].
+Second generation *p*-values (SGPV) were recently proposed as a statistic that represents ‘the proportion of data-supported hypotheses that are also null hypotheses’ [@blume_second-generation_2018]. 
 The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis. 
@@
 To examine the relation between the TOST *p*-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
-In Figure \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
+Replicating the example by @blume_second-generation_2018, in Figure \ref{fig:TOSTSGPV1} *p*-values are plotted for the TOST procedure and the SGPV.
 The statistics are calculated for hypothetical one-sample *t*-tests for observed means ranging from 140 to 150 (on the x-axis).
@@
 For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST *p*-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the *p*-value for the equivalence test is 1, and the SGPV is 0.
-Our conclusions about the relationship between TOST *p*-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.
-Readers can explore the relationship between TOST *p*-values and SGPV for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
 
@@
 ```
-```{r, TOSTSGPV1, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
+
+```{r, TOSTSGPV1, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2, illustrating that when the TOST *p*-value = 0.5, the SGPV = 0.5, when the TOST *p*-value is 0.975, 1-SGPV = 1, and when the TOST *p*-value = 0.025, 1-SGPV = 0."}
 plot(NA, 
@@
 axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)
-lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3)
 lines(p_tost_list, lwd = 3)
 ```
+
+Our conclusions about the relationship between TOST *p*-values and SGPV hold for second generation *p*-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution.
+Readers can explore the relationship between TOST *p*-values and SGPV for themselves in an online Shiny app: http://shiny.ieis.tue.nl/TOST_vs_SGPV/.
 
@@
 We see that the *p*-value from the TOST procedure and the SGPV follow each other closely.
-When we discuss the relationship between the p-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
+When we discuss the relationship between the *p*-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST *p* = 0.025 and SGPV is 1, where the TOST *p* = 0.5 and SGPV = 0.5, and where the TOST *p* = 0.975 and SGPV = 1.
 These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
-These three points of overlap are indicated by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2}.
-
-```{r, TOSTSGPV2, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
+These three points of overlap are indicated by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2} at TOST *p*-values of 0.975, 0.5, and 0.025.
+
+```{r, TOSTSGPV2, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 30 and a standard deviation of 2."}
 plot(NA, 
@@
 
-lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3)
 lines(p_tost_list, lwd = 3)
@@
 When the 95% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST *p*-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+Note that when sample sizes are small or equivalence bounds are narrow, small *p*-values for the TOST or a SGPV = 1 might not be observed in practice if too few observations are collected.
 The third point where the SGPV and the *p*-value from the TOST procedure should overlap is where the 95% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the *p*-value will always be 0.975, and the SGPV is 0.
@@
 The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
-An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test.
-The SGPV summarizes the information from an equivalence test and a minimum-effect test.
+An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST *p*-value is larger than 0.975, the *p*-value for the minimum effect test is smaller than 0.05 (and therefore the minimum effect test provides no additional information that can not be derived from the *p*-value from the equivalence test).
+The SGPV summarizes the information from an equivalence test (and the complementary minimum-effect test).
 These can be two relevant questions to ask, although it often makes sense to combine an equivalence test and a null-hypothesis test instead [@lakens_equivalence_2018].
@@
 The difference in the percentage of overlap between A and B (`r round(SGPV1-SGPV2, digits = 2)`) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (`r round(SGPV3-SGPV4, digits = 2)`).
-As the observed mean in a one-sample *t*-test lies closer to the test value, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly. 
+As the observed mean in a one-sample *t*-test lies closer to the test value, from situation A to D, the difference in the overlap changes uniformly. 
 As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data are not uniformly distributed.
-The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`.
-As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C and D (`r round(tail3-tail4, digits = 3)`).
+The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 4)`, `r round(tail2, digits = 4)`, `r round(tail3, digits = 4)`, and `r round(tail4, digits = 4)`.
+As we can see, the difference between A and B (`r round(tail1-tail2, digits = 4)`) is not the same as the difference between C and D (`r round(tail3-tail4, digits = 4)`).
 Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5.
@@
 When the SGPV is either 0 or 1, *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
-While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value).
+Where the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the *p*-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the *p*-value).
 The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure.
@@
 
-```{r, TOSTSGPV6, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+```{r, TOSTSGPV6, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis).
 Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means."}
@@
 
-lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
+lines(sgpv_list, type="l", col = "darkgrey", lwd = 3)
 lines(p_tost_list, lwd = 3)
@@
 In other words, we cannot conclude equivalence based on any of the observed means.
-This happens because the TOST *p*-value is smaller than 0.05 only when the 90% CI falls completely between the upper and lower equivalence bounds.
-However, we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds, and thus the equivalence test is never significant.
+This happens because the we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
 As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
@@
 
-```{r, TOSTSGPV9, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+```{r, TOSTSGPV9, fig.cap="Comparison of *p*-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis).
 The sample size is small (n = 10), but because the sd is half as big as in Figure \\ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
@@
 For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.993.
-Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally distributed, which allows one to compute symmetric confidence intervals, which are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.
+Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally z-distributed, which allows one to compute symmetric confidence intervals.
+These confidence intervals are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.
 
@@
 The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
-The *p*-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
+The *p*-value for the TOST procedure and 1-SGPV are still related as discussed above, with TOST *p*-values of 0.975 and 0.025 corresponding to a 1-SGPV of 1 and 0, respectively.
 There are two important differences, however.
@@
 
-```{r, TOSTSGPV11, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05."}
+```{r, TOSTSGPV11, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05."}
 par(xpd=F)
@@
 In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%.
+However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at *r* = -0.45 and *r* = 0.45 are larger than 50%.
 Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
 
-```{r, TOSTSGPV12, fig.cap="Three 95% confidence intervals for observed effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the confidence interval for r = 0 is symmetric."}
+```{r, TOSTSGPV12, fig.cap="Three 95% confidence intervals for observed effect sizes of *r* = -0.45, *r* = 0, and *r* = 0.45 for n = 30. Only the confidence interval for *r* = 0 is symmetric."}
 n=30
@@
 When introducing a new statistical method, it is important to compare it to existing approaches and specify its relative strengths and weaknesses.
+Here, we aimed to compare the SGPV against equivalence tests based on the TOST procedure.
 First of all, even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
@@
 As already mentioned, this interpretation of a SGPV is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).
-The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example *p* = 0.048 and *p* = 0.002.
+The difference is that where a SGPV of 1 can be interpreted as *p* < .025, equivalence tests provide exact *p*-values, and they continue to differentiate between for example *p* = 0.024 and *p* = 0.002.
 Whether this is desirable depends on the perspective that is used.
@@
 
-```{r, TOSTSGPV13, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05."}
+```{r, TOSTSGPV13, fig.cap="Comparison of *p*-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of *r* = 0.4 and *r* = 0.8 with n = 10 and an alpha of 0.05."}
 par(xpd=F)
@@
 
-@blume_second-generation_2018 claim that "Adjustments for multiple comparisons are obviated" (p.
+@blume_second-generation_2018 claim that when using the SGPV "Adjustments for multiple comparisons are obviated" (p.
 15).
 However, this is not correct.
-Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 

### 2019-03-10 manuscript.R1.tex
R1 final

@@
 
-Second generation \emph{p}-values (SGPV) were recently proposed to as a
+Second generation \emph{p}-values (SGPV) were recently proposed as a
 statistic that represents \enquote{the proportion of data-supported
@@
 the relation between the TOST \emph{p}-value and the SGPV we can
-calculate both statistics across a range of observed effect sizes. In
-Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST
-procedure and the SGPV. The statistics are calculated for hypothetical
-one-sample \emph{t}-tests for observed means ranging from 140 to 150 (on
-the x-axis). The equivalence range is set to 145 ± 2 (i.e., an
-equivalence range from 143 to 147), the observed standard deviation is
-assumed to be 2, and the sample size is 30. For example, for the
-left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST
-\emph{p}-value is calculated for a hypothetical study with a sample size
-of 30, an observed standard deviation of 2, and an observed mean of 140,
-where the \emph{p}-value for the equivalence test is 1, and the SGPV is
-0. Our conclusions about the relationship between TOST \emph{p}-values
-and SGPV hold for an SGPV calculated from confidence intervals, and
-assuming continuous normally distributed data. Readers can explore the
-relationship between TOST \emph{p}-values and SGPV for themselves in an
-online Shiny app: \url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
+calculate both statistics across a range of observed effect sizes.
+Replicating the example by Blume et al. (2018), in Figure
+\ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST procedure
+and the SGPV. The statistics are calculated for hypothetical one-sample
+\emph{t}-tests for observed means ranging from 140 to 150 (on the
+x-axis). The equivalence range is set to 145 ± 2 (i.e., an equivalence
+range from 143 to 147), the observed standard deviation is assumed to be
+2, and the sample size is 30. For example, for the left-most point in
+Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST \emph{p}-value is
+calculated for a hypothetical study with a sample size of 30, an
+observed standard deviation of 2, and an observed mean of 140, where the
+\emph{p}-value for the equivalence test is 1, and the SGPV is 0.
 
@@
 \caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis) tested against a mean of 145 in a one-sample
-\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
+line) and SGPV (grey line) across a range of observed sample means
+(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
+a sample size of 30 and a standard deviation of 2, illustrating that
+when the TOST \emph{p}-value = 0.5, the SGPV = 0.5, when the TOST
+\emph{p}-value is 0.975, 1-SGPV = 1, and when the TOST \emph{p}-value =
+0.025, 1-SGPV = 0.}
 \end{figure}
+
+Our conclusions about the relationship between TOST \emph{p}-values and
+SGPV hold for second generation \emph{p}-values calculated from
+confidence intervals, and assuming data is sampled from a bivariate
+normal distribution. Readers can explore the relationship between TOST
+\emph{p}-values and SGPV for themselves in an online Shiny app:
+\url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
 
@@
 that the \emph{p}-value from the TOST procedure and the SGPV follow each
-other closely. When we discuss the relationship between the p-values
-from TOST and the SGPV, we focus on their correspondence at three
-values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
-TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
-and SGPV = 1. These three values are important for the SGPV because they
-indicate the values at which the SGPV indicates the data should be
-interpreted as compatible with the null hypothesis (SGPV = 1), or with
-the alternative hypothesis (SGPV = 0), or when the data are strictly
-inconclusive (SGPV = 0.5). These three points of overlap are indicated
-by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2}.
+other closely. When we discuss the relationship between the
+\emph{p}-values from TOST and the SGPV, we focus on their correspondence
+at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1,
+where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST
+\emph{p} = 0.975 and SGPV = 1. These three values are important for the
+SGPV because they indicate the values at which the SGPV indicates the
+data should be interpreted as compatible with the null hypothesis (SGPV
+= 1), or with the alternative hypothesis (SGPV = 0), or when the data
+are strictly inconclusive (SGPV = 0.5). These three points of overlap
+are indicated by the horizontal dotted lines in Figure
+\ref{fig:TOSTSGPV2} at TOST \emph{p}-values of 0.975, 0.5, and 0.025.
 
@@
 \caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
-line) and 1-SGPV (dotted grey line) across a range of observed sample
-means (x-axis) tested against a mean of 145 in a one-sample
-\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
+line) and 1-SGPV (grey line) across a range of observed sample means
+(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
+a sample size of 30 and a standard deviation of 2.}
 \end{figure}
@@
 (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-The third point where the SGPV and the \emph{p}-value from the TOST
-procedure should overlap is where the 95\% CI falls completely outside
-of the equivalence range, but one endpoint of the confidence interval is
-equal to the equivalence bound (see situation C in Figure
-\ref{fig:TOSTSGPV3}), when the \emph{p}-value will always be 0.975, and
-the SGPV is 0. Note that this situation is in essence a minimum-effect
-test (Murphy, Myors, \& Wolach, 2014). The goal of a minimum-effect is
-not just to reject a difference of zero, but to reject the smallest
-effect size of interest (i.e., the equivalence bounds). An equivalence
-test and minimum effect test against the same equivalence bound are
-complementary, and when a TOST \emph{p}-value is larger than 0.975, the
-\emph{p}-value for the minimum effect test is smaller than 0.05, and the
-minimum effect test provides no additional information that can not be
-derived from the \emph{p}-value from the equivalence test. The SGPV
-summarizes the information from an equivalence test and a minimum-effect
-test. These can be two relevant questions to ask, although it often
-makes sense to combine an equivalence test and a null-hypothesis test
-instead (Lakens et al., 2018).
+Note that when sample sizes are small or equivalence bounds are narrow,
+small \emph{p}-values for the TOST or a SGPV = 1 might not be observed
+in practice if too few observations are collected. The third point where
+the SGPV and the \emph{p}-value from the TOST procedure should overlap
+is where the 95\% CI falls completely outside of the equivalence range,
+but one endpoint of the confidence interval is equal to the equivalence
+bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the
+\emph{p}-value will always be 0.975, and the SGPV is 0. Note that this
+situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
+2014). The goal of a minimum-effect is not just to reject a difference
+of zero, but to reject the smallest effect size of interest (i.e., the
+equivalence bounds). An equivalence test and minimum effect test against
+the same equivalence bound are complementary, and when a TOST
+\emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum
+effect test is smaller than 0.05 (and therefore the minimum effect test
+provides no additional information that can not be derived from the
+\emph{p}-value from the equivalence test). The SGPV summarizes the
+information from an equivalence test (and the complementary
+minimum-effect test). These can be two relevant questions to ask,
+although it often makes sense to combine an equivalence test and a
+null-hypothesis test instead (Lakens et al., 2018).
 
@@
 one-sample \emph{t}-test lies closer to the test value, from situation A
-to D, the mean gets closer to the test value by 0.1) the difference in
-the overlap changes uniformly. As we move the observed mean closer to
-the test value in steps of 0.1 across A to D the \emph{p}-value
-calculated for normally distributed data are not uniformly distributed.
-The probability of observing data more extreme than the upper bound of 2
-is (from A to D) 0.16, 0.12, 0.08, and 0.06. As we can see, the
-difference between A and B (0.04) is not the same as the difference
-between C and D (0.03). Indeed, the difference in \emph{p}-values is the
-largest as you start at \emph{p} = 0.5 (when the observed mean falls on
-the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is
-the steepest at \emph{p} = 0.5. Note that where the SGPV reaches 1 or 0,
-\emph{p}-values closely approximate 0 and 1, but never reach these
-values.
+to D, the difference in the overlap changes uniformly. As we move the
+observed mean closer to the test value in steps of 0.1 across A to D the
+\emph{p}-value calculated for normally distributed data are not
+uniformly distributed. The probability of observing data more extreme
+than the upper bound of 2 is (from A to D) 0.16, 0.12, 0.08, and 0.05.
+As we can see, the difference between A and B (0.04) is not the same as
+the difference between C and D (0.03). Indeed, the difference in
+\emph{p}-values is the largest as you start at \emph{p} = 0.5 (when the
+observed mean falls on the test value), which is why the line in Figure
+\ref{fig:TOSTSGPV1} is the steepest at \emph{p} = 0.5. Note that where
+the SGPV reaches 1 or 0, \emph{p}-values closely approximate 0 and 1,
+but never reach these values.
 
@@
 from the equivalence test fall between 0.975 and 1 or between 0 and
-0.025. While the SGPV is 1 as long as the confidence interval falls
+0.025. Where the SGPV is 1 as long as the confidence interval falls
 completely within the equivalence bounds, the \emph{p}-value for the
@@
 \caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis). Because the sample size is small (n = 10) and the CI is
-more than twice as wide as the equivalence range (set to -0.4 to 0.4),
-the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
+line) and SGPV (grey line) across a range of observed sample means
+(x-axis). Because the sample size is small (n = 10) and the CI is more
+than twice as wide as the equivalence range (set to -0.4 to 0.4), the
+SGPV is set to 0.5 (horizontal lightgrey line) across a range of
 observed means.}
@@
 equivalence based on any of the observed means. This happens because the
-TOST \emph{p}-value is smaller than 0.05 only when the 90\% CI falls
-completely between the upper and lower equivalence bounds. However, we
-are examining a scenario where the 90\% CI is so wide that it never
-falls completely within the two equivalence bounds, and thus the
-equivalence test is never significant. As Lakens (2017) notes:
-\enquote{in small samples (where CIs are wide), a study might have no
-statistical power (i.e., the CI will always be so wide that it is
-necessarily wider than the equivalence bounds).} None of the
+we are examining a scenario where the 90\% CI is so wide that it never
+falls completely within the two equivalence bounds. As Lakens (2017)
+notes: \enquote{in small samples (where CIs are wide), a study might
+have no statistical power (i.e., the CI will always be so wide that it
+is necessarily wider than the equivalence bounds).} None of the
 \emph{p}-values based on the TOST procedure are below 0.05, and thus, in
@@
 \caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis). The sample size is small (n = 10), but because the sd is
-half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is
-less than twice as wide as the equivalence range (set to -0.4 to 0.4).
-The SGPV is not set to 0.5 (horizontal light grey line) but reaches a
+line) and SGPV (grey line) across a range of observed sample means
+(x-axis). The sample size is small (n = 10), but because the sd is half
+as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less
+than twice as wide as the equivalence range (set to -0.4 to 0.4). The
+SGPV is not set to 0.5 (horizontal light grey line) but reaches a
 maximum slightly above 0.5 across a range of observed means.}
@@
 intervals for a correlation involves a Fisher's z-transformation, which
-transforms values such that they are approximately normally distributed,
-which allows one to compute symmetric confidence intervals, which are
-then retransformed into a correlation, where the confidence intervals
-are asymmetric if the correlation is not exactly zero.
+transforms values such that they are approximately normally
+z-distributed, which allows one to compute symmetric confidence
+intervals. These confidence intervals are then retransformed into a
+correlation, where the confidence intervals are asymmetric if the
+correlation is not exactly zero.
 
@@
 similar to that in Figure \ref{fig:TOSTSGPV2}. The \emph{p}-value for
-the TOST procedure and 1-SGPV are still identical when \emph{p}-values
-are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted
-lines). There are two important differences, however. First of all, the
-SGPV is no longer a straight line, but a curve, due to the asymmetry in
-the 95\% CI. Second, and most importantly, the \emph{p}-value for the
-equivalence test and the SGPV do no longer overlap at \emph{p} = 0.5.
+the TOST procedure and 1-SGPV are still related as discussed above, with
+TOST \emph{p}-values of 0.975 and 0.025 corresponding to a 1-SGPV of 1
+and 0, respectively. There are two important differences, however. First
+of all, the SGPV is no longer a straight line, but a curve, due to the
+asymmetry in the 95\% CI. Second, and most importantly, the
+\emph{p}-value for the equivalence test and the SGPV do no longer
+overlap at \emph{p} = 0.5.
 
@@
 \caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (dotted grey curve) across a range of observed
-sample correlations (x-axis) tested against equivalence bounds of r =
--0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
+(black line) and 1-SGPV (grey curve) across a range of observed sample
+correlations (x-axis) tested against equivalence bounds of r = -0.45 and
+r = 0.45 with n = 30 and an alpha of 0.05.}
 \end{figure}
@@
 be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation
-\emph{p}-values associated with the observed correlations at r = -0.45
-and r = 0.45 are larger than 50\%. Because the confidence intervals are
-asymmetric around the observed effect size of 0.45 (ranging from 0.11 to
-0.70) according to Blume et al. (2018) 58.11\% of the data-supported
-hypotheses are null hypotheses, and therefore 58.10\% of the
-data-supported hypotheses are compatible with the null premise.
+\emph{p}-values associated with the observed correlations at \emph{r} =
+-0.45 and \emph{r} = 0.45 are larger than 50\%. Because the confidence
+intervals are asymmetric around the observed effect size of 0.45
+(ranging from 0.11 to 0.70) according to Blume et al. (2018) 58.11\% of
+the data-supported hypotheses are null hypotheses, and therefore 58.10\%
+of the data-supported hypotheses are compatible with the null premise.
 
@@
 \caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
-effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the
-confidence interval for r = 0 is symmetric.}
+effect sizes of \emph{r} = -0.45, \emph{r} = 0, and \emph{r} = 0.45 for
+n = 30. Only the confidence interval for \emph{r} = 0 is symmetric.}
 \end{figure}
@@
 to existing approaches and specify its relative strengths and
-weaknesses. First of all, even though a SGPV of 1 or 0 has a clear
-interpretation (we can reject effects outside or inside the equivalence
-range), intermediate values are not as easy to interpret (especially for
-effects that have asymmetric confidence intervals). In one sense, they
-are what they are (the proportion of overlap), but it can be unclear
-what this number tells us about the data we have collected. This is not
-too problematic, since the main use of the SGPV (e.g., in all examples
-provided by Blume and colleagues) seems to be to examine whether the
-SGPV is 0, 1, or inconclusive. As already mentioned, this interpretation
-of a SGPV is very similar to the Neyman-Pearson interpretation of an
-equivalence test and a minimum effect tests (which are complementary).
-The difference is that where a SGPV of 1 can be interpreted as \emph{p}
-\textless{} .025, equivalence tests provide exact \emph{p}-values, and
-they continue to differentiate between for example \emph{p} = 0.048 and
-\emph{p} = 0.002. Whether this is desirable depends on the perspective
-that is used. From a Neyman-Pearson perspective on statistical
-inferences the main conclusion is based on whether or not
-\(p < \alpha\), and thus an equivalence test and SGPV can be performed
-by simply checking whether the confidence interval falls within the
-equivalence range, just as a null-hypothesis test can be performed by
-checking whether the confidence interval contains zero or not. At the
-same time, it is recommended to report exact \emph{p}-values (American
-Psychological Association, 2010), and exact \emph{p}-values might
-provide information of interest to readers about how precisely how
+weaknesses. Here, we aimed to compare the SGPV against equivalence tests
+based on the TOST procedure. First of all, even though a SGPV of 1 or 0
+has a clear interpretation (we can reject effects outside or inside the
+equivalence range), intermediate values are not as easy to interpret
+(especially for effects that have asymmetric confidence intervals). In
+one sense, they are what they are (the proportion of overlap), but it
+can be unclear what this number tells us about the data we have
+collected. This is not too problematic, since the main use of the SGPV
+(e.g., in all examples provided by Blume and colleagues) seems to be to
+examine whether the SGPV is 0, 1, or inconclusive. As already mentioned,
+this interpretation of a SGPV is very similar to the Neyman-Pearson
+interpretation of an equivalence test and a minimum effect tests (which
+are complementary). The difference is that where a SGPV of 1 can be
+interpreted as \emph{p} \textless{} .025, equivalence tests provide
+exact \emph{p}-values, and they continue to differentiate between for
+example \emph{p} = 0.024 and \emph{p} = 0.002. Whether this is desirable
+depends on the perspective that is used. From a Neyman-Pearson
+perspective on statistical inferences the main conclusion is based on
+whether or not \(p < \alpha\), and thus an equivalence test and SGPV can
+be performed by simply checking whether the confidence interval falls
+within the equivalence range, just as a null-hypothesis test can be
+performed by checking whether the confidence interval contains zero or
+not. At the same time, it is recommended to report exact \emph{p}-values
+(American Psychological Association, 2010), and exact \emph{p}-values
+might provide information of interest to readers about how precisely how
 surprising the data, or more extreme data, is under the null model. Some
@@
 \caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (dotted grey curve) across a range of observed
-sample correlations (x-axis) tested against equivalence bounds of r =
-0.4 and r = 0.8 with n = 10 and an alpha of 0.05.}
+(black line) and 1-SGPV (grey curve) across a range of observed sample
+correlations (x-axis) tested against equivalence bounds of \emph{r} =
+0.4 and \emph{r} = 0.8 with n = 10 and an alpha of 0.05.}
 \end{figure}
@@
 
-Blume et al. (2018) claim that \enquote{Adjustments for multiple
-comparisons are obviated} (p.~15). However, this is not correct. Given
-the direct relationship between TOST and SGPV highlighted in this
-manuscript (where to TOST \emph{p} = 0.025 equals SGPV = 1, as long as
-the SGPV is calculated based on confidence intervals, and assuming data
-sampled from a continuous bivariate normal distribution), not correcting
-for multiple comparisons will inflate the probability of concluding the
-absence of a meaningful effect based on the SGPV in exactly the same way
-as for equivalence tests. Whenever statistical tests are interpreted as
-support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do
-so erroneously, and if researchers want to control error rates, they
-need to correct for multiple comparisons.
+Blume et al. (2018) claim that when using the SGPV \enquote{Adjustments
+for multiple comparisons are obviated} (p.~15). However, this is not
+correct. Given the direct relationship between TOST and SGPV highlighted
+in this manuscript (where a TOST \emph{p} = 0.025 equals SGPV = 1, as
+long as the SGPV is calculated based on confidence intervals, and
+assuming data are sampled from a continuous bivariate normal
+distribution), not correcting for multiple comparisons will inflate the
+probability of concluding the absence of a meaningful effect based on
+the SGPV in exactly the same way as it will for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis
+(e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if
+researchers want to control error rates, they need to correct for
+multiple comparisons.
 

### 2019-03-10 manuscript.R1.Rmd
R1 final resubmission

@@
 author_note: |
-  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV.
+  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV and https://osf.io/8crkg/.
+The preprint can be found at https://psyarxiv.com/7k6ay/.
 This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.

### 2019-04-11 manuscript.Rmd
Correcting the misinterpretation of the p-value in correlation tests

@@
 The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
-If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test indicates that the probability of observing the observed or more extreme data, assuming the equivalence bound is the true effect size, is 50%.
-In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%.
+
+If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test is 50%.
+In correlation test, the *p* value is computed based on a transformed correlation score, computed as follows:
+
+$$
+z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
+$$
+
+Because the z distribution is symmetric, the probability of observing the observed z score or more extreme score, assuming the equivalence bound is the true effect size, is 50%.
+However, it does not mean that there is always a 50% probability of observing a correlation (r) smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
+
+As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%.
 Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
+The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
+The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
+
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, and in the same way of thinking, the probability of observing a correlation smaller or larger than the true correlation is also closer to 0.5.
+
+The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
+Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
+Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.
+a *p*-value of 0 or 1 are *not* affected by the scale changes."
 
@@
 ```
-
-This example illustrates the difference between a proportion and a probability.
-There is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
-The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
-The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
-It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a *p*-value answers.
-The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a *p* < 0.025 or *p* > 0.975 in an equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values.
-Although @blume_second-generation_2018 state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
-Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'.
-Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed.
-However definitive findings, i.e.
-a *p*-value of 0 or 1 are *not* affected by the scale changes."
 

### 2019-04-11 manuscript.tex
Correcting the misinterpretation of the p-value in correlation tests

@@
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-
-% Table formatting
-\usepackage{longtable, booktabs}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-
-\newenvironment{lltable}
-  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
-  {\end{ThreePartTable}\end{center}\end{landscape}}
-
-% The following enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand\getlongtablewidth{%
- \begingroup
-  \ifcsname LT@\roman{LT@tables}\endcsname
-  \global\longtablewidth=0pt
-  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
-  \@nameuse{LT@\roman{LT@tables}}%
-  \fi
-\endgroup}
-
-  \usepackage{graphicx}
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Equivalence Testing and the Second Generation P-Value},
+            pdfauthor={Daniël Lakens~\& Marie Delacre},
+            pdfkeywords={equivalence testing, second generation \emph{p}-values, hypothesis testing, TOST, statistical inference},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
 \fi
-\hypersetup{breaklinks=true,
-            pdfauthor={},
-            pdftitle={Equivalence Testing and the Second Generation P-Value},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\setlength{\parindent}{0pt}
-%\setlength{\parskip}{0pt plus 0pt minus 0pt}
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
+  \title{Equivalence Testing and the Second Generation \emph{P}-Value}
+    \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}
+    \date{}
 
-% Manuscript styling
-\captionsetup{font=singlespacing,justification=justified}
+\shorttitle{TOST vs. SGPV}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\\textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium}
+\keywords{equivalence testing, second generation *p*-values, hypothesis testing, TOST, statistical inference\newline\indent Word count: }
 \usepackage{csquotes}
 \usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-\usepackage{tikz} % Variable definition to generate author note
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
 
-% fix for \tightlist problem in pandoc 1.14
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
-% Essential manuscript parts
-  \title{Equivalence Testing and the Second Generation \emph{P}-Value}
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 
-  \shorttitle{TOST vs.~SGPV}
-
-  \author{Daniël Lakens\textsuperscript{1}~\& Marie Delacre\textsuperscript{2}}
-
-  \def\affdep{{"", ""}}%
-  \def\affcity{{"", ""}}%
-
-  \affiliation{
-    \vspace{0.5cm}
-          \textsuperscript{1} Eindhoven University of Technology, Eindhoven, The Netherlands\\
-          \textsuperscript{2} Service of Analysis of the Data, Université Libre de Bruxelles, Belgium  }
-
-  \authornote{
-    \newcounter{author}
-    All code associated with this article, including the reproducible
-    manuscript, is available from
-    \url{https://github.com/Lakens/TOST_vs_SGPV}. This work was supported by
-    the Netherlands Organization for Scientific Research (NWO) VIDI grant
-    452-17-013.
+\authornote{All code associated with this article, including the reproducible manuscript, is available from \url{https://github.com/Lakens/TOST_vs_SGPV}.
+This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
 
 Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
-E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}
-                          }
+E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
-  \abstract{To move beyond the limitations of null-hypothesis tests, statistical
-approaches have been developed where the observed data is compared
-against a range of values that are equivalent to the absence of a
-meaningful effect. Specifying a range of values around zero allows
-researchers to statistically reject the presence of effects large enough
-to matter, and prevents practically insignificant effects from being
-interpreted as a statistically significant difference. We compare the
-behavior of the recently proposed second generation \emph{p}-value
-(Blume, D'Agostino McGowan, Dupont, \& Greevy, 2018) with the more
-established Two One-Sided Tests (TOST) equivalence testing procedure
-(Schuirmann, 1987). We show that the two approaches yield almost
-identical results under optimal conditions. Under suboptimal conditions
-(e.g., when the confidence interval is wider than the equivalence range,
-or when confidence intervals are asymmetric) the second generation
-\emph{p}-value becomes difficult to interpret as a descriptive
-statistic. The second generation \emph{p}-value is interpretable in a
-dichotomous manner (i.e., when the SGPV equals 0 or 1 because the
-confidence intervals lies completely within or outside of the
-equivalence range), but this dichotomous interpretation does not require
-calculations. We conclude that equivalence tests yield more consistent
-\emph{p}-values, distinguish between datasets that yield the same second
-generation \emph{p}-value, and allow for easier control of Type I and
-Type II error rates.}
-  \keywords{equivalence testing, second generation \emph{p}-values, hypothesis
-testing, TOST, statistical inference \\
+\abstract{
+To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data is compared against a range of values that are equivalent to the absence of a meaningful effect.
+Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interpreted as a statistically significant difference.
+We compare the behavior of the recently proposed second generation \emph{p}-value (Blume, D'Agostino McGowan, Dupont, \& Greevy, 2018) with the more established Two One-Sided Tests (TOST) equivalence testing procedure (Schuirmann, 1987).
+We show that the two approaches yield almost identical results under optimal conditions.
+Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation \emph{p}-value becomes difficult to interpret as a descriptive statistic.
+The second generation \emph{p}-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
+We conclude that equivalence tests yield more consistent \emph{p}-values, distinguish between datasets that yield the same second generation \emph{p}-value, and allow for easier control of Type I and Type II error rates.
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
-
 \maketitle
 
-\setcounter{secnumdepth}{0}
+To test predictions researchers predominantly rely on null-hypothesis tests.\\
+This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero.
+Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for \emph{equivalence}.
+When testing for equivalence researchers aim to examine whether an observed effect is too small to be considered meaningful, and therefore is practically equivalent to zero.
+By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an \emph{equivalence range} and researchers can test if a meaningful effect is absent (Hauck \& Anderson, 1984; Kruschke, 2018; Rogers, Howard, \& Vessey, 1993; Serlin \& Lapsley, 1985; Spiegelhalter, Freedman, \& Parmar, 1994; Wellek, 2010; Westlake, 1972).
 
-To test predictions researchers predominantly rely on null-hypothesis
-tests.\\
-This statistical approach can be used to examine whether observed data
-is sufficiently surprising under the null hypothesis to reject an effect
-that equals exactly zero. Null-hypothesis tests have an important
-limitation, in that this procedure can only reject the hypothesis that
-there is no effect, while scientists should also be able to provide
-statistical support for \emph{equivalence}. When testing for equivalence
-researchers aim to examine whether an observed effect is too small to be
-considered meaningful, and therefore is practically equivalent to zero.
-By specifying a range around the null hypothesis of values that are
-deemed practically equivalent to the absence of an effect (i.e., 0 ±
-0.3) the observed data can be compared against an \emph{equivalence
-range} and researchers can test if a meaningful effect is absent (Hauck
-\& Anderson, 1984; Kruschke, 2018; Rogers, Howard, \& Vessey, 1993;
-Serlin \& Lapsley, 1985; Spiegelhalter, Freedman, \& Parmar, 1994;
-Wellek, 2010; Westlake, 1972).
+Second generation \emph{p}-values (SGPV) were recently proposed to as a descriptive statistic that represents \enquote{the proportion of data-supported hypotheses that are also null hypotheses} (Blume et al., 2018).
+The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis.
+The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis.
+If the estimation interval falls completely within the equivalence range, the SGPV is 1.
+If the confidence interval falls completely outside of the equivalence range, the SGPV is 0.
+Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although one could also choose to use credible intervals or Likelihood support intervals (SI).
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012; Quertemont, 2011; Schuirmann, 1987) appear to have close ties, because both tests compare a confidence interval against an equivalence range.
+Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
 
-Second generation \emph{p}-values (SGPV) were recently proposed to as a
-descriptive statistic that represents \enquote{the proportion of
-data-supported hypotheses that are also null hypotheses} (Blume et al.,
-2018). The researcher specifies an equivalence range around a null
-hypothesis of values that are considered practically equivalent to the
-null hypothesis. The SGPV measures the degree to which a set of
-data-supported parameter values falls within the interval null
-hypothesis. If the estimation interval falls completely within the
-equivalence range, the SGPV is 1. If the confidence interval falls
-completely outside of the equivalence range, the SGPV is 0. Otherwise
-the SGPV is a value between 0 and 1 that expresses the overlap of
-data-supported hypotheses and the equivalence range. When calculating
-the SGPV the set of data-supported parameter values can be represented
-by a confidence interval (CI), although one could also choose to use
-credible intervals or Likelihood support intervals (SI). When a
-confidence interval is used, the SGPV and equivalence tests such as the
-Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012;
-Quertemont, 2011; Schuirmann, 1987) appear to have close ties, because
-both tests compare a confidence interval against an equivalence range.
-Here, we aim to examine the similarities and differences between the
-TOST procedure and the SGPV.
+The TOST procedure also relies on the confidence interval around the effect.
+In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test (Lakens, Scheel, \& Isager, 2018).
+If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
+Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2\(\times\)\(\alpha\) confidence interval (e.g., when the alpha level is 0.05, a 90\% CI) falls completely within the equivalence bounds.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
 
-The TOST procedure also relies on the confidence interval around the
-effect. In the TOST procedure the data is tested against the lower
-equivalence bound in the first one-sided test, and against the upper
-equivalence bound in the second one-sided test (Lakens, Scheel, \&
-Isager, 2018). If both tests statistically reject an effect as extreme
-or more extreme than the equivalence bound, you can conclude the
-observed effect is practically equivalent to zero from a Neyman-Pearson
-approach to statistical inferences. Because one-sided tests are
-performed, one can also conclude equivalence by checking whether the
-1-2\(\times\)\(\alpha\) confidence interval (e.g., when the alpha level
-is 0.05, a 90\% CI) falls completely within the equivalence bounds.
-Because both equivalence tests as the SGPV are based on whether and how
-much a confidence interval overlaps with equivalence bounds, it seems
-worthwhile to compare the behavior of the newly proposed SGPV to
-equivalence tests to examine the unique contribution of the SGPV to the
-statistical toolbox.
+\#The relationship between \emph{p}-values from TOST and SGPV when confidence intervals are symmetrical
 
-\section{\texorpdfstring{The relationship between \emph{p}-values from
-TOST and SGPV when confidence intervals are
-symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}
-
-The second generation \emph{p}-value (SGPV) is calculated as: \[
+The second generation \emph{p}-value (SGPV) is calculated as:
+\[
   p _ { \delta } = \frac { \left| I \cap H _ { 0 } \right| } { | I | } \times \max \left\{ \frac { | I | } { 2 \left| H _ { 0 } \right| } , 1 \right\}
-\] where I is the interval based on the data (e.g., a 95\% confidence
-interval) and H\textsubscript{0} is the equivalence range. The first
-term of this formula implies that the second generation \emph{p}-value
-is the width of the confidence interval that overlaps with the
-equivalence range, divided by the total width of the confidence
-interval. The second term is a \enquote{small sample correction} (which
-will be discussed later) that comes into play whenever the confidence
-interval is more than twice as wide as the equivalence range. To examine
-the relation between the TOST \emph{p}-value and the SGPV we can
-calculate both statistics across a range of observed effect sizes. In
-Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST
-procedure and the SGPV. The statistics are calculated for hypothetical
-one-sample \emph{t}-tests for observed means ranging from 140 to 150 (on
-the x-axis). The equivalence range is set to 145 ± 2 (i.e., an
-equivalence range from 143 to 147), the observed standard deviation is
-assumed to be 2, and the sample size is 30. For example, for the
-left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST
-\emph{p}-value is calculated for a hypothetical study with a sample size
-of 30, an observed standard deviation of 2, and an observed mean of 140,
-where the \emph{p}-value for the equivalence test is 1, and the SGPV is
-0. Our conclusions about the relationship between TOST \emph{p}-values
-and SGPV in this article are not dependent upon any specific example, as
-readers can explore for themselves in an online Shiny app:
-\url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
+\]
+where I is the interval based on the data (e.g., a 95\% confidence interval) and H\textsubscript{0} is the equivalence range.
+The first term of this formula implies that the second generation \emph{p}-value is the width of the confidence interval that overlaps with the equivalence range, divided by the total width of the confidence interval.
+The second term is a \enquote{small sample correction} (which will be discussed later) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
+To examine the relation between the TOST \emph{p}-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
+In Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST procedure and the SGPV.
+The statistics are calculated for hypothetical one-sample \emph{t}-tests for observed means ranging from 140 to 150 (on the x-axis).
+The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 30.
+For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST \emph{p}-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the \emph{p}-value for the equivalence test is 1, and the SGPV is 0.
+Our conclusions about the relationship between TOST \emph{p}-values and SGPV in this article are not dependent upon any specific example, as readers can explore for themselves in an online Shiny app: \url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV1-1.pdf}
-\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis) tested against a mean of 145 in a one-sample
-\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
+\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2.}
 \end{figure}
 
-The SGPV treats the equivalence range as the null-hypothesis, while the
-TOST procedure treats the values outside of the equivalence range as the
-null-hypothesis. For ease of comparison we can reverse the SGPV (by
-calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values
-more easily comparable. We see that the \emph{p}-value from the TOST
-procedure and the SGPV follow each other closely.
+The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
+For ease of comparison we can reverse the SGPV (by calculating 1-SGPV in Figure \ref{fig:TOSTSGPV2}) to make the values more easily comparable.
+We see that the \emph{p}-value from the TOST procedure and the SGPV follow each other closely.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV2-1.pdf}
-\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
-line) and 1-SGPV (dotted grey line) across a range of observed sample
-means (x-axis) tested against a mean of 145 in a one-sample
-\emph{t}-test with a sample size of 30 and a standard deviation of 2.}
+\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2.}
 \end{figure}
 
-When the observed sample mean is 145, the sample size is 30, and the
-standard deviation is 2, and we are testing against equivalence bounds
-of 143 and 147 using the TOST procedure for a one-sample \emph{t}-test,
-the equivalence test is significant, \emph{t}(29) = 5.48, \emph{p}
-\textless{} .001. Because the 95\% CI falls completely within the
-equivalence bounds, the SGPV is 1 (see Figure \ref{fig:TOSTSGPV1}). On
-the other hand, when the observed mean is 140, the equivalence test is
-not significant (the observed mean is far outside the equivalence range
-of 143 to 147), \emph{t}(29) = -8.22, \emph{p} = 1 (or more accurately,
-\emph{p} \textgreater{} .999 as \emph{p}-values are bounded between 0
-and 1). Because the 95\% CI falls completely outside the equivalence
-bounds, the SGPV is 0 (see Figure \ref{fig:TOSTSGPV1}).
+When the observed sample mean is 145, the sample size is 30, and the standard deviation is 2, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample \emph{t}-test, the equivalence test is significant, \emph{t}(29) = 5.48, \emph{p} \textless{} .001.
+Because the 95\% CI falls completely within the equivalence bounds, the SGPV is 1 (see Figure \ref{fig:TOSTSGPV1}).
+On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), \emph{t}(29) = -8.22, \emph{p} = 1 (or more accurately, \emph{p} \textgreater{} .999 as \emph{p}-values are bounded between 0 and 1).
+Because the 95\% CI falls completely outside the equivalence bounds, the SGPV is 0 (see Figure \ref{fig:TOSTSGPV1}).
 
-\subsection{SGPV as a uniform measure of
-overlap}\label{sgpv-as-a-uniform-measure-of-overlap}
+\#\#SGPV as a uniform measure of overlap
 
-It is clear the SGPV and the \emph{p}-value from TOST are closely
-related. When confidence intervals are symmetric we can think of the
-SGPV as a straight line that is directly related to the \emph{p}-value
-from an equivalence test for three values. When the TOST \emph{p}-value
-is 0.5, the SGPV is also 0.5 (note that the reverse is not true). The
-SGPV is 50\% when the observed mean falls exactly on the lower or upper
-equivalence bound, because 50\% of the symmetrical confidence interval
-overlaps with the equivalence range. When the observed mean equals the
-equivalence bound, the difference between the mean in the data and the
-equivalence bound is 0, the \emph{t}-value for the equivalence test is
-also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure
-\ref{fig:TOSTSGPV3}).
+It is clear the SGPV and the \emph{p}-value from TOST are closely related.
+When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values.
+When the TOST \emph{p}-value is 0.5, the SGPV is also 0.5 (note that the reverse is not true).
+The SGPV is 50\% when the observed mean falls exactly on the lower or upper equivalence bound, because 50\% of the symmetrical confidence interval overlaps with the equivalence range.
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the \emph{t}-value for the equivalence test is also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure \ref{fig:TOSTSGPV3}).
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV3-1.pdf}
-\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for
-three example datasets that illustrate the relationship between
-\emph{p}-values from TOST and SGPV.}
+\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for three example datasets that illustrate the relationship between \emph{p}-values from TOST and SGPV.}
 \end{figure}
 
-Two other points always have to overlap. When the 95\% CI falls
-completely inside the equivalence region, and one endpoint of the
-confidence interval is exactly equal to one of the equivalence bounds
-(see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value
-(which relies on a one-sided test) is always 0.025. The third point
-where the SGPV and the \emph{p}-value from the TOST procedure should
-overlap is where the 95\% CI falls completely outside of the equivalence
-range, but one endpoint of the confidence interval is equal to the
-equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when
-the \emph{p}-value will always be 0.975. Note that this situation is in
-essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014). The goal
-of a minimum-effect is not just to reject a difference of zero, but to
-reject the smallest effect size of interest (i.e., the equivalence
-bounds). The SGPV summarizes the information from an equivalence test
-and a minimum-effect test. These can be two relevant questions to ask,
-although it often makes sense to combine an equivalence test and a
-null-hypothesis test instead (Lakens et al., 2018).
+Two other points always have to overlap.
+When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value (which relies on a one-sided test) is always 0.025.
+The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the \emph{p}-value will always be 0.975.
+Note that this situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014).
+The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
+The SGPV summarizes the information from an equivalence test and a minimum-effect test.
+These can be two relevant questions to ask, although it often makes sense to combine an equivalence test and a null-hypothesis test instead (Lakens et al., 2018).
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV4-1.pdf}
-\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for
-samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
+\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
 \end{figure}
 
-For example, the SGPV from A to D is 0.76, 0.81, 0.86, and 0.91. The
-difference in the percentage of overlap between A and B (-0.05) is
-identical to the difference in the percentage of overlap between C and D
-as the mean gets 0.1 closer to the test value (-0.05). As the observed
-mean in a one-sample \emph{t}-test lies closer to the test value (in
-Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer
-to the test value by 0.1) the difference in the overlap changes
-uniformly. As we move the observed mean closer to the test value in
-steps of 0.1 across A to D the \emph{p}-value calculated for normally
-distributed data is not uniformly distributed. The probability of
-observing data more extreme than the upper bound of 2 is (from A to D)
-0.16, 0.12, 0.08, and 0.06. As we can see, the difference between A and
-B (0.04) is not the same as the difference between C and D (0.03).
-Indeed, the difference in \emph{p}-values is the largest as you start at
-\emph{p} = 0.5 (when the observed mean falls on the test value), which
-is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at
-\emph{p} = 0.5. Note that where the SGPV reaches 1 or 0, \emph{p}-values
-closely approximate 0 and 1, but never reach these values.
+For example, the SGPV from A to D is 0.76, 0.81, 0.86, and 0.91.
+The difference in the percentage of overlap between A and B (-0.05) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (-0.05).
+As the observed mean in a one-sample \emph{t}-test lies closer to the test value (in Figure \ref{fig:TOSTSGPV4}), from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
+As we move the observed mean closer to the test value in steps of 0.1 across A to D the \emph{p}-value calculated for normally distributed data is not uniformly distributed.
+The probability of observing data more extreme than the upper bound of 2 is (from A to D) 0.16, 0.12, 0.08, and 0.06.
+As we can see, the difference between A and B (0.04) is not the same as the difference between C and D (0.03).
+Indeed, the difference in \emph{p}-values is the largest as you start at \emph{p} = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at \emph{p} = 0.5.
+Note that where the SGPV reaches 1 or 0, \emph{p}-values closely approximate 0 and 1, but never reach these values.
 
-\subsection{When are the SGPV and Equivalence Test
-Unrelated?}\label{when-are-the-sgpv-and-equivalence-test-unrelated}
+\#\#When are the SGPV and Equivalence Test Unrelated?
 
-There are three situations where \emph{p}-values from TOST and SGPV are
-unrelated. The first two situations were discussed before and can be
-seen in Figure \ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1
-\emph{p}-values from the equivalence test fall between 0.975 and 1 or
-between 0 and 0.025. Because \emph{p}-values approach 0 or 1, but are
-never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics
-are completely unrelated within these ranges. The easiest way to see
-this is by plotting the SGPV against the \emph{p}-value from the TOST
-procedure. The situations where the SPGV and \emph{p}-values from the
-TOST procedure are unrelated are indicated by the parts of the curve
-where there are vertical straight lines at second generation
-\emph{p}-values of 0 and 1.
+There are three situations where \emph{p}-values from TOST and SGPV are unrelated.
+The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
+When the SGPV is either 0 or 1 \emph{p}-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
+Because \emph{p}-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges.
+The easiest way to see this is by plotting the SGPV against the \emph{p}-value from the TOST procedure.
+The situations where the SPGV and \emph{p}-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation \emph{p}-values of 0 and 1.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV5-1.pdf}
-\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV1}.}
+\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV1}.}
 \end{figure}
 
-A third situation in which the SGPV deviates from the TOST
-\emph{p}-value is whenever the CI is wider than the equivalence range,
-and the CI overlaps with the upper \emph{and} lower equivalence bound.
-When the confidence interval is more than twice as wide as the
-equivalence range the SGPV is set to 0.5. Blume et al. (2018) call this
-the \enquote{small sample correction factor}. However, it is not a
-correction in the typical sense of the word, since the SGPV is not
-adjusted to any \enquote{correct} value. When the normal calculation
-would be \enquote{misleading} (i.e., the SGPV would be small, which
-normally would suggest support for the alternative hypothesis, but at
-the same time all values in the equivalence range are supported), the
-SGPV is set to 0.5 which according to Blume and colleagues signals that
-the SGPV is \enquote{uninformative}. Note that the CI can be twice as
-wide as the equivalence range whenever the sample size is small (and the
-confidence interval width is large) \emph{or} when then equivalence
-range is narrow. It is therefore not so much a \enquote{small sample
-correction} as it is an exception to the typical calculation of the SGPV
-whenever the ratio of the confidence interval width to the equivalence
-range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+A third situation in which the SGPV deviates from the TOST \emph{p}-value is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper \emph{and} lower equivalence bound.
+When the confidence interval is more than twice as wide as the equivalence range the SGPV is set to 0.5.
+Blume et al.
+(2018) call this the \enquote{small sample correction factor}.
+However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any \enquote{correct} value.
+When the normal calculation would be \enquote{misleading} (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signals that the SGPV is \enquote{uninformative}.
+Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) \emph{or} when then equivalence range is narrow.
+It is therefore not so much a \enquote{small sample correction} as it is an exception to the typical calculation of the SGPV whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV6-1.pdf}
-\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis). Because the sample size is small (n = 10) and the CI is
-more than twice as wide as the equivalence range (set to -0.4 to 0.4),
-the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
-observed means.}
+\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.}
 \end{figure}
 
-We can examine this situation by calculating the SGPV and performing the
-TOST for a situation where sample sizes are small and the equivalence
-range is narrow, such that the CI is more than twice as large as the
-equivalence range (see Figure \ref{fig:TOSTSGPV6}). When the two
-statistics are plotted against each other we can see where they are
-unrelated (indicated by straight lines in the curve, see Figure
-\ref{fig:TOSTSGPV7}). We see the SGPV is 0.5 for a range of observed
-means where the \emph{p}-value from the equivalence test still varies.
-It should be noted that in these calculations the \emph{p}-values for
-the TOST procedure are \emph{never} smaller than 0.05 (i.e., they do not
-get below 0.05 on the y-axis). In other words, we cannot conclude
-equivalence based on any of the observed means. This happens because the
-TOST \emph{p}-value is smaller than 0.05 only when the 90\% CI falls
-completely between the upper and lower equivalence bounds. However, we
-are examining a scenario where the 90\% CI is so wide that it never
-falls completely within the two equivalence bounds, and thus the
-equivalence test is never significant. As Lakens (2017) notes:
-\enquote{in small samples (where CIs are wide), a study might have no
-statistical power (i.e., the CI will always be so wide that it is
-necessarily wider than the equivalence bounds).} None of the
-\emph{p}-values based on the TOST procedure are below 0.05, and thus, in
-the long run we have 0\% power.
+We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
+When the two statistics are plotted against each other we can see where they are unrelated (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+We see the SGPV is 0.5 for a range of observed means where the \emph{p}-value from the equivalence test still varies.
+It should be noted that in these calculations the \emph{p}-values for the TOST procedure are \emph{never} smaller than 0.05 (i.e., they do not get below 0.05 on the y-axis).
+In other words, we cannot conclude equivalence based on any of the observed means.
+This happens because the TOST \emph{p}-value is smaller than 0.05 only when the 90\% CI falls completely between the upper and lower equivalence bounds.
+However, we are examining a scenario where the 90\% CI is so wide that it never falls completely within the two equivalence bounds, and thus the equivalence test is never significant.
+As Lakens (2017) notes: \enquote{in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).} None of the \emph{p}-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0\% power.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV7-1.pdf}
-\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV6}.}
+\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV6}.}
 \end{figure}
 
-The \emph{p}-value from the TOST procedure and the SGPV are also
-unrelated when the CI is wider than the equivalence range (so the
-precision is low) and overlaps with the upper and lower equivalence
-bound, but the CI is \emph{not} twice as wide as the equivalence range.
-In the example below, we see that the CI is only 1.79 times as wide as
-the equivalence bounds, but the CI overlaps with the lower and upper
-equivalence bounds (Figure \ref{fig:TOSTSGPV8}). This means the SGPV is
-not set to 0.5, but it is constant across a range of observed means.
+The \emph{p}-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is \emph{not} twice as wide as the equivalence range.
+In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
+This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV8-1.pdf}
-\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the
-lower and upper equivalence bound (indicated by the vertical dotted
-lines).}
+\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).}
 \end{figure}
 
-If the observed mean would be somewhat closer to 0, or further away from
-0, the SGPV remains constant (the CI width does not change, and it
-completely overlaps with the equivalence range) while the \emph{p}-value
-for the TOST procedure does vary. We can see this in Figure
-\ref{fig:TOSTSGPV9} below. The SGPV is not set to 0.5, but is slightly
-higher than 0.5 across a range of means. How high the SGPV will be for a
-CI that is not twice as wide as the equivalence range, but overlaps with
-the lower and upper equivalence bounds, depends on the width of the CI
-and the equivalence range.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV remains constant (the CI width does not change, and it completely overlaps with the equivalence range) while the \emph{p}-value for the TOST procedure does vary.
+We can see this in Figure \ref{fig:TOSTSGPV9} below.
+The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
+How high the SGPV will be for a CI that is not twice as wide as the equivalence range, but overlaps with the lower and upper equivalence bounds, depends on the width of the CI and the equivalence range.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV9-1.pdf}
-\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (dotted grey line) across a range of observed sample
-means (x-axis). The sample size is small (n = 10), but because the sd is
-half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is
-less than twice as wide as the equivalence range (set to -0.4 to 0.4).
-The SGPV is not set to 0.5 (horizontal light grey line) but reaches a
-maximum slightly above 0.5 across a range of observed means.}
+\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis).
+The sample size is small (n = 10), but because the sd is half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
+The SGPV is not set to 0.5 (horizontal light grey line) but reaches a maximum slightly above 0.5 across a range of observed means.}
 \end{figure}
 
-If we once more plot the two statistics against each other to see where
-they are unrelated (indicated by straight lines in the curve), we see
-the SGPV is 0.56 for a range of observed means where the \emph{p}-value
-from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
+If we once more plot the two statistics against each other to see where they are unrelated (indicated by straight lines in the curve), we see the SGPV is 0.56 for a range of observed means where the \emph{p}-value from the equivalence test still varies (Figure \ref{fig:TOSTSGPV10}).
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV10-1.pdf}
-\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV9}.}
+\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV9}.}
 \end{figure}
 
-To conclude this section, there are three situations where the
-\emph{p}-value from the TOST procedure is unrelated to the SGPV. In all
-these situations the \emph{p}-value for the equivalence test
-differentiates tests with different means, but the SGPV does not.
-Therefore, as a purely continuous descriptive statistic, the SGPV is
-more limited than the \emph{p}-value from the TOST procedure.
+To conclude this section, there are three situations where the \emph{p}-value from the TOST procedure is unrelated to the SGPV.
+In all these situations the \emph{p}-value for the equivalence test differentiates tests with different means, but the SGPV does not.
+Therefore, as a purely continuous descriptive statistic, the SGPV is more limited than the \emph{p}-value from the TOST procedure.
 
-\subsection{The relation between equivalence tests and SGPV when
-confidence intervals are not
-symmetrical}\label{the-relation-between-equivalence-tests-and-sgpv-when-confidence-intervals-are-not-symmetrical}
+\#\#The relation between equivalence tests and SGPV when confidence intervals are not symmetrical
 
-So far we have only looked at the relation between equivalence tests and
-the SGPV when confidence intervals are symmetric (e.g., for confidence
-intervals around mean differences). For correlations, which are bound
-between -1 and 1, confidence intervals are only symmetric for a
-correlation of exactly 0. The confidence interval becomes increasingly
-asymmetric as the observed correlation nears -1 or 1. For example, with
-ten observations, an observed correlation of 0 has a symmetric 95\%
-confidence interval ranging from -0.630 to 0.630, while and observed
-correlation of 0.7 has an asymmetric 95\% confidence interval ranging
-from 0.126 to 0.993.
+So far we have only looked at the relation between equivalence tests and the SGPV when confidence intervals are symmetric (e.g., for confidence intervals around mean differences).
+For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0.
+The confidence interval becomes increasingly asymmetric as the observed correlation nears -1 or 1.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95\% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95\% confidence interval ranging from 0.126 to 0.993.
 
-The effect of asymmetric confidence intervals is most noticeable at
-smaller sample sizes. In Figure \ref{fig:TOSTSGPV11} we plot the
-\emph{p}-values from equivalence tests and the SGPV (again plotted as
-1-SGPV for ease of comparison) for correlations. The sample size is 30
-pairs of observations, and the lower and upper equivalence bounds are
-set to -0.45 and 0.45, with an alpha of 0.05. As the observed
-correlation in the sample moves from -1 to 0 the \emph{p}-value from the
-equivalence test becomes smaller, as does 1-SGPV. The pattern is quite
-similar to that in Figure \ref{fig:TOSTSGPV2}. The \emph{p}-value for
-the TOST procedure and 1-SGPV are still identical when \emph{p}-values
-are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted
-lines). There are two important differences, however. First of all, the
-SGPV is no longer a straight line, but a curve, due to the asymmetry in
-the 95\% CI. Second, and most importantly, the \emph{p}-value for the
-equivalence test and the SGPV do no longer overlap at \emph{p} = 0.5.
+The effect of asymmetric confidence intervals is most noticeable at smaller sample sizes.
+In Figure \ref{fig:TOSTSGPV11} we plot the \emph{p}-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
+As the observed correlation in the sample moves from -1 to 0 the \emph{p}-value from the equivalence test becomes smaller, as does 1-SGPV.
+The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
+The \emph{p}-value for the TOST procedure and 1-SGPV are still identical when \emph{p}-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines).
+There are two important differences, however.
+First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95\% CI.
+Second, and most importantly, the \emph{p}-value for the equivalence test and the SGPV do no longer overlap at \emph{p} = 0.5.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV11-1.pdf}
-\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (dotted grey curve) across a range of observed
-sample correlations (x-axis) tested against equivalence bounds of r =
--0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
+\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
 \end{figure}
 
-The reason that the equivalence test and SGPV no longer overlap is also
-because of asymmetric confidence intervals. If the observed correlation
-falls exactly on the equivalence bound the \emph{p}-value for the
-equivalence test indicates that the probability of observing the
-observed or more extreme data, assuming the equivalence bound is the
-true effect size, is 50\%. In other words, if the true effect size is
-the same as the equivalence bound, it is equally likely to find an
-effect more extreme than the equivalence bound, as it is to observe an
-effect that is less extreme than the equivalence bound. However, as can
-be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation
-\emph{p}-values associated with the observed correlations at r = -0.45
-and r = 0.45 are larger than 50\%. Because the confidence intervals are
-asymmetric around the observed effect size of 0.45 (ranging from 0.11 to
-0.70) according to Blume et al. (2018) 58.11\% of the data-supported
-hypotheses are null hypotheses, and therefore 58.10\% of the
-data-supported hypotheses are compatible with the null premise.
+The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
+
+If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 50\%.
+In correlation test, the \emph{p} value is computed based on a transformed correlation score, computd as follows:
+
+\[
+z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
+\]
+
+Because the z distribution is symmetric, the probability of observing the observed z score or more extreme score, assuming the equivalence bound is the true effect size, is 50\%.
+However, it does not mean that there is always a 50\% probability of observing a correlation (r) smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
+
+As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al.
+(2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise.
+The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
+The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.
+
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a \emph{p}-value answers.
+The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at these values.
+Although Blume et al.
+(2018) state that \enquote{the degree of overlap conveys how compatible the data are with the null premise} this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis}.
+Indeed, Blume and colleagues write in the supplemental material that \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV12-1.pdf}
-\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
-effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the
-confidence interval for r = 0 is symmetric.}
+\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed effect sizes of r = -0.45, r = 0, and r = 0.45 for n = 30. Only the confidence interval for r = 0 is symmetric.}
 \end{figure}
 
-This example illustrates the difference between a proportion and a
-probability. There is always a 50\% probability of observing a
-correlation smaller or larger than the true correlation, but the SGPV
-for this situation depends on how far away the observed correlation is
-from 0. The further away from 0, the larger the SGPV when the observed
-mean falls on the equivalence bound. The SGPV is the proportion of
-values in a 95\% confidence interval that overlap with the equivalence
-range, but not the probability that these values will be observed. In
-the most extreme case (i.e., a sample size of 4, and equivalence bounds
-set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
-of the confidence interval overlaps with the equivalence range, even
-though in the long run only 50\% of the correlations observed in the
-future will fall in this range. It should be noted that in larger sample
-sizes the SGPV is closer to 0.5 whenever the observed correlation falls
-on the equivalence bound, but this extreme example nevertheless clearly
-illustrates the difference between question the SGPV answers, and the
-question a \emph{p}-value answers. The conclusion of this section on
-asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
-interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
-0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
-TOST procedure are always directly related at these values. Although
-Blume et al. (2018) state that \enquote{the degree of overlap conveys
-how compatible the data are with the null premise} this definition of
-what the SGPV provides does not hold for asymmetric confidence
-intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV
-between 0 and 1 is not interpretable as \enquote{compatibility with the
-null hypothesis}. Indeed, Blume and colleagues write in the supplemental
-material that \enquote{The magnitude of an inconclusive
-second-generation \emph{p}-value can vary slightly when the effect size
-scale is transformed. However definitive findings, i.e.~a \emph{p}-value
-of 0 or 1 are \emph{not} affected by the scale changes.}
+\#\#What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
 
-\subsection{What are the Relative Strengths and Weaknesses of
-Equivalence Testing and the
-SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}
+When introducing a new statistical method, it is important to compare it to existing approaches and specify its relative strengths and weaknesses.
+First of all, the SGPV is a descriptive statistic (unlike the \emph{p}-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.
+Even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+In one sense, they are what they are (the proportion of overlap), but it can be unclear what this number tells us about the data we have collected.
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) seems to be to examine whether the SGPV is 0, 1, or inconclusive.
+This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (Lakens et al., 2018).
+The difference is that where a SGPV of 1 can be interpreted as \emph{p} \textless{} .025, equivalence tests provide exact \emph{p}-values, and they continue to differentiate between for example \emph{p} = 0.048 and \emph{p} = 0.002.
+Whether this is desirable depends on the perspective that is used.
+From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not \(p < \alpha\), and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
+At the same time, it is recommended to report exact \emph{p}-values (American Psychological Association, 2010), and exact \emph{p}-values might provide information of interest to readers about how precisely how surprising the data is under the null model.
+Equivalence tests combined with null-hypothesis significance tests also allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful).
+Thus, the SGPV is used to classify results into one of three possible categories (with the data falling inside or outside the equivalence range, or being inconclusive), while equivalence tests combined with null-hypothesis tests classify results into four possible categories.
 
-When introducing a new statistical method, it is important to compare it
-to existing approaches and specify its relative strengths and
-weaknesses. First of all, the SGPV is a descriptive statistic (unlike
-the \emph{p}-value that is calculated for an equivalence test, which is
-an inferential statistic) that provides the proportion of overlap of the
-confidence interval and the equivalence range. Even though a SGPV of 1
-or 0 has a clear interpretation (we can reject effects outside or inside
-the equivalence range), intermediate values are not as easy to interpret
-(especially for effects that have asymmetric confidence intervals). In
-one sense, they are what they are (the proportion of overlap), but it
-can be unclear what this number tells us about the data we have
-collected. This is not too problematic, since the main use of the SGPV
-(e.g., in all examples provided by Blume and colleagues) seems to be to
-examine whether the SGPV is 0, 1, or inconclusive. This interpretation
-of a SGPV as allowing researchers to reject the null, reject the
-presence of a meaningful effect, or remaining inconclusive is very
-similar to the Neyman-Pearson interpretation of combining a
-null-hypothesis test and an equivalence test (Lakens et al., 2018). The
-difference is that where a SGPV of 1 can be interpreted as \emph{p}
-\textless{} .025, equivalence tests provide exact \emph{p}-values, and
-they continue to differentiate between for example \emph{p} = 0.048 and
-\emph{p} = 0.002. Whether this is desirable depends on the perspective
-that is used. From a Neyman-Pearson perspective on statistical
-inferences the main conclusion is based on whether or not
-\(p < \alpha\), and thus an equivalence test and SGPV can be performed
-by simply checking whether the confidence interval falls within the
-equivalence range, just as a null-hypothesis test can be performed by
-checking whether the confidence interval contains zero or not. At the
-same time, it is recommended to report exact \emph{p}-values (American
-Psychological Association, 2010), and exact \emph{p}-values might
-provide information of interest to readers about how precisely how
-surprising the data is under the null model. Equivalence tests combined
-with null-hypothesis significance tests also allow researchers to
-conclude an effect is significant \emph{and} equivalent (i.e.,
-statistically different from zero, but also too small to be considered
-meaningful). Thus, the SGPV is used to classify results into one of
-three possible categories (with the data falling inside or outside the
-equivalence range, or being inconclusive), while equivalence tests
-combined with null-hypothesis tests classify results into four possible
-categories.
-
-An important issue when calculating the SGPV is its reliance on the
-\enquote{small sample correction}, where the SGPV is set to 0.5 whenever
-the ratio of the confidence interval width to the equivalence range
-exceeds 2:1 and the CI overlaps with the upper and lower bounds. This
-exception to the normal calculation of the SGPV is introduced to prevent
-misleading values. Without this correction it is possible that a
-confidence interval is extremely wide, and an equivalence range is
-extremely narrow, which without the correction would lead to a very low
-value for the SGPV. Blume et al. (2018) suggest that under such a
-scenario \enquote{the data favor alternative hypotheses}, even when a
-better interpretation would be that there is not enough data to
-accurately estimate the true effect compared to the width of the
-equivalence range. Although it is necessary to set the SGPV to 0.5
-whenever the ratio of the confidence interval width to the equivalence
-range exceeds 2:1, it leads to a range of situations where the SGPV is
-set to 0.5, while the \emph{p}-value from the TOST procedure continues
-to differentiate (see for example Figure \ref{fig:TOSTSGPV6}). An
-important benefit of equivalence tests is that is does not need such a
-correction to prevent misleading results.
+An important issue when calculating the SGPV is its reliance on the \enquote{small sample correction}, where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
+Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV.
+Blume et al.
+(2018) suggest that under such a scenario \enquote{the data favor alternative hypotheses}, even when a better interpretation would be that there is not enough data to accurately estimate the true effect compared to the width of the equivalence range.
+Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the \emph{p}-value from the TOST procedure continues to differentiate (see for example Figure \ref{fig:TOSTSGPV6}).
+An important benefit of equivalence tests is that is does not need such a correction to prevent misleading results.
 
@@
 \includegraphics{manuscript_files/figure-latex/TOSTSGPV13-1.pdf}
-\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (dotted grey curve) across a range of observed
-sample correlations (x-axis) tested against equivalence bounds of r =
-0.4 and r = 0.8 with n = 10 and an alpha of 0.05.}
+\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (dotted grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = 0.4 and r = 0.8 with n = 10 and an alpha of 0.05.}
 \end{figure}
 
-As a more extreme example of the peculiar behavior of the \enquote{small
-sample correction} as currently implemented in the calculation of the
-SGPV see Figure \ref{fig:TOSTSGPV13} below. In this figure observed
-correlations (from a sample size of 10) from -1 to 1 are tested against
-an equivalence range from r = 0.4 to r = 0.8. We can see the SGPV has a
-peculiar shape because it is set to 0.5 for certain observed
-correlations, even though there is no risk of a \enquote{misleading}
-SGPV in this range. This example suggests that the current
-implementation of the \enquote{small sample correction} could be
-improved. If, on the other hand, the SGPV is mainly meant to be
-interpreted when it is 0 or 1, it might be preferable to simply never
-apply the \enquote{small sample correction}.
+As a more extreme example of the peculiar behavior of the \enquote{small sample correction} as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below.
+In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a \enquote{misleading} SGPV in this range.
+This example suggests that the current implementation of the \enquote{small sample correction} could be improved.
+If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the \enquote{small sample correction}.
 
-Blume et al. (2018) argue that the SGPV has improved error control, in
-that the conclusion that the 95\% confidence interval lies completely
-outside the equivalence range around zero will necessarily occur less
-frequently than a Type I error in a null-hypothesis test (where the 95\%
-confidence interval only needs to not overlap with zero). However, the
-SGPV has a \emph{lower} error rate than a null-hypothesis test, not a
-\emph{more accurate} error rate. In a Neyman-Pearson perspective (which
-forms the basis of equivalence tests) the goal is not to end up with an
-error rate that is as low as possible (to achieve that, one simply
-adjusts the alpha level), but with a decision procedure that, when
-applied, yields a desired error rate with high accuracy. We show here
-that the SGPV and equivalence tests are directly related, and so are
-their error rates. The TOST procedure uses a 90\% confidence interval
-because it is based on two \emph{one-sided} tests, and thus the
-confidence interval is 1-2\(\times\)\(\alpha\), and because both tests
-need to be significant to conclude equivalence, no adjustment for
-multiple comparisons is needed. The TOST procedure always has higher
-power to declare equivalence than the SGPV, which relies on a 95\%
-confidence interval (but note that there is no reason to always set the
-alpha level to 0.05).
+Blume et al.
+(2018) argue that the SGPV has improved error control, in that the conclusion that the 95\% confidence interval lies completely outside the equivalence range around zero will necessarily occur less frequently than a Type I error in a null-hypothesis test (where the 95\% confidence interval only needs to not overlap with zero).
+However, the SGPV has a \emph{lower} error rate than a null-hypothesis test, not a \emph{more accurate} error rate.
+In a Neyman-Pearson perspective (which forms the basis of equivalence tests) the goal is not to end up with an error rate that is as low as possible (to achieve that, one simply adjusts the alpha level), but with a decision procedure that, when applied, yields a desired error rate with high accuracy.
+We show here that the SGPV and equivalence tests are directly related, and so are their error rates.
+The TOST procedure uses a 90\% confidence interval because it is based on two \emph{one-sided} tests, and thus the confidence interval is 1-2\(\times\)\(\alpha\), and because both tests need to be significant to conclude equivalence, no adjustment for multiple comparisons is needed.
+The TOST procedure always has higher power to declare equivalence than the SGPV, which relies on a 95\% confidence interval (but note that there is no reason to always set the alpha level to 0.05).
 
-Blume et al. (2018) claim that \enquote{Adjustments for multiple
-comparisons are obviated} (p.~15) and that \enquote{second-generation
-\emph{p}-values provide a proper scientific adjustment for multiple
-comparisons}. However, this is not correct. With a sufficient number of
-looks error rates can rise above the nominal alpha level (both when
-compared to equivalence and minimal effect tests, but even when compared
-to a null-hypothesis test). When directly comparing equivalence tests
-and the SGPV, multiple comparisons inflate the probability that one
-erronously concludes there is \emph{no} effect, where there \emph{is} a
-true effect size that equals the equivalence bound, just as quickly for
-the SGPV as for equivalence tests, because they are directly related. To
-conclude, the idea that the SGPV improves error rates does not hold up
-under closer scrutiny, and the recommendation to ignore adjustments for
-multiple comparisons has the potential to increase false positives in
-the literature. Equivalence tests provide an easier and more formal way
-to control both Type I error rates (by setting the alpha level) and the
-Type II error rate (by performing an a-priori power analysis).
+Blume et al.
+(2018) claim that \enquote{Adjustments for multiple comparisons are obviated} (p.~15) and that \enquote{second-generation \emph{p}-values provide a proper scientific adjustment for multiple comparisons}.
+However, this is not correct.
+With a sufficient number of looks error rates can rise above the nominal alpha level (both when compared to equivalence and minimal effect tests, but even when compared to a null-hypothesis test).
+When directly comparing equivalence tests and the SGPV, multiple comparisons inflate the probability that one erronously concludes there is \emph{no} effect, where there \emph{is} a true effect size that equals the equivalence bound, just as quickly for the SGPV as for equivalence tests, because they are directly related.
+To conclude, the idea that the SGPV improves error rates does not hold up under closer scrutiny, and the recommendation to ignore adjustments for multiple comparisons has the potential to increase false positives in the literature.
+Equivalence tests provide an easier and more formal way to control both Type I error rates (by setting the alpha level) and the Type II error rate (by performing an a-priori power analysis).
 
-\section{Conclusion}\label{conclusion}
+\#Conclusion
 
-We believe that our explanation of the similarities between the TOST
-procedure and the SGPV provides context to interpret the contribution of
-second generation \emph{p}-values to the statistical toolbox. The
-novelty of the SGPV lies in its use as a descriptive statistic, but this
-use can be limited when confidence intervals are asymmetrical or wider
-than the equivalence range. There are strong similarities with
-\emph{p}-values from the TOST procedure, and in all situations where the
-statistics yield different results, the behavior of the \emph{p}-value
-from the TOST procedure is more consistent and easier to interpret. We
-hope this overview of the relationship between the SGPV and equivalence
-tests will help researchers to make an informed decision about which
-statistical approach provides the best answer to their question. Our
-comparisons show that when proposing alternatives to null-hypothesis
-tests, it is important to compare new proposals to already existing
-procedures. We believe equivalence tests achieve the goals of the second
-generation \emph{p}-value while allowing users to more easily control
-error rates, and while yielding more consistent statistical outcomes.
+We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation \emph{p}-values to the statistical toolbox.
+The novelty of the SGPV lies in its use as a descriptive statistic, but this use can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
+There are strong similarities with \emph{p}-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the \emph{p}-value from the TOST procedure is more consistent and easier to interpret.
+We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
+Our comparisons show that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
+We believe equivalence tests achieve the goals of the second generation \emph{p}-value while allowing users to more easily control error rates, and while yielding more consistent statistical outcomes.
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-american_psychological_association_publication_2010}{}
-American Psychological Association (Ed.). (2010). \emph{Publication
-manual of the American Psychological Association} (6th ed.). Washington,
-DC: American Psychological Association.
+\leavevmode\hypertarget{ref-american_psychological_association_publication_2010}{}%
+American Psychological Association (Ed.). (2010). \emph{Publication manual of the American Psychological Association} (6th ed.). Washington, DC: American Psychological Association.
 
-\hypertarget{ref-blume_second-generation_2018}{}
-Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
-(2018). Second-generation p-values: Improved rigor, reproducibility, \&
-transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
-e0188299.
+\leavevmode\hypertarget{ref-blume_second-generation_2018}{}%
+Blume, J.
+D., D'Agostino McGowan, L., Dupont, W.
+D., \& Greevy, R.
+A.
+(2018).
+Second-generation p-values: Improved rigor, reproducibility, \& transparency in statistical analyses.
+\emph{PLOS ONE}, \emph{13}(3), e0188299.
 doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}
 
-\hypertarget{ref-hauck_new_1984}{}
-Hauck, D. W. W., \& Anderson, S. (1984). A new statistical procedure for
-testing equivalence in two-group comparative bioavailability trials.
-\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1),
-83--91.
+\leavevmode\hypertarget{ref-hauck_new_1984}{}%
+Hauck, D.
+W.
+W., \& Anderson, S.
+(1984).
+A new statistical procedure for testing equivalence in two-group comparative bioavailability trials.
+\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1), 83--91.
 doi:\href{https://doi.org/10.1007/BF01063612}{10.1007/BF01063612}
 
-\hypertarget{ref-kruschke_rejecting_2018}{}
-Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in
-Bayesian Estimation. \emph{Advances in Methods and Practices in
-Psychological Science}, 2515245918771304.
+\leavevmode\hypertarget{ref-kruschke_rejecting_2018}{}%
+Kruschke, J.
+K.
+(2018).
+Rejecting or Accepting Parameter Values in Bayesian Estimation.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245918771304.
 doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}
 
-\hypertarget{ref-lakens_equivalence_2017}{}
-Lakens, D. (2017). Equivalence Tests: A Practical Primer for t Tests,
-Correlations, and Meta-Analyses. \emph{Social Psychological and
-Personality Science}, \emph{8}(4), 355--362.
+\leavevmode\hypertarget{ref-lakens_equivalence_2017}{}%
+Lakens, D.
+(2017).
+Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses.
+\emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362.
 doi:\href{https://doi.org/10.1177/1948550617697177}{10.1177/1948550617697177}
 
-\hypertarget{ref-lakens_equivalence_2018}{}
-Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing
-for Psychological Research: A Tutorial. \emph{Advances in Methods and
-Practices in Psychological Science}, 2515245918770963.
+\leavevmode\hypertarget{ref-lakens_equivalence_2018}{}%
+Lakens, D., Scheel, A.
+M., \& Isager, P.
+M.
+(2018).
+Equivalence Testing for Psychological Research: A Tutorial.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245918770963.
 doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}
 
-\hypertarget{ref-meyners_equivalence_2012}{}
-Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and
-Preference}, \emph{26}(2), 231--245.
-doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
+\leavevmode\hypertarget{ref-meyners_equivalence_2012}{}%
+Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
 
-\hypertarget{ref-murphy_statistical_2014}{}
-Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
-power analysis: A simple and general model for traditional and modern
-hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
-Francis Group.
+\leavevmode\hypertarget{ref-murphy_statistical_2014}{}%
+Murphy, K.
+R., Myors, B., \& Wolach, A.
+H.
+(2014).
+\emph{Statistical power analysis: A simple and general model for traditional and modern hypothesis tests} (Fourth edition.).
+New York: Routledge, Taylor \& Francis Group.
 
-\hypertarget{ref-quertemont_how_2011}{}
-Quertemont, E. (2011). How to Statistically Show the Absence of an
-Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127.
-doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}
+\leavevmode\hypertarget{ref-quertemont_how_2011}{}%
+Quertemont, E. (2011). How to Statistically Show the Absence of an Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127. doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}
 
-\hypertarget{ref-rogers_using_1993}{}
-Rogers, J. L., Howard, K. I., \& Vessey, J. T. (1993). Using
-significance tests to evaluate equivalence between two experimental
-groups. \emph{Psychological Bulletin}, \emph{113}(3), 553--565.
+\leavevmode\hypertarget{ref-rogers_using_1993}{}%
+Rogers, J.
+L., Howard, K.
+I., \& Vessey, J.
+T.
+(1993).
+Using significance tests to evaluate equivalence between two experimental groups.
+\emph{Psychological Bulletin}, \emph{113}(3), 553--565.
 doi:\href{https://doi.org/http://dx.doi.org/10.1037/0033-2909.113.3.553}{http://dx.doi.org/10.1037/0033-2909.113.3.553}
 
-\hypertarget{ref-schuirmann_comparison_1987}{}
-Schuirmann, D. J. (1987). A comparison of the two one-sided tests
-procedure and the power approach for assessing the equivalence of
-average bioavailability. \emph{Journal of Pharmacokinetics and
-Biopharmaceutics}, \emph{15}(6), 657--680.
+\leavevmode\hypertarget{ref-schuirmann_comparison_1987}{}%
+Schuirmann, D.
+J.
+(1987).
+A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability.
+\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.
 
-\hypertarget{ref-serlin_rationality_1985}{}
-Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological
-research: The good-enough principle.
+\leavevmode\hypertarget{ref-serlin_rationality_1985}{}%
+Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.
 
-\hypertarget{ref-spiegelhalter_bayesian_1994}{}
-Spiegelhalter, D. J., Freedman, L. S., \& Parmar, M. K. (1994). Bayesian
-approaches to randomized trials. \emph{Journal of the Royal Statistical
-Society. Series A (Statistics in Society)}, 357--416.
+\leavevmode\hypertarget{ref-spiegelhalter_bayesian_1994}{}%
+Spiegelhalter, D.
+J., Freedman, L.
+S., \& Parmar, M.
+K.
+(1994).
+Bayesian approaches to randomized trials.
+\emph{Journal of the Royal Statistical Society.
+Series A (Statistics in Society)}, 357--416.
 doi:\href{https://doi.org/10.2307/2983527}{10.2307/2983527}
 
-\hypertarget{ref-wellek_testing_2010}{}
-Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence
-and noninferiority} (2nd ed.). Boca Raton: CRC Press.
+\leavevmode\hypertarget{ref-wellek_testing_2010}{}%
+Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence and noninferiority} (2nd ed.). Boca Raton: CRC Press.
 
-\hypertarget{ref-westlake_use_1972}{}
-Westlake, W. J. (1972). Use of Confidence Intervals in Analysis of
-Comparative Bioavailability Trials. \emph{Journal of Pharmaceutical
-Sciences}, \emph{61}(8), 1340--1341.
+\leavevmode\hypertarget{ref-westlake_use_1972}{}%
+Westlake, W.
+J.
+(1972).
+Use of Confidence Intervals in Analysis of Comparative Bioavailability Trials.
+\emph{Journal of Pharmaceutical Sciences}, \emph{61}(8), 1340--1341.
 doi:\href{https://doi.org/10.1002/JPS.2600610845}{10.1002/JPS.2600610845}

### 2019-04-11 manuscript.Rmd
Correction for most extreme case when equivalence range are -.99 and .99, and n = 4

@@
 
+```{r, include=FALSE}
+low_eqbound_r = -0.99
+high_eqbound_r = 0.99
+res<-TOSTr(n = 4,
+           r = 0.99,
+           low_eqbound_r = low_eqbound_r,
+           high_eqbound_r = high_eqbound_r,
+           alpha = .05,
+           plot = FALSE,
+           verbose = FALSE)
+sgpv2 <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+```
+
 The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
@@
 The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% [UNTRUE: this is about 36% of the observed correlations...
+once again, due to asymmetric CI around r] of the correlations observed in the future will fall in this range.
 

### 2019-04-11 manuscript.tex
Correction for most extreme case when equivalence range are -.99 and .99, and n = 4

@@
 If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 50\%.
-In correlation test, the \emph{p} value is computed based on a transformed correlation score, computd as follows:
+In correlation test, the \emph{p} value is computed based on a transformed correlation score, computed as follows:
 
@@
 As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%.
-Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.60 to 1) according to Blume et al.
 (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise.
@@
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.
 
-It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a \emph{p}-value answers.
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, and in the same way of thinking, the probability of observing a correlation smaller or larger than the true correlation is also closer to 0.5.
+
 The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at these values.

### 2019-04-11 manuscript.Rmd
.
Correcting "50% of the correlation will fall" into "36% of the correlation will fall..."

@@
 The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% [UNTRUE: this is about 36% of the observed correlations...
-once again, due to asymmetric CI around r] of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run approximately 36% of the correlations observed in the future will fall in this range.
 

### 2019-04-11 manuscript.tex
Correcting "50% of the correlation will fall" into "36% of the correlation will fall..."

@@
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% {[}UNTRUE: this is about 36\% of the observed correlations\ldots{} once again, due to asymmetric CI around r{]} of the correlations observed in the future will fall in this range.
 

### 2019-04-21 reply_to_reviews.R1.tex
R1 final resubmission

--- 2019-03-09 reply_to_reviews.R1.tex
@@
 \abstract{
-We respond to all the comments raised by the two reviewers and the editors.
-We would like to thank the editor and reviewers for their suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct.
+We respond to all the comments on our submission that were raised by the two reviewers, as well as the comments you highlighted as editor.
+We would like to thank you and reviewers for suggestions for improvements, which we believe made our main argument much clearer, focussed, and formally correct.
 We feel we were able to accomodate all suggestions, and we hope you think our submission is ready to be accepted for publication in Meta-Psychology.
+All code associated with this article, including the reproducible manuscript, is available from \url{https://github.com/Lakens/TOST_vs_SGPV} and \url{https://osf.io/8crkg/}.
+The preprint can be found at \url{https://psyarxiv.com/7k6ay/}.
 
@@
 \item
-  We have changed the part of the sentence \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV in this article are not dependent upon any specific example} into \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for an SGPV calculated from confidence intervals, and assuming continuous normally distributed data.}.
-We mainly intended to refer to our conclusion that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
+  We have changed the part of the sentence \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV in this article are not dependent upon any specific example} into \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for second generation \emph{p}-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution}.
+We mainly intended to refer to our conclusion that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values} namely \emph{p} = 0.5 for TOST when the SGPV will be 0.5, and the \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the largest observed mean where the SGPV is 0 and the smallest observed mean where the SGPV is 1).
 We have now made it clearer that when we talk about \enquote{correspondence between TOST \emph{p}-values and the SGPV}, we mean that there is a direct relation between three points.
+We have added the explanation: \enquote{When we discuss the relationship between the \emph{p}-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
+These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).}
 \item
@@
 We now just directly say what we originally meant, and no longer use the word \enquote{unrelated}.
-For example, \enquote{There are three situations where \emph{p}-values for TOST differentiate between observed results, while the SGPV does not differentiate.} and \enquote{While the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the \emph{p}-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the \emph{p}-value).} and similarly \enquote{A third situation in which the SGPV remains stable across a range of observed effects, while the TOST \emph{p}-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper \emph{and} lower equivalence bound.}
+For example, \enquote{There are three situations where \emph{p}-values for TOST differentiate between observed results, while the SGPV does not differentiate} and \enquote{Where the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the \emph{p}-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds} and similarly \enquote{A third situation in which the SGPV remains stable across a range of observed effects, while the TOST \emph{p}-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper \emph{and} lower equivalence bound}.
+We have removed the word \enquote{unrelated} throughout the manuscript.
 \item
@@
 This is exactly why we submit our work for peer review - to be able to improve it based on feedback from experts.
-We now preface the sentence with \enquote{As long as data is normally distributed,}.
+We now preface the sentence with \enquote{As long as data are sampled from a bivariate normal distribution,}.
 We follow your recommendation throughout to not generalize beyond the scenarios we study.
-In the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} See also point 5 below.
+In the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to continuous data sampled from a bivariate normal distribution.} See also point 5 below.
 \item
-  After making the change at point 2 above, we now think the sentence \enquote{The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST
-  procedure are always directly related at these values.} should no longer be confusing.
-To make the sentence clearer, we have changed \enquote{these values} into \enquote{at the values p = 0.025 and p = 0.975} It should now be clear the sections are not contradictory - TOST differentiates below p \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
+  After making the change at point 2 above, we now think the sentence \enquote{The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a p \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at these values.} should no longer be confusing.
+To make the sentence clearer, we have changed \enquote{these values} into \enquote{at the values \emph{p} = 0.025 and \emph{p} = 0.975} It should now be clear the sections are not contradictory - TOST differentiates below \emph{p} \textless{} 0.025, when the SGPV is 1 for all \emph{p} \textless{} 0.025.
 \item
   We agree that is unclear whether the original statement by Blume et al that \enquote{the degree of overlap conveys how compatible the data are with the null premise} holds in general.
-We have now amended the sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis} under the assumption of normally distributed data, and the generalizability of this statement needs to be examined beyond normally distributed data requires further examination.}
+We have now amended the sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis} under the assumption of a bivariate normal distribution, and the generalizability of this statement needs to be examined beyond normal bivariate distributions.}
 \item
-  We have removed our earlier statements that the SGPV only works as a descriptive statistic.
+  We have removed all our earlier statements that the SGPV only works as a descriptive statistic.
 We deleted the sentence \enquote{the SGPV is a descriptive statistic (unlike the \emph{p}-value that is calculated for an equivalence test, which is an inferential statistic) that provides the proportion of overlap of the confidence interval and the equivalence range.} and deleted \enquote{The novelty of the SGPV lies in its use as a descriptive statistic} from the conclusion.
@@
 We will leave our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should be interpreted to future researchers, and we do not make any statements about whether such values are descriptive or inferential.
-\item
-  We agree that using TOST for small samples (e.g., N = 4) will not be useful.
-Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.
-\item
-  With our recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions.
+\end{enumerate}
+
+Based on your recommendations, we have limited our conclusions to the specific cases we have examined, and noted the possibility for future research to examine a wider set of assumptions.
 An additional change not mentioned above is that we renamed the section on asymmetric confidence intervals to the more specific \enquote{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations} instead of the more general \enquote{The relation between equivalence tests and SGPV when confidence intervals are not symmetrical}.
 We appreciate the very positive evaluation of our manuscript, but even more so the criticism which allowed us to improve the manuscript.
-\end{enumerate}
 
@@
 
-Before listing major points, the reviewer raises the point that we compare SGPV with \emph{p}-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we write:
+Before listing major points, the reviewer raises the point that we compare SGPV with \emph{p}-values from TOST throughout our paper, and in all figures, but then at the end, in page 20, we wrote:
 
@@
 However, we do not suggest to replace the SGPV with an equivalence test and a NHST at all.
-In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7):
+In our manuscript, we already pointed out how the SGPV is basically the same as an equivalence test and a minimum effect test (on page 7), and we have expanded this text to clarify that a minimum effects test and TOST are complementary:
 
 \enquote{The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the \emph{p}-value will always be 0.975.
-Note that this
-situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014).
+Note that this situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014).
 The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
-The SGPV summarizes the information from an equivalence test and a minimum-effect test.}
+An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST \emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum effect test is smaller than 0.05 (and therefore the minimum effect test provides no additional information that can not be derived from the \emph{p}-value from the equivalence test).
+The SGPV summarizes the information from an equivalence test (and the complementary minimum-effect test).}
 
-One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
-When the TOST \emph{p}-value is 0.975, the 95\% CI touches either the upper or lower equivalence bound, and fall complately outside of the equivalence range.
-This is mathematically identical to a statistically significant minimum effect test at p \textless{} 0.05.
-We didn't make this explicit, but we clearly should have.
-We have added the sentence (on page 7):
-
-\enquote{An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST \emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum effect test is smaller than 0.05, and the minimum effect test provides no additional information that can not be derived from the \emph{p}-value from the equivalence test.}
+The overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0 gives away that the equivalence test can be interpreted as a minimum effect test against the equivalence bound.
+When the TOST \emph{p}-value is 0.975, the 95\% CI touches either the upper or lower equivalence bound, and fall completely outside of the equivalence range.
+This is mathematically identical to a statistically significant minimum effect test at \emph{p} \textless{} 0.05.
+We clearly should have made this more explicit, and hope the additional text clarifies the statistical relationship between TOST, a minimum effect test, and the SGPV
 
@@
 And indeed, the sentence \enquote{This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test} was simply confusing.
-We have deleted this sentence and replaced it with \enquote{As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).}
-
-Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test.
-Part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
+We have deleted this sentence and replaced it with \enquote{As already mentioned, this interpretation of a SGPV as is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).} Furthermore, to prevent the apparent confusion about why we suggested to perform a null-hypothesis test and equivalence test: part of this confusion was our original sentence comparing the SGPV and a combination of NHST and an equivalence test which was not needed, and we understand it made it seem as if SGPV needs to be replaced by a combination of other tests.
 But that is not what we propose.
-Werewrote the paragraph:
+We rewrote the paragraph:
 
@@
 \item
-  In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to normally distributed continuous data.} After all, \emph{p}-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
+  In line with the comments by reviewer 1, in the second paragraph of the manuscript we now clearly state: \enquote{We limit our analysis to continuous data sampled from a bivariate normal distribution.} and \enquote{Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for second generation \emph{p}-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution.}.
+After all, \emph{p}-values and confidence are directly related, but Bayesian credible intervals would not necessarily be, depending on the prior.
 Blume et al (2018) limit their examples to confidence intervals, but explicitly acknowledge other possibilities (such as Bayesian intervals).
 We look forward to future papers that illustrate the SGPV with other interval estimates and are happy to add the limitation to continuous normally distributed data in our article.
-Note that we did not add that the correspondence only holds for situations where the SE's are small compared to the width of the equivalence range, as the reviewer suggests.
 \item
-  The reviewer repeats that the correspondence only holds when SE's are small compared to the width of the equivalence range.
-The correspondence is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
+  The reviewer notes that the correspondence only holds when SE's are small compared to the width of the equivalence range.
+The correspondence we refer to is not in the shape of the curve (which clearly differs across Figures 2, 6, and 9).
 We clearly state that: \enquote{When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values.} This correspondence is not dependent upon the SE's.
-It will always hold for continuous normal data.
-The reviewer says that \enquote{The paper does not provide theoretical justification for this connection nor any proofs.} We are unsure which proof is needed for the overlap between the three points, since it is rather trivial and we believe the explanation in the paper is very clear.
-\end{enumerate}
-
-For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and SGPV = 1, and TOST p = 0.975 and SGPV = 1: "The SGPV is 50\% when the observed mean falls exactly on the lower or upper equivalence bound, because 50\% of the symmetrical confidence interval overlaps with the equivalence range.
-When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the t-value for the equivalence test is also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure 3).
-Two other points always have to overlap.
-When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure 3), when the \emph{p}-value will always be 0.975, and the SGPV is 0.
-
-We do not think we can provide any other proof for this.
+It will always hold for CI based on bivariate continuous normally distributed data.
+The reviewer says that \enquote{The paper does not provide theoretical justification for this connection nor any proofs.} We do not think proof is needed (the \enquote{proof} is that the SGPV and the TOST both use the same confidence interval) and we believe the explanation in the paper of why this overlap must be so is very clear.
 A confidence interval and a \emph{p}-value are directly related.
@@
 To make it clearer that we talk about the overlap in these 3 critical points, we have added:
+\end{enumerate}
 
@@
 
-We believe this satisfactorily addresses the point by the reviewer that \enquote{Because of this
-lack of discussion, the reader can easily miss that the close correspondence only occurs when
-the sample size is large enough that the standard error is very small relative to the width of the
-equivalence zone.} Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a \emph{p}-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+We believe this satisfactorily addresses the point by the reviewer that \enquote{Because of this lack of discussion, the reader can easily miss that the close correspondence only occurs when the sample size is large enough that the standard error is very small relative to the width of the equivalence zone.} Indeed, the correspondence between the TOST and SGPV at these 3 points should be obvious to anyone who understands the relationship between a \emph{p}-value and a confidence interval, so we do not provide any further proof, but we hope that clarifying we talk about the correspondence of these 3 points, and not the entire curve, is sufficient to address point 2.
+We have also changed the figures, making the SGPV a solid line, to make the relationship more clearly visible compared to the previous dotted curve.
 
@@
   We tried to find the passage the reviewer refers to when he writes \enquote{In light of this, the assertion without proof that classical \emph{p}-values provide more or better assessments of the ``evidence} appear out of place." but we could not.
-We do not use the word \enquote{evidence} in the text (because neither the \emph{p}-value from TOST nor the SGPV are measures of \enquote{evidence} - we fully agree with BLume et al., 2018, in this respect).
+We do not use the word \enquote{evidence} in the text (because neither the \emph{p}-value from TOST nor the SGPV are measures of \enquote{evidence} - we fully agree with Bume et al., 2018, in this respect).
 We also do not say the \emph{p}-value is \enquote{naturally informative}.
@@
 \item
-  We fully agree with the reviewer on point 5 that \enquote{The maximum Type I Error rate for the SGPV over the null
-  interval is 5\%, exactly like the TOST test.} Indeed, given the direct overlap between the TOST \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical.
+  We fully agree with the reviewer on point 5 that \enquote{The maximum Type I Error rate for the SGPV over the null interval is 5\%, exactly like the TOST test.} Indeed, given the direct overlap between the TOST \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of 1 and 0, any error rates (when concluding support for the null or alternative when the SGPV is either 1 or 0) must be identical.
 This is why we were so surprised when Blume et al (2018) write \enquote{They control the Type I error naturally, forcing it to zero as the sample size grows.
@@
 
-Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that \enquote{Adjustments for multiple comparisons are obviated} (p.~15).
+\enquote{Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that when using the SGPV}Adjustments for multiple comparisons are obviated" (p.~15).
 However, this is not correct.
-Given the direct relationship between TOST and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming continuous and normally distributed data), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV =1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST \emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons."
 
@@
 \item
-  In line with comments by reviewer 1, we removed statemetns about SGPV not being inferential, thereby solving the issue reviewer 2 raised.
+  In line with comments by reviewer 1, we removed statements about SGPV not being inferential, thereby solving the issue reviewer 2 raised.
 \item
-  In line with major point 8, we added information that asymmetric condifence intervals around a correlation are symmetric when Fisher z-transformed.
+  In line with major point 8, we added information that asymmetric confidence intervals around a correlation are symmetric when Fisher z-transformed.
 This is just an example of what Blume et al (2018) refer to when they write \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed.
-However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.} We beieve this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that \enquote{The asymmetric CI case is very interesting}).
+However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.} We believe this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that \enquote{The asymmetric CI case is very interesting}).
 We have made our point less general, now only talking about correlations, by changing the title of this section into \enquote{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations}.
@@
 \item
+  We agree that using TOST for small samples (e.g., N = 4) will not be useful.
+Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.
 It is a well-known fact that the TOST can have 0 power (and indeed, this is one of the main issues in the Perlman and Wu (1999) paper the reviewer cited).
@@
 Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study.
-Not that the exact same issue applies to the SGPV.
+The paper already contained a section explaining this (\enquote{This happens because the we are examining a scenario where the 90\% CI is so wide that it never falls completely within the two equivalence bounds.
+As Lakens (2017) notes: ``in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).} None of the \emph{p}-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0\% power").
+\end{enumerate}
+
+Note that the exact same issue applies to the SGPV.
 It is also possible to have 0 power for the SGPV - so we do not understand why the reviewer is so surprised about this.
 The question \enquote{Why use the TOST test then?} equally applies to \enquote{Why use the SGPV then?} if you, from the outset, know that the \enquote{small sample correction} will lead to a SGPV of 0.5.
+Note that, following Reviewer 1's caution in using words ike \enquote{always}, we have added a comment about the overlap between the 3 points of TOST and SGPV where we say: \enquote{Two other points always have to overlap.} which we now follow with: \enquote{Note that when sample sizes are small or equivalence bounds are narrow, small \emph{p}-values for the TOST or a SGPV = 1 might not be observed in practice if too few observations are collected.}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{7}
+\tightlist
 \item
@@
 
-As a final comment, altough not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an \enquote{outright ban of TOST}.
+As a final comment, although not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an \enquote{outright ban of TOST}.
 The best summary of this discussion (of which Perlman \& Wu is one contribution) can be found in Meyners (2012), which we cited.
@@
 We would like to emphasize again that the differences between the approaches are minor and to a large extent of academic interest only, as is this debate.} and concludes: \enquote{To summarize, there is no right or wrong in most of the arguments; the two opposing parties rather apply different criteria to select the most appropriate test, one group focusing rather on mathematical/statistical criteria, the other one more on interpretability and reasonability.} We have added a reference to this discussion for the interested reader, and added \enquote{For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see Meyners, 2012.}
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
+\leavevmode\hypertarget{ref-murphy_statistical_2014}{}%
+Murphy, K.
+R., Myors, B., \& Wolach, A.
+H.
+(2014).
+\emph{Statistical power analysis: A simple and general model for traditional and modern hypothesis tests} (Fourth edition.).
+New York: Routledge, Taylor \& Francis Group.
+
 \endgroup

### 2019-04-21 manuscript.Rmd

@@
 If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test is 50%.
-In correlation test, the *p* value is computed based on a transformed correlation score, computed as follows:
+In correlation test, the *p* value is computed based on a transformed correlation score, computed as follows, with  r = the observed correlation and $\rho$ = the theoretical correlation under the null :
 
@@
 Because the z distribution is symmetric, the probability of observing the observed z score or more extreme score, assuming the equivalence bound is the true effect size, is 50%.
-However, it does not mean that there is always a 50% probability of observing a correlation (r) smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
+However, it does not mean that there is always a 50% probability of observing a correlation smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
 

### 2019-04-21 manuscript.tex

--- 2019-04-11 manuscript.tex
@@
 If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 50\%.
-In correlation test, the \emph{p} value is computed based on a transformed correlation score, computed as follows:
+In correlation test, the \emph{p} value is computed based on a transformed correlation score, computed as follows, with r = the observed correlation and \(\rho\) = the theoretical correlation under the null :
 
@@
 Because the z distribution is symmetric, the probability of observing the observed z score or more extreme score, assuming the equivalence bound is the true effect size, is 50\%.
-However, it does not mean that there is always a 50\% probability of observing a correlation (r) smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
+However, it does not mean that there is always a 50\% probability of observing a correlation smaller or larger than the true correlation: while the z distribution is symmetrically distributed around the observed z score, the r distribution is not.
 
@@
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run approximately 36\% of the correlations observed in the future will fall in this range.
 

### 2019-04-22 reply_to_reviews.R2.tex
reply to reviews 2

--- 2019-03-09 reply_to_reviews.R1.tex
@@
 
-\shorttitle{Reply R1}
+\shorttitle{Reply R2}
 \affiliation{
@@
 
-Correspondence concerning this article should be addressed to Daniël
-Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
-E-mail:
-\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
+E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
 \abstract{
-We respond to all the comments raised by the two reviewers and the
-editors. We would like to thank the editor and reviewers for their
-suggestions for improvements, which we believe made our main argument
-much clearer, focussed, and formally correct. We feel we were able to
-accomodate all suggestions, and we hope you think our submission is
-ready to be accepted for publication in Meta-Psychology.
+In this second revision we are responding to the last issue you raised, about our incorrect statement that 50\% of the correlations fall below the observed correlation.
+We are extrmely grateful you pointed out this incorrect statement, and have corrected it as explained below.
+We hope you think our submission is ready to be accepted for publication in Meta-Psychology.
 
@@
 
-Dear editor,
+\textbf{Dear editor,}
 
-Thank you for your comments on our submitted manuscript. We have
-incorporated your three comments:
+\textbf{thank you for your comments on our revised manuscript.
+You rightly noted that our statement that \enquote{There is always a 50\% probability of observing a correlation smaller or larger than the true correlation} was not correct.
+Our statement was true for the corresponding z-value when transforming the correlation while calculating confidence intervals, but not for correlations, which are not symmetrically distributed.
+We have deleted the following:}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  We moved the first sentence on page 3 into the next paragraph (well
-  spotted).
-\item
-  The code for the Shiny app was on GitHub, and the GitHub repository is
-  linked to the OSF project page, but we have added a component to the
-  OSF page and also directly added the Shiny App code there to make it
-  easier to find: \url{https://osf.io/7f8uq/}
-\item
-  We now immediately refer to Figure 4 in the beginning of the paragraph
-  in which the Figure is described.
-\end{enumerate}
+\begin{quote}
+\emph{In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.}
+\end{quote}
 
-We will respond to the points raised by both reviewers in turn. Our
-points below detail 1) that we limit ourselves to a comparison of SGPV
-and TOST, and do not require researchers to perform both an equivalence
-test and a NHST (and therefore we did not add these curves to the
-Figures), 2) we rewrote the frequency claims, 3) we provide more detail
-about confidence intervals around correlations, and 4) removed all
-statements about the SGPV being a descriptive statistic.
+\textbf{We have made a number of small changes.
+First, we clearly explain that, although the z-distribution is symmetrical, the correlation is not.
+We note how the transformation has the goal to yield accurate error rates (which is important in the TOST procedure) on page 18, lines 250-255.}
 
-\section{Reply to Reviewer 1}\label{reply-to-reviewer-1}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  We have changed the part of the sentence \enquote{Our conclusions
-  about the relationship between TOST \emph{p}-values and SGPV in this
-  article are not dependent upon any specific example} into \enquote{Our
-  conclusions about the relationship between TOST \emph{p}-values and
-  SGPV hold for an SGPV calculated from confidence intervals, and
-  assuming continuous normally distributed data.}. We mainly intended to
-  refer to our conclusion that: \enquote{When confidence intervals are
-  symmetric we can think of the SGPV as a straight line that is directly
-  related to the \emph{p}-value from an equivalence test for three
-  values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
-  \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the
-  largest observed mean where the SGPV is 0 and the smallest observed
-  mean where the SGPV is 1). We have now made it clearer that when we
-  talk about \enquote{correspondence between TOST \emph{p}-values and
-  the SGPV}, we mean that there is a direct relation between three
-  points.
-\item
-  We appreciate correcting our use of the term \enquote{unrelated} and
-  teaching us the word \enquote{bijective}. We used the word
-  \enquote{unrelated} somewhat naievely, looking at the Figures and
-  wanting to express that across the three identified situations, a
-  different TOST \emph{p}-value does not imply a different SGPV - the
-  SGPV across these ranges of means is aways the same (either 0, 0.5, or
-  1) while the TOST \emph{p}-value differs across this range of means.
-  We now just directly say what we originally meant, and no longer use
-  the word \enquote{unrelated}. For example, \enquote{There are three
-  situations where \emph{p}-values for TOST differentiate between
-  observed results, while the SGPV does not differentiate.} and
-  \enquote{While the SGPV is 1 as long as the confidence interval falls
-  completely within the equivalence bounds, the \emph{p}-value for the
-  TOST continues to differentiate between results as a function of how
-  far the confidence interval lies within the equivalence bounds (the
-  further the confidence interval is from both bounds, the lower the
-  \emph{p}-value).} and similarly \enquote{A third situation in which
-  the SGPV remains stable across a range of observed effects, while the
-  TOST \emph{p}-value continues to differentiate, is whenever the CI is
-  wider than the equivalence range, and the CI overlaps with the upper
-  \emph{and} lower equivalence bound.} We have removed the word
-  \enquote{unrelated} throughout the manuscript.
-\item
-  Please do not feel like you ever need to apologize for having formal
-  training we lack, that allows you to point out whenever we make
-  formally incorrect statements. This is exactly why we submit our work
-  for peer review - to be able to improve it based on feedback from
-  experts. We now preface the sentence with \enquote{As long as data is
-  normally distributed,}. We follow your recommendation throughout to
-  not generalize beyond the scenarios we study. In the second paragraph
-  of the manuscript we now clearly state: \enquote{We limit our analysis
-  to normally distributed continuous data.} See also point 5 below.
-\item
-  After making the change at point 2 above, we now think the sentence
-  \enquote{The conclusion of this section on asymmetric confidence
-  intervals is that a SGPV of 1 or 0 can still be interpreted as a p
-  \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test,
-  since the SGPV and \emph{p}-value for the TOST procedure are always
-  directly related at these values.} should no longer be confusing. To
-  make the sentence clearer, we have changed \enquote{these values} into
-  \enquote{at the values p = 0.025 and p = 0.975} It should now be clear
-  the sections are not contradictory - TOST differentiates below p
-  \textless{} 0.025, when the SGPV is 1 for all p \textless{} 0.025.
-\item
-  We agree that is unclear whether the original statement by Blume et al
-  that \enquote{the degree of overlap conveys how compatible the data
-  are with the null premise} holds in general. We have now amended the
-  sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly
-  interpreted, a SGPV between 0 and 1 is not interpretable as
-  \enquote{compatibility with the null hypothesis} under the assumption
-  of normally distributed data, and the generalizability of this
-  statement needs to be examined beyond normally distributed data
-  requires further examination.}
-\item
-  We have removed all our earlier statements that the SGPV only works as
-  a descriptive statistic. We deleted the sentence \enquote{the SGPV is
-  a descriptive statistic (unlike the \emph{p}-value that is calculated
-  for an equivalence test, which is an inferential statistic) that
-  provides the proportion of overlap of the confidence interval and the
-  equivalence range.} and deleted \enquote{The novelty of the SGPV lies
-  in its use as a descriptive statistic} from the conclusion. Indeed, we
-  acknowledge that \enquote{Although a SGPV of 1 or 0 can be directly
-  interpreted, a SGPV between 0 and 1 is not interpretable as
-  \enquote{compatibility with the null hypothesis}.} So the SGPV is an
-  inferential statistic when interpreted dichotomously. We will leave
-  our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should
-  be interpreted to future researchers, and we do not make any
-  statements about whether such values are descriptive or inferential.
-\item
-  We agree that using TOST for small samples (e.g., N = 4) will not be
-  useful. Indeed, an a-priori power analysis for equivalence tests would
-  prevent anyone from planning such a study, since the result will be
-  that such a study has 0 power - the CI will never fit withing the
-  equivalence bounds.
-\item
-  With our recommendations, we have limited our conclusions to the
-  specific cases we have examined, and noted the possibility for future
-  research to examine a wider set of assumptions. An additional change
-  not mentioned above is that we renamed the section on asymmetric
-  confidence intervals to the more specific \enquote{The relation
-  between equivalence tests and SGPV for asymmetrical confidence
-  intervals around correlations} instead of the more general
-  \enquote{The relation between equivalence tests and SGPV when
-  confidence intervals are not symmetrical}. We appreciate the very
-  positive evaluation of our manuscript, but even more so the criticism
-  which allowed us to improve the manuscript.
-\end{enumerate}
+If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 0.5.
+In the equivalence test for correlations the \emph{p} value is computed based on a z-transformation which better controls error rates (Goertzen \& Cribbie, 2010).
+This transformation is computed as follows, where \emph{r} is the observed correlation and \(\rho\) is the theoretical correlation under the null:
 
-\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}
+\[
+z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
+\]
 
-Before listing major points, the reviewer raises the point that we
-compare SGPV with \emph{p}-values from TOST throughout our paper, and in
-all figures, but then at the end, in page 20, we write:
+Because the z-distribution is symmetric, the probability of observing the observed or more extreme z-score, assuming the equivalence bound is the true effect size, is 50\%.
+However, because the \emph{r} distribution is not symmetric, this does not mean that there is always a 50\% probability of observing a correlation smaller or larger than the true correlation.
 
-\enquote{Equivalence tests combined with null-hypothesis significance
-tests also allow researchers to conclude an effect is significant and
-equivalent (i.e., statistically different from zero, but also too small
-to be considered meaningful). Thus, the SGPV is used to classify results
-into one of three possible categories (with the data falling inside or
-outside the equivalence range, or being inconclusive), while equivalence
-tests combined with null-hypothesis tests classify results into four
-possible categories.}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-The reviewer says that \enquote{the authors suddenly switch the premise;
-now the SGPV should be replaced by two \emph{p}-values, one from an
-equivalence test and one from a NHST}. However, we do not suggest to
-replace the SGPV with an equivalence test and a NHST at all. In our
-manuscript, we already pointed out how the SGPV is basically the same as
-an equivalence test and a minimum effect test (on page 7):
+\textbf{Second, we have added an explicit statement that in the extreme case, the probability of observing a correlation smaller than the equivalence bound is not 50\%, but in our example, 36\% on page 19, lines 271-275.}
 
-\enquote{The third point where the SGPV and the \emph{p}-value from the
-TOST procedure should overlap is where the 95\% CI falls completely
-outside of the equivalence range, but one endpoint of the confidence
-interval is equal to the equivalence bound (see situation C in Figure
-3), when the \emph{p}-value will always be 0.975. Note that this
-situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
-2014). The goal of a minimum-effect is not just to reject a difference
-of zero, but to reject the smallest effect size of interest (i.e., the
-equivalence bounds). The SGPV summarizes the information from an
-equivalence test and a minimum-effect test.}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-One might argue that we suggest to replace the SGPV with two tests.
-However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0
-gives away that the equivalence test can be interpreted as a minimum
-effect test against the equivalence bound. When the TOST \emph{p}-value
-is 0.975, the 95\% CI touches either the upper or lower equivalence
-bound, and fall completely outside of the equivalence range. This is
-mathematically identical to a statistically significant minimum effect
-test at p \textless{} 0.05. We didn't make this explicit, but we clearly
-should have. We have added the sentence (on page 7):
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 36\% of the correlations observed in the future will fall in this range.
 
-\enquote{An equivalence test and minimum effect test against the same
-equivalence bound are complementary, and when a TOST \emph{p}-value is
-larger than 0.975, the \emph{p}-value for the minimum effect test is
-smaller than 0.05, and the minimum effect test provides no additional
-information that can not be derived from the \emph{p}-value from the
-equivalence test.}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-One might wonder why then, on page 20, why we introduce the idea to
-perform both a null-hypothesis significance test and an equivalence
-test. We were not clear enough. And indeed, the sentence \enquote{This
-interpretation of a SGPV as allowing researchers to reject the null,
-reject the presence of a meaningful effect, or remaining inconclusive is
-very similar to the Neyman-Pearson interpretation of combining a
-null-hypothesis test and an equivalence test} was simply confusing. We
-have deleted this sentence and replaced it with \enquote{As already
-mentioned, this interpretation of a SGPV as is very similar to the
-Neyman-Pearson interpretation of an equivalence test and a minimum
-effect tests (which are complementary).} Furthermore, to prevent the
-apparent confusion about why we suggested to perform a null-hypothesis
-test and equivalence test: part of this confusion was our original
-sentence comparing the SGPV and a combination of NHST and an equivalence
-test which was not needed, and we understand it made it seem as if SGPV
-needs to be replaced by a combination of other tests. But that is not
-what we propose. We rewrote the paragraph:
+\textbf{We again want to sincerely thank you for catching this error before our paper was publlished.}
 
-\enquote{Some researchers might be interested in combining an
-equivalence tests with a null-hypothesis significance test. This allows
-a researcher to ask whether there is an effect that is statistically
-different from zero, and whether effect sizes that are considered
-meaningful can be rejected. Equivalence tests combined with
-null-hypothesis tests classify results into four possible categories,
-and for example allow researchers to conclude an effect is significant
-and equivalent (i.e., statistically different from zero, but also too
-small to be considered meaningful, see (Lakens et al., 2018)).}
+\newpage
 
-We hope this makes it clear we are not pulling a bait and switch. The
-SGPV is strongly related to an equivalence test (or it's complement, a
-minimum effect test). Describing the relation between the SGPV and TOST
-is our main contribution. We just wanted to mention that researchers
-might want to combine an equivalence test with a NHST, because in the
-literature, this is a question we see many psychologists ask.
-
-We will now discuss the major points in turn.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  In line with the comments by reviewer 1, in the second paragraph of
-  the manuscript we now clearly state: \enquote{We limit our analysis to
-  normally distributed continuous data.} After all, \emph{p}-values and
-  confidence are directly related, but Bayesian credible intervals would
-  not necessarily be, depending on the prior. Blume et al (2018) limit
-  their examples to confidence intervals, but explicitly acknowledge
-  other possibilities (such as Bayesian intervals). We look forward to
-  future papers that illustrate the SGPV with other interval estimates
-  and are happy to add the limitation to continuous normally distributed
-  data in our article. Note that we did not add that the correspondence
-  only holds for situations where the SE's are small compared to the
-  width of the equivalence range, as the reviewer suggests.
-\item
-  The reviewer repeats that the correspondence only holds when SE's are
-  small compared to the width of the equivalence range. The
-  correspondence is not in the shape of the curve (which clearly differs
-  across Figures 2, 6, and 9). We clearly state that: \enquote{When
-  confidence intervals are symmetric we can think of the SGPV as a
-  straight line that is directly related to the \emph{p}-value from an
-  equivalence test for three values.} This correspondence is not
-  dependent upon the SE's. It will always hold for continuous normal
-  data. The reviewer says that \enquote{The paper does not provide
-  theoretical justification for this connection nor any proofs.} We are
-  unsure which proof is needed for the overlap between the three points,
-  since it is rather trivial and we believe the explanation in the paper
-  is very clear.
-\end{enumerate}
-
-For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and
-SGPV = 1, and TOST p = 0.975 and SGPV = 1: ``The SGPV is 50\% when the
-observed mean falls exactly on the lower or upper equivalence bound,
-because 50\% of the symmetrical confidence interval overlaps with the
-equivalence range. When the observed mean equals the equivalence bound,
-the difference between the mean in the data and the equivalence bound is
-0, the \emph{t}-value for the equivalence test is also 0, and thus the
-\emph{p}-value is 0.5 (situation A, Figure 3). Two other points always
-have to overlap. When the 95\% CI falls completely inside the
-equivalence region, and one endpoint of the confidence interval is
-exactly equal to one of the equivalence bounds (see situation B in
-Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is
-always 0.025, and the SGPV is 1. The third point where the SGPV and the
-\emph{p}-value from the TOST procedure should overlap is where the 95\%
-CI falls completely outside of the equivalence range, but one endpoint
-of the confidence interval is equal to the equivalence bound (see
-situation C in Figure 3), when the \emph{p}-value will always be 0.975,
-and the SGPV is 0.
-
-We do not think we can provide any other proof for this. A confidence
-interval and a \emph{p}-value are directly related. The TOST procedure
-is a test using the confidence interval, and the SGPV (now that we
-clearly limited our discussion to a SGPV based on a confidence interval
-calculated from continuous normal data) compared against the same
-equivalence bounds will be related as we describe. But we believe our
-article might not have been clear enough about that we limit our
-discussion about the correspondence of the curves to these 3 points.
-Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
-13). Nevertheless, in these graphs, we still have the correspondence
-between these 3 points (or at least the 2 points if the CI is too wide
-compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
-To make it clearer that we talk about the overlap in these 3 critical
-points, we have added:
-
-\enquote{When we discuss the relationship between the \emph{p}-values
-from TOST and the SGPV, we focus on their correspondence at three
-values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
-TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
-and SGPV = 1. These three values are important for the SGPV because they
-indicate the values at which the SGPV indicates the data should be
-interpreted as compatible with the null hypothesis (SGPV = 1), or with
-the alternative hypothesis (SGPV = 0), or when the data are strictly
-inconclusive (SGPV = 0.5). These three points of overlap are indicated
-by the horizontal dotted lines in Figure 2.}
-
-We believe this satisfactorily addresses the point by the reviewer that
-\enquote{Because of this lack of discussion, the reader can easily miss
-that the close correspondence only occurs when the sample size is large
-enough that the standard error is very small relative to the width of
-the equivalence zone.} Indeed, the correspondence between the TOST and
-SGPV at these 3 points should be obvious to anyone who understands the
-relationship between a \emph{p}-value and a confidence interval, so we
-do not provide any further proof, but we hope that clarifying we talk
-about the correspondence of these 3 points, and not the entire curve, is
-sufficient to address point 2.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\item
-  We are aware of the Beger and Hsu (1996) article. But if the reviewer
-  reads more closely, it should be clear that we never say the TOST is
-  UMP. We say that TOST is a test procedure that aims to control error
-  rates - our use of the term \enquote{Neyman-Pearson perspective}
-  refers to the classic difference between significance tests (Fisher)
-  and hypothesis tests (Neyman-Pearson). We do not imply that any test
-  that fixes an error rate is a NP test. Because many psychologists are
-  not trained in the difference between a Fisherian approach and a
-  Neyman Pearson approach to the use of \emph{p}-values, we are simply
-  adding a \enquote{Neyman-Pearson} approach in the text to explain that
-  \enquote{From a Neyman-Pearson perspective on statistical inferences
-  the main conclusion is based on whether or not \(p < \alpha\), and
-  thus an equivalence test and SGPV can be performed by simply checking
-  whether the confidence interval falls within the equivalence range,
-  just as a null-hypothesis test can be performed by checking whether
-  the confidence interval contains zero or not.} We believe this is a
-  correct use of the term \enquote{Neyman-Pearson perspective on
-  statistical inferences}.
-\item
-  We tried to find the passage the reviewer refers to when he writes
-  \enquote{In light of this, the assertion without proof that classical
-  \emph{p}-values provide more or better assessments of the
-  \enquote{evidence} appear out of place.} but we could not. We do not
-  use the word \enquote{evidence} in the text (because neither the
-  \emph{p}-value from TOST nor the SGPV are measures of
-  \enquote{evidence} - we fully agree with BLume et al., 2018, in this
-  respect). We also do not say the \emph{p}-value is \enquote{naturally
-  informative}. Indeed, related to point 3 above, we tried to be
-  consistent in interpreting the TOST procedure from a Neyman-Pearson
-  perspective, and focus on error control. So we regrettably do not know
-  how to incorporate this point.
-\item
-  We fully agree with the reviewer on point 5 that \enquote{The maximum
-  Type I Error rate for the SGPV over the null interval is 5\%, exactly
-  like the TOST test.} Indeed, given the direct overlap between the TOST
-  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
-  1 and 0, any error rates (when concluding support for the null or
-  alternative when the SGPV is either 1 or 0) must be identical. This is
-  why we were so surprised when Blume et al (2018) write \enquote{They
-  control the Type I error naturally, forcing it to zero as the sample
-  size grows. This, in turn, offsets Type I Error inflation that results
-  from multiple comparisons or multiple examinations of accumulating
-  data. Findings identified by second-generation \emph{p}-values are
-  less likely to be false discoveries than findings identified by
-  classical \emph{p}-values. Consequently, second-generation
-  \emph{p}-values do not require ad-hoc adjustments to provide strict
-  error control and this improves power in studies with massive multiple
-  comparisons.} Clearly, it can not both be true that the error rate of
-  SGPV and TOST is identical, TOST requires adjusting for multiple
-  comparisons, but the SGPV does not.
-\end{enumerate}
-
-The editor asks us to better substantiate the frequency claims for the
-comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value
-are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1)
-we do not think any additional substantiation is possible, especially
-since the reviewer agrees that (as long as confidence intervals are used
-to calculate the SGPV, which we now clearly limit our conclusions to)
-\enquote{The maximum Type I Error rate for the SGPV over the null
-interval is 5\%, exactly like the TOST test}.
-
-Nevertheless, we agree this discussion was a bit too extensive. Given my
-own fondness of error control in statistical inferences, I get worried
-if researchers suggest we can ignore it, especially when making multiple
-comparisons. Imagine people start to use the SGPV instead of the TOST
-procedure whenever they perform 20 tests, and then argue they do not
-need to correct for multiple comparison - I think we can all agree this
-is undesireable! We have reduced the two paragraphs to one hopefully
-clear statement about the need to control error rates, also when using
-the SGPV. We hope this addresses the concerns by the editor as well as
-the reviewer, while still making an important point in the literature
-about the need to control error rates (if one cares about drawing
-incorrect conclusions).
-
-Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
-\enquote{Adjustments for multiple comparisons are obviated} (p.~15).
-However, this is not correct. Given the direct relationship between TOST
-and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025
-equals SGPV = 1, as long as the SGPV is calculated based on confidence
-intervals, and assuming continuous and normally distributed data), not
-correcting for multiple comparisons will inflate the probability of
-concluding the absence of a meaningful effect based on the SGPV in
-exactly the same way as for equivalence tests. Whenever statistical
-tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or
-SGPV =1), it is possible do so erroneously, and if researchers want to
-control error rates, they need to correct for multiple comparisons.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{5}
-\item
-  We have removed this section while addressing point 5 above, and thus
-  incorporated the reviewers'suggestion to remove these statements.
-\item
-  We have not removed the paragraph about multiple comparisons, as the
-  reviewer asks, but we have simplified our treatment of it. We do not
-  need any other argument to make our claims about multiple comparisons
-  that fact, noted by the reviewer, that \enquote{The maximum Type I
-  Error rate for the SGPV over the null interval is 5\%, exactly like
-  the TOST test.} This is true, and it logically follows (hence, no
-  mathematical proof is needed) that error rates need to be controlled
-  when using SGPV to conclude support for the null-hypothesis. We
-  believe error control is important enough to include this paragraph in
-  the paper, as we believe that lack of error control was one of the
-  causes of the replication crisis in psychology.
-\item
-  We thank the reviewer for this comment. Indeed, to calculate
-  confidence intervals around a correlation, the Fisher's
-  z-transformation is used, which is approximately normally distributed,
-  and symmatric CI are calculated. When transforming these confidence
-  intervals back to correlations, they become asymmetric. We have added
-  to the text: \enquote{Note that calculating confidence intervals for a
-  correlation involves a Fisher's z-transformation, which transforms
-  values such that they are approximately normally distributed, which
-  allows one to compute symmetric confidence intervals, which are then
-  retransformed into a correlation, where the confidence intervals are
-  asymmetric if the correlation is not exactly zero.} This is simply one
-  example of a general effect mentioned in Blume et al (2018), which we
-  already cited in the main text: \enquote{The magnitude of an
-  inconclusive second-generation \emph{p}-value can vary slightly when
-  the effect size scale is transformed. However definitive findings,
-  i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
-  changes.}
-\end{enumerate}
-
-Minor Concerns:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  We added \enquote{,or more extreme data,}
-\item
-  This text was deleted (see major point 5 above)
-\item
-  We see how \enquote{reverse the SGPV} might have been confusing. We
-  did not mean to imply to reverse the null and alternative. We now just
-  say that we plot 1-SGPV (which is what we incorrectly tried to express
-  with \enquote{reverse}).
-\item
-  The issue of the SGPV needing a \enquote{correction} by setting it to
-  0.5 is not related to the fact that large \emph{p}-values are not
-  evidence for the null. The \emph{p}-value is behaving as it is
-  intended to, without any correction. A high \emph{p}-value is not a
-  \enquote{misleading result} - although it can be misinterpreted (which
-  is exactly what we try to prevent with our work on equivalence
-  testing). We therefore did not incorporate this point.
-\item
-  In line with comments by reviewer 1, we removed statemetns about SGPV
-  not being inferential, thereby solving the issue reviewer 2 raised.
-\item
-  In line with major point 8, we added information that asymmetric
-  confidence intervals around a correlation are symmetric when Fisher
-  z-transformed. This is just an example of what Blume et al (2018)
-  refer to when they write \enquote{The magnitude of an inconclusive
-  second-generation \emph{p}-value can vary slightly when the effect
-  size scale is transformed. However definitive findings, i.e.~a
-  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
-  changes.} We believe this section, although the most detailed, is
-  interesting, even only for more expert readers (indeed, Reviewer 1
-  notes that \enquote{The asymmetric CI case is very interesting}). We
-  have made our point less general, now only talking about correlations,
-  by changing the title of this section into \enquote{The relation
-  between equivalence tests and SGPV for asymmetrical confidence
-  intervals around correlations}. The reviewer is correct confidence
-  intervals can be created in many difference ways (e.g., with holes in
-  the middle), but for this paper, we just focus on one specific case
-  now, which we believe might be closest to what researchers would use
-  in real life, the confidence interval around a correlation.
-\item
-  It is a well-known fact that the TOST can have 0 power (and indeed,
-  this is one of the main issues in the Perlman and Wu (1999) paper the
-  reviewer cited). As explained in Lakens (2017): \enquote{It is
-  important to take statistical power into account when determining the
-  equivalence bounds because, in small samples (where CIs are wide), a
-  study might have no statistical power (i.e., the CI will always be so
-  wide that it is necessarily wider than the equivalence bounds).} We
-  agree with the reviewer it is not interesting to do a test if you have
-  0 power. People should design informative experiments by doing an
-  a-priori power analysis. Any problem in this respect is not a problem
-  with equivalence tests, but a problem with designing a bad study. Note
-  that the exact same issue applies to the SGPV. It is also possible to
-  have 0 power for the SGPV - so we do not understand why the reviewer
-  is so surprised about this. The question \enquote{Why use the TOST
-  test then?} equally applies to \enquote{Why use the SGPV then?} if
-  you, from the outset, know that the \enquote{small sample correction}
-  will lead to a SGPV of 0.5.
-\item
-  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an
-  estimate to some value. Regardless of how correction factors are
-  applied in statistics, we are trying to educate our readers about what
-  the \enquote{small sample correction} does. We believe our readers
-  will associate \enquote{correction} with \enquote{correcting}, and
-  want to explain that the SGPV is not set to a \enquote{correct} value.
-  We are not talking about statistical terms here - we are warning the
-  reader to not interpret \enquote{correction} in terms of normal
-  language use. This is similar to warning readers that
-  \enquote{significant} does not have the normal language connotation of
-  \enquote{important}. We have therefore kept our original sentence.
-\end{enumerate}
-
-As a final comment, altough not explicitly listed as a major point of
-minor point, we are happy to respond to the reviewers' suggestion that
-Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
-best summary of this discussion (of which Perlman \& Wu is one
-contribution) can be found in Meyners (2012), which we cited. The
-discussion has different arguments, and Meyners draws the conclusion
-that there is no universially preferred approach. The power benefits of
-alternative approaches are typically modest, or only noticeable in
-situations where all alternatives are underpowered. The power issue is
-not that important - the main discussion is about whether equivalence
-tests should have a bounded rejection region, like TOST, or an unbounded
-rejection region. It might be useful to note that TOST and SGPV are
-similar in this respect - both have bounded rejection regions, and if
-the reviewer agrees with Perlman and Wu (1999) in the criticism against
-TOST, the same criticism applies to the SGPV. If the reviewer reads
-Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
-an argument to ban the SGPV. We agree with Meyners, who writes:
-\enquote{The debate has been quite heated in times; this section intends
-to give a brief overview of the debate. We would like to emphasize again
-that the differences between the approaches are minor and to a large
-extent of academic interest only, as is this debate.} and concludes:
-\enquote{To summarize, there is no right or wrong in most of the
-arguments; the two opposing parties rather apply different criteria to
-select the most appropriate test, one group focusing rather on
-mathematical/statistical criteria, the other one more on
-interpretability and reasonability.} We have added a reference to this
-discussion for the interested reader, and added \enquote{For an
-excellent discussion of the strengths and weaknesses of different
-frequentist equivalence tests, including alternatives to the TOST
-procedure, see Meyners, 2012.}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-blume_second-generation_2018}{}
-Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
-(2018). Second-generation p-values: Improved rigor, reproducibility, \&
-transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
-e0188299.
-doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}
+\leavevmode\hypertarget{ref-goertzen_detecting_2010}{}%
+Goertzen, J.
+R., \& Cribbie, R.
+A.
+(2010).
+Detecting a lack of association: An equivalence testing approach.
+\emph{British Journal of Mathematical and Statistical Psychology}, \emph{63}(3), 527--537.
+doi:\href{https://doi.org/10.1348/000711009X475853}{10.1348/000711009X475853}
 

### 2019-04-22 manuscript.R2.Rmd
reply to reviews 2

--- 2019-03-10 manuscript.R1.Rmd
@@
 
-#The relationship between *p*-values from TOST and SGPV when confidence intervals are symmetrical
+# The relationship between *p*-values from TOST and SGPV when confidence intervals are symmetrical
 
@@
 
-##SGPV as a uniform measure of overlap
+## SGPV as a uniform measure of overlap
 
@@
 
-##When different *p*-values for equivalence tests yield the same SGPV
+## When different *p*-values for equivalence tests yield the same SGPV
 
@@
      xlab = "SGPV")
+
 ```
@@
 
-##The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations
+## The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations
 
@@
 The confidence interval for a correlation becomes increasingly asymmetric as the observed correlation nears -1 or 1.
-For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from -0.630 to 0.630, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from 0.126 to 0.993.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from `r round(TOSTr(r = 0, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$LL_CI_TTEST,3)` to `r round(TOSTr(r = 0, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$UL_CI_TTEST,3)`, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from `r round(TOSTr(r = 0.7, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$LL_CI_TTEST,3)` to `r round(TOSTr(r = 0.7, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$UL_CI_TTEST,3)`.
 Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally z-distributed, which allows one to compute symmetric confidence intervals.
@@
 high_eqbound_r = 0.45
-res<-TOSTr(n = 30,
+res_1<-TOSTr(n = 30,
            r = 0.45,
@@
            verbose = FALSE)
-sgpv <- p_delta(res$LL_CI_TTEST,res$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
-```
-
-The reason that the equivalence test and SGPV no longer overlap is also because of asymmetric confidence intervals.
-If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test indicates that the probability of observing the observed or more extreme data, assuming the equivalence bound is the true effect size, is 50%.
-In other words, if the true effect size is the same as the equivalence bound, it is equally likely to find an effect more extreme than the equivalence bound, as it is to observe an effect that is less extreme than the equivalence bound.
-However, as can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at *r* = -0.45 and *r* = 0.45 are larger than 50%.
-Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise.
+sgpv <- p_delta(res_1$LL_CI_TTEST,res_1$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+
+low_eqbound_r = -0.99
+high_eqbound_r = 0.99
+res_2<-TOSTr(n = 4,
+           r = 0.99,
+           low_eqbound_r = low_eqbound_r,
+           high_eqbound_r = high_eqbound_r,
+           alpha = .05,
+           plot = FALSE,
+           verbose = FALSE)
+sgpv2 <- p_delta(res_2$LL_CI_TTEST,res_2$UL_CI_TTEST, low_eqbound_r, high_eqbound_r)
+
+```
+
+The reason that the equivalence test and SGPV no longer overlap is due to asymmetric confidence intervals.
+If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test is 0.5.
+In the equivalence test for correlations the *p* value is computed based on a z-transformation which better controls error rates [@goertzen_detecting_2010].
+This transformation is computed as follows, where  *r* is the observed correlation and $\rho$ is the theoretical correlation under the null:
+
+$$
+z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
+$$
+
+Because the z-distribution is symmetric, the probability of observing the observed or more extreme z-score, assuming the equivalence bound is the true effect size, is 50%.
+However, because the *r* distribution is not symmetric, this does not mean that there is always a 50% probability of observing a correlation smaller or larger than the true correlation.
+As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at *r* = -0.45 and *r* = 0.45 are larger than 50%.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res_1$LL_CI_TTEST,2)` to `r round(res_1$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv*100,3)`% of the data-supported hypotheses are compatible with the null premise.
 
@@
 The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 36% of the correlations observed in the future will fall in this range.
+
 It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a *p*-value answers.
@@
 
-##What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
+## What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?
 
@@
 
-#Conclusion
+# Conclusion
 

### 2019-04-22 manuscript.R2.tex
reply to reviews 2

--- 2019-03-10 manuscript.R1.tex
@@
             pdfauthor={Daniël Lakens~\& Marie Delacre},
-            pdfkeywords={equivalence testing, second generation p-values, hypothesis testing,
-TOST, statistical inference},
+            pdfkeywords={equivalence testing, second generation p-values, hypothesis testing, TOST, statistical inference},
             pdfborder={0 0 0},
@@
 
-\authornote{All code associated with this article, including
-the reproducible manuscript, is available from
-\url{https://github.com/Lakens/TOST_vs_SGPV}. This work was supported by
-the Netherlands Organization for Scientific Research (NWO) VIDI grant
-452-17-013.
+\authornote{All code associated with this article, including the reproducible manuscript, is available from \url{https://github.com/Lakens/TOST_vs_SGPV} and \url{https://osf.io/8crkg/}.
+The preprint can be found at \url{https://psyarxiv.com/7k6ay/}.
+This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
 
-Correspondence concerning this article should be addressed to Daniël
-Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
-E-mail:
-\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
+E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
 \abstract{
-To move beyond the limitations of null-hypothesis tests, statistical
-approaches have been developed where the observed data are compared
-against a range of values that are equivalent to the absence of a
-meaningful effect. Specifying a range of values around zero allows
-researchers to statistically reject the presence of effects large enough
-to matter, and prevents practically insignificant effects from being
-interpreted as a statistically significant difference. We compare the
-behavior of the recently proposed second generation \emph{p}-value
-(Blume, D'Agostino McGowan, Dupont, \& Greevy, 2018) with the more
-established Two One-Sided Tests (TOST) equivalence testing procedure
-(Schuirmann, 1987). We show that the two approaches yield almost
-identical results under optimal conditions. Under suboptimal conditions
-(e.g., when the confidence interval is wider than the equivalence range,
-or when confidence intervals are asymmetric) the second generation
-\emph{p}-value becomes difficult to interpret. The second generation
-\emph{p}-value is interpretable in a dichotomous manner (i.e., when the
-SGPV equals 0 or 1 because the confidence intervals lies completely
-within or outside of the equivalence range), but this dichotomous
-interpretation does not require calculations. We conclude that
-equivalence tests yield more consistent \emph{p}-values, distinguish
-between datasets that yield the same second generation \emph{p}-value,
-and allow for easier control of Type I and Type II error rates.
+To move beyond the limitations of null-hypothesis tests, statistical approaches have been developed where the observed data are compared against a range of values that are equivalent to the absence of a meaningful effect.
+Specifying a range of values around zero allows researchers to statistically reject the presence of effects large enough to matter, and prevents practically insignificant effects from being interpreted as a statistically significant difference.
+We compare the behavior of the recently proposed second generation \emph{p}-value (Blume, D'Agostino McGowan, Dupont, \& Greevy, 2018) with the more established Two One-Sided Tests (TOST) equivalence testing procedure (Schuirmann, 1987).
+We show that the two approaches yield almost identical results under optimal conditions.
+Under suboptimal conditions (e.g., when the confidence interval is wider than the equivalence range, or when confidence intervals are asymmetric) the second generation \emph{p}-value becomes difficult to interpret.
+The second generation \emph{p}-value is interpretable in a dichotomous manner (i.e., when the SGPV equals 0 or 1 because the confidence intervals lies completely within or outside of the equivalence range), but this dichotomous interpretation does not require calculations.
+We conclude that equivalence tests yield more consistent \emph{p}-values, distinguish between datasets that yield the same second generation \emph{p}-value, and allow for easier control of Type I and Type II error rates.
 
@@
 
-To test predictions researchers predominantly rely on null-hypothesis
-tests. This statistical approach can be used to examine whether observed
-data are sufficiently surprising under the null hypothesis to reject an
-effect that equals exactly zero. Null-hypothesis tests have an important
-limitation, in that this procedure can only reject the hypothesis that
-there is no effect, while scientists should also be able to provide
-statistical support for \emph{equivalence}. When testing for equivalence
-researchers aim to examine whether an observed effect is too small to be
-considered meaningful, and therefore is practically equivalent to zero.
-By specifying a range around the null hypothesis of values that are
-deemed practically equivalent to the absence of an effect (i.e., 0 ±
-0.3) the observed data can be compared against an \emph{equivalence
-range} and researchers can test if a meaningful effect is absent (Hauck
-\& Anderson, 1984; Kruschke, 2018; Rogers, Howard, \& Vessey, 1993;
-Serlin \& Lapsley, 1985; Spiegelhalter, Freedman, \& Parmar, 1994;
-Wellek, 2010; Westlake, 1972).
+To test predictions researchers predominantly rely on null-hypothesis tests.
+This statistical approach can be used to examine whether observed data are sufficiently surprising under the null hypothesis to reject an effect that equals exactly zero.
+Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for \emph{equivalence}.
+When testing for equivalence researchers aim to examine whether an observed effect is too small to be considered meaningful, and therefore is practically equivalent to zero.
+By specifying a range around the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an \emph{equivalence range} and researchers can test if a meaningful effect is absent (Hauck \& Anderson, 1984; Kruschke, 2018; Rogers, Howard, \& Vessey, 1993; Serlin \& Lapsley, 1985; Spiegelhalter, Freedman, \& Parmar, 1994; Wellek, 2010; Westlake, 1972).
 
-Second generation \emph{p}-values (SGPV) were recently proposed as a
-statistic that represents \enquote{the proportion of data-supported
-hypotheses that are also null hypotheses} (Blume et al., 2018). The
-researcher specifies an equivalence range around a null hypothesis of
-values that are considered practically equivalent to the null
-hypothesis. The SGPV measures the degree to which a set of
-data-supported parameter values falls within the interval null
-hypothesis. If the estimation interval falls completely within the
-equivalence range, the SGPV is 1. If the confidence interval falls
-completely outside of the equivalence range, the SGPV is 0. Otherwise
-the SGPV is a value between 0 and 1 that expresses the overlap of
-data-supported hypotheses and the equivalence range. When calculating
-the SGPV the set of data-supported parameter values can be represented
-by a confidence interval (CI), although one could also choose to use
-credible intervals or Likelihood support intervals (SI). When a
-confidence interval is used, the SGPV and equivalence tests such as the
-Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012;
-Quertemont, 2011; Schuirmann, 1987) appear to have close ties, because
-both tests compare a confidence interval against an equivalence range.
-Here, we aim to examine the similarities and differences between the
-TOST procedure and the SGPV. We limit our analysis to continuous data
-sampled from a bivariate normal distribution.
+Second generation \emph{p}-values (SGPV) were recently proposed as a statistic that represents \enquote{the proportion of data-supported hypotheses that are also null hypotheses} (Blume et al., 2018).
+The researcher specifies an equivalence range around a null hypothesis of values that are considered practically equivalent to the null hypothesis.
+The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis.
+If the estimation interval falls completely within the equivalence range, the SGPV is 1.
+If the confidence interval falls completely outside of the equivalence range, the SGPV is 0.
+Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range.
+When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI), although one could also choose to use credible intervals or Likelihood support intervals (SI).
+When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012; Quertemont, 2011; Schuirmann, 1987) appear to have close ties, because both tests compare a confidence interval against an equivalence range.
+Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.
+We limit our analysis to continuous data sampled from a bivariate normal distribution.
 
-The TOST procedure also relies on the confidence interval around the
-effect. In the TOST procedure the data are tested against the lower
-equivalence bound in the first one-sided test, and against the upper
-equivalence bound in the second one-sided test (Lakens, Scheel, \&
-Isager, 2018). For an excellent discussion of the strengths and
-weaknesses of different frequentist equivalence tests, including
-alternatives to the TOST procedure, see Meyners (2012). If both tests
-statistically reject an effect as extreme or more extreme than the
-equivalence bound, you can conclude the observed effect is practically
-equivalent to zero from a Neyman-Pearson approach to statistical
-inferences. Because one-sided tests are performed, one can also conclude
-equivalence by checking whether the 1-2\(\times\)\(\alpha\) confidence
-interval (e.g., when the alpha level is 0.05, a 90\% CI) falls
-completely within the equivalence bounds. Because both equivalence tests
-as the SGPV are based on whether and how much a confidence interval
-overlaps with equivalence bounds, it seems worthwhile to compare the
-behavior of the newly proposed SGPV to equivalence tests to examine the
-unique contribution of the SGPV to the statistical toolbox.
+The TOST procedure also relies on the confidence interval around the effect.
+In the TOST procedure the data are tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test (Lakens, Scheel, \& Isager, 2018).
+For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see Meyners (2012).
+If both tests statistically reject an effect as extreme or more extreme than the equivalence bound, you can conclude the observed effect is practically equivalent to zero from a Neyman-Pearson approach to statistical inferences.
+Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2\(\times\)\(\alpha\) confidence interval (e.g., when the alpha level is 0.05, a 90\% CI) falls completely within the equivalence bounds.
+Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems worthwhile to compare the behavior of the newly proposed SGPV to equivalence tests to examine the unique contribution of the SGPV to the statistical toolbox.
 
-\section{\texorpdfstring{The relationship between \emph{p}-values from
-TOST and SGPV when confidence intervals are
-symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}
+\hypertarget{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}{%
+\section{\texorpdfstring{The relationship between \emph{p}-values from TOST and SGPV when confidence intervals are symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}}
 
-The second generation \emph{p}-value (SGPV) is calculated as: \[
+The second generation \emph{p}-value (SGPV) is calculated as:
+\[
   p _ { \delta } = \frac { \left| I \cap H _ { 0 } \right| } { | I | } \times \max \left\{ \frac { | I | } { 2 \left| H _ { 0 } \right| } , 1 \right\}
-\] where I is the interval based on the data (e.g., a 95\% confidence
-interval) and H\textsubscript{0} is the equivalence range. The first
-term of this formula implies that the second generation \emph{p}-value
-is the width of the confidence interval that overlaps with the
-equivalence range, divided by the total width of the confidence
-interval. The second term is a \enquote{small sample correction} (which
-will be discussed later) that comes into play whenever the confidence
-interval is more than twice as wide as the equivalence range. To examine
-the relation between the TOST \emph{p}-value and the SGPV we can
-calculate both statistics across a range of observed effect sizes.
-Replicating the example by Blume et al. (2018), in Figure
-\ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST procedure
-and the SGPV. The statistics are calculated for hypothetical one-sample
-\emph{t}-tests for observed means ranging from 140 to 150 (on the
-x-axis). The equivalence range is set to 145 ± 2 (i.e., an equivalence
-range from 143 to 147), the observed standard deviation is assumed to be
-2, and the sample size is 30. For example, for the left-most point in
-Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST \emph{p}-value is
-calculated for a hypothetical study with a sample size of 30, an
-observed standard deviation of 2, and an observed mean of 140, where the
-\emph{p}-value for the equivalence test is 1, and the SGPV is 0.
+\]
+where I is the interval based on the data (e.g., a 95\% confidence interval) and H\textsubscript{0} is the equivalence range.
+The first term of this formula implies that the second generation \emph{p}-value is the width of the confidence interval that overlaps with the equivalence range, divided by the total width of the confidence interval.
+The second term is a \enquote{small sample correction} (which will be discussed later) that comes into play whenever the confidence interval is more than twice as wide as the equivalence range.
+To examine the relation between the TOST \emph{p}-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
+Replicating the example by Blume et al.
+(2018), in Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST procedure and the SGPV.
+The statistics are calculated for hypothetical one-sample \emph{t}-tests for observed means ranging from 140 to 150 (on the x-axis).
+The equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), the observed standard deviation is assumed to be 2, and the sample size is 30.
+For example, for the left-most point in Figure \ref{fig:TOSTSGPV1} the SGPV and the TOST \emph{p}-value is calculated for a hypothetical study with a sample size of 30, an observed standard deviation of 2, and an observed mean of 140, where the \emph{p}-value for the equivalence test is 1, and the SGPV is 0.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV1-1.pdf}
-\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (grey line) across a range of observed sample means
-(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
-a sample size of 30 and a standard deviation of 2, illustrating that
-when the TOST \emph{p}-value = 0.5, the SGPV = 0.5, when the TOST
-\emph{p}-value is 0.975, 1-SGPV = 1, and when the TOST \emph{p}-value =
-0.025, 1-SGPV = 0.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV1-1.pdf}
+\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2, illustrating that when the TOST \emph{p}-value = 0.5, the SGPV = 0.5, when the TOST \emph{p}-value is 0.975, 1-SGPV = 1, and when the TOST \emph{p}-value = 0.025, 1-SGPV = 0.}
 \end{figure}
 
-Our conclusions about the relationship between TOST \emph{p}-values and
-SGPV hold for second generation \emph{p}-values calculated from
-confidence intervals, and assuming data is sampled from a bivariate
-normal distribution. Readers can explore the relationship between TOST
-\emph{p}-values and SGPV for themselves in an online Shiny app:
-\url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
+Our conclusions about the relationship between TOST \emph{p}-values and SGPV hold for second generation \emph{p}-values calculated from confidence intervals, and assuming data is sampled from a bivariate normal distribution.
+Readers can explore the relationship between TOST \emph{p}-values and SGPV for themselves in an online Shiny app: \url{http://shiny.ieis.tue.nl/TOST_vs_SGPV/}.
 
-The SGPV treats the equivalence range as the null-hypothesis, while the
-TOST procedure treats the values outside of the equivalence range as the
-null-hypothesis. For ease of comparison we can plot 1-SGPV (see Figure
-\ref{fig:TOSTSGPV2}) to make the values more easily comparable. We see
-that the \emph{p}-value from the TOST procedure and the SGPV follow each
-other closely. When we discuss the relationship between the
-\emph{p}-values from TOST and the SGPV, we focus on their correspondence
-at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1,
-where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST
-\emph{p} = 0.975 and SGPV = 1. These three values are important for the
-SGPV because they indicate the values at which the SGPV indicates the
-data should be interpreted as compatible with the null hypothesis (SGPV
-= 1), or with the alternative hypothesis (SGPV = 0), or when the data
-are strictly inconclusive (SGPV = 0.5). These three points of overlap
-are indicated by the horizontal dotted lines in Figure
-\ref{fig:TOSTSGPV2} at TOST \emph{p}-values of 0.975, 0.5, and 0.025.
+The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis.
+For ease of comparison we can plot 1-SGPV (see Figure \ref{fig:TOSTSGPV2}) to make the values more easily comparable.
+We see that the \emph{p}-value from the TOST procedure and the SGPV follow each other closely.
+When we discuss the relationship between the \emph{p}-values from TOST and the SGPV, we focus on their correspondence at three values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
+These three values are important for the SGPV because they indicate the values at which the SGPV indicates the data should be interpreted as compatible with the null hypothesis (SGPV = 1), or with the alternative hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV = 0.5).
+These three points of overlap are indicated by the horizontal dotted lines in Figure \ref{fig:TOSTSGPV2} at TOST \emph{p}-values of 0.975, 0.5, and 0.025.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV2-1.pdf}
-\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
-line) and 1-SGPV (grey line) across a range of observed sample means
-(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
-a sample size of 30 and a standard deviation of 2.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV2-1.pdf}
+\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2.}
 \end{figure}
 
-When the observed sample mean is 145, the sample size is 30, and the
-standard deviation is 2, and we are testing against equivalence bounds
-of 143 and 147 using the TOST procedure for a one-sample \emph{t}-test,
-the equivalence test is significant, \emph{t}(29) = 5.48, \emph{p}
-\textless{} .001. Because the 95\% CI falls completely within the
-equivalence bounds, the SGPV is 1 (see Figure \ref{fig:TOSTSGPV1}). On
-the other hand, when the observed mean is 140, the equivalence test is
-not significant (the observed mean is far outside the equivalence range
-of 143 to 147), \emph{t}(29) = -8.22, \emph{p} = 1 (or more accurately,
-\emph{p} \textgreater{} .999 as \emph{p}-values are bounded between 0
-and 1). Because the 95\% CI falls completely outside the equivalence
-bounds, the SGPV is 0 (see Figure \ref{fig:TOSTSGPV1}).
+When the observed sample mean is 145, the sample size is 30, and the standard deviation is 2, and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample \emph{t}-test, the equivalence test is significant, \emph{t}(29) = 5.48, \emph{p} \textless{} .001.
+Because the 95\% CI falls completely within the equivalence bounds, the SGPV is 1 (see Figure \ref{fig:TOSTSGPV1}).
+On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), \emph{t}(29) = -8.22, \emph{p} = 1 (or more accurately, \emph{p} \textgreater{} .999 as \emph{p}-values are bounded between 0 and 1).
+Because the 95\% CI falls completely outside the equivalence bounds, the SGPV is 0 (see Figure \ref{fig:TOSTSGPV1}).
 
-\subsection{SGPV as a uniform measure of
-overlap}\label{sgpv-as-a-uniform-measure-of-overlap}
+\hypertarget{sgpv-as-a-uniform-measure-of-overlap}{%
+\subsection{SGPV as a uniform measure of overlap}\label{sgpv-as-a-uniform-measure-of-overlap}}
 
-It is clear the SGPV and the \emph{p}-value from TOST are closely
-related. When confidence intervals are symmetric we can think of the
-SGPV as a straight line that is directly related to the \emph{p}-value
-from an equivalence test for three values. When the TOST \emph{p}-value
-is 0.5, the SGPV is also 0.5 (note that the reverse is not true). The
-SGPV is 50\% when the observed mean falls exactly on the lower or upper
-equivalence bound, because 50\% of the symmetrical confidence interval
-overlaps with the equivalence range. When the observed mean equals the
-equivalence bound, the difference between the mean in the data and the
-equivalence bound is 0, the \emph{t}-value for the equivalence test is
-also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure
-\ref{fig:TOSTSGPV3}).
+It is clear the SGPV and the \emph{p}-value from TOST are closely related.
+When confidence intervals are symmetric we can think of the SGPV as a straight line that is directly related to the \emph{p}-value from an equivalence test for three values.
+When the TOST \emph{p}-value is 0.5, the SGPV is also 0.5 (note that the reverse is not true).
+The SGPV is 50\% when the observed mean falls exactly on the lower or upper equivalence bound, because 50\% of the symmetrical confidence interval overlaps with the equivalence range.
+When the observed mean equals the equivalence bound, the difference between the mean in the data and the equivalence bound is 0, the \emph{t}-value for the equivalence test is also 0, and thus the \emph{p}-value is 0.5 (situation A, Figure \ref{fig:TOSTSGPV3}).
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV3-1.pdf}
-\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for
-three example datasets that illustrate the relationship between
-\emph{p}-values from TOST and SGPV.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV3-1.pdf}
+\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for three example datasets that illustrate the relationship between \emph{p}-values from TOST and SGPV.}
 \end{figure}
 
-Two other points always have to overlap. When the 95\% CI falls
-completely inside the equivalence region, and one endpoint of the
-confidence interval is exactly equal to one of the equivalence bounds
-(see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value
-(which relies on a one-sided test) is always 0.025, and the SGPV is 1.
-Note that when sample sizes are small or equivalence bounds are narrow,
-small \emph{p}-values for the TOST or a SGPV = 1 might not be observed
-in practice if too few observations are collected. The third point where
-the SGPV and the \emph{p}-value from the TOST procedure should overlap
-is where the 95\% CI falls completely outside of the equivalence range,
-but one endpoint of the confidence interval is equal to the equivalence
-bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the
-\emph{p}-value will always be 0.975, and the SGPV is 0. Note that this
-situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
-2014). The goal of a minimum-effect is not just to reject a difference
-of zero, but to reject the smallest effect size of interest (i.e., the
-equivalence bounds). An equivalence test and minimum effect test against
-the same equivalence bound are complementary, and when a TOST
-\emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum
-effect test is smaller than 0.05 (and therefore the minimum effect test
-provides no additional information that can not be derived from the
-\emph{p}-value from the equivalence test). The SGPV summarizes the
-information from an equivalence test (and the complementary
-minimum-effect test). These can be two relevant questions to ask,
-although it often makes sense to combine an equivalence test and a
-null-hypothesis test instead (Lakens et al., 2018).
+Two other points always have to overlap.
+When the 95\% CI falls completely inside the equivalence region, and one endpoint of the confidence interval is exactly equal to one of the equivalence bounds (see situation B in Figure \ref{fig:TOSTSGPV3}) the TOST \emph{p}-value (which relies on a one-sided test) is always 0.025, and the SGPV is 1.
+Note that when sample sizes are small or equivalence bounds are narrow, small \emph{p}-values for the TOST or a SGPV = 1 might not be observed in practice if too few observations are collected.
+The third point where the SGPV and the \emph{p}-value from the TOST procedure should overlap is where the 95\% CI falls completely outside of the equivalence range, but one endpoint of the confidence interval is equal to the equivalence bound (see situation C in Figure \ref{fig:TOSTSGPV3}), when the \emph{p}-value will always be 0.975, and the SGPV is 0.
+Note that this situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach, 2014).
+The goal of a minimum-effect is not just to reject a difference of zero, but to reject the smallest effect size of interest (i.e., the equivalence bounds).
+An equivalence test and minimum effect test against the same equivalence bound are complementary, and when a TOST \emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum effect test is smaller than 0.05 (and therefore the minimum effect test provides no additional information that can not be derived from the \emph{p}-value from the equivalence test).
+The SGPV summarizes the information from an equivalence test (and the complementary minimum-effect test).
+These can be two relevant questions to ask, although it often makes sense to combine an equivalence test and a null-hypothesis test instead (Lakens et al., 2018).
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV4-1.pdf}
-\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for
-samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV4-1.pdf}
+\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
 \end{figure}
@@
 For example, in Figure \ref{fig:TOSTSGPV4} we have plotted four SGPV's.
-From A to D the SGPV is 0.76, 0.81, 0.86, and 0.91. The difference in
-the percentage of overlap between A and B (-0.05) is identical to the
-difference in the percentage of overlap between C and D as the mean gets
-0.1 closer to the test value (-0.05). As the observed mean in a
-one-sample \emph{t}-test lies closer to the test value, from situation A
-to D, the difference in the overlap changes uniformly. As we move the
-observed mean closer to the test value in steps of 0.1 across A to D the
-\emph{p}-value calculated for normally distributed data are not
-uniformly distributed. The probability of observing data more extreme
-than the upper bound of 2 is (from A to D) 0.16, 0.12, 0.08, and 0.05.
-As we can see, the difference between A and B (0.04) is not the same as
-the difference between C and D (0.03). Indeed, the difference in
-\emph{p}-values is the largest as you start at \emph{p} = 0.5 (when the
-observed mean falls on the test value), which is why the line in Figure
-\ref{fig:TOSTSGPV1} is the steepest at \emph{p} = 0.5. Note that where
-the SGPV reaches 1 or 0, \emph{p}-values closely approximate 0 and 1,
-but never reach these values.
+From A to D the SGPV is 0.76, 0.81, 0.86, and 0.91.
+The difference in the percentage of overlap between A and B (-0.05) is identical to the difference in the percentage of overlap between C and D as the mean gets 0.1 closer to the test value (-0.05).
+As the observed mean in a one-sample \emph{t}-test lies closer to the test value, from situation A to D, the difference in the overlap changes uniformly.
+As we move the observed mean closer to the test value in steps of 0.1 across A to D the \emph{p}-value calculated for normally distributed data are not uniformly distributed.
+The probability of observing data more extreme than the upper bound of 2 is (from A to D) 0.16, 0.12, 0.08, and 0.05.
+As we can see, the difference between A and B (0.04) is not the same as the difference between C and D (0.03).
+Indeed, the difference in \emph{p}-values is the largest as you start at \emph{p} = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at \emph{p} = 0.5.
+Note that where the SGPV reaches 1 or 0, \emph{p}-values closely approximate 0 and 1, but never reach these values.
 
-\subsection{\texorpdfstring{When different \emph{p}-values for
-equivalence tests yield the same
-SGPV}{When different p-values for equivalence tests yield the same SGPV}}\label{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}
+\hypertarget{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}{%
+\subsection{\texorpdfstring{When different \emph{p}-values for equivalence tests yield the same SGPV}{When different p-values for equivalence tests yield the same SGPV}}\label{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}}
 
-There are three situations where \emph{p}-values for TOST differentiate
-between observed results, while the SGPV does not differentiate. The
-first two situations were discussed before and can be seen in Figure
-\ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1, \emph{p}-values
-from the equivalence test fall between 0.975 and 1 or between 0 and
-0.025. Where the SGPV is 1 as long as the confidence interval falls
-completely within the equivalence bounds, the \emph{p}-value for the
-TOST continues to differentiate between results as a function of how far
-the confidence interval lies within the equivalence bounds (the further
-the confidence interval is from both bounds, the lower the
-\emph{p}-value). The easiest way to see this is by plotting the SGPV
-against the \emph{p}-value from the TOST procedure. The situations where
-the \emph{p}-values from the TOST procedure continue to differentiate
-based on how extreme the results are, but the SGPV is a fixed value are
-indicated by the parts of the curve where there are vertical straight
-lines at second generation \emph{p}-values of 0 and 1.
+There are three situations where \emph{p}-values for TOST differentiate between observed results, while the SGPV does not differentiate.
+The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}.
+When the SGPV is either 0 or 1, \emph{p}-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025.
+Where the SGPV is 1 as long as the confidence interval falls completely within the equivalence bounds, the \emph{p}-value for the TOST continues to differentiate between results as a function of how far the confidence interval lies within the equivalence bounds (the further the confidence interval is from both bounds, the lower the \emph{p}-value).
+The easiest way to see this is by plotting the SGPV against the \emph{p}-value from the TOST procedure.
+The situations where the \emph{p}-values from the TOST procedure continue to differentiate based on how extreme the results are, but the SGPV is a fixed value are indicated by the parts of the curve where there are vertical straight lines at second generation \emph{p}-values of 0 and 1.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV5-1.pdf}
-\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV1}.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV5-1.pdf}
+\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV1}.}
 \end{figure}
 
-A third situation in which the SGPV remains stable across a range of
-observed effects, while the TOST \emph{p}-value continues to
-differentiate, is whenever the CI is wider than the equivalence range,
-and the CI overlaps with the upper \emph{and} lower equivalence bound.
-When the confidence interval is more than twice as wide as the
-equivalence range the SGPV is set to 0.5. Blume et al. (2018) call this
-the \enquote{small sample correction factor}. However, it is not a
-correction in the typical sense of the word, since the SGPV is not
-adjusted to any \enquote{correct} value. When the normal calculation
-would be \enquote{misleading} (i.e., the SGPV would be small, which
-normally would suggest support for the alternative hypothesis, but at
-the same time all values in the equivalence range are supported), the
-SGPV is set to 0.5 which according to Blume and colleagues signals that
-the SGPV is \enquote{uninformative}. Note that the CI can be twice as
-wide as the equivalence range whenever the sample size is small (and the
-confidence interval width is large) \emph{or} when then equivalence
-range is narrow. It is therefore not so much a \enquote{small sample
-correction} as it is an exception to the typical calculation of the SGPV
-whenever the ratio of the confidence interval width to the equivalence
-range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+A third situation in which the SGPV remains stable across a range of observed effects, while the TOST \emph{p}-value continues to differentiate, is whenever the CI is wider than the equivalence range, and the CI overlaps with the upper \emph{and} lower equivalence bound.
+When the confidence interval is more than twice as wide as the equivalence range the SGPV is set to 0.5.
+Blume et al.
+(2018) call this the \enquote{small sample correction factor}.
+However, it is not a correction in the typical sense of the word, since the SGPV is not adjusted to any \enquote{correct} value.
+When the normal calculation would be \enquote{misleading} (i.e., the SGPV would be small, which normally would suggest support for the alternative hypothesis, but at the same time all values in the equivalence range are supported), the SGPV is set to 0.5 which according to Blume and colleagues signals that the SGPV is \enquote{uninformative}.
+Note that the CI can be twice as wide as the equivalence range whenever the sample size is small (and the confidence interval width is large) \emph{or} when then equivalence range is narrow.
+It is therefore not so much a \enquote{small sample correction} as it is an exception to the typical calculation of the SGPV whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV6-1.pdf}
-\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (grey line) across a range of observed sample means
-(x-axis). Because the sample size is small (n = 10) and the CI is more
-than twice as wide as the equivalence range (set to -0.4 to 0.4), the
-SGPV is set to 0.5 (horizontal lightgrey line) across a range of
-observed means.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV6-1.pdf}
+\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis).
+Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.}
 \end{figure}
 
-We can examine this situation by calculating the SGPV and performing the
-TOST for a situation where sample sizes are small and the equivalence
-range is narrow, such that the CI is more than twice as large as the
-equivalence range (see Figure \ref{fig:TOSTSGPV6}). When the two
-statistics are plotted against each other we can see where the SGPV is
-the same while the TOST \emph{p}-value still differentiates different
-observed means (indicated by straight lines in the curve, see Figure
-\ref{fig:TOSTSGPV7}). We see the SGPV is 0.5 for a range of observed
-means where the \emph{p}-value from the equivalence test still varies.
-It should be noted that in these calculations the \emph{p}-values for
-the TOST procedure are \emph{never} smaller than 0.05 (i.e., they do not
-get below 0.05 on the y-axis). In other words, we cannot conclude
-equivalence based on any of the observed means. This happens because the
-we are examining a scenario where the 90\% CI is so wide that it never
-falls completely within the two equivalence bounds. As Lakens (2017)
-notes: \enquote{in small samples (where CIs are wide), a study might
-have no statistical power (i.e., the CI will always be so wide that it
-is necessarily wider than the equivalence bounds).} None of the
-\emph{p}-values based on the TOST procedure are below 0.05, and thus, in
-the long run we have 0\% power.
+We can examine this situation by calculating the SGPV and performing the TOST for a situation where sample sizes are small and the equivalence range is narrow, such that the CI is more than twice as large as the equivalence range (see Figure \ref{fig:TOSTSGPV6}).
+When the two statistics are plotted against each other we can see where the SGPV is the same while the TOST \emph{p}-value still differentiates different observed means (indicated by straight lines in the curve, see Figure \ref{fig:TOSTSGPV7}).
+We see the SGPV is 0.5 for a range of observed means where the \emph{p}-value from the equivalence test still varies.
+It should be noted that in these calculations the \emph{p}-values for the TOST procedure are \emph{never} smaller than 0.05 (i.e., they do not get below 0.05 on the y-axis).
+In other words, we cannot conclude equivalence based on any of the observed means.
+This happens because the we are examining a scenario where the 90\% CI is so wide that it never falls completely within the two equivalence bounds.
+As Lakens (2017) notes: \enquote{in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).} None of the \emph{p}-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0\% power.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV7-1.pdf}
-\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV6}.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV7-1.pdf}
+\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV6}.}
 \end{figure}
 
-The \emph{p}-value from the TOST procedure still differentiates observed
-means, while the SGPV does not, when the CI is wider than the
-equivalence range (so the precision is low) and overlaps with the upper
-and lower equivalence bound, but the CI is \emph{not} twice as wide as
-the equivalence range. In the example below, we see that the CI is only
-1.79 times as wide as the equivalence bounds, but the CI overlaps with
-the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
-This means the SGPV is not set to 0.5, but it is constant across a range
-of observed means, while the TOST \emph{p}-value is not constant across
-this range.
+The \emph{p}-value from the TOST procedure still differentiates observed means, while the SGPV does not, when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is \emph{not} twice as wide as the equivalence range.
+In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
+This means the SGPV is not set to 0.5, but it is constant across a range of observed means, while the TOST \emph{p}-value is not constant across this range.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV8-1.pdf}
-\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the
-lower and upper equivalence bound (indicated by the vertical dotted
-lines).}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV8-1.pdf}
+\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).}
 \end{figure}
 
-If the observed mean would be somewhat closer to 0, or further away from
-0, the SGPV remains constant (the CI width does not change, and it
-completely overlaps with the equivalence range) while the \emph{p}-value
-for the TOST procedure does vary. We can see this in Figure
-\ref{fig:TOSTSGPV9} below. The SGPV is not set to 0.5, but is slightly
-higher than 0.5 across a range of means. How high the SGPV will be for a
-CI that is not twice as wide as the equivalence range, but overlaps with
-the lower and upper equivalence bounds, depends on the width of the CI
-and the equivalence range.
+If the observed mean would be somewhat closer to 0, or further away from 0, the SGPV remains constant (the CI width does not change, and it completely overlaps with the equivalence range) while the \emph{p}-value for the TOST procedure does vary.
+We can see this in Figure \ref{fig:TOSTSGPV9} below.
+The SGPV is not set to 0.5, but is slightly higher than 0.5 across a range of means.
+How high the SGPV will be for a CI that is not twice as wide as the equivalence range, but overlaps with the lower and upper equivalence bounds, depends on the width of the CI and the equivalence range.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV9-1.pdf}
-\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
-line) and SGPV (grey line) across a range of observed sample means
-(x-axis). The sample size is small (n = 10), but because the sd is half
-as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less
-than twice as wide as the equivalence range (set to -0.4 to 0.4). The
-SGPV is not set to 0.5 (horizontal light grey line) but reaches a
-maximum slightly above 0.5 across a range of observed means.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV9-1.pdf}
+\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis).
+The sample size is small (n = 10), but because the sd is half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4).
+The SGPV is not set to 0.5 (horizontal light grey line) but reaches a maximum slightly above 0.5 across a range of observed means.}
 \end{figure}
 
-If we once more plot the two statistics against each other we see the
-SGPV is 0.56 for a range of observed means where the \emph{p}-value from
-the equivalence test still varies, as indicated by the straight section
-of the line (Figure \ref{fig:TOSTSGPV10}).
+If we once more plot the two statistics against each other we see the SGPV is 0.56 for a range of observed means where the \emph{p}-value from the equivalence test still varies, as indicated by the straight section of the line (Figure \ref{fig:TOSTSGPV10}).
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV10-1.pdf}
-\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from
-the TOST procedure and the SGPV for the same scenario as in Figure
-\ref{fig:TOSTSGPV9}.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV10-1.pdf}
+\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV9}.}
 \end{figure}
 
-To conclude this section, there are situations where the \emph{p}-value
-from the TOST procedure continues to differentiate, while the SGPV does
-not. Therefore, interpreted as a continuous statistic, the SGPV is more
-limited than the \emph{p}-value from the TOST procedure.
+To conclude this section, there are situations where the \emph{p}-value from the TOST procedure continues to differentiate, while the SGPV does not.
+Therefore, interpreted as a continuous statistic, the SGPV is more limited than the \emph{p}-value from the TOST procedure.
 
-\subsection{The relation between equivalence tests and SGPV for
-asymmetrical confidence intervals around
-correlations}\label{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}
+\hypertarget{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}{%
+\subsection{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations}\label{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}}
 
-So far we have only looked at the relation between equivalence tests and
-the SGPV when confidence intervals are symmetric (e.g., for confidence
-intervals around mean differences). For correlations, which are bound
-between -1 and 1, confidence intervals are only symmetric for a
-correlation of exactly 0. The confidence interval for a correlation
-becomes increasingly asymmetric as the observed correlation nears -1 or
-1. For example, with ten observations, an observed correlation of 0 has
-a symmetric 95\% confidence interval ranging from -0.630 to 0.630, while
-and observed correlation of 0.7 has an asymmetric 95\% confidence
-interval ranging from 0.126 to 0.993. Note that calculating confidence
-intervals for a correlation involves a Fisher's z-transformation, which
-transforms values such that they are approximately normally
-z-distributed, which allows one to compute symmetric confidence
-intervals. These confidence intervals are then retransformed into a
-correlation, where the confidence intervals are asymmetric if the
-correlation is not exactly zero.
+So far we have only looked at the relation between equivalence tests and the SGPV when confidence intervals are symmetric (e.g., for confidence intervals around mean differences).
+For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0.
+The confidence interval for a correlation becomes increasingly asymmetric as the observed correlation nears -1 or 1.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95\% confidence interval ranging from -0.63 to 0.63, while and observed correlation of 0.7 has an asymmetric 95\% confidence interval ranging from 0.13 to 0.92.
+Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally z-distributed, which allows one to compute symmetric confidence intervals.
+These confidence intervals are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.
 
-The effect of asymmetric confidence intervals around correlations is
-most noticeable at smaller sample sizes. In Figure \ref{fig:TOSTSGPV11}
-we plot the \emph{p}-values from equivalence tests and the SGPV (again
-plotted as 1-SGPV for ease of comparison) for correlations. The sample
-size is 30 pairs of observations, and the lower and upper equivalence
-bounds are set to -0.45 and 0.45, with an alpha of 0.05. As the observed
-correlation in the sample moves from -1 to 0 the \emph{p}-value from the
-equivalence test becomes smaller, as does 1-SGPV. The pattern is quite
-similar to that in Figure \ref{fig:TOSTSGPV2}. The \emph{p}-value for
-the TOST procedure and 1-SGPV are still related as discussed above, with
-TOST \emph{p}-values of 0.975 and 0.025 corresponding to a 1-SGPV of 1
-and 0, respectively. There are two important differences, however. First
-of all, the SGPV is no longer a straight line, but a curve, due to the
-asymmetry in the 95\% CI. Second, and most importantly, the
-\emph{p}-value for the equivalence test and the SGPV do no longer
-overlap at \emph{p} = 0.5.
+The effect of asymmetric confidence intervals around correlations is most noticeable at smaller sample sizes.
+In Figure \ref{fig:TOSTSGPV11} we plot the \emph{p}-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations.
+The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
+As the observed correlation in the sample moves from -1 to 0 the \emph{p}-value from the equivalence test becomes smaller, as does 1-SGPV.
+The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
+The \emph{p}-value for the TOST procedure and 1-SGPV are still related as discussed above, with TOST \emph{p}-values of 0.975 and 0.025 corresponding to a 1-SGPV of 1 and 0, respectively.
+There are two important differences, however.
+First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95\% CI.
+Second, and most importantly, the \emph{p}-value for the equivalence test and the SGPV do no longer overlap at \emph{p} = 0.5.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV11-1.pdf}
-\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (grey curve) across a range of observed sample
-correlations (x-axis) tested against equivalence bounds of r = -0.45 and
-r = 0.45 with n = 30 and an alpha of 0.05.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV11-1.pdf}
+\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
 \end{figure}
 
-The reason that the equivalence test and SGPV no longer overlap is also
-because of asymmetric confidence intervals. If the observed correlation
-falls exactly on the equivalence bound the \emph{p}-value for the
-equivalence test indicates that the probability of observing the
-observed or more extreme data, assuming the equivalence bound is the
-true effect size, is 50\%. In other words, if the true effect size is
-the same as the equivalence bound, it is equally likely to find an
-effect more extreme than the equivalence bound, as it is to observe an
-effect that is less extreme than the equivalence bound. However, as can
-be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation
-\emph{p}-values associated with the observed correlations at \emph{r} =
--0.45 and \emph{r} = 0.45 are larger than 50\%. Because the confidence
-intervals are asymmetric around the observed effect size of 0.45
-(ranging from 0.11 to 0.70) according to Blume et al. (2018) 58.11\% of
-the data-supported hypotheses are null hypotheses, and therefore 58.10\%
-of the data-supported hypotheses are compatible with the null premise.
+The reason that the equivalence test and SGPV no longer overlap is due to asymmetric confidence intervals.
+If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 0.5.
+In the equivalence test for correlations the \emph{p} value is computed based on a z-transformation which better controls error rates (Goertzen \& Cribbie, 2010).
+This transformation is computed as follows, where \emph{r} is the observed correlation and \(\rho\) is the theoretical correlation under the null:
+
+\[
+z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
+\]
+
+Because the z-distribution is symmetric, the probability of observing the observed or more extreme z-score, assuming the equivalence bound is the true effect size, is 50\%.
+However, because the \emph{r} distribution is not symmetric, this does not mean that there is always a 50\% probability of observing a correlation smaller or larger than the true correlation.
+As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at \emph{r} = -0.45 and \emph{r} = 0.45 are larger than 50\%.
+Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al.
+(2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.11\% of the data-supported hypotheses are compatible with the null premise.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV12-1.pdf}
-\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
-effect sizes of \emph{r} = -0.45, \emph{r} = 0, and \emph{r} = 0.45 for
-n = 30. Only the confidence interval for \emph{r} = 0 is symmetric.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV12-1.pdf}
+\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed effect sizes of \emph{r} = -0.45, \emph{r} = 0, and \emph{r} = 0.45 for n = 30.
+Only the confidence interval for \emph{r} = 0 is symmetric.}
 \end{figure}
 
-This example illustrates the difference between a proportion and a
-probability. As long as data are sampled from a bivariate normal
-distribution, there is always a 50\% probability of observing a
-correlation smaller or larger than the true correlation, but the SGPV
-for this situation depends on how far away the observed correlation is
-from 0. The further away from 0, the larger the SGPV when the observed
-mean falls on the equivalence bound. The SGPV is the proportion of
-values in a 95\% confidence interval that overlap with the equivalence
-range, but not the probability that these values will be observed. In
-the most extreme case (i.e., a sample size of 4, and equivalence bounds
-set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
-of the confidence interval overlaps with the equivalence range, even
-though in the long run only 50\% of the correlations observed in the
-future will fall in this range. It should be noted that in larger sample
-sizes the SGPV is closer to 0.5 whenever the observed correlation falls
-on the equivalence bound, but this extreme example nevertheless clearly
-illustrates the difference between question the SGPV answers, and the
-question a \emph{p}-value answers. The conclusion of this section on
-asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
-interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
-0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
-TOST procedure are always directly related at the values \emph{p} =
-0.025 and \emph{p} = 0.975. Although Blume et al. (2018) state that
-\enquote{the degree of overlap conveys how compatible the data are with
-the null premise} this definition of what the SGPV provides does not
-hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can
-be directly interpreted, a SGPV between 0 and 1 is not interpretable as
-\enquote{compatibility with the null hypothesis} under the assumption of
-a bivariate normal distribution, and the generalizability of this
-statement needs to be examined beyond normal bivariate distributions.
-Indeed, Blume and colleagues write in the supplemental material that
-\enquote{The magnitude of an inconclusive second-generation
-\emph{p}-value can vary slightly when the effect size scale is
-transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or
-1 are \emph{not} affected by the scale changes.}
+This example illustrates the difference between a proportion and a probability.
+As long as data are sampled from a bivariate normal distribution, there is always a 50\% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
+The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 36\% of the correlations observed in the future will fall in this range.
 
-\subsection{What are the Relative Strengths and Weaknesses of
-Equivalence Testing and the
-SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}
+It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a \emph{p}-value answers.
+The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at the values \emph{p} = 0.025 and \emph{p} = 0.975.
+Although Blume et al.
+(2018) state that \enquote{the degree of overlap conveys how compatible the data are with the null premise} this definition of what the SGPV provides does not hold for asymmetric confidence intervals.
+Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis} under the assumption of a bivariate normal distribution, and the generalizability of this statement needs to be examined beyond normal bivariate distributions.
+Indeed, Blume and colleagues write in the supplemental material that \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed.
+However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}
 
-When introducing a new statistical method, it is important to compare it
-to existing approaches and specify its relative strengths and
-weaknesses. Here, we aimed to compare the SGPV against equivalence tests
-based on the TOST procedure. First of all, even though a SGPV of 1 or 0
-has a clear interpretation (we can reject effects outside or inside the
-equivalence range), intermediate values are not as easy to interpret
-(especially for effects that have asymmetric confidence intervals). In
-one sense, they are what they are (the proportion of overlap), but it
-can be unclear what this number tells us about the data we have
-collected. This is not too problematic, since the main use of the SGPV
-(e.g., in all examples provided by Blume and colleagues) seems to be to
-examine whether the SGPV is 0, 1, or inconclusive. As already mentioned,
-this interpretation of a SGPV is very similar to the Neyman-Pearson
-interpretation of an equivalence test and a minimum effect tests (which
-are complementary). The difference is that where a SGPV of 1 can be
-interpreted as \emph{p} \textless{} .025, equivalence tests provide
-exact \emph{p}-values, and they continue to differentiate between for
-example \emph{p} = 0.024 and \emph{p} = 0.002. Whether this is desirable
-depends on the perspective that is used. From a Neyman-Pearson
-perspective on statistical inferences the main conclusion is based on
-whether or not \(p < \alpha\), and thus an equivalence test and SGPV can
-be performed by simply checking whether the confidence interval falls
-within the equivalence range, just as a null-hypothesis test can be
-performed by checking whether the confidence interval contains zero or
-not. At the same time, it is recommended to report exact \emph{p}-values
-(American Psychological Association, 2010), and exact \emph{p}-values
-might provide information of interest to readers about how precisely how
-surprising the data, or more extreme data, is under the null model. Some
-researchers might be interested in combining an equivalence tests with a
-null-hypothesis significance test. This allows a researcher to ask
-whether there is an effect that is statistically different from zero,
-and whether effect sizes that are considered meaningful can be rejected.
-Equivalence tests combined with null-hypothesis tests classify results
-into four possible categories, and for example allow researchers to
-conclude an effect is significant \emph{and} equivalent (i.e.,
-statistically different from zero, but also too small to be considered
-meaningful, see Lakens et al. (2018)).
+\hypertarget{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}{%
+\subsection{What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}}
 
-An important issue when calculating the SGPV is its reliance on the
-\enquote{small sample correction}, where the SGPV is set to 0.5 whenever
-the ratio of the confidence interval width to the equivalence range
-exceeds 2:1 and the CI overlaps with the upper and lower bounds. This
-exception to the normal calculation of the SGPV is introduced to prevent
-misleading values. Without this correction it is possible that a
-confidence interval is extremely wide, and an equivalence range is
-extremely narrow, which without the correction would lead to a very low
-value for the SGPV. Blume et al. (2018) suggest that under such a
-scenario \enquote{the data favor alternative hypotheses}, even when a
-better interpretation would be that there is not enough data to
-accurately estimate the true effect compared to the width of the
-equivalence range. Although it is necessary to set the SGPV to 0.5
-whenever the ratio of the confidence interval width to the equivalence
-range exceeds 2:1, it leads to a range of situations where the SGPV is
-set to 0.5, while the \emph{p}-value from the TOST procedure continues
-to differentiate (see for example Figure \ref{fig:TOSTSGPV6}). An
-important benefit of equivalence tests is that it does not need such a
-correction to prevent misleading results.
+When introducing a new statistical method, it is important to compare it to existing approaches and specify its relative strengths and weaknesses.
+Here, we aimed to compare the SGPV against equivalence tests based on the TOST procedure.
+First of all, even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals).
+In one sense, they are what they are (the proportion of overlap), but it can be unclear what this number tells us about the data we have collected.
+This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) seems to be to examine whether the SGPV is 0, 1, or inconclusive.
+As already mentioned, this interpretation of a SGPV is very similar to the Neyman-Pearson interpretation of an equivalence test and a minimum effect tests (which are complementary).
+The difference is that where a SGPV of 1 can be interpreted as \emph{p} \textless{} .025, equivalence tests provide exact \emph{p}-values, and they continue to differentiate between for example \emph{p} = 0.024 and \emph{p} = 0.002.
+Whether this is desirable depends on the perspective that is used.
+From a Neyman-Pearson perspective on statistical inferences the main conclusion is based on whether or not \(p < \alpha\), and thus an equivalence test and SGPV can be performed by simply checking whether the confidence interval falls within the equivalence range, just as a null-hypothesis test can be performed by checking whether the confidence interval contains zero or not.
+At the same time, it is recommended to report exact \emph{p}-values (American Psychological Association, 2010), and exact \emph{p}-values might provide information of interest to readers about how precisely how surprising the data, or more extreme data, is under the null model.
+Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test.
+This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see Lakens et al.
+(2018)).
+
+An important issue when calculating the SGPV is its reliance on the \enquote{small sample correction}, where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds.
+This exception to the normal calculation of the SGPV is introduced to prevent misleading values.
+Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV.
+Blume et al.
+(2018) suggest that under such a scenario \enquote{the data favor alternative hypotheses}, even when a better interpretation would be that there is not enough data to accurately estimate the true effect compared to the width of the equivalence range.
+Although it is necessary to set the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1, it leads to a range of situations where the SGPV is set to 0.5, while the \emph{p}-value from the TOST procedure continues to differentiate (see for example Figure \ref{fig:TOSTSGPV6}).
+An important benefit of equivalence tests is that it does not need such a correction to prevent misleading results.
 
@@
 \centering
-\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV13-1.pdf}
-\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
-(black line) and 1-SGPV (grey curve) across a range of observed sample
-correlations (x-axis) tested against equivalence bounds of \emph{r} =
-0.4 and \emph{r} = 0.8 with n = 10 and an alpha of 0.05.}
+\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV13-1.pdf}
+\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of \emph{r} = 0.4 and \emph{r} = 0.8 with n = 10 and an alpha of 0.05.}
 \end{figure}
 
-As a more extreme example of the peculiar behavior of the \enquote{small
-sample correction} as currently implemented in the calculation of the
-SGPV see Figure \ref{fig:TOSTSGPV13}. In this figure observed
-correlations (from a sample size of 10) from -1 to 1 are tested against
-an equivalence range from r = 0.4 to r = 0.8. We can see the SGPV has a
-peculiar shape because it is set to 0.5 for certain observed
-correlations, even though there is no risk of a \enquote{misleading}
-SGPV in this range. This example suggests that the current
-implementation of the \enquote{small sample correction} could be
-improved. If, on the other hand, the SGPV is mainly meant to be
-interpreted when it is 0 or 1, it might be preferable to simply never
-apply the \enquote{small sample correction}.
+As a more extreme example of the peculiar behavior of the \enquote{small sample correction} as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13}.
+In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
+We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a \enquote{misleading} SGPV in this range.
+This example suggests that the current implementation of the \enquote{small sample correction} could be improved.
+If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the \enquote{small sample correction}.
 
-Blume et al. (2018) claim that when using the SGPV \enquote{Adjustments
-for multiple comparisons are obviated} (p.~15). However, this is not
-correct. Given the direct relationship between TOST and SGPV highlighted
-in this manuscript (where a TOST \emph{p} = 0.025 equals SGPV = 1, as
-long as the SGPV is calculated based on confidence intervals, and
-assuming data are sampled from a continuous bivariate normal
-distribution), not correcting for multiple comparisons will inflate the
-probability of concluding the absence of a meaningful effect based on
-the SGPV in exactly the same way as it will for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis
-(e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if
-researchers want to control error rates, they need to correct for
-multiple comparisons.
+Blume et al.
+(2018) claim that when using the SGPV \enquote{Adjustments for multiple comparisons are obviated} (p.~15).
+However, this is not correct.
+Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST \emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 
-\section{Conclusion}\label{conclusion}
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
-We believe that our explanation of the similarities between the TOST
-procedure and the SGPV provides context to interpret the contribution of
-second generation \emph{p}-values to the statistical toolbox. The
-novelty of the SGPV can be limited when confidence intervals are
-asymmetrical or wider than the equivalence range. There are strong
-similarities with \emph{p}-values from the TOST procedure, and in all
-situations where the statistics yield different results, the behavior of
-the \emph{p}-value from the TOST procedure is more consistent and easier
-to interpret. We hope this overview of the relationship between the SGPV
-and equivalence tests will help researchers to make an informed decision
-about which statistical approach provides the best answer to their
-question. Our comparisons show that when proposing alternatives to
-null-hypothesis tests, it is important to compare new proposals to
-already existing procedures. We believe equivalence tests achieve the
-goals of the second generation \emph{p}-value while allowing users to
-easily control error rates, and while yielding more consistent
-statistical outcomes.
+We believe that our explanation of the similarities between the TOST procedure and the SGPV provides context to interpret the contribution of second generation \emph{p}-values to the statistical toolbox.
+The novelty of the SGPV can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
+There are strong similarities with \emph{p}-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the \emph{p}-value from the TOST procedure is more consistent and easier to interpret.
+We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
+Our comparisons show that when proposing alternatives to null-hypothesis tests, it is important to compare new proposals to already existing procedures.
+We believe equivalence tests achieve the goals of the second generation \emph{p}-value while allowing users to easily control error rates, and while yielding more consistent statistical outcomes.
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-american_psychological_association_publication_2010}{}
-American Psychological Association (Ed.). (2010). \emph{Publication
-manual of the American Psychological Association} (6th ed.). Washington,
-DC: American Psychological Association.
+\leavevmode\hypertarget{ref-american_psychological_association_publication_2010}{}%
+American Psychological Association (Ed.). (2010). \emph{Publication manual of the American Psychological Association} (6th ed.). Washington, DC: American Psychological Association.
 
-\hypertarget{ref-blume_second-generation_2018}{}
-Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
-(2018). Second-generation p-values: Improved rigor, reproducibility, \&
-transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
-e0188299.
+\leavevmode\hypertarget{ref-blume_second-generation_2018}{}%
+Blume, J.
+D., D'Agostino McGowan, L., Dupont, W.
+D., \& Greevy, R.
+A.
+(2018).
+Second-generation p-values: Improved rigor, reproducibility, \& transparency in statistical analyses.
+\emph{PLOS ONE}, \emph{13}(3), e0188299.
 doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}
 
-\hypertarget{ref-hauck_new_1984}{}
-Hauck, D. W. W., \& Anderson, S. (1984). A new statistical procedure for
-testing equivalence in two-group comparative bioavailability trials.
-\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1),
-83--91.
+\leavevmode\hypertarget{ref-goertzen_detecting_2010}{}%
+Goertzen, J.
+R., \& Cribbie, R.
+A.
+(2010).
+Detecting a lack of association: An equivalence testing approach.
+\emph{British Journal of Mathematical and Statistical Psychology}, \emph{63}(3), 527--537.
+doi:\href{https://doi.org/10.1348/000711009X475853}{10.1348/000711009X475853}
+
+\leavevmode\hypertarget{ref-hauck_new_1984}{}%
+Hauck, D.
+W.
+W., \& Anderson, S.
+(1984).
+A new statistical procedure for testing equivalence in two-group comparative bioavailability trials.
+\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1), 83--91.
 doi:\href{https://doi.org/10.1007/BF01063612}{10.1007/BF01063612}
 
-\hypertarget{ref-kruschke_rejecting_2018}{}
-Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in
-Bayesian Estimation. \emph{Advances in Methods and Practices in
-Psychological Science}, 2515245918771304.
+\leavevmode\hypertarget{ref-kruschke_rejecting_2018}{}%
+Kruschke, J.
+K.
+(2018).
+Rejecting or Accepting Parameter Values in Bayesian Estimation.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245918771304.
 doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}
 
-\hypertarget{ref-lakens_equivalence_2017}{}
-Lakens, D. (2017). Equivalence Tests: A Practical Primer for t Tests,
-Correlations, and Meta-Analyses. \emph{Social Psychological and
-Personality Science}, \emph{8}(4), 355--362.
+\leavevmode\hypertarget{ref-lakens_equivalence_2017}{}%
+Lakens, D.
+(2017).
+Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses.
+\emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362.
 doi:\href{https://doi.org/10.1177/1948550617697177}{10.1177/1948550617697177}
 
-\hypertarget{ref-lakens_equivalence_2018}{}
-Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing
-for Psychological Research: A Tutorial. \emph{Advances in Methods and
-Practices in Psychological Science}, 2515245918770963.
+\leavevmode\hypertarget{ref-lakens_equivalence_2018}{}%
+Lakens, D., Scheel, A.
+M., \& Isager, P.
+M.
+(2018).
+Equivalence Testing for Psychological Research: A Tutorial.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245918770963.
 doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}
 
-\hypertarget{ref-meyners_equivalence_2012}{}
-Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and
-Preference}, \emph{26}(2), 231--245.
-doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
+\leavevmode\hypertarget{ref-meyners_equivalence_2012}{}%
+Meyners, M. (2012). Equivalence tests A review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
 
-\hypertarget{ref-murphy_statistical_2014}{}
-Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
-power analysis: A simple and general model for traditional and modern
-hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
-Francis Group.
+\leavevmode\hypertarget{ref-murphy_statistical_2014}{}%
+Murphy, K.
+R., Myors, B., \& Wolach, A.
+H.
+(2014).
+\emph{Statistical power analysis: A simple and general model for traditional and modern hypothesis tests} (Fourth edition.).
+New York: Routledge, Taylor \& Francis Group.
 
-\hypertarget{ref-quertemont_how_2011}{}
-Quertemont, E. (2011). How to Statistically Show the Absence of an
-Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127.
-doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}
+\leavevmode\hypertarget{ref-quertemont_how_2011}{}%
+Quertemont, E. (2011). How to Statistically Show the Absence of an Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127. doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}
 
-\hypertarget{ref-rogers_using_1993}{}
-Rogers, J. L., Howard, K. I., \& Vessey, J. T. (1993). Using
-significance tests to evaluate equivalence between two experimental
-groups. \emph{Psychological Bulletin}, \emph{113}(3), 553--565.
+\leavevmode\hypertarget{ref-rogers_using_1993}{}%
+Rogers, J.
+L., Howard, K.
+I., \& Vessey, J.
+T.
+(1993).
+Using significance tests to evaluate equivalence between two experimental groups.
+\emph{Psychological Bulletin}, \emph{113}(3), 553--565.
 doi:\href{https://doi.org/http://dx.doi.org/10.1037/0033-2909.113.3.553}{http://dx.doi.org/10.1037/0033-2909.113.3.553}
 
-\hypertarget{ref-schuirmann_comparison_1987}{}
-Schuirmann, D. J. (1987). A comparison of the two one-sided tests
-procedure and the power approach for assessing the equivalence of
-average bioavailability. \emph{Journal of Pharmacokinetics and
-Biopharmaceutics}, \emph{15}(6), 657--680.
+\leavevmode\hypertarget{ref-schuirmann_comparison_1987}{}%
+Schuirmann, D.
+J.
+(1987).
+A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability.
+\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.
 
-\hypertarget{ref-serlin_rationality_1985}{}
-Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological
-research: The good-enough principle.
+\leavevmode\hypertarget{ref-serlin_rationality_1985}{}%
+Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.
 
-\hypertarget{ref-spiegelhalter_bayesian_1994}{}
-Spiegelhalter, D. J., Freedman, L. S., \& Parmar, M. K. (1994). Bayesian
-approaches to randomized trials. \emph{Journal of the Royal Statistical
-Society. Series A (Statistics in Society)}, 357--416.
+\leavevmode\hypertarget{ref-spiegelhalter_bayesian_1994}{}%
+Spiegelhalter, D.
+J., Freedman, L.
+S., \& Parmar, M.
+K.
+(1994).
+Bayesian approaches to randomized trials.
+\emph{Journal of the Royal Statistical Society.
+Series A (Statistics in Society)}, 357--416.
 doi:\href{https://doi.org/10.2307/2983527}{10.2307/2983527}
 
-\hypertarget{ref-wellek_testing_2010}{}
-Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence
-and noninferiority} (2nd ed.). Boca Raton: CRC Press.
+\leavevmode\hypertarget{ref-wellek_testing_2010}{}%
+Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence and noninferiority} (2nd ed.). Boca Raton: CRC Press.
 
-\hypertarget{ref-westlake_use_1972}{}
-Westlake, W. J. (1972). Use of Confidence Intervals in Analysis of
-Comparative Bioavailability Trials. \emph{Journal of Pharmaceutical
-Sciences}, \emph{61}(8), 1340--1341.
+\leavevmode\hypertarget{ref-westlake_use_1972}{}%
+Westlake, W.
+J.
+(1972).
+Use of Confidence Intervals in Analysis of Comparative Bioavailability Trials.
+\emph{Journal of Pharmaceutical Sciences}, \emph{61}(8), 1340--1341.
 doi:\href{https://doi.org/10.1002/JPS.2600610845}{10.1002/JPS.2600610845}

### 2019-04-23 manuscript.R2.Rmd
Marie last modifications

@@
 In other words, we cannot conclude equivalence based on any of the observed means.
-This happens because the we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
-As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power.
+This happens because we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds.
+
+```{r, include=FALSE}
+pt.est <- function(n,m,mu,sd){
+  x <- rnorm(n,m,sd)
+  res <- TOSTone.raw(m=mean(x),mu=mu,sd=sd(x),n=n, low_eqbound=mu-.4, high_eqbound=mu+.4,verbose=FALSE,plot=FALSE)
+  pval <- max(res$TOST_p1,res$TOST_p2)  
+}
+
+pt.sampling.dist <- replicate(10000,(pt.est(n=10,m=0,mu=0,sd=2)))
+```
+
+As @lakens_equivalence_2017 notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have `r round(sum(pt.sampling.dist<.05)/length(pt.sampling.dist))`% power.
 
@@
 
-The *p*-value from the TOST procedure still differentiates observed means, while the  SGPV does not, when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
-In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
-This means the SGPV is not set to 0.5, but it is constant across a range of observed means, while the TOST *p*-value is not constant across this range.
-
 ```{r, include=FALSE}
@@
 #Ratio CI to equivalence bounds
-(tost_res1$UL_CI_TTEST - tost_res1$LL_CI_TTEST) / (d.hi - d.lo)
-
-```
+ratio_CI<-(tost_res1$UL_CI_TTEST - tost_res1$LL_CI_TTEST) / (d.hi - d.lo)
+```
+
+The *p*-value from the TOST procedure still differentiates observed means, while the  SGPV does not, when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range.
+In the example below, we see that the CI is only `r round(ratio_CI,2)` times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds (Figure \ref{fig:TOSTSGPV8}).
+This means the SGPV is not set to 0.5, but it is constant across a range of observed means, while the TOST *p*-value is not constant across this range.
 
@@
 
-If we once more plot the two statistics against each other we see the SGPV is 0.56 for a range of observed means where the *p*-value from the equivalence test still varies, as indicated by the straight section of the line (Figure \ref{fig:TOSTSGPV10}).
+If we once more plot the two statistics against each other we see the SGPV is `r round(max(sgpv_list),2)` for a range of observed means where the *p*-value from the equivalence test still varies, as indicated by the straight section of the line (Figure \ref{fig:TOSTSGPV10}).
 
@@
 
+```{r, include=FALSE}
+
+  ## Confidence Interval around r
+  r_CI <- function(r,n){
+
+  # convert r into z
+  z <- log((1+r)/(1-r))/2
+
+  # computing z bounds 
+  binf_z <- z-qnorm(1-alpha/2)/sqrt(n-3)
+  bsup_z <- z+qnorm(1-alpha/2)/sqrt(n-3)
+
+  # convert z bounds into r bounds
+  binf <- (exp(2*binf_z)-1)/(1+exp(2*binf_z))
+  bsup <- (exp(2*bsup_z)-1)/(1+exp(2*bsup_z))
+
+  invisible(list(binf=binf,bsup=bsup))  
+  }
+```
+
 So far we have only looked at the relation between equivalence tests and the SGPV when confidence intervals are symmetric (e.g., for confidence intervals around mean differences).
@@
 The confidence interval for a correlation becomes increasingly asymmetric as the observed correlation nears -1 or 1.
-For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from `r round(TOSTr(r = 0, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$LL_CI_TTEST,3)` to `r round(TOSTr(r = 0, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$UL_CI_TTEST,3)`, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from `r round(TOSTr(r = 0.7, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$LL_CI_TTEST,3)` to `r round(TOSTr(r = 0.7, n = 10, low_eqbound_r = -0.45, high_eqbound_r = 0.45, alpha = 0.05, plot = FALSE, verbose = FALSE)$UL_CI_TTEST,3)`.
+For example, with ten observations, an observed correlation of 0 has a symmetric 95% confidence interval ranging from `r r_CI(r=0,n=10)$binf` to `r r_CI(r=0,n=10)$bsup`, while and observed correlation of 0.7 has an asymmetric 95% confidence interval ranging from `r r_CI(r=.7,n=10)$binf` to `r r_CI(r=.7,n=10)$bsup`.
 Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally z-distributed, which allows one to compute symmetric confidence intervals.
@@
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
-As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
+As the observed correlation in the sample moves from -.99 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV.
 The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
@@
 If the observed correlation falls exactly on the equivalence bound the *p*-value for the equivalence test is 0.5.
-In the equivalence test for correlations the *p* value is computed based on a z-transformation which better controls error rates [@goertzen_detecting_2010].
+In the equivalence test for correlations the *p*-value is computed based on a z-transformation which better controls error rates [@goertzen_detecting_2010].
 This transformation is computed as follows, where  *r* is the observed correlation and $\rho$ is the theoretical correlation under the null:
@@
 
-This example illustrates the difference between a proportion and a probability.
-As long as data are sampled from a bivariate normal distribution, there is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
+```{r, include=FALSE}
+
+library(mvtnorm)
+
+r.est <- function(n,r){
+    x <- rmvnorm(n,c(0,0),sigma=matrix(c(1,r,r,1),nrow=2))
+    est <- cor(x)[1,2]
+    est
+}
+
+r.sampling.dist <- replicate(10000,r.est(4,.99))
+prop <- sum(r.sampling.dist <=.99)/length(r.sampling.dist)
+```
+
 The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
 The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 36% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only `r prop*100`% of the correlations observed in the future will fall in this range.
 
@@
 At the same time, it is recommended to report exact *p*-values [@american_psychological_association_publication_2010], and exact *p*-values might provide information of interest to readers about how precisely how surprising the data, or more extreme data, is under the null model.
-Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test.
+Some researchers might be interested in combining an equivalence test with a null-hypothesis significance test.
 This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
-Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see @lakens_equivalence_2018).
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful; see @lakens_equivalence_2018).
 
@@
 
-As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13}.
-In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
+As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV, see Figure \ref{fig:TOSTSGPV13}.
+In this figure observed correlations (from a sample size of 10) from -.99 to .99 are tested against an equivalence range from r = 0.4 to r = 0.8.
 We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a 'misleading' SGPV in this range.
@@
 Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST *p* = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible to do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 

### 2019-04-23 manuscript.R2.tex
Marie last modifications

@@
 In other words, we cannot conclude equivalence based on any of the observed means.
-This happens because the we are examining a scenario where the 90\% CI is so wide that it never falls completely within the two equivalence bounds.
+This happens because we are examining a scenario where the 90\% CI is so wide that it never falls completely within the two equivalence bounds.
+
 As Lakens (2017) notes: \enquote{in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).} None of the \emph{p}-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0\% power.
@@
 The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05.
-As the observed correlation in the sample moves from -1 to 0 the \emph{p}-value from the equivalence test becomes smaller, as does 1-SGPV.
+As the observed correlation in the sample moves from -.99 to 0 the \emph{p}-value from the equivalence test becomes smaller, as does 1-SGPV.
 The pattern is quite similar to that in Figure \ref{fig:TOSTSGPV2}.
@@
 If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 0.5.
-In the equivalence test for correlations the \emph{p} value is computed based on a z-transformation which better controls error rates (Goertzen \& Cribbie, 2010).
+In the equivalence test for correlations the \emph{p}-value is computed based on a z-transformation which better controls error rates (Goertzen \& Cribbie, 2010).
 This transformation is computed as follows, where \emph{r} is the observed correlation and \(\rho\) is the theoretical correlation under the null:
@@
 
-This example illustrates the difference between a proportion and a probability.
-As long as data are sampled from a bivariate normal distribution, there is always a 50\% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0.
 The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound.
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 36\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.29\% of the correlations observed in the future will fall in this range.
 
@@
 At the same time, it is recommended to report exact \emph{p}-values (American Psychological Association, 2010), and exact \emph{p}-values might provide information of interest to readers about how precisely how surprising the data, or more extreme data, is under the null model.
-Some researchers might be interested in combining an equivalence tests with a null-hypothesis significance test.
+Some researchers might be interested in combining an equivalence test with a null-hypothesis significance test.
 This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
-Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful, see Lakens et al.
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful; see Lakens et al.
 (2018)).
@@
 
-As a more extreme example of the peculiar behavior of the \enquote{small sample correction} as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13}.
-In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8.
+As a more extreme example of the peculiar behavior of the \enquote{small sample correction} as currently implemented in the calculation of the SGPV, see Figure \ref{fig:TOSTSGPV13}.
+In this figure observed correlations (from a sample size of 10) from -.99 to .99 are tested against an equivalence range from r = 0.4 to r = 0.8.
 We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a \enquote{misleading} SGPV in this range.
@@
 Given the direct relationship between TOST and SGPV highlighted in this manuscript (where a TOST \emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated based on confidence intervals, and assuming data are sampled from a continuous bivariate normal distribution), not correcting for multiple comparisons will inflate the probability of concluding the absence of a meaningful effect based on the SGPV in exactly the same way as it will for equivalence tests.
-Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
+Whenever statistical tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible to do so erroneously, and if researchers want to control error rates, they need to correct for multiple comparisons.
 
@@
 \leavevmode\hypertarget{ref-meyners_equivalence_2012}{}%
-Meyners, M. (2012). Equivalence tests A review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
+Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
 

### 2019-04-24 manuscript.R2.Rmd
rounding a % based on simulations

@@
 The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only `r prop*100`% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only `r round(prop*100`)% of the correlations observed in the future will fall in this range.
 

### 2019-04-24 manuscript.R2.tex
rounding a % based on simulations

@@
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.29\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.08\% of the correlations observed in the future will fall in this range.
 

### 2019-04-24 reply_to_reviews.R2.tex
R2 submission

@@
 \abstract{
-In this second revision we are responding to the last issue you raised, about our incorrect statement that 50\% of the correlations fall below the observed correlation.
-We are extrmely grateful you pointed out this incorrect statement, and have corrected it as explained below.
+In this second revision we are responding to the last issue you raised concerning our incorrect statement that 50\% of the expected correlations fall below the observed correlation.
+We are extremely grateful you pointed out this incorrect statement, and have corrected it as explained below.
+We have also made some minor changes after carefully re-reading the manuscript that we detail at the end of this letter.
 We hope you think our submission is ready to be accepted for publication in Meta-Psychology.
@@
 
+\hypertarget{additional-minor-changes}{%
+\section{Additional Minor changes}\label{additional-minor-changes}}
+
+\textbf{We replaced some values in the document that were hard-coded with the R scripts that produced these values, making the document (as far as we can see) 100\% reproducible.
+(note that this is not noticeable in the PDF)}
+
+\textbf{We wrote we \enquote{replicated} Blume, but we now say we \enquote{build on} Blume - all our examples use a mean of 145, where upon rereading Blume et al we noticed they use a mean of 146 - an inconsequential difference, but instead of changing all our examples to a mean of 146, we just changed the word \enquote{replicated} to \enquote{build on}.}
+
+\textbf{We removed \enquote{if too few observations are collected} which was redundant with the \enquote{note that when sample sizes are small} earlier in the same sentence.}
+
+\textbf{We added in Figure 6 that the standard deviation for the visualized example is 2.}
+
+\textbf{We added some clarification when describing Figure 12, replacing} \enquote{the two second generation \emph{p}-values associated with the observed correlations at \emph{r} = -0.45 and \emph{r} = 0.45 are larger than 50\%} \textbf{with} \enquote{the proportion of the confidence interval that overlaps with the equivalence range is larger than 50\% when the observed correlations are \emph{r} = -.45 and \emph{r} = .45, meaning that the two second generation p-values associated with these correlations are larger than 50\%.}
+
+\textbf{In the conclusion, we noted that p-values from TOST are more consistent, and easier to interpret.
+Upon re-reading our manuscript, we chose to delete the \enquote{and easier to interpret} part of that sentence, since this is an empirical claim, and we have no data to support it, and is not relevant for the points we make.}
+
 \newpage

### 2019-04-24 manuscript.R2.tex
R2 submission

@@
-\documentclass[,man,floatsintext]{apa6}
+\documentclass[,jou,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 
-\usepackage{lineno}
-
-\linenumbers
-
 \authornote{All code associated with this article, including the reproducible manuscript, is available from \url{https://github.com/Lakens/TOST_vs_SGPV} and \url{https://osf.io/8crkg/}.
@@
 To examine the relation between the TOST \emph{p}-value and the SGPV we can calculate both statistics across a range of observed effect sizes.
-Replicating the example by Blume et al.
+Building on the example by Blume et al.
 (2018), in Figure \ref{fig:TOSTSGPV1} \emph{p}-values are plotted for the TOST procedure and the SGPV.
@@
 \caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis).
-Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.}
+Because the sample size is small (n = 10) and with a standard deviation of 2 the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.}
 \end{figure}
@@
 However, because the \emph{r} distribution is not symmetric, this does not mean that there is always a 50\% probability of observing a correlation smaller or larger than the true correlation.
-As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at \emph{r} = -0.45 and \emph{r} = 0.45 are larger than 50\%.
+As can be seen in Figure \ref{fig:TOSTSGPV12}, the proportion of the confidence interval that overlaps with the equivalence range is larger than 50\% when the observed correlations are \emph{r} = -.45 and \emph{r} = .45, meaning that the two second generation p-values associated with these correlations are larger than 50\%.
 Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al.
@@
 The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed.
-In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.08\% of the correlations observed in the future will fall in this range.
+In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 36\% of the correlations observed in the future will fall in this range.
 
@@
 This allows a researcher to ask whether there is an effect that is statistically different from zero, and whether effect sizes that are considered meaningful can be rejected.
-Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful; see Lakens et al.
-(2018)).
+Equivalence tests combined with null-hypothesis tests classify results into four possible categories, and for example allow researchers to conclude an effect is significant \emph{and} equivalent (i.e., statistically different from zero, but also too small to be considered meaningful; see Lakens et al., 2018).
 
@@
 The novelty of the SGPV can be limited when confidence intervals are asymmetrical or wider than the equivalence range.
-There are strong similarities with \emph{p}-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the \emph{p}-value from the TOST procedure is more consistent and easier to interpret.
+There are strong similarities with \emph{p}-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the \emph{p}-value from the TOST procedure is more consistent.
 We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.
@@
 Rejecting or Accepting Parameter Values in Bayesian Estimation.
-\emph{Advances in Methods and Practices in Psychological Science}, 2515245918771304.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 270--280.
 doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}
@@
 
-\leavevmode\hypertarget{ref-lakens_equivalence_2018}{}%
+\leavevmode\hypertarget{ref-lakens_equivalence_2018-1}{}%
 Lakens, D., Scheel, A.
@@
 Equivalence Testing for Psychological Research: A Tutorial.
-\emph{Advances in Methods and Practices in Psychological Science}, 2515245918770963.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
 doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}
@@
 \leavevmode\hypertarget{ref-meyners_equivalence_2012}{}%
-Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
+Meyners, M. (2012). Equivalence tests A review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}
 
@@
 \emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.
+doi:\href{https://doi.org/https://doi.org/10.1007/BF01068419}{https://doi.org/10.1007/BF01068419}
 
 \leavevmode\hypertarget{ref-serlin_rationality_1985}{}%
-Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.
+Serlin, R.
+C., \& Lapsley, D.
+K.
+(1985).
+Rationality in psychological research: The good-enough principle.
+\emph{American Psychologist}, \emph{40}(1), 73--83.
+doi:\href{https://doi.org/http://dx.doi.org/10.1037/0003-066X.40.1.73}{http://dx.doi.org/10.1037/0003-066X.40.1.73}
 
